### 2021-07-13 Submission/Paper/Models/neurIPs.tex
source code for neurIPs paper submission

% use the "wcp" class option for workshop and conference
 % proceedings
 %\documentclass[gray]{jmlr} % test grayscale version
 %\documentclass[tablecaption=bottom]{jmlr}% journal article
 \documentclass[pmlr,twocolumn]{jmlr} % W&CP article
\let\SUP\textsuperscript
 % The following packages will be automatically loaded:
 % amsmath, amssymb, natbib, graphicx, url, algorithm2e
 \usepackage{rotating}% for sideways figures and tables
 %\usepackage{longtable}% for long tables

 % The booktabs package is used by this sample document
 % (it provides \toprule, \midrule and \bottomrule).
 % Remove the next line if you don't require it.
\usepackage{booktabs}
 % The siunitx package is used by this sample document
 % to align numbers in a column by their decimal point.
 % Remove the next line if you don't require it.
\usepackage[load-configurations=version-1]{siunitx} % newer version
 %\usepackage{siunitx}

 % The following command is just for this sample document:
\newcommand{\cs}[1]{\texttt{\char`\\#1}}% remove this in your real article

 % Define an unnumbered theorem just for this sample document for
 % illustrative purposes:
\theorembodyfont{\upshape}
\theoremheaderfont{\scshape}
\theorempostheader{:}
\theoremsep{\newline}
\newtheorem*{note}{Note}

 % change the arguments, as appropriate, in the following:
\jmlrvolume{ML4H Extended Abstract Arxiv Index}
\jmlryear{2020}
\jmlrsubmitted{2020}
\jmlrpublished{}
\jmlrworkshop{Machine Learning for Health (ML4H) 2020} % W&CP title

 % The optional argument of \title is used in the header
% \title[Short Title]{Full Title of Article\titlebreak This Title Has
% A Line Break}

\title[NLP to Detect Cognitive Concerns]{Natural Language Processing to Detect Cognitive Concerns in Electronic Health Records Using Deep Learning}

 % Anything in the title that should appear in the main title but 
 % not in the article's header or the volume's table of
 % contents should be placed inside \titletag{}

 %\title{Title of the Article\titletag{\thanks{Some footnote}}}

 % Use \Name{Author Name} to specify the name.
 % If the surname contains spaces, enclose the surname
 % in braces, e.g. \Name{John {Smith Jones}} similarly
 % if the name has a "von" part, e.g \Name{Jane {de Winter}}.
 % If the first letter in the forenames is a diacritic
 % enclose the diacritic in braces, e.g. \Name{{\'E}louise Smith}

 % \thanks must come after \Name{...} not inside the argument for
 % example \Name{John Smith}\nametag{\thanks{A note}} NOT \Name{John
 % Smith\thanks{A note}}

 % Anything in the name that should appear in the title but not in the 
 % article's header or footer or in the volume's
 % table of contents should be placed inside \nametag{}

 % Two authors with the same address
%   \author{%
%   \Name{Author Name1\nametag{\thanks{A note}}} \Email{abc@sample.com}\and
%   \Name{Author Name2} \Email{xyz@sample.com}\\
%   \addr Address
%   }

 % Three or more authors with the same address:
 % Option 1
 % ===============================================================
%   \author{%
%   \Name{Zhuoqiao Hong} \nametag{\thanks{Authors contributed equally}}\Email{zhong1@mgh.harvard.edu}\\
%   \Name{Colin G. Magdamo} \nametag{\footnotemark[1] }\Email{cmagdamo@mgh.harvard.edu}\\
%   \Name{Yi-han Sheu}\nametag{\footnotemark[1]} \Email{yis828@mail.harvard.edu}\\
%   \Name{Prathamesh Mohite} \Email{pmohite@mgh.harvard.edu}\\
%   \Name{Elissa M. Ye} \Email{emye@mgh.harvard.edu}\\
%   \Name{Wendong Ge} \Email{wendong.ge@mgh.harvard.edu }\\
%   \Name{Haoqi Sun} \Email{hsun8@mgh.harvard.edu}\\
%   \Name{Laura Brenner} \Email{lnbrenner@mgh.harvard.edu}\\
%   \Name{Gregory Robbins} \Email{grobbins@mgh.harvard.edu}\\
%   \Name{Shibani Mukerji} \Email{smukerji@mgh.harvard.edu}\\
%   \Name{Sahar Zahar} \Email{sfzafar@mgh.harvard.edu}\\
%   \Name{Nicole Benson} \Email{nbenson@mgh.harvard.edu}\\
%   \Name{Lidia Moura} \Email{lidia.moura@mgh.harvard.edu }\\
%   \Name{John Hsu} \Email{john.hsu@mgh.harvard.edu}\\
%   \Name{Bradley T. Hyman} \Email{bhyman@mgh.harvard.edu}\\
%   \Name{Michael B. Westover} \Email{mwestover@mgh.harvard.edu}\\
%   \Name{Deborah Blacker} \Email{dblacker@mgh.harvard.edu}\\
%   \Name{Sudeshna Das} \Email{sdas5@mgh.harvard.edu}\\
%   \addr Massachusetts General Hospital, Boston, MA
%   }

% Option 2
% ===============================================================
% Alternative author
\author{Zhuoqiao Hong\nametag{\thanks{Authors contributed equally}\SUP{1}},
Colin G. Magdamo\nametag{\footnotemark[1]\SUP{1}}, 
Yi-han Sheu\nametag{\footnotemark[1]\SUP{1}},
Prathamesh Mohite\SUP{1},
Ayush Noori\SUP{1},
Elissa M. Ye\SUP{1},
Wendong Ge\SUP{1},
Haoqi Sun\SUP{1},
Laura Brenner\SUP{1},
Gregory Robbins\SUP{1},
Shibani Mukerji\SUP{1},
Sahar Zafar\SUP{1},
Nicole Benson\SUP{1},
Lidia Moura\SUP{1},
John Hsu\SUP{1},
Bradley T. Hyman\SUP{1},
Michael B. Westover\SUP{1},
Deborah Blacker\SUP{1},
Sudeshna Das\SUP{1}
\centering \Email{
\\[\bigskipamount] 
\SUP{1}\{zhong1, 
cmagdamo,
ysheu,
pmohite,
anoori1,
emye,
wendong.ge,
hsun8,
lnbrenner,
grobbins,
smukerji,
sfzafar,
nbenson,
lidia.moura,
john.hsu,
bhyman,
mwestover,
dblacker,
sdas5\}
@mgh.harvard.edu}
% \\ 
% \SUP{2} 
% yis828@mail.harvard.edu}\\
\begin{center}\addr Massachusetts General Hospital, Boston, MA\end{center}
}

% ===============================================================

 % Authors with different addresses:
% \author{%
% \Name{Zhuoqiao Hong} \Email{zhong1@mgh.harvard.edu}\\
% \addr Address 1
% \AND
% \Name{Colin G. Magdamo} \Email{cmagdamo@mgh.harvard.edu}\\
% \addr Address 2
% }

\begin{document}

\maketitle

\begin{abstract}

 Dementia is under-recognized in the community, under-diagnosed by healthcare professionals, and under-coded in claims data. Information on cognitive dysfunction, however, is often found in unstructured clinician notes within medical records but manual review by experts is time consuming and often prone to errors. Automated mining of these notes presents a potential opportunity to label patients with cognitive concerns who could benefit from an evaluation or be referred to specialist care.  In order to identify patients with cognitive concerns in electronic medical records, we applied natural language processing (NLP) algorithms and compared model performance to a baseline model that used structured diagnosis codes and medication data only. An attention-based deep learning model outperformed the baseline model and other simpler models.
\end{abstract}

\begin{keywords}
NLP, EHR, Dementia
\end{keywords}

\section{Introduction}
\label{sec:intro}
Early detection of dementia is important for improving clinical outcomes and management of dementia, as well as for lifestyle, financial, and future planning for patients and their caregivers \citep{robinson_dementia_2015, borson_improving_2013}. Yet, dementia is not formally diagnosed or coded in claims for over 50\% of older adults living with probable dementia \citep{amjad_underdiagnosis_2018,alzheimers_association_2019_2019}. Tools that screen medical records for warning signs and present the digested information to providers may prove to be an important step for early intervention. 
In this study, we aim to use NLP to detect signs of cognitive dysfunction from clinician notes in electronic health records (EHR) by applying deep learning techniques that have not been hitherto applied to this problem. We present an attention-based transformer model that allows for long text sequences to reveal signs of cognitive concerns and compare its performance to baseline models.

\section{Related Work}
\label{sec:relatedwork}
Prior works have used pattern based text-analytics to detect dementia in electronic health records. Dementia detection using NLP on provider notes has been applied to a cohort of acute-care EHRs of hip and stroke fracture patients \citep{gilmore-bykovskyi_unstructured_2018}; a sample of patients enrolled in the UCLA Alzheimer's and Dementia Care (ADC) program \citep{reuben_automated_2017}; and a group of patients who had a formal cognitive evaluation by the Mayo Clinic Study of Aging and were hospitalized at their institution \citep{amra_derivation_2017}. These studies demonstrated that the incorporation of NLP on EHR notes improves sensitivity of dementia detection. The current work uses deep learning based NLP, which has achieved numerous breakthroughs when applied to general text thanks to the use of word embeddings and attention-based models \citep{vaswani2017attention,mikolov2013distributed,pennington2014glove,peters2018deep, devlin2018bert}, while it has had limited application on healthcare data. Our work builds upon the idea in \citep{sheu2019can}, where a deep-learning based model was applied to classify the outcome for treatment of depression, a phenotype also not captured well by structured data or term-based NLP, therefore motivating the use of deep learning techniques.

\section{Datasets and Preprocessing}
\label{sec:dataset_preprocessing}

\paragraph{Datasets}
\label{sec:dataset}Our gold-standard dataset consisted of 1K randomly sampled patients at Mass General Brigham (MGB) HealthCare (formerly Partner’s Healthcare, comprising two major academic hospitals, community hospitals, and community health centers in the Boston area). Each patient’s EHR record between 01/01/2018 – 12/31/2018 was reviewed by an expert clinician (neurologist, psychiatrist, or geriatric psychiatrist) to label patients with presence or absence of any cognitive concerns (signs of dementia).

\paragraph{Data Preprocessing}
\label{sec:preprocessing}

For each patient in the gold-standard dataset, we extracted the diagnosis, medication history, and progress notes from the window between 01/01/2018 – 12/31/2018. We flagged all medications related to cognitive concern (Galantamine, Donepezil, Rivastigmine, Memantine) as well as all International Classification of Diseases (ICD) diagnoses pertaining to cognitive concern (ICD 9 codes: 290.X, 294.X, 331.X, 780.93; ICD 10 codes: G30.X and G31.X). For each patient, we added the number of records pertaining to the medications of interest and the number of ICD codes of interest, yielding two features designed to capture the presence of cognitive concerns in the structured data. We filtered for patients that had progress notes. Several preprocessing steps were involved to trim the notes to reduce noise, and note length was decreased by 50\% after these steps, details of which are described in \appendixref{apd:app6}. The preprocessed notes were used as input for all three models that use notes as input. For the model based on regular expression matches, we constructed 15 categories of keywords (\appendixref{apd:app1}). Each category contained multiple regular expressions that were then flagged within our filtered set of notes. We then added the number of pattern matches per patient per category across all notes, resulting in 15 features per patient.

The final dataset of 767 patients was randomly split between train (90\%) and hold-out test (10\%) sets. Validation datasets were split within the train set using different methods for the various models as described in the Methodology section. \tableref{tab:example-booktabs} shows the demographics of the patients in the training and test sets.

\begin{table*}[hbtp]
\floatconts
  {tab:example-booktabs}
  {\caption{Demographics of Train/Val and Test Sets}}
 {
  \begin{tabular}{lccc}
  \toprule
  \bfseries Dataset & \bfseries Age (Mean and SD) & \bfseries \% Female & \bfseries Cognitive Concern (N) \\
  \midrule
  Train/Val (N = 690) & 81.2 (7.4) & 58.2\% & 308 (44.64\%) \\
  Test (N = 77) & 80.19 (6.79) & 54.5\% & 34 (44.16\%) \\
  \bottomrule
  \end{tabular}}
\end{table*}

\section{Methodology}
\label{sec:methodology}
We built three models and compared the performance to the baseline  model.
\paragraph{(1) Baseline Model}In model 1, we performed a regularized logistic regression where the cognitive concern label was regressed on counts of medications and ICD codes related to cognitive concern. We used the glmnet package \citep{glmnet} in R and performed L1 regularization. The lambda value in our regularization penalty was selected via 10-fold cross validation (CV), with the optimal lambda chosen to maximize the average area under the Receiver Operator Characteristic (ROC) curve across folds.

\paragraph{(2) Logistic Regression with Regular Expression Counts} In model 2, we again utilized regularized logistic regression. We regressed the cognitive concern label against the 15 features corresponding to counts of the 15 regular expression categories per patient. We similarly used L1 regularization and 10-fold CV to choose our lambda value.

\paragraph{(3) Logistic Regression with TF-IDF Vectors} In model 3, we performed a TF-IDF (term frequency–inverse document frequency) vectorization to select features based on the term's correlation coefficient, and performed a regularized logistic regression using the cognitive concern label as the outcome. We used different correlation coefficients as thresholds to select word features, and iterated with different lambda values on a validation dataset (10\% from train dataset) to determine our best lambda value and the specific correlation cutoff threshold.

\paragraph{(4) Transformer Based Sequence Classification Language Model}

In model 4, we utilized a pre-trained language model with an attention mechanism, Longformer \citep{beltagy2020longformer}, which deploys a modified self-attention mechanism whose complexity scales linearly with sequence length and thus allows accommodation of longer sequences. The model was initialized with pre-trained parameters and was later fine-tuned with our labeled training dataset. Hyperparameters were tuned on a held out validation dataset (10\% from the train dataset) for the cognitive concern classification task.

\section{Experiments and Results}
\label{sec:experiments}

\subsection{Description of Computational Experiments}
 In model 4 with Longformer (model diagram is shown in \appendixref{apd:app4}), we utilized the implementation in the Huggingface Transformer \citep{Wolf2019HuggingFacesTS} and Simpletransformers packages \citep{simple2020thilina}. After text preprocessing, input texts were tokenized with the default tokenizer and converted to embeddings. Due to the limitation of sequence lengths of Longformer, we used the “sliding windows” option available in the Simpletransformers package to automatically slice the input text into windows of 4096 tokens, with 20\% overlapping content between windows \emph{i} and \emph{i+1}. We used the Adam optimizer \citep{kingma2014adam} and tuned the model with an initial learning rate of 7.09e-6, Epsilon value of 1e-9, and 4 training epochs. Classification of each window was aggregated (mode) to obtain patient level class assignments. All performance metrics below are based on patient level class assignments.

\begin{table*}[hbtp]
\floatconts
  {tab:performance}
  {\caption{Model Performance Comparison}}
  {\begin{tabular}{lllllllll}
  \toprule
  \bfseries Model &\bfseries AUC& \bfseries Accuracy & \bfseries FP & \bfseries FN &\bfseries Sensitivity &\bfseries Specificity &\bfseries PPV &\bfseries NPV\\
  \midrule
  Model 1 & 0.79 & 0.82 & 0 & 14 & 0.59 & 1.00 & 1.00 & 0.75\\
  Model 2 & 0.88 & 0.84 & 4 & 8 & 0.76 & 0.91 & 0.87 & 0.83\\
  Model 3 & 0.90 & 0.86 & 6 & 5 & 0.85 & 0.86 & 0.83 & 0.88\\
  Model 4 & 0.93 & 0.90 & 1 & 7 & 0.79 & 0.98 & 0.96 & 0.86\\
  \bottomrule
  \end{tabular}}
\end{table*}

\subsection{Model Results and Comparison}
 We evaluated each model using a prediction threshold to maximize the accuracy and calculated performance metrics based on that threshold. The performance of the four models are shown in \tableref{tab:performance}.  Specifically, PPV, the positive predictive value is defined as the percentage of true positives among all cases predicted as positive; NPV, the negative predictive value is defined as the percentage of true negatives among all cases predicted as negative. The baseline model had an AUC-ROC of 0.79 and while the specificity was 1.0, the sensitivity was 0.59. There were 14 false negatives; of these patients with no record of ICD codes or medications in EHR, 8 were patients with subjective concern or mild cognitive impairment (MCI) and 6 were patients with dementia. The regular-expression based logistic regression had a substantial improvement in performance over the baseline model with an AUC-ROC of 0.88. The percentage of patients with dementia-related concepts shown in \appendixref{apd:app1}; terms related to memory and dementia-related medications had the highest coefficients in the regression model. The sensitivity of detection improved to 0.76 but the specificity was 0.91. The TF-IDF model demonstrated higher performance than the regular expression-based model (AUC-ROC=0.90). The 20 words with the highest correlation coefficients using TF-IDF vectorization are shown in  \tableref{table:tdf} in the Appendix \ref{apd:app2}.  The deep learning model outperformed all the models (AUC-ROC=0.93). The patients misclassified in the models were different, demonstrating that each model had its own advantages.

\section{Conclusion and Future Work}
\label{sec:conclusion}

We applied NLP algorithms to identify patients with cognitive concerns in EHR and compared model performance. While the deep learning model's performance was the best, it was only marginally better than the term based NLP models. We posit that deeper representations will be required for more complex tasks requiring syntactical and contextual information such as classifying the stage of cognitive impairment: MCI, mild, moderate or severe dementia. Our gold standard set had a relatively smaller proportion of patients with subjective concerns or mild cognitive impairment (28.6 \% with cognitive concern), and the overall sample size was small. To address these issues, we plan to implement an active learning loop, starting from querying additional at-risk patients over age 65 and without a dementia related ICD code or medication, and apply the fine-tuned model to derive the probability of having cognitive concerns for these patients. For the edge cases, the notes will be manually reviewed and labeled. To improve the efficiency of this review process, we designed an annotation tool that highlights the sections with regular expression matches or higher attention weights (UI design in Appendix \ref{apd:app5}). The new gold-standard data will serve as the basis for the next iteration of the active learning loop to further improve model performance and potentially detect patients with an earlier stage of cognitive decline.

\clearpage

\bibliographystyle{plain}
\bibliography{jmlr-sample}

% \bibliography{NeurIPs 2020}

\clearpage
\appendix

\section{Clinical Note Data Preprocessing Steps}\label{apd:app6}

In order to reduce the input unstructured data dimensionality and work with a smaller vocabulary, we adopt a series of preprocessing steps  to trim the notes to reduce noise for all three proposed models. Those steps include:
\begin{enumerate}

 \item Removed all empty lines and multiple white spaces.
 \item Removed the fixed header section which only contains non-diagnostic info. \item Remove all note section content that was verified to be unimportant by experts (either not relevant to the cognitive concern detection or contained the same info already stored in structured data format outside the note space).
 \item Utilized SpaCy's default name entity recognition package to detect and remove certain non-relevant name entities includes date, time, person, quantity info.
 \item Removed all special characters and all other numbers after SpaCy entity removal.
 \item Normalized all rest of the text to lower case.
 \item For model 4 only, we further used the tokenizer provided by the pre-trained Longformer \citep{beltagy2020longformer} model as tokenization in the model preprocessing steps, since the Longformer tokenizer, like other attention-based model, has a its particular way of handling out-of-vocabulary words.
\end{enumerate}

% \clearpage

\hfill \break

\section{TF-IDF Feature Correlation Rank}\label{apd:app2}

\begin{table}[hbtp]
\floatconts
  {tab:tfidf}
%   {\caption{TF-IDF Vector Features Correlation}}
  {\begin{tabular}{rrr}
  \toprule 
  \bfseries Rank & \bfseries Terms & \bfseries CorrCoef\\
  \midrule
  1 & dementia    & 0.4364 \\
  2 & memory      & 0.3587 \\
  3 & daughter    & 0.2959 \\
  4 & cognitive   & 0.2955 \\
  5 & alzheimer   & 0.2940 \\
  6 & accompanied & 0.2890 \\
  7 & behavioral  & 0.2809 \\
  8 & unable      & 0.2756 \\
  9 & confused    & 0.2754 \\
  10 & donepezil  & 0.2738 \\
  11 & mental     & 0.2686 \\
  12 & aricept    & 0.2664 \\
  13 & care       & 0.2580 \\
  14 & impairment & 0.2529 \\
  15 & nursing    & 0.2402 \\
  16 & assistance & 0.2365 \\
  17 & nurse      & 0.2306 \\
  18 & living     & 0.2294 \\
  19 & rn         & 0.2285 \\
  20 & dnr        & 0.2271 \\
  \bottomrule
  \end{tabular}
  \label{table:tdf}}
  {\caption{TF-IDF Vector Features Correlation}}
\end{table}

% \begin{table}[hbtp]
% \floatconts
%   {tab:count}
%   {\caption{Count Vector Features Correlation}}
%   {\begin{tabular}{rrr}
%   \toprule 
%   \bfseries Rank & \bfseries Terms & \bfseries CorrCoef\\
%   \midrule
%   1 & memory         & 0.3327 \\
%   2 & aricept        & 0.2968 \\
%   3 & alzheimer      & 0.2663 \\
%   4 & dementia       & 0.2506 \\
%   5 & daughter       & 0.2300 \\
%   6 & donepezil      & 0.2186 \\
%   7 & confused       & 0.2103 \\
%   8 & mental         & 0.2042 \\
%   9 & care           & 0.1896 \\
%   10 & decline       & 0.1870 \\
%   11 & behavioral    & 0.1855 \\
%   12 & memantine     & 0.1841 \\
%   13 & recall        & 0.1841 \\
%   14 & accompanied   & 0.1807 \\
%   15 & molst         & 0.1794 \\
%   16 & conversation  & 0.1785 \\
%   17 & remember      & 0.1784 \\
%   18 & executive     & 0.1774 \\
%   19 & cognitive     & 0.1768 \\
%   20 & unable        & 0.1749 \\

%   \bottomrule
%   \end{tabular}
%   \label{table:count}}
% \end{table}

\clearpage

\section{Dementia Related Concepts}\label{apd:app1}

\begin{figure}[htbp]
 % Caption and label go in the first argument and the figure contents
 % go in the second argument
\floatconts
  {fig:regex}
  {\caption{Dementia Related Concepts}}
  {\includegraphics[width=2\linewidth]{images/Dementia_Concepts.png}}
\end{figure}
\clearpage

\section{Longformer with Additional Sliding Windows}\label{apd:app4}

\begin{figure}[htbp]
 % Caption and label go in the first argument and the figure contents
 % go in the second argument
\floatconts
  {fig:longformer}
  {\caption{Longformer Model with Additional Sliding Window Strategy}}
  {\includegraphics[width=2\linewidth]{images/longformer2.png}}
\end{figure}
\clearpage

\section{Active Learning Annotation User Interface}\label{apd:app5}

\begin{figure}[htbp]
 % Caption and label go in the first argument and the figure contents
 % go in the second argument
\floatconts
  {fig:LabelingUI}
  {\caption{Active Learning Annotation User Interface}}
  {\includegraphics[width=2\linewidth]{images/new_UI.png}}
\end{figure}

\end{document}

### 2021-07-20 nlp_annotator-dev/app/load_data/load_data.py
got 5000 Diversity Sample read for SLAT import

@@ -11,7 +11,7 @@ from gui.models import Sentence, SeedRegex, PatientDemographic, Note
 ROOT_DIR = Path(__file__).parent
 
 # specify the import filename
-filename = "test_data.csv"
+filename = r"C:\Users\MIND_DS\Dropbox (Partners HealthCare)\NLP\Tanish\BigDataSets\Regex_match\Diversity_Sampling\5000_SLAT_import_7_19.csv"
 
 columns = [
     "PatientID",

### 2021-07-20 nlp_annotator-dev/app/annotator_gui/settings.py
SLAT update and attempts at loading CSV in

@@ -34,7 +34,7 @@ else:
     raise ValueError(f"Invalid DJANGO_ENVIRONMENT {ENVIRONMENT}! Must be 'dev' or 'prod'")
 
 
-_hosts = ['rc-slat.partners.org', 'slat.partners.org', '127.0.0.1', 'localhost']
+_hosts = ['127.0.0.1', 'localhost', '0.0.0.0', 'rc-nat.partners.org', 'nat.partners.org']
 ALLOWED_HOSTS = _hosts
 
 CSRF_TRUSTED_ORIGINS = _hosts

### 2021-07-20 nlp_annotator-dev/app/gui/models.py

@@ -27,6 +27,11 @@ class Sentence(BaseModel):
     Contents = models.TextField(blank = False, null = False)
     Note = models.ForeignKey("gui.Note", null = False, on_delete=models.PROTECT)
 
+    @classmethod
+    def unassigned(cls):
+        return cls.objects.filter(sentenceassignment__isnull=True).order_by('id')
+
+
 class SentenceAssignment(BaseModel):
     User = models.ForeignKey("accounts.CustomUser", null = False, on_delete=models.PROTECT)
     Sentence = models.ForeignKey("gui.Sentence", null = False, on_delete=models.PROTECT)
@@ -70,6 +75,10 @@ class AlwaysRegex(BaseModel):
     @property
     def regex(self):
         return re.compile(self.Pattern, flags=re.IGNORECASE)
+
+    @property
+    def Count(self):
+        return SentenceAlwaysRegex.objects.filter(AlwaysRegex=self).count()
 
 class SentenceAlwaysRegex(BaseModel):
     Sentence = models.ForeignKey("gui.Sentence", null = False, on_delete=models.PROTECT)

### 2021-07-20 nlp_annotator-dev/app/gui/urls.py

@@ -18,5 +18,10 @@ urlpatterns = [
     path('home',views.annotator_home,name='annotator_home'),
     path('highlight',views.highlight_sentence,name='highlight_sentence'),
     path('annotate/<int:patient_id>/<int:local_note_id>',views.show_note,name='show_note'),
-    path("favicon.ico", RedirectView.as_view(url=staticfiles_storage.url("favicon.ico")))
+    path("favicon.ico", RedirectView.as_view(url=staticfiles_storage.url("favicon.ico"))),
+    path("admin-menu", views.admin_menu, name='admin_menu'),
+    path("new-user", views.create_user, name='new_user'),
+    path("assign", views.assign_new, name='assign_new'),
+    path("patterns", views.always_pattern_list, name="pattern_list"),
+    path("pattern/<int:pattern_id>/undo", views.undo_always_pattern, name="undo_pattern"),
 ]

### 2021-07-20 nlp_annotator-dev/app/gui/views.py

@@ -1,13 +1,16 @@
 from django import forms
 from django.core.exceptions import ObjectDoesNotExist
 from django.forms import Form, ModelForm, Textarea
+from django.http.response import HttpResponseNotAllowed, HttpResponseNotFound
 from django.shortcuts import render, get_list_or_404, get_object_or_404, redirect
-from django.http import HttpResponse, HttpResponseRedirect, JsonResponse
+from django.http import HttpResponse, HttpResponseRedirect, JsonResponse, HttpResponseForbidden
 from django.template import loader
+from django import forms
 from django.template.response import TemplateResponse
 from django.views.decorators.csrf import csrf_exempt
 from django.db.models import FilteredRelation, Q, Count
-from django.db import IntegrityError
+from django.db import IntegrityError, transaction
+from django.core.paginator import Paginator
 import json
 import regex as re
 import functools
@@ -26,6 +29,7 @@ from accounts.forms import SignUpForm
 from django.contrib import messages
 
 from accounts.models import CustomUser
+User = CustomUser
 
 #reading in headers
 import pandas as pd
@@ -34,6 +38,8 @@ import pandas as pd
 from django.contrib.auth.forms import AuthenticationForm
 from django.contrib.auth import login, logout, authenticate
 from django.contrib.auth.decorators import login_required
+
+Form = forms.Form
 
 
 def custom_error_404(request, exception):
@@ -53,6 +59,12 @@ def custom_error_403(request, exception):
     context = {'exception': "403"}
     print("403 for: ", request)
     return HttpResponse(template.render(context, request), status=403)
+
+
+def get_page_params(request):
+    page = request.GET.get("page", 1)
+    page_size = request.GET.get("page_size", 100)
+    return page, page_size
 
 ## INDEX VIEW
 def index(request):
@@ -399,6 +411,135 @@ def annotator_home(request):
 
     return HttpResponse(template.render(context, request))
 
+@login_required()
+def admin_menu(request):
+    current_user = request.user
+    # if not current_user.is_staff:
+    #     return HttpResponseForbidden()
+    return render(request, "gui/admin/menu.html")
+
+
+class CreateUserForm(Form):
+    username = forms.CharField(label="username")
+    password = forms.CharField(label="password")
+
+
+@login_required()
+def create_user(request):
+    current_user = request.user
+    # if not current_user.is_staff:
+    #     return HttpResponseForbidden()
+    if request.method == "POST":
+        form = CreateUserForm(request.POST)
[…]

### 2021-07-20 nlp_annotator-dev/app/load_data/load_data.py

@@ -11,7 +11,7 @@ from gui.models import Sentence, SeedRegex, PatientDemographic, Note
 ROOT_DIR = Path(__file__).parent
 
 # specify the import filename
-filename = r"C:\Users\MIND_DS\Dropbox (Partners HealthCare)\NLP\Tanish\BigDataSets\Regex_match\Diversity_Sampling\5000_SLAT_import_7_19.csv"
+filename = "5000_SLAT_import_7_20_v4.csv"
 
 columns = [
     "PatientID",
@@ -25,18 +25,19 @@ columns = [
 ]
 column_overrides = {
     "Sentence": "regex_sent",
-    "RegexMatches": "regex_matches"
+    "RegexMatches": "regex_match"
 }
 column_mapping = {
     c: column_overrides.get(c, c) for c in columns
 }
 
+print("CM: ", column_mapping)
 
 patients = {}
 notes = {}
 regexes = {}
 # read file and create patients, notes and seed regexes
-with open(ROOT_DIR / filename, "r") as f:
+with open(ROOT_DIR / filename, "r", encoding = 'utf-8') as f:
     rows = csv.DictReader(f)
     patient_ids = set() # (patient_id, mrn, empi)
     note_ids = set() # (patient_id, note_id, encounter_id)
@@ -59,7 +60,9 @@ with open(ROOT_DIR / filename, "r") as f:
     for patient_id, mrn, empi in patient_ids:
         p = PatientDemographic(PatientID=patient_id, MRN=mrn, EMPI=empi).save()
         patients[patient_id] = p
+    print("NoteIDS: ", note_ids)
     for patient_id, note_id, encounter_id in note_ids:
+        print("PI: ", patient_id, "NI: ", note_id, "EI: ", encounter_id, "Date: ", Note(PatientID=patient_id, PatientEncounterID=encounter_id, NoteID=note_id).Date)
         n = Note(PatientID=patient_id, PatientEncounterID=encounter_id, NoteID=note_id).save()
         notes[note_id] = n
     for regex in all_regexes:
@@ -67,7 +70,7 @@ with open(ROOT_DIR / filename, "r") as f:
         regexes[regex] = r
 
 # start
-with open(ROOT_DIR / filename, "r") as f:
+with open(ROOT_DIR / filename, "r", encoding = 'utf-8') as f:
     rows = csv.DictReader(f)
     sentences = []
     for row in rows:
[…]

### 2021-07-20 Submission/Paper/Paper.tex

% Basic Setup
\documentclass[12pt]{article}

% Imports
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage{rotating}
\usepackage{booktabs}
\usepackage{natbib} %comment out if you do not have the package
\usepackage{url} % not crucial - just used below for the URL 
\usepackage[load-configurations=version-1]{siunitx}

% Macros
%\pdfminorversion=4
% NOTE: To produce blinded version, replace "0" with "1" below.
\newcommand{\blind}{0}
\newcommand\tab[1][1cm]{\hspace*{#1}}

% Margins
% DON'T change margins - should be 1 inch all around.
\addtolength{\oddsidemargin}{-.5in}%
\addtolength{\evensidemargin}{-1in}%
\addtolength{\textwidth}{1in}%
\addtolength{\textheight}{1.7in}%
\addtolength{\topmargin}{-1in}%

\def\spacingset#1{\renewcommand{\baselinestretch}%
{#1}\small\normalsize} \spacingset{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\if0\blind {
    \title {
        \bf Natural Language Processing to Detect Cognitive Concerns in Electronic Health Records Using Deep Learning
    }

    \author {
        Author 1 \\
        Department of YYY, University of XXX\\
        and \\
        Author 2 \\
        Department of ZZZ, University of WWW
    }

    \maketitle
} \fi

\newpage
\doublespacing
    \tableofcontents
\newpage

\bigskip
\begin{abstract}
The text of your abstract.  100 or fewer words.
\end{abstract}

\noindent%
{\it Keywords:}  3 to 6 keywords, that do not appear in the title
\vfill

\newpage
\newpage
\newpage
\newpage
\spacingset{1.8} % DON'T change the spacing!
\section{Introduction}
\label{sec:intro}

Body of paper.  Margins in this document are roughly 0.75 inches all
around, letter size paper.

\begin{figure}
\begin{center}
\includegraphics[width=3in]{fig1.pdf}
\end{center}
\caption{Consistency comparison in fitting surrogate model in the tidal
power example. \label{fig:first}}
\end{figure}

\begin{table}
\caption{D-optimality values for design $X$ under five different scenarios.  \label{tab:tabone}}
\begin{center}
\begin{tabular}{rrrrr}
one & two & three & four & five\\\hline
1.23 & 3.45 & 5.00 & 1.21 & 3.41 \\
1.23 & 3.45 & 5.00 & 1.21 & 3.42 \\
1.23 & 3.45 & 5.00 & 1.21 & 3.43 \\
\end{tabular}
\end{center}
\end{table}

\begin{itemize}
\item Note that figures and tables (such as Figure~\ref{fig:first} and
Table~\ref{tab:tabone}) should appear in the paper, not at the end or
in separate files.
\item In the latex source, near the top of the file the command
\verb+\newcommand{\blind}{1}+ can be used to hide the authors and
acknowledgements, producing the required blinded version.
\item Remember that in the blind version, you should not identify authors
indirectly in the text.  That is, don't say ``In Smith et. al.  (2009) we
showed that ...''.  Instead, say ``Smith et. al. (2009) showed that ...''.
\item These points are only intended to remind you of some requirements.
Please refer to the instructions for authors
at \url{http://www.tandfonline.com/action/authorSubmission?journalCode=utch20&page=instructions#.UieFdDafgx0}
\item If you have Supplementary Material (eg software, data, technical
proofs), identify them in the section below.  In early stages of the
submission process, you may be unsure what to include as supplementary
material.  Don't worry---this is something that can be worked out at later stages.
\end{itemize}

\section{Methods}
\label{sec:meth}
Don't take any of these section titles seriously.  They're just for
illustration.

\section{Verifications}
\label{sec:verify}
This section will be just long enough to illustrate what a full page of
text looks like, for margins and spacing.

\cite{Campbell02}, \cite{Schubert13}, \cite{Chi81}

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
{\bf With this spacing we have 26 lines per page.}
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

\section{Conclusion}
\label{sec:conc}

\bigskip
\begin{center}
{\large\bf SUPPLEMENTARY MATERIAL}
\end{center}

\begin{description}

\item[Title:] Brief description. (file type)

\item[R-package for  MYNEW routine:] R-package ÒMYNEWÓ containing code to perform the diagnostic methods described in the article. The package also contains all datasets used as examples in the article. (GNU zipped tar file)

\item[HIV data set:] Data set used in the illustration of MYNEW method in Section~ 3.2. (.txt file)

\end{description}

%\bibliographystyle{Chicago}

%\bibliography{Bibliography-MM-MC}

\begin{thebibliography}{}

\bibitem[\protect\citeauthoryear{Campbell and Austin}{Campbell and
  Austin}{2002}]{Campbell02}
Campbell, J.~I. and S.~Austin (2002).
\newblock Effects of response time deadlines on adults' strategy choices for
  simple addition.
\newblock {\em Memory \& Cognition\/}~{\em 30\/}(6), 988--994.

\bibitem[\protect\citeauthoryear{Chi, Feltovich, and Glaser}{Chi
  et~al.}{1981}]{Chi81}
Chi, M.~T., P.~J. Feltovich, and R.~Glaser (1981).
\newblock Categorization and representation of physics problems by experts and
  novices.
\newblock {\em Cognitive science\/}~{\em 5\/}(2), 121--152.

\bibitem[\protect\citeauthoryear{Schubert, Denmark, Crandall, Grome, and
  Pappas}{Schubert et~al.}{2013}]{Schubert13}
Schubert, C.~C., T.~K. Denmark, B.~Crandall, A.~Grome, and J.~Pappas (2013).
\newblock Characterizing novice-expert differences in macrocognition: an
  exploratory study of cognitive work in the emergency department.
\newblock {\em Annals of emergency medicine\/}~{\em 61\/}(1), 96--109.

\end{thebibliography}

\end{document}

### 2021-07-21 nlp_annotator-dev/app/load_data/load_data.py
fixed load_data issue

@@ -60,7 +60,7 @@ with open(ROOT_DIR / filename, "r", encoding = 'utf-8') as f:
     for patient_id, mrn, empi in patient_ids:
         p = PatientDemographic(PatientID=patient_id, MRN=mrn, EMPI=empi).save()
         patients[patient_id] = p
-    print("NoteIDS: ", note_ids)
+    #print("NoteIDS: ", note_ids)
     for patient_id, note_id, encounter_id in note_ids:
         print("PI: ", patient_id, "NI: ", note_id, "EI: ", encounter_id, "Date: ", Note(PatientID=patient_id, PatientEncounterID=encounter_id, NoteID=note_id).Date)
         n = Note(PatientID=patient_id, PatientEncounterID=encounter_id, NoteID=note_id).save()

### 2021-07-22 nlp_annotator-dev/app/load_data/load_data.py
reading for production SLAT import

@@ -11,7 +11,7 @@ from gui.models import Sentence, SeedRegex, PatientDemographic, Note
 ROOT_DIR = Path(__file__).parent
 
 # specify the import filename
-filename = "5000_SLAT_import_7_20_v4.csv"
+filename = "SLAT_production_7_22.csv"
 
 columns = [
     "PatientID",

### 2021-07-24 nlp_annotator-dev/app/load_data/load_data.py
fixed regex_match display issue in SLAT - had to re-run match code and not cast to string

@@ -6,12 +6,15 @@ import json
 from pathlib import Path
 import django.shortcuts
 from gui.models import Sentence, SeedRegex, PatientDemographic, Note
+import sys
+
+csv.field_size_limit(1000000000)
 
 # everything is relative to this file
 ROOT_DIR = Path(__file__).parent
 
 # specify the import filename
-filename = "SLAT_production_7_22.csv"
+filename = "char_limit.csv"
 
 columns = [
     "PatientID",

### 2021-07-27 nlp_annotator-dev/app/gui/views.py
SLAT db changes and new migrations

@@ -457,19 +457,25 @@ def create_user(request):
 
 
 class AssignmentForm(Form):
-    username = forms.CharField(label="Username to assign to", required=True)
-    number = forms.IntegerField(label="Number of sentences to assign", required=True, min_value=1)
+    username = forms.CharField(label="Username to assign to")
+    number = forms.IntegerField(label="Number of sentences to assign", min_value=1)
 
-def _assign(username, number):
+def _assign(request, username, number):
     user = User.objects.get(username=username)
     sentences = Sentence.unassigned()[:number]
+    #messages.error(request, str(user))
     if not sentences:
         raise ValueError('No sentences available to assign!')
     else:    
         assigned = 0
+        #messages.error(request, "entering for loop")
         for sentence in sentences:
+            messages.error(request, "starting first step", str(sentence))
+            #print("------------------------sentence ", sentence, " --------------------------------")
             sentence, created = SentenceAssignment.objects.get_or_create(Sentence=sentence, User=user)
+            #messages.error(request, "Attemping to Save")
             sentence.save()
+            #messages.error(request, "Save Done")
             if created:
                 assigned +=1 
         return assigned
@@ -486,7 +492,7 @@ def assign_new(request):
             username = form.cleaned_data['username']
             num = form.cleaned_data['number']
             try:
-                assigned = _assign(username, num)
+                assigned = _assign(request, username, num)
                 messages.success(request, f"Assigned {assigned} sentences to {username}")
             except Exception as e:
                 messages.error(request, str(e))

### 2021-07-27 nlp_annotator-dev/save_migrations_2/0001_initial.py

@@ -1,0 +1,94 @@
+# Generated by Django 3.1.6 on 2021-04-27 04:49
+
+from django.conf import settings
+from django.db import migrations, models
+import django.db.models.deletion
+
+
+class Migration(migrations.Migration):
+
+    initial = True
+
+    dependencies = [
+        migrations.swappable_dependency(settings.AUTH_USER_MODEL),
+    ]
+
+    operations = [
+        migrations.CreateModel(
+            name='AlwaysRegex',
+            fields=[
+                ('id', models.AutoField(auto_created=True, primary_key=True, serialize=False, verbose_name='ID')),
+                ('Pattern', models.TextField(unique=True)),
+                ('Annotation', models.CharField(choices=[('Y', 'Always Yes'), ('N', 'Always No'), ('T', 'Always Neither')], max_length=1)),
+                ('CreatedBy', models.ForeignKey(on_delete=django.db.models.deletion.PROTECT, to=settings.AUTH_USER_MODEL)),
+            ],
+        ),
+        migrations.CreateModel(
+            name='Note',
+            fields=[
+                ('id', models.AutoField(auto_created=True, primary_key=True, serialize=False, verbose_name='ID')),
+                ('PatientID', models.IntegerField(blank=True, null=True)),
+                ('PatientEncounterID', models.CharField(blank=True, max_length=100, null=True)),
+                ('NoteID', models.IntegerField(blank=True, null=True, unique=True)),
+                ('Date', models.DateField()),
+            ],
+        ),
+        migrations.CreateModel(
+            name='PatientDemographic',
+            fields=[
+                ('id', models.AutoField(auto_created=True, primary_key=True, serialize=False, verbose_name='ID')),
+                ('PatientID', models.IntegerField(blank=True, unique=True)),
+                ('MRN', models.TextField(blank=True, null=True)),
+                ('EMPI', models.TextField()),
+            ],
+        ),
+        migrations.CreateModel(
+            name='SeedRegex',
+            fields=[
+                ('id', models.AutoField(auto_created=True, primary_key=True, serialize=False, verbose_name='ID')),
+                ('Pattern', models.TextField(unique=True)),
+            ],
+        ),
+        migrations.CreateModel(
+            name='Sentence',
+            fields=[
+                ('id', models.AutoField(auto_created=True, primary_key=True, serialize=False, verbose_name='ID')),
[…]

### 2021-07-27 nlp_annotator-dev/save_migrations/0001_initial.py
organized saved migrations

@@ -1,94 +1,0 @@
-# Generated by Django 3.1.6 on 2021-04-27 04:49
-
-from django.conf import settings
-from django.db import migrations, models
-import django.db.models.deletion
-
-
-class Migration(migrations.Migration):
-
-    initial = True
-
-    dependencies = [
-        migrations.swappable_dependency(settings.AUTH_USER_MODEL),
-    ]
-
-    operations = [
-        migrations.CreateModel(
-            name='AlwaysRegex',
-            fields=[
-                ('id', models.AutoField(auto_created=True, primary_key=True, serialize=False, verbose_name='ID')),
-                ('Pattern', models.TextField(unique=True)),
-                ('Annotation', models.CharField(choices=[('Y', 'Always Yes'), ('N', 'Always No'), ('T', 'Always Neither')], max_length=1)),
-                ('CreatedBy', models.ForeignKey(on_delete=django.db.models.deletion.PROTECT, to=settings.AUTH_USER_MODEL)),
-            ],
-        ),
-        migrations.CreateModel(
-            name='Note',
-            fields=[
-                ('id', models.AutoField(auto_created=True, primary_key=True, serialize=False, verbose_name='ID')),
-                ('PatientID', models.IntegerField(blank=True, null=True)),
-                ('PatientEncounterID', models.CharField(blank=True, max_length=100, null=True)),
-                ('NoteID', models.IntegerField(blank=True, null=True, unique=True)),
-                ('Date', models.DateField()),
-            ],
-        ),
-        migrations.CreateModel(
-            name='PatientDemographic',
-            fields=[
-                ('id', models.AutoField(auto_created=True, primary_key=True, serialize=False, verbose_name='ID')),
-                ('PatientID', models.IntegerField(blank=True, unique=True)),
-                ('MRN', models.TextField(blank=True, null=True)),
-                ('EMPI', models.TextField()),
-            ],
-        ),
-        migrations.CreateModel(
-            name='SeedRegex',
-            fields=[
-                ('id', models.AutoField(auto_created=True, primary_key=True, serialize=False, verbose_name='ID')),
-                ('Pattern', models.TextField(unique=True)),
-            ],
-        ),
-        migrations.CreateModel(
-            name='Sentence',
-            fields=[
-                ('id', models.AutoField(auto_created=True, primary_key=True, serialize=False, verbose_name='ID')),
[…]

### 2021-07-27 nlp_annotator-dev/save_migrations/0004_auto_20210428_1548.py

@@ -1,23 +1,0 @@
-# Generated by Django 3.1.6 on 2021-04-28 15:48
-
-from django.db import migrations, models
-
-
-class Migration(migrations.Migration):
-
-    dependencies = [
-        ('gui', '0003_auto_20210428_1544'),
-    ]
-
-    operations = [
-        migrations.AlterField(
-            model_name='note',
-            name='NoteID',
-            field=models.TextField(blank=True, null=True, unique=True),
-        ),
-        migrations.AlterField(
-            model_name='note',
-            name='PatientID',
-            field=models.TextField(blank=True, null=True),
-        ),
-    ]

### 2021-07-27 Submission/Paper/ML4H/Paper.tex
file structure changes

% Basic Setup
\documentclass[12pt]{article}

% Imports
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage{rotating}
\usepackage{booktabs}
\usepackage{natbib} %comment out if you do not have the package
\usepackage{url} % not crucial - just used below for the URL 
\usepackage{siunitx}

% Macros
%\pdfminorversion=4
% NOTE: To produce blinded version, replace "0" with "1" below.
\newcommand{\blind}{0}
\newcommand\tab[1][1cm]{\hspace*{#1}}
\def\l@subsubsubsection{\@dottedtocline{4}{7em}{4em}}
\def\spacingset#1{\renewcommand{\baselinestretch}%
{#1}\small\normalsize} \spacingset{1}
\def\l@paragraph{\@dottedtocline{5}{10em}{5em}}
\def\l@subparagraph{\@dottedtocline{6}{14em}{6em}}

% Margins
% DON'T change margins - should be 1 inch all around.
\addtolength{\oddsidemargin}{-.5in}%
\addtolength{\evensidemargin}{-1in}%
\addtolength{\textwidth}{1in}%
\addtolength{\textheight}{1.7in}%
\addtolength{\topmargin}{-1in}%

% Graphics
\graphicspath{images/}

\usepackage{subfiles} % Best loaded last in the preamble

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

% Authors
\if0\blind {
    \title {
        \bf Title
    }

    \author {
        Author 1 \\
        Department of YYY, University of XXX\\
        and \\
        Author 2 \\
        Department of ZZZ, University of WWW
    }

    \maketitle
} \fi

% TOC
\newpage
    \tableofcontents
\newpage

% Abstract
\section{Abstract}

\input{sections/abstract}

% Introduction
\section{Introduction}
	\subsection{Background}

	\subsection{Related Work}

% Methodology
\section{Methodology}
	\subsection{Acquisition of Data}
	\tab Our gold-standard dataset consisted of 16K sampled patients with APOE gene <insert info about Biobank>. Each patient's EHR record was reviewed by an expert clinician (neurologist, psychiatrist, or geriatric psychiatrist) to annotate patients with presence, absence, or inconclusiveness of cognitive impairment.

	\subsection{Preprocessing}
	\tab We first created a list of keywords related to cognitive impairment (full list with frequency matches in Appendix A). For each patient in the BioBank data repository (mentioned above), we extracted all sequences containing any of the keywords. Several preprocessing steps were completed to increase the sequences to 800 characters minimum (more details in Appendix B) to allow for annotators to have more context when evaluating sequences.The preprocessed sequences were used as input for all models.

	% \subsubsection{Obtaining Gold Standard Labels} Fair Header (where you would talk about SLAT)

	\subsection{Machine Learning Models}
		% \subsubsection{TFIDF Vectors} Fair Header

	\subsection{Deep Learning Model}
		% \subsubsection{BERT and Transformers} Fair Header

% Results
\section{Results}
	\subsection{Model Results and Comparison}

% Conclusion
\section{Conclusion}

% Future Work
\section{Future Work}

% References
\section{References}

\section{Appendix A}

\begin{table*}[htbp]

	{
		\begin{tabular}{c|c|c}
		\toprule
	    \textbf{Rank} & \textbf{Keyword} & \textbf{Match Count} \\
	    \midrule

		1 & \textbf{Memory} & 109218 \\ 
		2 & \textbf{Cognition}  & 87655 \\ 
		3 & \textbf{Dementia} & 51034 \\ 
		4 & \textbf{Cerebral} &  45886 \\ 
		5 & \textbf{Cerebrovascular} & 36370 \\ 
		6 & \textbf{Cerebellar} & 26863 \\
		7 & \textbf{Cognitive Impairment} & 20267 \\ 
		8 & \textbf{Alzheimer} & 20581 \\ 
		9 & \textbf{MOCA} & 9767 \\ 
		10 & \textbf{Neurocognitive} & 7711 \\ 
		11 & \textbf{MCI} & 3889 \\ 
		12 & \textbf{Amnesia} & 3695 \\ 
		13 & \textbf{AD} & 2673 \\ 
		14 & \textbf{Lewy} & 2561 \\ 
		15 & \textbf{MMSE} & 2134 \\ 
		16 & \textbf{LBD} & 224 \\ 
		17 & \textbf{Corticobasal} & 147 \\ 
		18 & \textbf{Pick's} & 41 \\

	    \bottomrule
		\end{tabular}
	}
	{\caption{Keywords indicative of Cognitive Impairment}}

\end{table*}

\section{Appendix B}

\end{document}

### 2021-07-27 nlp_annotator-dev/app/load_data/load_data.py

@@ -65,7 +65,7 @@ with open(ROOT_DIR / filename, "r", encoding = 'utf-8') as f:
         patients[patient_id] = p
     #print("NoteIDS: ", note_ids)
     for patient_id, note_id, encounter_id in note_ids:
-        print("PI: ", patient_id, "NI: ", note_id, "EI: ", encounter_id, "Date: ", Note(PatientID=patient_id, PatientEncounterID=encounter_id, NoteID=note_id).Date)
+        #print("PI: ", patient_id, "NI: ", note_id, "EI: ", encounter_id, "Date: ", Note(PatientID=patient_id, PatientEncounterID=encounter_id, NoteID=note_id).Date)
         n = Note(PatientID=patient_id, PatientEncounterID=encounter_id, NoteID=note_id).save()
         notes[note_id] = n
     for regex in all_regexes:

### 2021-08-08 Modeling/BertV2.py
reorganization of Modeling folder

@@ -32,7 +32,7 @@ import time
 data_dir = Path("../Data")
 results_dir = Path("../Results/")
 
-# set seeds to make computations deterministic
+# set seeds
 np.random.seed(1234)
 torch.manual_seed(1234)
 
@@ -41,21 +41,18 @@ cuda_available = torch.cuda.is_available()
 print("Is CUDA available? ", "Yes" if cuda_available else "No")
 
 always_patterns = pd.read_csv("input_optimized.csv") 
-manual_review = pd.read_csv(r"C:\Users\MIND_DS\Dropbox (Partners HealthCare)\NLP\Tanish\APOE-SLAT\Modeling\test_and_validation.csv")
+manual_review = pd.read_csv(r"C:\\Users\\MIND_DS\\Dropbox (Partners HealthCare)\\NLP\\Tanish\\APOE-SLAT\\Modeling\\test_and_validation.csv")
 manual_review = manual_review[['patient_id', 'sequence', 'annotator_label']]
 always_patterns = always_patterns[['patient_id', 'sequence', 'annotator_label']]
 
 def split_data(trial):
-    # stratify across sequences with and without always pattern matches and class_label (Y, N, NTR)
-    
+    # stratify across sequences with and without always pattern matches and class_label (Y, N, NTR)    
     # stratifying across sequences with always pattern
     X_train, X_other = train_test_split(always_patterns, random_state = 0,test_size = 0.1, stratify = always_patterns["annotator_label"].to_numpy())
-
     X_valid, X_test = train_test_split(X_other, random_state = 0, test_size = 0.25, stratify = X_other["annotator_label"].to_numpy())
     
     # stratifying across sequences without always pattern
     X_train_2, X_other_2 = train_test_split(manual_review, random_state = 0,test_size = 0.6, stratify = manual_review["annotator_label"].to_numpy())
-
     X_valid_2, X_test_2 = train_test_split(X_other_2, random_state = 0, test_size = (0.25/0.6), stratify = X_test_2["annotator_label"].to_numpy())
     
     # combining to get final train, test, validation splits
@@ -123,7 +120,7 @@ def fpr_tpr(df, val):
 
     for thres in thres_list:
         # compare the CB prediction to the threshold of current iteration, convert to binary prediction
-        df['PatientLabel'] = df['SeqProbs'].apply(lambda x: 1 if x > thres else 0)
[…]

### 2021-08-10 Baseline_Model/Create_Baseline_Model.Rmd
baseline model and paper

---
title: "R Notebook"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

---
title: "R Notebook"
output: html_notebook
editor_options: 
  chunk_output_type: console
---

Questions for Sudeshna:

1. Label symmetry - baseline model is per patient, Tanish is per sequence
2. Tanish has patients in both train and test set 
3. either we need to make structured data sequence level OR make tanish's sequence date patient level 
4. rule: if ANY sequence is labeled as cognitive impairment, do we give patient that label? 
5. How do we handle folding in neither/no? 
6. If we want to employ this strategy, all patients that get a label of cognitive impairment should instantly have a patient label of cognitive concern

Okay to leave patients in test/train but make sure labels are on patient level

Ask how long it will take to retrain, ensuring accurate test/train split

next monday APOE (and maybe COVID NAT)

```{r}
library(glmnet)
library(ROCR)
library(tidyverse)
library(data.table)
library(lubridate)

# update file paths from Mayuresh
meds<-fread("data/medications.csv")
diagnoses <- fread('data/icd_diagnosis.csv')

diagnoses[,Date := ymd(ContactDTS)]
meds[,Date := mdy(Medication_Date)]

# date time filters
#diagnoses <- diagnoses[Date >= '2018-01-01' & Date <= '2018-12-31']
#meds <- meds[Medication_Date >= '2018-01-01' & Date <= '2018-12-31']

AD_Meds <- c("Galantamine", "Donepezil", "Rivastigmine", "Razadyne", "Razadyne ER", "Aricept", "Exelon","Namenda","Memantine");

meds[,AD := grepl(paste(AD_Meds, collapse="|"),Medication,ignore.case = T)]

diagnoses[,AD := (grepl("Dementia|Alzheimer's|cognitive impairment|frontotemporal dementia",DiagnosisNM,ignore.case = TRUE) | grepl("^290|^294|^331|G30|G31|780.93",ICD9CD,ignore.case = TRUE) | grepl("^290|^294|^331|G30|G31|780.93",ICD10CD,ignore.case = TRUE)) & !grepl("hydrocephalus",DiagnosisNM,ignore.case = TRUE)];

structured_variables <- data.table(EMPI = unique(c(diagnoses$EMPI,meds$EMPI)))

structured_variables[diagnoses[AD==1,.N,by=.(EMPI)],on=.(EMPI),Dx_Count := i.N]
structured_variables[meds[AD==1,.N,by=.(EMPI)],on=.(EMPI),Med_Count := i.N]
structured_variables[is.na(structured_variables)] <- 0

## read in gold standards 
gold <- fread("data/Dementia_ReferenceStandardDataset_08292019_subset_mrn.csv")
gold[,Label := ifelse(syndromic_dx %in% c(1,2,3,4,9),1,0)]
structured_variables[gold,on= .(EMPI = empi),Label := i.syndromic_dx]

test_set_EMPIs <- fread('test_empi_0.csv')
test_set <- structured_variables[EMPI %in% test_set_EMPIs$EMPI]
structured_variables <- structured_variables[!EMPI %in% test_set_EMPIs$EMPI] 
train_set_EMPIs <- fread('train_empi_0.csv')
structured_variables <- structured_variables[EMPI %in% train_set_EMPIs$EMPI]

structured_variables[,.N,by = .(Label)]
structured_variables[,EMPI := NULL]
test_set <- test_set[,.(Dx_Count,Med_Count,Label,EMPI)]
structured_variables[,Label := ifelse(Label %in% c(1,2,3,4,9),1,0)]
test_set[,Label := ifelse(Label %in% c(1,2,3,4,9),1,0)]

```

```{r}
set.seed(5281995)
f <- as.formula(Label ~ .)
x <- model.matrix(f, structured_variables)[, -1]
y <- as.matrix(structured_variables[,3])

fit = cv.glmnet(x, y, family = "binomial",type.measure = "auc")

plot(fit)
coef(fit, s = "lambda.min")

saveRDS(fit,file = "glmnet.rds")

predict(fit, newx = x, s = "lambda.min", type = "class")

results <- data.table(Prediction = predict(fit, newx = x, s = "lambda.min", type = "class")[,1],Target = y)

results[,Correct := ifelse(Prediction == Target.Label,1,0)]
results[,sum(Correct)]

# need new x

#AUC_ROC	ACC	MCC	TP	TN	FP	FN	PPV (Precision) 	NPV	TPR (Sensitivity, Recall)	TNR (Secificity, selectivity)	F1-score

perf_auc <- performance(prediction(predict(fit, s=fit$lambda.min, as.matrix(test_set[,1:2]), type="response"), as.matrix(test_set[,3])),'auc')
print(perf_auc@y.values)  # .794

# write out predictions for Ayush 
test_x <- model.matrix(f, test_set)
test_y <- as.matrix(test_set[,3])
roc_data <- data.table(Prediction = predict(fit, newx = test_x, s = "lambda.min", type = "class")[,1],Target = test_y)
roc_data[,Correct := ifelse(Prediction == Target.Label,1,0)]
roc_data[,sum(Correct)]

fwrite()
```

```{r}

sens_spec <- performance(prediction(predict(fit, s=fit$lambda.min, as.matrix(test_set[,1:2]), type="response"),  as.matrix(test_set[,3])), "tpr", "fpr")

saveRDS(sens_spec, "sens_spec.RDS")
saveRDS(prediction(predict(fit, s=fit$lambda.min, as.matrix(test_set[,1:2]), type="response"),  as.matrix(test_set[,3])), "predict_prob.RDS")
saveRDS(as.matrix(test_set[,3]), "Test_labels.RDS")

perf_acc <- performance(prediction(predict(fit, s=fit$lambda.min, as.matrix(test_set[,1:2]), type="response"), as.matrix(test_set[,3])),'acc')
print(perf_acc@y.values) # .81

# TP
res <- data.table(preds = predict(fit, s=fit$lambda.min, as.matrix(test_set[,1:2]), type="class"),truth =  as.matrix(test_set[,3]))
res[,.(TP = preds.1 == '1' & truth.Label == 1)][,.N,by=.(TP)] # 18

# TN
res[,.(TN = preds.1 == '0' & truth.Label == 0)][,.N,by=.(TN)] # 43

# FP
res[,.(FP = preds.1 == '1' & truth.Label == 0)][,.N,by=.(FP)] # 0

# FN
res[,.(FN = preds.1 == '0' & truth.Label == 1)][,.N,by=.(FN)] # 16

metrics <- data.table(
cutoffs = performance(prediction(predict(fit, s=fit$lambda.min, as.matrix(test_set[,1:2]), type="response"), as.matrix(test_set[,3])),'ppv')@x.values[[1]], perf_ppv = performance(prediction(predict(fit, s=fit$lambda.min, as.matrix(test_set[,1:2]), type="response"), as.matrix(test_set[,3])),'ppv')@y.values[[1]], perf_npv = performance(prediction(predict(fit, s=fit$lambda.min, as.matrix(test_set[,1:2]), type="response"), as.matrix(test_set[,3])),'npv')@y.values[[1]], perf_tpr = performance(prediction(predict(fit, s=fit$lambda.min, as.matrix(test_set[,1:2]), type="response"), as.matrix(test_set[,3])),'tpr')@y.values[[1]], perf_tnr = performance(prediction(predict(fit, s=fit$lambda.min, as.matrix(test_set[,1:2]), type="response"), as.matrix(test_set[,3])),'tnr')@y.values[[1]], perf_f1 = performance(prediction(predict(fit, s=fit$lambda.min, as.matrix(test_set[,1:2]), type="response"), as.matrix(test_set[,3])),'f')@y.values[[1]], acc = performance(prediction(predict(fit, s=fit$lambda.min, as.matrix(test_set[,1:2]), type="response"), as.matrix(test_set[,3])),'acc')@y.values[[1]])

# do 1 minus this so mirror image
jpeg("ROC.jpeg",height=500,width=500)
plot(sens_spec,cex.axis=5)
dev.off()

fpr_tpr <-performance(prediction(predict(fit, s=fit$lambda.min, x, type="response"), y), "tpr","fpr")

cutoffs <- data.table(cut=fpr_tpr@alpha.values[[1]], fpr=fpr_tpr@x.values[[1]], 
                      tpr=fpr_tpr@y.values[[1]])

cutoffs <- cutoffs[order(-tpr)]   # 0.6402498 seems to be optimal threshold to get sensitivity equal to current test

fwrite(cutoffs,file="sens_spec_cutoffs.csv")

new_results[,.N,by=.(Target.Label)] # 452 true negatives, 452/778 = .58097

best.threshold <- .35
ux <- predict(fit,as.matrix(test_set[,1:2]),s=fit$lambda.min, type="response")
probs.new <- ifelse(ux>best.threshold,1,0)
new_results <- data.table(Predicted = probs.new[,1],Target = as.matrix(test_set[,3]))
new_results[,Correct := ifelse(Predicted == Target.Label,1,0)]
new_results[,sum(Correct)]

new_results[,EMPI := test_set$EMPI]
new_results[gold,on=.(EMPI = empi),Label := i.syndromic_dx]

fwrite(new_results,file= 'results_structured_only.csv')

# best.threshold <- 0
# ux <- predict(fit,x,s=fit$lambda.min, type="response")
# probs.new <- ifelse(ux>best.threshold,1,0)
# new_results <- data.table(Predicted = probs.new[,1],Target = y)

# new_results[Predicted == 1 & Target.Label == 0,.N]/nrow(new_results[Target.Label==0])
# 
# # values between  0.3983138 and .4001
# 
# best.threshold <- .3983138
# ux <- predict(fit,x,s=fit$lambda.min, type="response")
# probs.new <- ifelse(ux>best.threshold,1,0)
# new_results <- data.table(Predicted = probs.new[,1],Target = y)
# 
# new_results[Predicted == 1 & Target.Label == 0,.N]/nrow(new_results[Target.Label==0])

threshold_function <- function(threshold){
  best.threshold <- threshold;
  ux <- predict(fit,x,s=fit$lambda.min, type="response");
  probs.new <- ifelse(ux>best.threshold,1,0);
  new_results <- data.table(Predicted = probs.new[,1],Target = y);
  new_results[Predicted == 1 & Target.Label == 0,.N]/nrow(new_results[Target.Label==0]);
}

test_fpr <- map_dfr(c(seq(.3983138,.4001,by=.00001),.42),~data.table(Cut = .x,FPR = threshold_function(.x)))

threshold_random <- function(threshold){
  best.threshold <- threshold;
  ux <- predict(fit,x,s=fit$lambda.min, type="response");
  ux <- ux + rnorm(length(ux),.00001,.0001);
  probs.new <- ifelse(ux>best.threshold,1,0);
  new_results <- data.table(Predicted = probs.new[,1],Target = y);
  new_results[Predicted == 1 & Target.Label == 0,.N]/nrow(new_results[Target.Label==0]);
}

# number of rows that are equal to min response

responses <- data.table(Response = predict(fit,x,s=fit$lambda.min, type="response"))
responses <- responses + rnorm(nrow(responses),.0000001,.000001);

perf <- performance(prediction(responses, y),'auc')
print(perf@y.values)
sens_spec <- performance(prediction(responses, y), "tpr", "fpr")

plot(sens_spec,cex.axis=5)

```

### 2021-08-11 Baseline_Model/Create_Baseline_Model.Rmd
structed data

@@
 
-# update file paths from Mayuresh
+# read in EDW data 
 meds<-fread("data/medications.csv")
 diagnoses <- fread('data/icd_diagnosis.csv')
-
 diagnoses[,Date := ymd(ContactDTS)]
-meds[,Date := mdy(Medication_Date)]
+meds[,Date := ymd(OrderDTS)]
 
@@
 
-meds[,AD := grepl(paste(AD_Meds, collapse="|"),Medication,ignore.case = T)]
+meds[,AD := grepl(paste(AD_Meds, collapse="|"),MedicationDSC,ignore.case = T)]
 
-diagnoses[,AD := (grepl("Dementia|Alzheimer's|cognitive impairment|frontotemporal dementia",DiagnosisNM,ignore.case = TRUE) | grepl("^290|^294|^331|G30|G31|780.93",ICD9CD,ignore.case = TRUE) | grepl("^290|^294|^331|G30|G31|780.93",ICD10CD,ignore.case = TRUE)) & !grepl("hydrocephalus",DiagnosisNM,ignore.case = TRUE)];
+diagnoses[,AD := (grepl("Dementia|Alzheimer's|cognitive impairment|memory loss|frontotemporal dementia",DiagnosisNM,ignore.case = TRUE) | grepl("^290|^294|^331|G30|G31|780.93",ICD9CD,ignore.case = TRUE) | grepl("^290|^294|^331|G30|G31|780.93",ICD10CD,ignore.case = TRUE)) & !grepl("hydrocephalus",DiagnosisNM,ignore.case = TRUE)];
 
-structured_variables <- data.table(EMPI = unique(c(diagnoses$EMPI,meds$EMPI)))
+structured_variables <- data.table(PatientID = unique(c(diagnoses$PatientID,meds$PatientID)))
 
-structured_variables[diagnoses[AD==1,.N,by=.(EMPI)],on=.(EMPI),Dx_Count := i.N]
-structured_variables[meds[AD==1,.N,by=.(EMPI)],on=.(EMPI),Med_Count := i.N]
+structured_variables[diagnoses[AD==1,.N,by=.(PatientID)],on=.(PatientID),Dx_Count := i.N]
+structured_variables[meds[AD==1,.N,by=.(PatientID)],on=.(PatientID),Med_Count := i.N]
 structured_variables[is.na(structured_variables)] <- 0
+structured_variables[,AD_Med_or_ICD_Code := ifelse(Dx_Count > 0 | Med_Count > 0,1,0)]
+
+# tanish set
+
+tanish <- fread('data/20K_sample.csv')
+# need EMPI for tanish's set, get from EDW data
+tanish[rbindlist(list(meds,diagnoses),fill =T),on=.(patient_id = PatientID),EMPI := i.EMPI]
+# 0 = no, 1 = neither, 2 = CI
+tanish[,Binary_CI := ifelse(prediction == 2,1,0)]
+# at least one CI, give 1 for patient level cognitive impairment 
+tanish[,patient_CI := ifelse(sum(Binary_CI) > 0,1,0),by=.(patient_id)]
+tanish[,num_sequences_patient := .N,by=.(patient_id)]
+
+# one row per patient 
+tanish_predictions <- tanish[,.SD[1],by=.(patient_id)][,.(patient_id,patient_CI,num_sequences_patient,EMPI)]
+# merge structured data back on 
+tanish_predictions[structured_variables,on=.(patient_id=PatientID),`:=` (Dx_Count = i.Dx_Count, Med_Count = i.Med_Count, AD_Med_or_ICD_Code = i.AD_Med_or_ICD_Code)]
+
+# any missing data? NO
+nrow(tanish_predictions[is.na(AD_Med_or_ICD_Code)])
+
+# patient cognitive impairment by whether they have med/code 
+tanish_predictions[,.N,by=.(patient_CI,AD_Med_or_ICD_Code)]
+
+# read in APOE data 
+apoe <- fread('data/apoe/Partners_biobank_APOE_nodup.csv')
+bib <- rbindlist(list(fread('data/apoe/sd587_03212118253982866_6375194824947826181_Bib.txt'),fread('data/apoe/sd587_03212118253982866_6375194824947826182_Bib.txt')))
+# join back EMPI from mapping
+apoe[bib,on=.(subject_id = Subject_Id),EMPI := i.EMPI]
+
+tanish_predictions[apoe,on=.(EMPI),APOE := i.APOE]
+
+##### need collapsed APOE definition
+
+tanish_predictions[,.N,by=.(patient_CI,AD_Med_or_ICD_Code,APOE)]
+
+fwrite(tanish_predictions,file='data/tanish_predictions_with_structured_features.csv')
+
+# view false negatives
+View(tanish[patient_id %in% tanish_predictions[patient_CI == 0 & AD_Med_or_ICD_Code == 1,patient_id]])
+#view false positives
+View(tanish[patient_id %in% tanish_predictions[patient_CI == 1 & AD_Med_or_ICD_Code == 0,patient_id]])
 
 ## read in gold standards 
-gold <- fread("data/Dementia_ReferenceStandardDataset_08292019_subset_mrn.csv")
-gold[,Label := ifelse(syndromic_dx %in% c(1,2,3,4,9),1,0)]
-structured_variables[gold,on= .(EMPI = empi),Label := i.syndromic_dx]
-
-test_set_EMPIs <- fread('test_empi_0.csv')
-test_set <- structured_variables[EMPI %in% test_set_EMPIs$EMPI]
-structured_variables <- structured_variables[!EMPI %in% test_set_EMPIs$EMPI] 
-train_set_EMPIs <- fread('train_empi_0.csv')
-structured_variables <- structured_variables[EMPI %in% train_set_EMPIs$EMPI]
-
-structured_variables[,.N,by = .(Label)]
-structured_variables[,EMPI := NULL]
-test_set <- test_set[,.(Dx_Count,Med_Count,Label,EMPI)]
-structured_variables[,Label := ifelse(Label %in% c(1,2,3,4,9),1,0)]
-test_set[,Label := ifelse(Label %in% c(1,2,3,4,9),1,0)]
+# gold <- fread("data/Dementia_ReferenceStandardDataset_08292019_subset_mrn.csv")
+# gold[,Label := ifelse(syndromic_dx %in% c(1,2,3,4,9),1,0)]
+# structured_variables[gold,on= .(EMPI = empi),Label := i.syndromic_dx]
+# 
+# test_set_EMPIs <- fread('test_empi_0.csv')
+# test_set <- structured_variables[EMPI %in% test_set_EMPIs$EMPI]
+# structured_variables <- structured_variables[!EMPI %in% test_set_EMPIs$EMPI] 
+# train_set_EMPIs <- fread('train_empi_0.csv')
+# structured_variables <- structured_variables[EMPI %in% train_set_EMPIs$EMPI] 
+# 
+# structured_variables[,.N,by = .(Label)]
+# structured_variables[,EMPI := NULL]
+# test_set <- test_set[,.(Dx_Count,Med_Count,Label,EMPI)]
+# structured_variables[,Label := ifelse(Label %in% c(1,2,3,4,9),1,0)]
+# test_set[,Label := ifelse(Label %in% c(1,2,3,4,9),1,0)]
 
@@
 
+Modeling: ONLY RUN IF BASELINE MODEL MAKES SENSE 
 ```{r}

### 2021-08-12 Baseline_Model/baseline_model.R
test

@@ -1,0 +1,91 @@
+library(glmnet)
+library(ROCR)
+library(tidyverse)
+library(data.table)
+library(lubridate)
+
+# read in EDW data 
+meds<-fread("data/medications.csv")
+diagnoses <- fread('data/icd_diagnosis.csv')
+diagnoses[,Date := ymd(ContactDTS)]
+meds[,Date := ymd(OrderDTS)]
+
+# date time filters
+#diagnoses <- diagnoses[Date >= '2018-01-01' & Date <= '2018-12-31']
+#meds <- meds[Medication_Date >= '2018-01-01' & Date <= '2018-12-31']
+
+AD_Meds <- c("Galantamine", "Donepezil", "Rivastigmine", "Razadyne", "Razadyne ER", "Aricept", "Exelon","Namenda","Memantine");
+
+meds[,AD := grepl(paste(AD_Meds, collapse="|"),MedicationDSC,ignore.case = T)]
+
+diagnoses[,AD := (grepl("Dementia|Alzheimer's|cognitive impairment|memory loss|frontotemporal dementia",DiagnosisNM,ignore.case = TRUE) | grepl("^290|^294|^331|G30|G31|780.93",ICD9CD,ignore.case = TRUE) | grepl("^290|^294|^331|G30|G31|780.93",ICD10CD,ignore.case = TRUE)) & !grepl("hydrocephalus",DiagnosisNM,ignore.case = TRUE)];
+
+structured_variables <- data.table(PatientID = unique(c(diagnoses$PatientID,meds$PatientID)))
+
+structured_variables[diagnoses[AD==1,.N,by=.(PatientID)],on=.(PatientID),Dx_Count := i.N]
+structured_variables[meds[AD==1,.N,by=.(PatientID)],on=.(PatientID),Med_Count := i.N]
+structured_variables[is.na(structured_variables)] <- 0
+structured_variables[,AD_Med_or_ICD_Code := ifelse(Dx_Count > 0 | Med_Count > 0,1,0)]
+
+
+# tanish set 
+
+tanish <- fread('data/20K_sample.csv')
+# need EMPI for tanish's set, get from EDW data
+tanish[rbindlist(list(meds,diagnoses),fill =T),on=.(patient_id = PatientID),EMPI := i.EMPI]
+# 0 = no, 1 = neither, 2 = CI
+tanish[,Binary_CI := ifelse(prediction == 2,1,0)]
+# at least one CI, give 1 for patient level cognitive impairment 
[…]

### 2021-08-16 Submission/Paper/ML4H/Template.tex
ML4H overleaf template

 % use the "wcp" class option for workshop and conference
 % proceedings
 %\documentclass[gray]{jmlr} % test grayscale version
 %\documentclass[tablecaption=bottom]{jmlr}% journal article
 \documentclass[pmlr,twocolumn,10pt]{jmlr} % W&CP article

% \usepackage{geometry}
% \geometry{margins=0.1in,textwidth=7in}

 % The following packages will be automatically loaded:
 % amsmath, amssymb, natbib, graphicx, url, algorithm2e

 %\usepackage{rotating}% for sideways figures and tables
 %\usepackage{longtable}% for long tables

 % The booktabs package is used by this sample document
 % (it provides \toprule, \midrule and \bottomrule).
 % Remove the next line if you don't require it.

\usepackage{booktabs}
 % The siunitx package is used by this sample document
 % to align numbers in a column by their decimal point.
 % Remove the next line if you don't require it.
\usepackage[load-configurations=version-1]{siunitx} % newer version 
%\usepackage{siunitx}

 % The following command is just for this sample document:
\newcommand{\cs}[1]{\texttt{\char`\\#1}}% remove this in your real article

% The following is to recognise equal contribution for authorship
\newcommand{\equal}[1]{{\hypersetup{linkcolor=black}\thanks{#1}}}

 % Define an unnumbered theorem just for this sample document for
 % illustrative purposes:
\theorembodyfont{\upshape}
\theoremheaderfont{\scshape}
\theorempostheader{:}
\theoremsep{\newline}
\newtheorem*{note}{Note}

 % change the arguments, as appropriate, in the following:
\jmlrvolume{LEAVE UNSET}
\jmlryear{2021}
\jmlrsubmitted{LEAVE UNSET}
\jmlrpublished{LEAVE UNSET}
\jmlrworkshop{Machine Learning for Health (ML4H) 2021} % W&CP title

 % The optional argument of \title is used in the header
\title[Short Title]{Full Title of Article\titlebreak This Title Has
A Line Break}

 % Anything in the title that should appear in the main title but 
 % not in the article's header or the volume's table of
 % contents should be placed inside \titletag{}

 %\title{Title of the Article\titletag{\thanks{Some footnote}}}

 % Use \Name{Author Name} to specify the name.
 % If the surname contains spaces, enclose the surname
 % in braces, e.g. \Name{John {Smith Jones}} similarly
 % if the name has a "von" part, e.g \Name{Jane {de Winter}}.
 % If the first letter in the forenames is a diacritic
 % enclose the diacritic in braces, e.g. \Name{{\'E}louise Smith}

 % \thanks must come after \Name{...} not inside the argument for
 % example \Name{John Smith}\nametag{\thanks{A note}} NOT \Name{John
 % Smith\thanks{A note}}

 % Anything in the name that should appear in the title but not in the 
 % article's header or footer or in the volume's
 % table of contents should be placed inside \nametag{}

 % Two authors with the same address
 % \author{%
 %  \Name{Author Name1\nametag{\thanks{A note}}} \Email{abc@sample.com}\and
 %  \Name{Author Name2} \Email{xyz@sample.com}\\
 %  \addr Address
 % }

 % Three or more authors with the same address:
 % \author{%
 %  \Name{Author Name1} \Email{an1@sample.com}\\
 %  \Name{Author Name2} \Email{an2@sample.com}\\
 %  \Name{Author Name3} \Email{an3@sample.com}\\
 %  \Name{Author Name4} \Email{an4@sample.com}\\
 %  \Name{Author Name5} \Email{an5@sample.com}\\
 %  \Name{Author Name6} \Email{an6@sample.com}\\
 %  \Name{Author Name7} \Email{an7@sample.com}\\
 %  \Name{Author Name8} \Email{an8@sample.com}\\
 %  \Name{Author Name9} \Email{an9@sample.com}\\
 %  \Name{Author Name10} \Email{an10@sample.com}\\
 %  \Name{Author Name11} \Email{an11@sample.com}\\
 %  \Name{Author Name12} \Email{an12@sample.com}\\
 %  \Name{Author Name13} \Email{an13@sample.com}\\
 %  \Name{Author Name14} \Email{an14@sample.com}\\
 %  \addr Address
 % }

 % Authors with different addresses and equal first authors:
\author{%
\Name{First Author 1}\equal{These authors contributed equally} \Email{abc@sample.com}\\
\addr University X, Country 1
\AND
% footnotemark[1] is to refer to the \equal footnote
\Name{First Author 2}\footnotemark[1] \Email{def@sample.com}\\
\addr University Y, Country 2
\AND
\Name{Last Author} \Email{ghi@sample.com}\\
\addr University Z, Country 3
}

\begin{document}

\maketitle

\begin{abstract}
This is the abstract for this article.
\end{abstract}
\begin{keywords}
List of keywords
\end{keywords}

\section{Introduction}
\label{sec:intro}

This is a sample article that uses the \textsf{jmlr} class with
the \texttt{wcp} class option.  Please follow the guidelines in
this sample document as it can help to reduce complications when
combining the articles into a book. Please avoid using obsolete
commands, such as \verb|\rm|, and obsolete packages, such as
\textsf{epsfig}.\footnote{See
\url{http://www.ctan.org/pkg/l2tabu}} Some packages that are known
to cause problems for the production editing process are checked for
by the \textsf{jmlr} class and will generate an error. (If you want
to know more about the production editing process, have a look at
the video tutorials for the production editors at
\url{http://www.dickimaw-books.com/software/makejmlrbookgui/videos/}.)

Please also ensure that your document will compile with PDF\LaTeX.
If you have an error message that's puzzling you, first check for it
at the UK TUG FAQ
\url{https://texfaq.org/FAQ-man-latex}.  If
that doesn't help, create a minimal working example (see
\url{https://www.dickimaw-books.com/latex/minexample/}) and post
to somewhere like \TeX\ on StackExchange
(\url{http://tex.stackexchange.com/}) or the \LaTeX\ Community Forum
(\url{http://www.latex-community.org/forum/}).

\begin{note}
This is an numbered theorem-like environment that was defined in
this document's preamble.
\end{note}

\subsection{Sub-sections}

Sub-sections are produced using \verb|\subsection|.

\subsubsection{Sub-sub-sections}

Sub-sub-sections are produced using \verb|\subsubsection|.

\paragraph{Sub-sub-sub-sections}

Sub-sub-sub-sections are produced using \verb|\paragraph|.
These are unnumbered with a running head.

\subparagraph{Sub-sub-sub-sub-sections}

Sub-sub-sub-sub-sections are produced using \verb|\subparagraph|.
These are unnumbered with a running head.

\section{Cross-Referencing}

Always use \verb|\label| and \verb|\ref| (or one of the commands
described below) when cross-referencing.  For example, the next
section is Section~\ref{sec:math} but you can also refer to it using
\sectionref{sec:math}. The \textsf{jmlr} class
provides some convenient cross-referencing commands:
\verb|\sectionref|, \verb|\equationref|, \verb|\tableref|,
\verb|\figureref|, \verb|\algorithmref|, \verb|\theoremref|,
\verb|\lemmaref|, \verb|\remarkref|, \verb|\corollaryref|,
\verb|\definitionref|, \verb|\conjectureref|, \verb|\axiomref|,
\verb|\exampleref| and \verb|\appendixref|. The argument of these
commands may either be a single label or a comma-separated list
of labels. Examples:

Referencing sections: \sectionref{sec:math} or
\sectionref{sec:intro,sec:math} or
\sectionref{sec:intro,sec:math,sec:tables,sec:figures}.

Referencing equations: \equationref{eq:trigrule} or
\equationref{eq:trigrule,eq:df} or
\equationref{eq:trigrule,eq:f,eq:df,eq:y}.

Referencing tables: \tableref{tab:operatornames} or
\tableref{tab:operatornames,tab:example} or
\tableref{tab:operatornames,tab:example,tab:example-booktabs}.

Referencing figures: \figureref{fig:nodes} or
\figureref{fig:nodes,fig:teximage} or
\figureref{fig:nodes,fig:teximage,fig:subfigex} or
\figureref{fig:circle,fig:square}.

Referencing algorithms: \algorithmref{alg:gauss} or
\algorithmref{alg:gauss,alg:moore} or
\algorithmref{alg:gauss,alg:moore,alg:net}.

Referencing theorem-like environments: \theoremref{thm:eigenpow},
\lemmaref{lem:sample}, \remarkref{rem:sample}, 
\corollaryref{cor:sample}, \definitionref{def:sample},
\conjectureref{con:sample}, \axiomref{ax:sample} and
\exampleref{ex:sample}.

Referencing appendices: \appendixref{apd:first} or
\appendixref{apd:first,apd:second}.

\section{Equations}
\label{sec:math}

The \textsf{jmlr} class loads the \textsf{amsmath} package, so
you can use any of the commands and environments defined there.
(See the \textsf{amsmath} documentation for further
details.\footnote{Either \texttt{texdoc amsmath} or
\url{http://www.ctan.org/pkg/amsmath}})

Unnumbered single-lined equations should be displayed using
\verb|\[| and \verb|\]|. For example:
\[E = m c^2\]
or you can use the \texttt{displaymath} environment:
\begin{displaymath}
E = m c^2
\end{displaymath}
Numbered single-line equations should be displayed using the
\texttt{equation} environment. For example:
\begin{equation}\label{eq:trigrule}
\cos^2\theta + \sin^2\theta \equiv 1
\end{equation}
This can be referenced using \verb|\label| and \verb|\equationref|.
For example, \equationref{eq:trigrule}.

Multi-lined numbered equations should be displayed using the
\texttt{align} environment.\footnote{For reasons why you 
shouldn't use the obsolete \texttt{eqnarray} environment, see
Lars Madsen, \emph{Avoid eqnarray!} TUGboat 33(1):21--25, 2012.} For example:
\begin{align}
f(x) &= x^2 + x\label{eq:f}\\
f'(x) &= 2x + 1\label{eq:df}
\end{align}
Unnumbered multi-lined equations can be displayed using the
\texttt{align*} environment. For example:
\begin{align*}
f(x) &= (x+1)(x-1)\\
&= x^2 - 1
\end{align*}
If you want to mix numbered with unnumbered lines use the
\texttt{align} environment and suppress unwanted line numbers with
\verb|\nonumber|. For example:
\begin{align}
y &= x^2 + 3x - 2x + 1\nonumber\\
&= x^2 + x + 1\label{eq:y}
\end{align}
An equation that is too long to fit on a single line can be
displayed using the \texttt{split} environment. 
Text can be embedded in an equation using \verb|\text| or
\verb|\intertext| (as used in \theoremref{thm:eigenpow}).
See the \textsf{amsmath} documentation for further details.

\subsection{Operator Names}
\label{sec:op}

Predefined operator names are listed in \tableref{tab:operatornames}.
For additional operators, either use \verb|\operatorname|,
for example $\operatorname{var}(X)$ or declare it with
\verb|\DeclareMathOperator|, for example
\begin{verbatim}
\DeclareMathOperator{\var}{var}
\end{verbatim}
and then use this new command. If you want limits that go above and
below the operator (like \verb|\sum|) use the starred versions
(\verb|\operatorname*| or \verb|\DeclareMathOperator*|).

\begin{table*}[htbp]
\floatconts
  {tab:operatornames}%
  {\caption{Predefined Operator Names (taken from 
   \textsf{amsmath} documentation)}}%
  {%
\begin{tabular}{rlrlrlrl}
\cs{arccos} & $\arccos$ &  \cs{deg} & $\deg$ &  \cs{lg} & $\lg$ &  \cs{projlim} & $\projlim$ \\
\cs{arcsin} & $\arcsin$ &  \cs{det} & $\det$ &  \cs{lim} & $\lim$ &  \cs{sec} & $\sec$ \\
\cs{arctan} & $\arctan$ &  \cs{dim} & $\dim$ &  \cs{liminf} & $\liminf$ &  \cs{sin} & $\sin$ \\
\cs{arg} & $\arg$ &  \cs{exp} & $\exp$ &  \cs{limsup} & $\limsup$ &  \cs{sinh} & $\sinh$ \\
\cs{cos} & $\cos$ &  \cs{gcd} & $\gcd$ &  \cs{ln} & $\ln$ &  \cs{sup} & $\sup$ \\
\cs{cosh} & $\cosh$ &  \cs{hom} & $\hom$ &  \cs{log} & $\log$ &  \cs{tan} & $\tan$ \\
\cs{cot} & $\cot$ &  \cs{inf} & $\inf$ &  \cs{max} & $\max$ &  \cs{tanh} & $\tanh$ \\
\cs{coth} & $\coth$ &  \cs{injlim} & $\injlim$ &  \cs{min} & $\min$ \\
\cs{csc} & $\csc$ &  \cs{ker} & $\ker$ &  \cs{Pr} & $\Pr$
\end{tabular}\par
\begin{tabular}{rlrl}
\cs{varlimsup} & $\varlimsup$ 
& \cs{varinjlim} & $\varinjlim$\\
\cs{varliminf} & $\varliminf$ 
& \cs{varprojlim} & $\varprojlim$
\end{tabular}
}
\end{table*}

\section{Vectors and Sets}
\label{sec:vec}

Vectors should be typeset using \cs{vec}. For example $\vec{x}$.
(The original version of \cs{vec} can also be accessed using
\cs{orgvec}, for example $\orgvec{x}$.)
The \textsf{jmlr} class also provides \cs{set} to typeset a
set. For example $\set{S}$.

\section{Floats}
\label{sec:floats}

Floats, such as figures, tables and algorithms, are moving
objects and are supposed to float to the nearest convenient
location. Please don't force them to go in a particular place. In
general it's best to use the \texttt{htbp} specifier and don't
put the figure or table in the middle of a paragraph (that is
make sure there's a paragraph break above and below the float).
Floats are supposed to have a little extra space above and below
them to make them stand out from the rest of the text. This extra
spacing is put in automatically and shouldn't need modifying.

If your article will later be reprinted in the Challenges for
Machine Learning, please be aware that the CiML books use a
different paper size, so if you want to resize any images use a
scale relative to the line width (\verb|\linewidth|), text width
(\verb|\textwidth|) or text height (\verb|\textheight|).

To ensure consistency, please \emph{don't} try changing the format of the caption by doing
something like:
\begin{verbatim}
\caption{\textit{A Sample Caption.}}
\end{verbatim}
or
\begin{verbatim}
\caption{\em A Sample Caption.}
\end{verbatim}
You can, of course, change the font for individual words or 
phrases, for example:
\begin{verbatim}
\caption{A Sample Caption With Some \emph{Emphasized Words}.}
\end{verbatim}

\subsection{Tables}
\label{sec:tables}

Tables should go in the \texttt{table} environment. Within this
environment use \verb|\floatconts| (defined by \textsf{jmlr})
to set the caption correctly and center the table contents.
The location of the caption depends on the \verb|tablecaption|
setting in the document class options.

\begin{table}[htbp]
 % The first argument is the label.
 % The caption goes in the second argument, and the table contents
 % go in the third argument.
\floatconts
  {tab:example}%
  {\caption{An Example Table}}%
  {\begin{tabular}{ll}
  \bfseries Dataset & \bfseries Result\\
  Data1 & 0.12345\\
  Data2 & 0.67890\\
  Data3 & 0.54321\\
  Data4 & 0.09876
  \end{tabular}}
\end{table}

If you want horizontal rules you can use the \textsf{booktabs}
package which provides the commands \verb|\toprule|, 
\verb|\midrule| and \verb|\bottomrule|. For example, see
\tableref{tab:example-booktabs}.

\begin{table}[hbtp]
\floatconts
  {tab:example-booktabs}
  {\caption{A Table With Horizontal Lines}}
  {\begin{tabular}{ll}
  \toprule
  \bfseries Dataset & \bfseries Result\\
  \midrule
  Data1 & 0.12345\\
  Data2 & 0.67890\\
  Data3 & 0.54321\\
  Data4 & 0.09876\\
  \bottomrule
  \end{tabular}}
\end{table}

If you really want vertical lines as well, you can't use the
\textsf{booktabs} commands as there'll be some unwanted gaps.
Instead you can use \LaTeX's \verb|\hline|, but the rows may
appear a bit cramped.  You can add extra space above or below a
row using \verb|\abovestrut| and \verb|\belowstrut|. For example,
see \tableref{tab:example-hline}. However, you might want to read
the \textsf{booktabs} documentation regarding the use of vertical
lines.

\begin{table}[htbp]
\floatconts
  {tab:example-hline}
  {\caption{A Table With Horizontal and Vertical Lines}}%
  {%
    \begin{tabular}{|l|l|}
    \hline
    \abovestrut{2.2ex}\bfseries Dataset & \bfseries Result\\\hline
    \abovestrut{2.2ex}Data1 & 0.12345\\
    Data2 & 0.67890\\
    Data3 & 0.54321\\
    \belowstrut{0.2ex}Data4 & 0.09876\\\hline
    \end{tabular}
  }
\end{table}

If you want to align numbers on their decimal point, you can
use the \textsf{siunitx} package. For example, see
\tableref{tab:example-siunitx}. For further details see the
\textsf{siunitx} documentation\footnote{Either \texttt{texdoc
siunitx} or \url{http://www.ctan.org/pkg/siunitx}}.

\begin{table}[htbp]
\floatconts
  {tab:example-siunitx}
  {\caption{A Table With Numbers Aligned on the Decimal Point}}
  {\begin{tabular}{lS[tabformat=3.5]}
  \bfseries Dataset & {\bfseries Result}\\
  Data1 & 0.12345\\
  Data2 & 10.6789\\
  Data3 & 50.543\\
  Data4 & 200.09876
  \end{tabular}}
\end{table}

If the table is too wide, you can adjust the inter-column
spacing by changing the value of \verb|\tabcolsep|. For
example:
\begin{verbatim}
\setlength{\tabcolsep}{3pt}
\end{verbatim}
If the table is very wide but not very long, you can use the
\texttt{sidewaystable} environment defined in the
\textsf{rotating} package (so use \verb|\usepackage{rotating}|).
If the table is too long to fit on a page, you can use the
\texttt{longtable} environment defined in the \textsf{longtable}
package (so use \verb|\usepackage{longtable}|).

\subsection{Figures}
\label{sec:figures}

Figures should go in the \texttt{figure} environment. Within this
environment, use \verb|\floatconts| to correctly position the
caption and center the image. Use \verb|\includegraphics|
for external graphics files but omit the file extension. Do not
use \verb|\epsfig| or \verb|\psfig|. If you want to scale the
image, it's better to use a fraction of the line width rather
than an explicit length. For example, see \figureref{fig:nodes}.

\begin{figure}[htbp]
 % Caption and label go in the first argument and the figure contents
 % go in the second argument
\floatconts
  {fig:nodes}
  {\caption{Example Image}}
  {\includegraphics[width=0.5\linewidth]{images/nodes}}
\end{figure}

If your image is made up of \LaTeX\ code (for example, commands
provided by the \textsf{pgf} package) you can include it using
\cs{includeteximage} (defined by the \textsf{jmlr} class). This
can be scaled and rotated in the same way as \cs{includegraphics}.
For example, see \figureref{fig:teximage}.

\begin{figure}[htbp]
\floatconts
  {fig:teximage}
  {\caption{Image Created Using \LaTeX\ Code}}
  {\includeteximage[angle=45]{images/teximage}}
\end{figure}

If the figure is too wide to fit on the page, you can use the
\texttt{sidewaysfigure} environment defined in the
\textsf{rotating} package.

Don't use \verb|\graphicspath|.\footnote{This is specific to the
\textsf{jmlr} class, not a general recommendation. The main file
that generates the proceedings or the CiML book is typically in a
different directory to the imported articles, so it modifies the
graphics path when it imports an article.} If the images 
are contained in a subdirectory, specify this when you include the image, for
example \verb|\includegraphics{figures/mypic}|.

\subsubsection{Sub-Figures}
\label{sec:subfigures}

Sub-figures can be created using \verb|\subfigure|, which is
defined by the \textsf{jmlr} class. The optional argument allows
you to provide a subcaption. The label should be placed in the
mandatory argument of \verb|\subfigure|. You can reference the
entire figure, for example \figureref{fig:subfigex}, or you can
reference part of the figure using \verb|\figureref|, for example
\figureref{fig:circle}. Alternatively you can reference the
subfigure using \verb|\subfigref|, for example
\subfigref{fig:circle,fig:square} in \figureref{fig:subfigex}.

\begin{figure}[htbp]
\floatconts
  {fig:subfigex}
  {\caption{An Example With Sub-Figures.}}
  {%
    \subfigure[A Circle]{\label{fig:circle}%
      \includegraphics[width=0.2\linewidth]{images/circle}}%
    \qquad
    \subfigure[A Square]{\label{fig:square}%
      \includegraphics[width=0.2\linewidth]{images/square}}
  }
\end{figure}

By default, the sub-figures are aligned on the baseline.
This can be changed using the second optional argument
of \verb|\subfigure|. This may be \texttt{t} (top), \texttt{c}
(centered) or \texttt{b} (bottom). For example, the subfigures
\subfigref{fig:circle2,fig:square2} in \figureref{fig:subfigex2}
both have \verb|[c]| as the second optional argument.

\begin{figure}[htbp]
\floatconts
  {fig:subfigex2}
  {\caption{Another Example With Sub-Figures.}}
  {%
    \subfigure[A Small Circle][c]{\label{fig:circle2}%
      \includegraphics[width=0.1\linewidth]{images/circle}}%
    \qquad
    \subfigure[A Square][c]{\label{fig:square2}%
      \includegraphics[width=0.2\linewidth]{images/square}}
  }
\end{figure}

\subsection{Sub-Tables}
\label{sec:subtables}
There is an analogous command \verb|\subtable| for sub-tables.
It has the same syntax as \verb|\subfigure| described above.
You can reference the table using \verb|\tableref|, for example
\tableref{tab:subtabex} or you can reference part of the table,
for example \tableref{tab:ab}. Alternatively you can reference the
subtable using \verb|\subtabref|, for example
\subtabref{tab:ab,tab:cd} in \tableref{tab:subtabex}.

\begin{table}[htbp]
\floatconts
 {tab:subtabex}
 {\caption{An Example With Sub-Tables}}
 {%
   \subtable{%
     \label{tab:ab}%
     \begin{tabular}{cc}
     \bfseries A & \bfseries B\\
     1 & 2
     \end{tabular}
   }\qquad
   \subtable{%
     \label{tab:cd}%
     \begin{tabular}{cc}
     \bfseries C & \bfseries D\\
     3 & 4\\
     5 & 6
     \end{tabular}
   }
 }
\end{table}

By default, the sub-tables are aligned on the top.
This can be changed using the second optional argument
of \verb|\subtable|. This may be \texttt{t} (top), \texttt{c}
(centered) or \texttt{b} (bottom). For example, the sub-tables
\subtabref{tab:ab2,tab:cd2} in \tableref{tab:subtabex2}
both have \verb|[c]| as the second optional argument.

\begin{table}[htbp]
\floatconts
 {tab:subtabex2}
 {\caption{Another Example With Sub-Tables}}
 {%
   \subtable[][c]{%
     \label{tab:ab2}%
     \begin{tabular}{cc}
     \bfseries A & \bfseries B\\
     1 & 2
     \end{tabular}
   }\qquad
   \subtable[][c]{%
     \label{tab:cd2}%
     \begin{tabular}{cc}
     \bfseries C & \bfseries D\\
     3 & 4\\
     5 & 6
     \end{tabular}
   }
 }
\end{table}

\subsection{Algorithms}
\label{sec:algorithms}

Enumerated textual algorithms can be displayed using the
\texttt{algorithm} environment. Within this environment, use
\verb|\caption| to set the caption and you can use an
\texttt{enumerate} or nested \texttt{enumerate} environments.
For example, see \algorithmref{alg:gauss}. Note that algorithms
float like figures and tables.

\begin{algorithm}[htbp]
\floatconts
  {alg:gauss}%
  {\caption{The Gauss-Seidel Algorithm}}%
{%
\begin{enumerate}
  \item For $k=1$ to maximum number of iterations
    \begin{enumerate}
      \item For $i=1$ to $n$
        \begin{enumerate}
        \item $x_i^{(k)} = 
          \frac{b_i - \sum_{j=1}^{i-1}a_{ij}x_j^{(k)}
          - \sum_{j=i+1}^{n}a_{ij}x_j^{(k-1)}}{a_{ii}}$
        \item If $\|\vec{x}^{(k)}-\vec{x}^{(k-1)} < \epsilon\|$,
          where $\epsilon$ is a specified stopping criteria, stop.
      \end{enumerate}
    \end{enumerate}
\end{enumerate}
}%
\end{algorithm}

If you'd rather have the same numbering throughout the algorithm
but still want the convenient indentation of nested 
\texttt{enumerate} environments, you can use the
\texttt{enumerate*} environment provided by the \textsf{jmlr}
class. For example, see \algorithmref{alg:moore}.

\begin{algorithm}
\floatconts
  {alg:moore}%
  {\caption{Moore's Shortest Path}}%
{%
Given a connected graph $G$, where the length of each edge is 1:
\begin{enumerate*}
  \item Set the label of vertex $s$ to 0
  \item Set $i=0$
  \begin{enumerate*}
    \item \label{step:locate}Locate all unlabelled vertices 
          adjacent to a vertex labelled $i$ and label them $i+1$
    \item If vertex $t$ has been labelled,
    \begin{enumerate*}
      \item[] the shortest path can be found by backtracking, and 
      the length is given by the label of $t$.
    \end{enumerate*}
    otherwise
    \begin{enumerate*}
      \item[] increment $i$ and return to step~\ref{step:locate}
    \end{enumerate*}
  \end{enumerate*}
\end{enumerate*}
}%
\end{algorithm}

Pseudo code can be displayed using the \texttt{algorithm2e}
environment. This is defined by the \textsf{algorithm2e} package
(which is automatically loaded) so check the \textsf{algorithm2e}
documentation for further details.\footnote{Either \texttt{texdoc
algorithm2e} or \url{http://www.ctan.org/pkg/algorithm2e}}
For an example, see \algorithmref{alg:net}.

\begin{algorithm2e}
\caption{Computing Net Activation}
\label{alg:net}
 % older versions of algorithm2e have \dontprintsemicolon instead
 % of the following:
 %\DontPrintSemicolon
 % older versions of algorithm2e have \linesnumbered instead of the
 % following:
 %\LinesNumbered
\KwIn{$x_1, \ldots, x_n, w_1, \ldots, w_n$}
\KwOut{$y$, the net activation}
$y\leftarrow 0$\;
\For{$i\leftarrow 1$ \KwTo $n$}{
  $y \leftarrow y + w_i*x_i$\;
}
\end{algorithm2e}

\section{Description Lists}

The \textsf{jmlr} class also provides a description-like 
environment called \texttt{altdescription}. This has an
argument that should be the widest label in the list. Compare:
\begin{description}
\item[add] A method that adds two variables.
\item[differentiate] A method that differentiates a function.
\end{description}
with
\begin{altdescription}{differentiate}
\item[add] A method that adds two variables.
\item[differentiate] A method that differentiates a function.
\end{altdescription}

\section{Theorems, Lemmas etc}
\label{sec:theorems}

The following theorem-like environments are predefined by
the \textsf{jmlr} class: \texttt{theorem}, \texttt{example},
\texttt{lemma}, \texttt{proposition}, \texttt{remark}, 
\texttt{corollary}, \texttt{definition}, \texttt{conjecture}
and \texttt{axiom}. You can use the \texttt{proof} environment
to display the proof if need be, as in \theoremref{thm:eigenpow}.

\begin{theorem}[Eigenvalue Powers]\label{thm:eigenpow}
If $\lambda$ is an eigenvalue of $\vec{B}$ with eigenvector
$\vec{\xi}$, then $\lambda^n$ is an eigenvalue of $\vec{B}^n$
with eigenvector $\vec{\xi}$.
\begin{proof}
Let $\lambda$ be an eigenvalue of $\vec{B}$ with eigenvector
$\xi$, then
\begin{align*}
\vec{B}\vec{\xi} &= \lambda\vec{\xi}
\intertext{premultiply by $\vec{B}$:}
\vec{B}\vec{B}\vec{\xi} &= \vec{B}\lambda\vec{\xi}\\
\Rightarrow \vec{B}^2\vec{\xi} &= \lambda\vec{B}\vec{\xi}\\
&= \lambda\lambda\vec{\xi}\qquad
\text{since }\vec{B}\vec{\xi}=\lambda\vec{\xi}\\
&= \lambda^2\vec{\xi}
\end{align*}
Therefore true for $n=2$. Now assume true for $n=k$:
\begin{align*}
\vec{B}^k\vec{\xi} &= \lambda^k\vec{\xi}
\intertext{premultiply by $\vec{B}$:}
\vec{B}\vec{B}^k\vec{\xi} &= \vec{B}\lambda^k\vec{\xi}\\
\Rightarrow \vec{B}^{k+1}\vec{\xi} &= \lambda^k\vec{B}\vec{\xi}\\
&= \lambda^k\lambda\vec{\xi}\qquad
\text{since }\vec{B}\vec{\xi}=\lambda\vec{\xi}\\
&= \lambda^{k+1}\vec{\xi}
\end{align*}
Therefore true for $n=k+1$. Therefore, by induction, true for all
$n$.
\end{proof}
\end{theorem}

\begin{lemma}[A Sample Lemma]\label{lem:sample}
This is a lemma.
\end{lemma}

\begin{remark}[A Sample Remark]\label{rem:sample}
This is a remark.
\end{remark}

\begin{corollary}[A Sample Corollary]\label{cor:sample}
This is a corollary.
\end{corollary}

\begin{definition}[A Sample Definition]\label{def:sample}
This is a definition.
\end{definition}

\begin{conjecture}[A Sample Conjecture]\label{con:sample}
This is a conjecture.
\end{conjecture}

\begin{axiom}[A Sample Axiom]\label{ax:sample}
This is an axiom.
\end{axiom}

\begin{example}[An Example]\label{ex:sample}
This is an example.
\end{example}

\section{Color vs Grayscale}
\label{sec:color}

It's helpful if authors supply grayscale versions of their
images in the event that the article is to be incorporated into
a black and white printed book. With external PDF, PNG or JPG
graphic files, you just need to supply a grayscale version of the
file. For example, if the file is called \texttt{myimage.png},
then the gray version should be \texttt{myimage-gray.png} or
\texttt{myimage-gray.pdf} or \texttt{myimage-gray.jpg}. You don't
need to modify your code. The \textsf{jmlr} class checks for
the existence of the grayscale version if it is print mode 
(provided you have used \verb|\includegraphics| and haven't
specified the file extension).

You can use \verb|\ifprint| to determine which mode you are in.
For example, in \figureref{fig:nodes}, the 
\ifprint{dark gray}{purple} ellipse represents an input and the
\ifprint{light gray}{yellow} ellipse represents an output.
Another example: {\ifprint{\bfseries}{\color{red}}important text!}

You can use the class option \texttt{gray} to see how the
document will appear in gray scale mode. \textcolor{blue}{Colored
text} will automatically be converted to gray scale in print mode.

The \textsf{jmlr} class loads the \textsf{xcolor}
package, so you can also define your own colors. For example:
\ifprint
  {\definecolor{myred}{gray}{0.5}}%
  {\definecolor{myred}{rgb}{0.5,0,0}}%
\textcolor{myred}{XYZ}.

The \textsf{xcolor} class is loaded with the \texttt{x11names}
option, so you can use any of the x11 predefined colors (listed
in the \textsf{xcolor} documentation\footnote{either 
\texttt{texdoc xcolor} or \url{http://www.ctan.org/pkg/xcolor}}).

\section{Citations and Bibliography}
\label{sec:cite}

The \textsf{jmlr} class automatically loads \textsf{natbib}
and automatically sets the bibliography style, so you don't need to
use \verb|\bibliographystyle|.
This sample file has the citations defined in the accompanying
BibTeX file \texttt{jmlr-sample.bib}. For a parenthetical
citation use \verb|\citep|. For example
\citep{guyon-elisseeff-03}. For a textual citation use
\verb|\citet|. For example \citet{guyon2007causalreport}. 
Both commands may take a comma-separated list, for example
\citet{guyon-elisseeff-03,guyon2007causalreport}.

These commands have optional arguments and have a starred
version. See the \textsf{natbib} documentation for further
details.\footnote{Either \texttt{texdoc natbib} or
\url{http://www.ctan.org/pkg/natbib}}

The bibliography is displayed using \verb|\bibliography|.

\acks{Acknowledgements go here.}

\bibliography{jmlr-sample}

\appendix

\section{First Appendix}\label{apd:first}

This is the first appendix.

\section{Second Appendix}\label{apd:second}

This is the second appendix.

\end{document}

### 2021-08-17 Baseline_Model/Create_Baseline_Model.Rmd
analysis on FP

@@
 
-tanish <- fread('data/20K_sample.csv')
+tanish <- fread('data/sample_8_12.csv')
 # need EMPI for tanish's set, get from EDW data
@@
 # 0 = no, 1 = neither, 2 = CI
-tanish[,Binary_CI := ifelse(prediction == 2,1,0)]
+tanish[,Binary_CI := ifelse(predictions == 2,1,0)]
 # at least one CI, give 1 for patient level cognitive impairment 
@@
 View(tanish[patient_id %in% tanish_predictions[patient_CI == 1 & AD_Med_or_ICD_Code == 0,patient_id]])
+fwrite(tanish[patient_id %in% tanish_predictions[patient_CI == 1 & AD_Med_or_ICD_Code == 0,patient_id]][order(patient_id,-predictions)],file='data/false_positive_sequences.csv')
+
+##### TANISH - ACCURACY MAXIMIZING THRESHOLD #####
+
+library(ROCR)
+library(data.table)
+
+# put your test set with binary probs here, 1 col named 'probability' and one named 'annotator_label'
+tanish_test_set <- fread("data/test_binary_classification.csv")
+# tanish_test_set[,annotator_label := ifelse(annotator_label == 2,1,0)]
+# tanish_test_set[annotator_label == 0,probability := 1 - probability]
+
+acc <- performance(prediction(tanish_test_set$probability,tanish_test_set$annotator_label),measure = 'acc')
+acc <- data.table(cutoffs = acc@x.values[[1]],accuracy = acc@y.values[[1]])
+threshold <- acc[acc[,.I[which.max(accuracy)]],cutoffs]
+
+# .729 sens
+sens <- performance(prediction(tanish_test_set$probability,tanish_test_set$annotator_label),measure = 'sens')
+sens <- data.table(cutoffs = sens@x.values[[1]],sens = sens@y.values[[1]])
+sens[cutoffs == threshold]
+
+# 0.9346939	
+spec <- performance(prediction(tanish_test_set$probability,tanish_test_set$annotator_label),measure = 'spec')
+spec <- data.table(cutoffs = spec@x.values[[1]],spec= spec@y.values[[1]])
+spec[cutoffs == threshold]
+
+# 0.9343537
+auc <- performance(prediction(tanish_test_set$probability,tanish_test_set$annotator_label),measure = 'auc')
 

### 2021-08-18 Submission/Paper/ML4H/Paper.tex
Dataset, Preprocessing, Annotations sections first draft

@@
-% Basic Setup
-\documentclass[12pt]{article}
+ % use the "wcp" class option for workshop and conference
+ % proceedings
+ %\documentclass[gray]{jmlr} % test grayscale version
+ %\documentclass[tablecaption=bottom]{jmlr}% journal article
+ \documentclass[pmlr,twocolumn,10pt]{jmlr} % W&CP article
 
-% Imports
-\usepackage{amsmath}
+% \usepackage{geometry}
+% \geometry{margins=0.1in,textwidth=7in}
+
+ % The following packages will be automatically loaded:
+ % amsmath, amssymb, natbib, graphicx, url, algorithm2e
+
+ %\usepackage{rotating}% for sideways figures and tables
+ %\usepackage{longtable}% for long tables
+
+ % The booktabs package is used by this sample document
+ % (it provides \toprule, \midrule and \bottomrule).
+ % Remove the next line if you don't require it.
+\usepackage{tabto}    
 \usepackage{graphicx}
-\usepackage{enumerate}
-\usepackage{rotating}
+\usepackage{natbib}
+\usepackage{url}
+
 \usepackage{booktabs}
-\usepackage{natbib} %comment out if you do not have the package
-\usepackage{url} % not crucial - just used below for the URL 
-\usepackage{siunitx}
+ % The siunitx package is used by this sample document
+ % to align numbers in a column by their decimal point.
+ % Remove the next line if you don't require it.
+\usepackage[load-configurations=version-1]{siunitx} % newer version 
+%\usepackage{siunitx}
 
-% Macros
-%\pdfminorversion=4
-% NOTE: To produce blinded version, replace "0" with "1" below.
-\newcommand{\blind}{0}
-\newcommand\tab[1][1cm]{\hspace*{#1}}
-\def\l@subsubsubsection{\@dottedtocline{4}{7em}{4em}}
-\def\spacingset#1{\renewcommand{\baselinestretch}%
-{#1}\small\normalsize} \spacingset{1}
-\def\l@paragraph{\@dottedtocline{5}{10em}{5em}}
-\def\l@subparagraph{\@dottedtocline{6}{14em}{6em}}
+ % The following command is just for this sample document:
+\newcommand{\cs}[1]{\texttt{\char`\\#1}}% remove this in your real article
 
-% Margins
-% DON'T change margins - should be 1 inch all around.
-\addtolength{\oddsidemargin}{-.5in}%
-\addtolength{\evensidemargin}{-1in}%
-\addtolength{\textwidth}{1in}%
-\addtolength{\textheight}{1.7in}%
-\addtolength{\topmargin}{-1in}%
+% The following is to recognise equal contribution for authorship
+\newcommand{\equal}[1]{{\hypersetup{linkcolor=black}\thanks{#1}}}
 
-% Graphics
-\graphicspath{images/}
+% Customized Tabs
+\newcommand\mytab{\tab \hspace{-5cm}}
 
-\usepackage{subfiles} % Best loaded last in the preamble
+ % Define an unnumbered theorem just for this sample document for
+ % illustrative purposes:
+\theorembodyfont{\upshape}
+\theoremheaderfont{\scshape}
+\theorempostheader{:}
+\theoremsep{\newline}
+\newtheorem*{note}{Note}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+ % change the arguments, as appropriate, in the following:
+\jmlrvolume{LEAVE UNSET}
+\jmlryear{2021}
+\jmlrsubmitted{LEAVE UNSET}
+\jmlrpublished{LEAVE UNSET}
+\jmlrworkshop{Machine Learning for Health (ML4H) 2021} % W&CP title
+
+ % The optional argument of \title is used in the header
+\title[Short Title]{Full Title of Article\titlebreak This Title Has
+A Line Break}
+
+ % Anything in the title that should appear in the main title but 
+ % not in the article's header or the volume's table of
+ % contents should be placed inside \titletag{}
+
+ %\title{Title of the Article\titletag{\thanks{Some footnote}}}
+
+ % Use \Name{Author Name} to specify the name.
+ % If the surname contains spaces, enclose the surname
+ % in braces, e.g. \Name{John {Smith Jones}} similarly
+ % if the name has a "von" part, e.g \Name{Jane {de Winter}}.
+ % If the first letter in the forenames is a diacritic
+ % enclose the diacritic in braces, e.g. \Name{{\'E}louise Smith}
+
+ % \thanks must come after \Name{...} not inside the argument for
+ % example \Name{John Smith}\nametag{\thanks{A note}} NOT \Name{John
+ % Smith\thanks{A note}}
+
+ % Anything in the name that should appear in the title but not in the 
+ % article's header or footer or in the volume's
+ % table of contents should be placed inside \nametag{}
+
+ % Two authors with the same address
+ % \author{%
+ %  \Name{Author Name1\nametag{\thanks{A note}}} \Email{abc@sample.com}\and
+ %  \Name{Author Name2} \Email{xyz@sample.com}\\
+ %  \addr Address
+ % }
+
+ % Three or more authors with the same address:
+ % \author{%
+ %  \Name{Author Name1} \Email{an1@sample.com}\\
+ %  \Name{Author Name2} \Email{an2@sample.com}\\
+ %  \Name{Author Name3} \Email{an3@sample.com}\\
+ %  \Name{Author Name4} \Email{an4@sample.com}\\
+ %  \Name{Author Name5} \Email{an5@sample.com}\\
+ %  \Name{Author Name6} \Email{an6@sample.com}\\
+ %  \Name{Author Name7} \Email{an7@sample.com}\\
+ %  \Name{Author Name8} \Email{an8@sample.com}\\
+ %  \Name{Author Name9} \Email{an9@sample.com}\\
+ %  \Name{Author Name10} \Email{an10@sample.com}\\
+ %  \Name{Author Name11} \Email{an11@sample.com}\\
+ %  \Name{Author Name12} \Email{an12@sample.com}\\
+ %  \Name{Author Name13} \Email{an13@sample.com}\\
+ %  \Name{Author Name14} \Email{an14@sample.com}\\
+ %  \addr Address
+ % }
+
+ % Authors with different addresses and equal first authors:
+\author{%
+\Name{First Author 1}\equal{These authors contributed equally} \Email{abc@sample.com}\\
+\addr University X, Country 1
+\AND
+% footnotemark[1] is to refer to the \equal footnote
+\Name{First Author 2}\footnotemark[1] \Email{def@sample.com}\\
+\addr University Y, Country 2
+\AND
+\Name{Last Author} \Email{ghi@sample.com}\\
+\addr University Z, Country 3
+}
 
@@
 
-% Authors
-\if0\blind {
-    \title {
-        \bf Title
-    }
+\maketitle
 
-    \author {
-        Author 1 \\
-        Department of YYY, University of XXX\\
-        and \\
-        Author 2 \\
-        Department of ZZZ, University of WWW
-    }
+\begin{abstract}
+\tab Dementia is a neurodegenerative disorder that causes cognitive decline and affects more than 50 million people worldwide.
+Dementia is under-diagnosed by healthcare professionals—only one in four people who suffer from dementia are diagnosed.
+Even when a diagnosis is made, it may not be entered as a structured diagnosis code in a patient’s charts.
+Information relevant to cognitive impairment is often found within electronic health records but manual review of clinician notes by experts is both time consuming and often prone to errors.
+Automated evaluation of these notes presents an opportunity to label patients with cognitive impairment (CI) in real-world data.
+\end{abstract}
+\begin{keywords}
+EHR, NLP, Demetia
+\end{keywords}
 
-    \maketitle
-} \fi
+\section{Introduction}
+\label{sec:intro}
 
-% TOC
-\newpage
-    \tableofcontents
-\newpage
+This is a sample article that uses the \textsf{jmlr} class with
+the \texttt{wcp} class option.  Please follow the guidelines in
+this sample document as it can help to reduce complications when
+combining the articles into a book. Please avoid using obsolete
+commands, such as \verb|\rm|, and obsolete packages, such as
+\textsf{epsfig}.\footnote{See
+\url{http://www.ctan.org/pkg/l2tabu}} Some packages that are known
+to cause problems for the production editing process are checked for
+by the \textsf{jmlr} class and will generate an error. (If you want
+to know more about the production editing process, have a look at
+the video tutorials for the production editors at
+\url{http://www.dickimaw-books.com/software/makejmlrbookgui/videos/}.)
 
-% Abstract
-\section{Abstract}
+Please also ensure that your document will compile with PDF\LaTeX.
+If you have an error message that's puzzling you, first check for it
+at the UK TUG FAQ
+\url{https://texfaq.org/FAQ-man-latex}.  If
+that doesn't help, create a minimal working example (see
+\url{https://www.dickimaw-books.com/latex/minexample/}) and post
+to somewhere like \TeX\ on StackExchange
+(\url{http://tex.stackexchange.com/}) or the \LaTeX\ Community Forum
+(\url{http://www.latex-community.org/forum/}).
 
-\input{sections/abstract}
+\begin{note}
+This is an numbered theorem-like environment that was defined in
+this document's preamble.
+\end{note}
 
-% Introduction
-\section{Introduction}
-	\subsection{Background}
+\subsection{Sub-sections}
 
-	\subsection{Related Work}
+Sub-sections are produced using \verb|\subsection|.
 
-% Methodology
-\section{Methodology}
-	\subsection{Acquisition of Data}
-	\tab Our gold-standard dataset consisted of 16K sampled patients with APOE gene <insert info about Biobank>.
-Each patient's EHR record was reviewed by an expert clinician (neurologist, psychiatrist, or geriatric psychiatrist) to annotate patients with presence, absence, or inconclusiveness of cognitive impairment.
+\subsubsection{Sub-sub-sections}
 
-	\subsection{Preprocessing}
-	\tab We first created a list of keywords related to cognitive impairment (full list with frequency matches in Appendix A).
-For each patient in the BioBank data repository (mentioned above), we extracted all sequences containing any of the keywords.
-Several preprocessing steps were completed to increase the sequences to 800 characters minimum (more details in Appendix B) to allow for annotators to have more context when evaluating sequences.The preprocessed sequences were used as input for all models.
+Sub-sub-sections are produced using \verb|\subsubsection|.
 
-	% \subsubsection{Obtaining Gold Standard Labels} Fair Header (where you would talk about SLAT)
+\paragraph{Sub-sub-sub-sections}
 
-	\subsection{Machine Learning Models}
-		% \subsubsection{TFIDF Vectors} Fair Header
+Sub-sub-sub-sections are produced using \verb|\paragraph|.
+These are unnumbered with a running head.
 
-	\subsection{Deep Learning Model}
-		% \subsubsection{BERT and Transformers} Fair Header
+\subparagraph{Sub-sub-sub-sub-sections}
 
-% Results
-\section{Results}
-	\subsection{Model Results and Comparison}
+Sub-sub-sub-sub-sections are produced using \verb|\subparagraph|.
+These are unnumbered with a running head.
 
-% Conclusion
-\section{Conclusion}
+\section{Related Works}
 
-% Future Work
-\section{Future Work}
+Always use \verb|\label| and \verb|\ref| (or one of the commands
+described below) when cross-referencing.  For example, the next
+section is Section~\ref{sec:math} but you can also refer to it using
+\sectionref{sec:math}. The \textsf{jmlr} class
+provides some convenient cross-referencing commands:
+\verb|\sectionref|, \verb|\equationref|, \verb|\tableref|,
+\verb|\figureref|, \verb|\algorithmref|, \verb|\theoremref|,
+\verb|\lemmaref|, \verb|\remarkref|, \verb|\corollaryref|,
+\verb|\definitionref|, \verb|\conjectureref|, \verb|\axiomref|,
+\verb|\exampleref| and \verb|\appendixref|. The argument of these
+commands may either be a single label or a comma-separated list
+of labels. Examples:
 
-% References
-\section{References}
+Referencing sections: \sectionref{sec:math} or
+\sectionref{sec:intro,sec:math} or
+\sectionref{sec:intro,sec:math,sec:tables,sec:figures}.
 
-\section{Appendix A}
+Referencing equations: \equationref{eq:trigrule} or
+\equationref{eq:trigrule,eq:df} or
+\equationref{eq:trigrule,eq:f,eq:df,eq:y}.
+
+Referencing tables: \tableref{tab:operatornames} or
+\tableref{tab:operatornames,tab:example} or
+\tableref{tab:operatornames,tab:example,tab:example-booktabs}.
+
+Referencing figures: \figureref{fig:nodes} or
+\figureref{fig:nodes,fig:teximage} or
+\figureref{fig:nodes,fig:teximage,fig:subfigex} or
+\figureref{fig:circle,fig:square}.
+
+Referencing algorithms: \algorithmref{alg:gauss} or
+\algorithmref{alg:gauss,alg:moore} or
+\algorithmref{alg:gauss,alg:moore,alg:net}.
+
+Referencing theorem-like environments: \theoremref{thm:eigenpow},
+\lemmaref{lem:sample}, \remarkref{rem:sample}, 
+\corollaryref{cor:sample}, \definitionref{def:sample},
+\conjectureref{con:sample}, \axiomref{ax:sample} and
+\exampleref{ex:sample}.
+
+Referencing appendices: \appendixref{apd:first} or
+\appendixref{apd:first,apd:second}.
+
+\section{Dataset, Preprocessing, and Annotations}
+
+\paragraph{Dataset}
+\label{sec:Dataset} Our gold-standard dataset consisted of a cohort (N=16,428) of patients from the Mass General Brigham (MGB) HealthCare (formerly Partner's Healthcare, comprising two major academic hospitals, community hospitals, and community health centers in the Boston area) system who were older than 60 years (as of July 13, 2021) and had APOE genotype data available from the BioBank.
+Each patients' EHR record was then annotated by neurologists using a web-based annotation tool (UI Interface in Appendix A) as 1) Yes, i.e., patient has CI; 2) No i.e., Patient does not have CI; and 3) Neither i.e., sequence has no information on patient’s cognition.
+
+\paragraph{Preprocessing}
+\label{sec:Preprocessing} For each patient in our gold-standard dataset, we extracted unstructured clinician notes, identified matches to dementia-related keywords (listed in Table 1), and constructed 800 character sequences from the note text around each of these matches.
+Our cohort of 16,428 patients had 279,224 sequences in total.
 
 \begin{table*}[htbp]
-
-	{
-		\begin{tabular}{c|c|c}
+\floatconts
+  {tab:operatornames}%
+  {\caption{Keywords indicative of Cognitive Impairment}}%
+  {%
+\begin{tabular}{lcc}
     \toprule
-	    \textbf{Rank} & \textbf{Keyword} & \textbf{Match Count} \\
+    \bfseries Keyword & \bfseries Match Count \\
     \midrule
 
-		1 & \textbf{Memory} & 109218 \\ 
-		2 & \textbf{Cognition}  & 87655 \\ 
-		3 & \textbf{Dementia} & 51034 \\ 
-		4 & \textbf{Cerebral} &  45886 \\ 
-		5 & \textbf{Cerebrovascular} & 36370 \\ 
-		6 & \textbf{Cerebellar} & 26863 \\
-		7 & \textbf{Cognitive Impairment} & 20267 \\ 
-		8 & \textbf{Alzheimer} & 20581 \\ 
-		9 & \textbf{MOCA} & 9767 \\ 
-		10 & \textbf{Neurocognitive} & 7711 \\ 
-		11 & \textbf{MCI} & 3889 \\ 
-		12 & \textbf{Amnesia} & 3695 \\ 
-		13 & \textbf{AD} & 2673 \\ 
-		14 & \textbf{Lewy} & 2561 \\ 
-		15 & \textbf{MMSE} & 2134 \\ 
-		16 & \textbf{LBD} & 224 \\ 
-		17 & \textbf{Corticobasal} & 147 \\ 
-		18 & \textbf{Pick's} & 41 \\
+    \textbf{Memory} & \fseries 109218 \\ 
+    \textbf{Cognition}  & \fseries 87655 \\ 
+    \textbf{Dementia} & \fseries 51034 \\ 
+    \textbf{Cerebral} & \fseries 45886 \\ 
+    \textbf{Cerebrovascular} & \fseries 36370 \\ 
+    \textbf{Cerebellar} & \fseries 26863 \\
+    \textbf{Cognitive Impairment} & \fseries 20267 \\ 
+    \textbf{Alzheimer} & \fseries 20581 \\ 
+    \textbf{MOCA} & \fseries 9767 \\ 
+    \textbf{Neurocognitive} & \fseries 7711 \\ 
+    \textbf{MCI} & \fseries 3889 \\ 
+    \textbf{Amnesia} & \fseries 3695 \\ 
+    \textbf{AD} & \fseries 2673 \\ 
+    \textbf{Lewy} & \fseries 2561 \\ 
+    \textbf{MMSE} & \fseries 2134 \\ 
+    \textbf{LBD} & \fseries 224 \\ 
+    \textbf{Corticobasal} & \fseries 147 \\ 
+    \textbf{Pick's} & \fseries 41 \\
 
@@
 }
-	{\caption{Keywords indicative of Cognitive Impairment}}
-
 \end{table*}
 
-\section{Appendix B}
+\paragraph{Annotations}
+\label{sec:Annotations} We initially assigned 5,000 sequences diversified by keyword matches from 5,000 unique patients for neurologist labeling.
+As the manual annotation of 279,000+ sequences in not feasible, we devised a scheme to expedite annotations known as "always patterns".
+An always pattern is defined as a phrase or regex expression that in any context indicates the phrase will be labeled with a particular class (i.e.
+yes, no, or neither).
+If an always pattern is inputted, all other sequences have language that matches with the phrase will be automatically labeled accordingly.
+{List any other sequence assignment schemes}
+
+% The \textsf{jmlr} class loads the \textsf{amsmath} package, so
+% you can use any of the commands and environments defined there.
+% (See the \textsf{amsmath} documentation for further
+% details.\footnote{Either \texttt{texdoc amsmath} or
+% \url{http://www.ctan.org/pkg/amsmath}})
+
+% Unnumbered single-lined equations should be displayed using
+% \verb|\[| and \verb|\]|. For example:
+% \[E = m c^2\]
+% or you can use the \texttt{displaymath} environment:
+% \begin{displaymath}
+% E = m c^2
+% \end{displaymath}
+% Numbered single-line equations should be displayed using the
+% \texttt{equation} environment. For example:
+% \begin{equation}\label{eq:trigrule}
+% \cos^2\theta + \sin^2\theta \equiv 1
+% \end{equation}
+% This can be referenced using \verb|\label| and \verb|\equationref|.
+% For example, \equationref{eq:trigrule}.
+
+% Multi-lined numbered equations should be displayed using the
+% \texttt{align} environment.\footnote{For reasons why you 
+% shouldn't use the obsolete \texttt{eqnarray} environment, see
+% Lars Madsen, \emph{Avoid eqnarray!} TUGboat 33(1):21--25, 2012.} For example:
+% \begin{align}
+% f(x) &= x^2 + x\label{eq:f}\\
+% f'(x) &= 2x + 1\label{eq:df}
+% \end{align}
+% Unnumbered multi-lined equations can be displayed using the
+% \texttt{align*} environment. For example:
+% \begin{align*}
+% f(x) &= (x+1)(x-1)\\
+% &= x^2 - 1
+% \end{align*}
+% If you want to mix numbered with unnumbered lines use the
+% \texttt{align} environment and suppress unwanted line numbers with
+% \verb|\nonumber|. For example:
+% \begin{align}
+% y &= x^2 + 3x - 2x + 1\nonumber\\
+% &= x^2 + x + 1\label{eq:y}
+% \end{align}
+% An equation that is too long to fit on a single line can be
+% displayed using the \texttt{split} environment. 
+% Text can be embedded in an equation using \verb|\text| or
+% \verb|\intertext| (as used in \theoremref{thm:eigenpow}).
+% See the \textsf{amsmath} documentation for further details.
+
+% \subsection{Operator Names}
+% \label{sec:op}
+
+% Predefined operator names are listed in \tableref{tab:operatornames}.
+% For additional operators, either use \verb|\operatorname|,
+% for example $\operatorname{var}(X)$ or declare it with
+% \verb|\DeclareMathOperator|, for example
+% \begin{verbatim}
+% \DeclareMathOperator{\var}{var}
+% \end{verbatim}
+% and then use this new command. If you want limits that go above and
+% below the operator (like \verb|\sum|) use the starred versions
+% (\verb|\operatorname*| or \verb|\DeclareMathOperator*|).
+
+% \begin{table*}[htbp]
+% \floatconts
+%   {tab:operatornames}%
+%   {\caption{Predefined Operator Names (taken from 
+%   \textsf{amsmath} documentation)}}%
+%   {%
+% \begin{tabular}{rlrlrlrl}
+% \cs{arccos} & $\arccos$ &  \cs{deg} & $\deg$ &  \cs{lg} & $\lg$ &  \cs{projlim} & $\projlim$ \\
+% \cs{arcsin} & $\arcsin$ &  \cs{det} & $\det$ &  \cs{lim} & $\lim$ &  \cs{sec} & $\sec$ \\
+% \cs{arctan} & $\arctan$ &  \cs{dim} & $\dim$ &  \cs{liminf} & $\liminf$ &  \cs{sin} & $\sin$ \\
+% \cs{arg} & $\arg$ &  \cs{exp} & $\exp$ &  \cs{limsup} & $\limsup$ &  \cs{sinh} & $\sinh$ \\
+% \cs{cos} & $\cos$ &  \cs{gcd} & $\gcd$ &  \cs{ln} & $\ln$ &  \cs{sup} & $\sup$ \\
+% \cs{cosh} & $\cosh$ &  \cs{hom} & $\hom$ &  \cs{log} & $\log$ &  \cs{tan} & $\tan$ \\
+% \cs{cot} & $\cot$ &  \cs{inf} & $\inf$ &  \cs{max} & $\max$ &  \cs{tanh} & $\tanh$ \\
+% \cs{coth} & $\coth$ &  \cs{injlim} & $\injlim$ &  \cs{min} & $\min$ \\
+% \cs{csc} & $\csc$ &  \cs{ker} & $\ker$ &  \cs{Pr} & $\Pr$
+% \end{tabular}\par
+% \begin{tabular}{rlrl}
+% \cs{varlimsup} & $\varlimsup$ 
+% & \cs{varinjlim} & $\varinjlim$\\
+% \cs{varliminf} & $\varliminf$ 
+% & \cs{varprojlim} & $\varprojlim$
+% \end{tabular}
+% }
+% \end{table*}
+
+\section{Vectors and Sets}
+\label{sec:vec}
+
+Vectors should be typeset using \cs{vec}. For example $\vec{x}$.
+(The original version of \cs{vec} can also be accessed using
+\cs{orgvec}, for example $\orgvec{x}$.)
+The \textsf{jmlr} class also provides \cs{set} to typeset a
+set. For example $\set{S}$.
+
+\section{Floats}
+\label{sec:floats}
+
+Floats, such as figures, tables and algorithms, are moving
+objects and are supposed to float to the nearest convenient
+location. Please don't force them to go in a particular place. In
+general it's best to use the \texttt{htbp} specifier and don't
+put the figure or table in the middle of a paragraph (that is
+make sure there's a paragraph break above and below the float).
+Floats are supposed to have a little extra space above and below
+them to make them stand out from the rest of the text. This extra
+spacing is put in automatically and shouldn't need modifying.
+
+If your article will later be reprinted in the Challenges for
+Machine Learning, please be aware that the CiML books use a
+different paper size, so if you want to resize any images use a
+scale relative to the line width (\verb|\linewidth|), text width
+(\verb|\textwidth|) or text height (\verb|\textheight|).
+
+To ensure consistency, please \emph{don't} try changing the format of the caption by doing
+something like:
+\begin{verbatim}
+\caption{\textit{A Sample Caption.}}
+\end{verbatim}
+or
+\begin{verbatim}
+\caption{\em A Sample Caption.}
+\end{verbatim}
+You can, of course, change the font for individual words or 
+phrases, for example:
+\begin{verbatim}
+\caption{A Sample Caption With Some \emph{Emphasized Words}.}
+\end{verbatim}
+
+\subsection{Tables}
+\label{sec:tables}
+
+Tables should go in the \texttt{table} environment. Within this
+environment use \verb|\floatconts| (defined by \textsf{jmlr})
+to set the caption correctly and center the table contents.
+The location of the caption depends on the \verb|tablecaption|
+setting in the document class options.
+
+\begin{table}[htbp]
+ % The first argument is the label.
+ % The caption goes in the second argument, and the table contents
+ % go in the third argument.
+\floatconts
+  {tab:example}%
+  {\caption{An Example Table}}%
+  {\begin{tabular}{ll}
+  \bfseries Dataset & \bfseries Result\\
+  Data1 & 0.12345\\
+  Data2 & 0.67890\\
+  Data3 & 0.54321\\
+  Data4 & 0.09876
+  \end{tabular}}
+\end{table}
+
+If you want horizontal rules you can use the \textsf{booktabs}
+package which provides the commands \verb|\toprule|, 
+\verb|\midrule| and \verb|\bottomrule|. For example, see
+\tableref{tab:example-booktabs}.
+
+\begin{table}[hbtp]
+\floatconts
+  {tab:example-booktabs}
+  {\caption{A Table With Horizontal Lines}}
+  {\begin{tabular}{ll}
+  \toprule
+  \bfseries Dataset & \bfseries Result\\
+  \midrule
+  Data1 & 0.12345\\
+  Data2 & 0.67890\\
+  Data3 & 0.54321\\
+  Data4 & 0.09876\\
+  \bottomrule
+  \end{tabular}}
+\end{table}
+
+If you really want vertical lines as well, you can't use the
+\textsf{booktabs} commands as there'll be some unwanted gaps.
+Instead you can use \LaTeX's \verb|\hline|, but the rows may
+appear a bit cramped.  You can add extra space above or below a
+row using \verb|\abovestrut| and \verb|\belowstrut|. For example,
+see \tableref{tab:example-hline}. However, you might want to read
+the \textsf{booktabs} documentation regarding the use of vertical
+lines.
+
+\begin{table}[htbp]
+\floatconts
+  {tab:example-hline}
+  {\caption{A Table With Horizontal and Vertical Lines}}%
+  {%
+    \begin{tabular}{|l|l|}
+    \hline
+    \abovestrut{2.2ex}\bfseries Dataset & \bfseries Result\\\hline
+    \abovestrut{2.2ex}Data1 & 0.12345\\
+    Data2 & 0.67890\\
+    Data3 & 0.54321\\
+    \belowstrut{0.2ex}Data4 & 0.09876\\\hline
+    \end{tabular}
+  }
+\end{table}
+
+If you want to align numbers on their decimal point, you can
+use the \textsf{siunitx} package. For example, see
+\tableref{tab:example-siunitx}. For further details see the
+\textsf{siunitx} documentation\footnote{Either \texttt{texdoc
+siunitx} or \url{http://www.ctan.org/pkg/siunitx}}.
+
+\begin{table}[htbp]
+\floatconts
+  {tab:example-siunitx}
+  {\caption{A Table With Numbers Aligned on the Decimal Point}}
+  {\begin{tabular}{lS[tabformat=3.5]}
+  \bfseries Dataset & {\bfseries Result}\\
+  Data1 & 0.12345\\
+  Data2 & 10.6789\\
+  Data3 & 50.543\\
+  Data4 & 200.09876
+  \end{tabular}}
+\end{table}
+
+If the table is too wide, you can adjust the inter-column
+spacing by changing the value of \verb|\tabcolsep|. For
+example:
+\begin{verbatim}
+\setlength{\tabcolsep}{3pt}
+\end{verbatim}
+If the table is very wide but not very long, you can use the
+\texttt{sidewaystable} environment defined in the
+\textsf{rotating} package (so use \verb|\usepackage{rotating}|).
+If the table is too long to fit on a page, you can use the
+\texttt{longtable} environment defined in the \textsf{longtable}
+package (so use \verb|\usepackage{longtable}|).
+
+\subsection{Figures}
+\label{sec:figures}
+
+Figures should go in the \texttt{figure} environment. Within this
+environment, use \verb|\floatconts| to correctly position the
+caption and center the image. Use \verb|\includegraphics|
+for external graphics files but omit the file extension. Do not
+use \verb|\epsfig| or \verb|\psfig|. If you want to scale the
+image, it's better to use a fraction of the line width rather
+than an explicit length. For example, see \figureref{fig:nodes}.
+
+\begin{figure}[htbp]
+ % Caption and label go in the first argument and the figure contents
+ % go in the second argument
+\floatconts
+  {fig:nodes}
+  {\caption{Example Image}}
+  {\includegraphics[width=0.5\linewidth]{images/nodes}}
+\end{figure}
+
+If your image is made up of \LaTeX\ code (for example, commands
+provided by the \textsf{pgf} package) you can include it using
+\cs{includeteximage} (defined by the \textsf{jmlr} class). This
+can be scaled and rotated in the same way as \cs{includegraphics}.
+For example, see \figureref{fig:teximage}.
+
+\begin{figure}[htbp]
+\floatconts
+  {fig:teximage}
+  {\caption{Image Created Using \LaTeX\ Code}}
+  {\includeteximage[angle=45]{images/teximage}}
+\end{figure}
+
+If the figure is too wide to fit on the page, you can use the
+\texttt{sidewaysfigure} environment defined in the
+\textsf{rotating} package.
+
+Don't use \verb|\graphicspath|.\footnote{This is specific to the
+\textsf{jmlr} class, not a general recommendation. The main file
+that generates the proceedings or the CiML book is typically in a
+different directory to the imported articles, so it modifies the
+graphics path when it imports an article.} If the images 
+are contained in a subdirectory, specify this when you include the image, for
+example \verb|\includegraphics{figures/mypic}|.
+
+\subsubsection{Sub-Figures}
+\label{sec:subfigures}
+
+Sub-figures can be created using \verb|\subfigure|, which is
+defined by the \textsf{jmlr} class. The optional argument allows
+you to provide a subcaption. The label should be placed in the
+mandatory argument of \verb|\subfigure|. You can reference the
+entire figure, for example \figureref{fig:subfigex}, or you can
+reference part of the figure using \verb|\figureref|, for example
+\figureref{fig:circle}. Alternatively you can reference the
+subfigure using \verb|\subfigref|, for example
+\subfigref{fig:circle,fig:square} in \figureref{fig:subfigex}.
+
+\begin{figure}[htbp]
+\floatconts
+  {fig:subfigex}
+  {\caption{An Example With Sub-Figures.}}
+  {%
+    \subfigure[A Circle]{\label{fig:circle}%
+      \includegraphics[width=0.2\linewidth]{images/circle}}%
+    \qquad
+    \subfigure[A Square]{\label{fig:square}%
+      \includegraphics[width=0.2\linewidth]{images/square}}
+  }
+\end{figure}
+
+By default, the sub-figures are aligned on the baseline.
+This can be changed using the second optional argument
+of \verb|\subfigure|. This may be \texttt{t} (top), \texttt{c}
+(centered) or \texttt{b} (bottom). For example, the subfigures
+\subfigref{fig:circle2,fig:square2} in \figureref{fig:subfigex2}
+both have \verb|[c]| as the second optional argument.
+
+\begin{figure}[htbp]
+\floatconts
+  {fig:subfigex2}
+  {\caption{Another Example With Sub-Figures.}}
+  {%
+    \subfigure[A Small Circle][c]{\label{fig:circle2}%
+      \includegraphics[width=0.1\linewidth]{images/circle}}%
+    \qquad
+    \subfigure[A Square][c]{\label{fig:square2}%
+      \includegraphics[width=0.2\linewidth]{images/square}}
+  }
+\end{figure}
+
+\subsection{Sub-Tables}
+\label{sec:subtables}
+There is an analogous command \verb|\subtable| for sub-tables.
+It has the same syntax as \verb|\subfigure| described above.
+You can reference the table using \verb|\tableref|, for example
+\tableref{tab:subtabex} or you can reference part of the table,
+for example \tableref{tab:ab}. Alternatively you can reference the
+subtable using \verb|\subtabref|, for example
+\subtabref{tab:ab,tab:cd} in \tableref{tab:subtabex}.
+
+\begin{table}[htbp]
+\floatconts
+ {tab:subtabex}
+ {\caption{An Example With Sub-Tables}}
+ {%
+   \subtable{%
+     \label{tab:ab}%
+     \begin{tabular}{cc}
+     \bfseries A & \bfseries B\\
+     1 & 2
+     \end{tabular}
+   }\qquad
+   \subtable{%
+     \label{tab:cd}%
+     \begin{tabular}{cc}
+     \bfseries C & \bfseries D\\
+     3 & 4\\
+     5 & 6
+     \end{tabular}
+   }
+ }
+\end{table}
+
+By default, the sub-tables are aligned on the top.
+This can be changed using the second optional argument
+of \verb|\subtable|. This may be \texttt{t} (top), \texttt{c}
+(centered) or \texttt{b} (bottom). For example, the sub-tables
+\subtabref{tab:ab2,tab:cd2} in \tableref{tab:subtabex2}
+both have \verb|[c]| as the second optional argument.
+
+\begin{table}[htbp]
+\floatconts
+ {tab:subtabex2}
+ {\caption{Another Example With Sub-Tables}}
+ {%
+   \subtable[][c]{%
+     \label{tab:ab2}%
+     \begin{tabular}{cc}
+     \bfseries A & \bfseries B\\
+     1 & 2
+     \end{tabular}
+   }\qquad
+   \subtable[][c]{%
+     \label{tab:cd2}%
+     \begin{tabular}{cc}
+     \bfseries C & \bfseries D\\
+     3 & 4\\
+     5 & 6
+     \end{tabular}
+   }
+ }
+\end{table}
+
+\subsection{Algorithms}
+\label{sec:algorithms}
+
+Enumerated textual algorithms can be displayed using the
+\texttt{algorithm} environment. Within this environment, use
+\verb|\caption| to set the caption and you can use an
+\texttt{enumerate} or nested \texttt{enumerate} environments.
+For example, see \algorithmref{alg:gauss}. Note that algorithms
+float like figures and tables.
+
+\begin{algorithm}[htbp]
+\floatconts
+  {alg:gauss}%
+  {\caption{The Gauss-Seidel Algorithm}}%
+{%
+\begin{enumerate}
+  \item For $k=1$ to maximum number of iterations
+    \begin{enumerate}
+      \item For $i=1$ to $n$
+        \begin{enumerate}
+        \item $x_i^{(k)} = 
+          \frac{b_i - \sum_{j=1}^{i-1}a_{ij}x_j^{(k)}
+          - \sum_{j=i+1}^{n}a_{ij}x_j^{(k-1)}}{a_{ii}}$
+        \item If $\|\vec{x}^{(k)}-\vec{x}^{(k-1)} < \epsilon\|$,
+          where $\epsilon$ is a specified stopping criteria, stop.
+      \end{enumerate}
+    \end{enumerate}
+\end{enumerate}
+}%
+\end{algorithm}
+
+If you'd rather have the same numbering throughout the algorithm
+but still want the convenient indentation of nested 
+\texttt{enumerate} environments, you can use the
+\texttt{enumerate*} environment provided by the \textsf{jmlr}
+class. For example, see \algorithmref{alg:moore}.
+
+\begin{algorithm}
+\floatconts
+  {alg:moore}%
+  {\caption{Moore's Shortest Path}}%
+{%
+Given a connected graph $G$, where the length of each edge is 1:
+\begin{enumerate*}
+  \item Set the label of vertex $s$ to 0
+  \item Set $i=0$
+  \begin{enumerate*}
+    \item \label{step:locate}Locate all unlabelled vertices 
+          adjacent to a vertex labelled $i$ and label them $i+1$
+    \item If vertex $t$ has been labelled,
+    \begin{enumerate*}
+      \item[] the shortest path can be found by backtracking, and 
+      the length is given by the label of $t$.
+    \end{enumerate*}
+    otherwise
+    \begin{enumerate*}
+      \item[] increment $i$ and return to step~\ref{step:locate}
+    \end{enumerate*}
+  \end{enumerate*}
+\end{enumerate*}
+}%
+\end{algorithm}
+
+Pseudo code can be displayed using the \texttt{algorithm2e}
+environment. This is defined by the \textsf{algorithm2e} package
+(which is automatically loaded) so check the \textsf{algorithm2e}
+documentation for further details.\footnote{Either \texttt{texdoc
+algorithm2e} or \url{http://www.ctan.org/pkg/algorithm2e}}
+For an example, see \algorithmref{alg:net}.
+
+\begin{algorithm2e}
+\caption{Computing Net Activation}
+\label{alg:net}
+ % older versions of algorithm2e have \dontprintsemicolon instead
+ % of the following:
+ %\DontPrintSemicolon
+ % older versions of algorithm2e have \linesnumbered instead of the
+ % following:
+ %\LinesNumbered
+\KwIn{$x_1, \ldots, x_n, w_1, \ldots, w_n$}
+\KwOut{$y$, the net activation}
+$y\leftarrow 0$\;
+\For{$i\leftarrow 1$ \KwTo $n$}{
+  $y \leftarrow y + w_i*x_i$\;
+}
+\end{algorithm2e}
+
+\section{Description Lists}
+
+The \textsf{jmlr} class also provides a description-like 
+environment called \texttt{altdescription}. This has an
+argument that should be the widest label in the list. Compare:
+\begin{description}
+\item[add] A method that adds two variables.
+\item[differentiate] A method that differentiates a function.
+\end{description}
+with
+\begin{altdescription}{differentiate}
+\item[add] A method that adds two variables.
+\item[differentiate] A method that differentiates a function.
+\end{altdescription}
+
+\section{Theorems, Lemmas etc}
+\label{sec:theorems}
+
+The following theorem-like environments are predefined by
+the \textsf{jmlr} class: \texttt{theorem}, \texttt{example},
+\texttt{lemma}, \texttt{proposition}, \texttt{remark}, 
+\texttt{corollary}, \texttt{definition}, \texttt{conjecture}
+and \texttt{axiom}. You can use the \texttt{proof} environment
+to display the proof if need be, as in \theoremref{thm:eigenpow}.
+
+\begin{theorem}[Eigenvalue Powers]\label{thm:eigenpow}
+If $\lambda$ is an eigenvalue of $\vec{B}$ with eigenvector
+$\vec{\xi}$, then $\lambda^n$ is an eigenvalue of $\vec{B}^n$
+with eigenvector $\vec{\xi}$.
+\begin{proof}
+Let $\lambda$ be an eigenvalue of $\vec{B}$ with eigenvector
+$\xi$, then
+\begin{align*}
+\vec{B}\vec{\xi} &= \lambda\vec{\xi}
+\intertext{premultiply by $\vec{B}$:}
+\vec{B}\vec{B}\vec{\xi} &= \vec{B}\lambda\vec{\xi}\\
+\Rightarrow \vec{B}^2\vec{\xi} &= \lambda\vec{B}\vec{\xi}\\
+&= \lambda\lambda\vec{\xi}\qquad
+\text{since }\vec{B}\vec{\xi}=\lambda\vec{\xi}\\
+&= \lambda^2\vec{\xi}
+\end{align*}
+Therefore true for $n=2$. Now assume true for $n=k$:
+\begin{align*}
+\vec{B}^k\vec{\xi} &= \lambda^k\vec{\xi}
+\intertext{premultiply by $\vec{B}$:}
+\vec{B}\vec{B}^k\vec{\xi} &= \vec{B}\lambda^k\vec{\xi}\\
+\Rightarrow \vec{B}^{k+1}\vec{\xi} &= \lambda^k\vec{B}\vec{\xi}\\
+&= \lambda^k\lambda\vec{\xi}\qquad
+\text{since }\vec{B}\vec{\xi}=\lambda\vec{\xi}\\
+&= \lambda^{k+1}\vec{\xi}
+\end{align*}
+Therefore true for $n=k+1$. Therefore, by induction, true for all
+$n$.
+\end{proof}
+\end{theorem}
+
+\begin{lemma}[A Sample Lemma]\label{lem:sample}
+This is a lemma.
+\end{lemma}
+
+\begin{remark}[A Sample Remark]\label{rem:sample}
+This is a remark.
+\end{remark}
+
+\begin{corollary}[A Sample Corollary]\label{cor:sample}
+This is a corollary.
+\end{corollary}
+
+\begin{definition}[A Sample Definition]\label{def:sample}
+This is a definition.
+\end{definition}
+
+\begin{conjecture}[A Sample Conjecture]\label{con:sample}
+This is a conjecture.
+\end{conjecture}
+
+\begin{axiom}[A Sample Axiom]\label{ax:sample}
+This is an axiom.
+\end{axiom}
+
+\begin{example}[An Example]\label{ex:sample}
+This is an example.
+\end{example}
+
+\section{Color vs Grayscale}
+\label{sec:color}
+
+It's helpful if authors supply grayscale versions of their
+images in the event that the article is to be incorporated into
+a black and white printed book. With external PDF, PNG or JPG
+graphic files, you just need to supply a grayscale version of the
+file. For example, if the file is called \texttt{myimage.png},
+then the gray version should be \texttt{myimage-gray.png} or
+\texttt{myimage-gray.pdf} or \texttt{myimage-gray.jpg}. You don't
+need to modify your code. The \textsf{jmlr} class checks for
+the existence of the grayscale version if it is print mode 
+(provided you have used \verb|\includegraphics| and haven't
+specified the file extension).
+
+You can use \verb|\ifprint| to determine which mode you are in.
+For example, in \figureref{fig:nodes}, the 
+\ifprint{dark gray}{purple} ellipse represents an input and the
+\ifprint{light gray}{yellow} ellipse represents an output.
+Another example: {\ifprint{\bfseries}{\color{red}}important text!}
+
+You can use the class option \texttt{gray} to see how the
+document will appear in gray scale mode. \textcolor{blue}{Colored
+text} will automatically be converted to gray scale in print mode.
+
+The \textsf{jmlr} class loads the \textsf{xcolor}
+package, so you can also define your own colors. For example:
+\ifprint
+  {\definecolor{myred}{gray}{0.5}}%
+  {\definecolor{myred}{rgb}{0.5,0,0}}%
+\textcolor{myred}{XYZ}.
+
+The \textsf{xcolor} class is loaded with the \texttt{x11names}
+option, so you can use any of the x11 predefined colors (listed
+in the \textsf{xcolor} documentation\footnote{either 
+\texttt{texdoc xcolor} or \url{http://www.ctan.org/pkg/xcolor}}).
+
+\section{Citations and Bibliography}
+\label{sec:cite}
+
+The \textsf{jmlr} class automatically loads \textsf{natbib}
+and automatically sets the bibliography style, so you don't need to
+use \verb|\bibliographystyle|.
+This sample file has the citations defined in the accompanying
+BibTeX file \texttt{jmlr-sample.bib}. For a parenthetical
+citation use \verb|\citep|. For example
+\citep{guyon-elisseeff-03}. For a textual citation use
+\verb|\citet|. For example \citet{guyon2007causalreport}. 
+Both commands may take a comma-separated list, for example
+\citet{guyon-elisseeff-03,guyon2007causalreport}.
+
+These commands have optional arguments and have a starred
+version. See the \textsf{natbib} documentation for further
+details.\footnote{Either \texttt{texdoc natbib} or
+\url{http://www.ctan.org/pkg/natbib}}
+
+The bibliography is displayed using \verb|\bibliography|.
+
+\acks{Acknowledgements go here.}
+
+\bibliography{jmlr-sample}
+
+\appendix
+
+\section{First Appendix}\label{apd:first}
+
+This is the first appendix.
+
+\section{Second Appendix}\label{apd:second}
+
+This is the second appendix.
 

### 2021-08-18 Submission/Paper/ML4H/Paper.tex
section 3 draft

@@
 If an always pattern is inputted, all other sequences have language that matches with the phrase will be automatically labeled accordingly.
-{List any other sequence assignment schemes}
+% {List any other sequence assignment schemes} %
+Currently, 8,656 sequences have been annotated, 8,050 through always patterns and 606 manually. % {Will change} %
 
-% The \textsf{jmlr} class loads the \textsf{amsmath} package, so
-% you can use any of the commands and environments defined there.
-% (See the \textsf{amsmath} documentation for further
-% details.\footnote{Either \texttt{texdoc amsmath} or
-% \url{http://www.ctan.org/pkg/amsmath}})
+The final dataset was split between train (95\%) and holdout test (5\%) sets, stratified across label and proportion of sequences annotated manually and through always patterns. % {Will change} % 
+Validation datsets were split from the train set using techniques described in the Methodology section. Table 2 shows demographics of the cohort of patients.
 
-% Unnumbered single-lined equations should be displayed using
-% \verb|\[| and \verb|\]|. For example:
-% \[E = m c^2\]
-% or you can use the \texttt{displaymath} environment:
-% \begin{displaymath}
-% E = m c^2
-% \end{displaymath}
-% Numbered single-line equations should be displayed using the
-% \texttt{equation} environment. For example:
-% \begin{equation}\label{eq:trigrule}
-% \cos^2\theta + \sin^2\theta \equiv 1
-% \end{equation}
-% This can be referenced using \verb|\label| and \verb|\equationref|.
-% For example, \equationref{eq:trigrule}.
+\section{Methodology}
+\label{sec:Methodology}
 
-% Multi-lined numbered equations should be displayed using the
-% \texttt{align} environment.\footnote{For reasons why you 
-% shouldn't use the obsolete \texttt{eqnarray} environment, see
-% Lars Madsen, \emph{Avoid eqnarray!} TUGboat 33(1):21--25, 2012.} For example:
-% \begin{align}
-% f(x) &= x^2 + x\label{eq:f}\\
-% f'(x) &= 2x + 1\label{eq:df}
-% \end{align}
-% Unnumbered multi-lined equations can be displayed using the
-% \texttt{align*} environment. For example:
-% \begin{align*}
-% f(x) &= (x+1)(x-1)\\
-% &= x^2 - 1
-% \end{align*}
-% If you want to mix numbered with unnumbered lines use the
-% \texttt{align} environment and suppress unwanted line numbers with
-% \verb|\nonumber|. For example:
-% \begin{align}
-% y &= x^2 + 3x - 2x + 1\nonumber\\
-% &= x^2 + x + 1\label{eq:y}
-% \end{align}
-% An equation that is too long to fit on a single line can be
-% displayed using the \texttt{split} environment. 
-% Text can be embedded in an equation using \verb|\text| or
-% \verb|\intertext| (as used in \theoremref{thm:eigenpow}).
-% See the \textsf{amsmath} documentation for further details.
+We built x models and compared performance to baseline model.
 
-% \subsection{Operator Names}
-% \label{sec:op}
+\paragraph{(1) Structured Features Model}
 
-% Predefined operator names are listed in \tableref{tab:operatornames}.
-% For additional operators, either use \verb|\operatorname|,
-% for example $\operatorname{var}(X)$ or declare it with
-% \verb|\DeclareMathOperator|, for example
-% \begin{verbatim}
-% \DeclareMathOperator{\var}{var}
-% \end{verbatim}
-% and then use this new command. If you want limits that go above and
-% below the operator (like \verb|\sum|) use the starred versions
-% (\verb|\operatorname*| or \verb|\DeclareMathOperator*|).
+\paragraph{(2) Logistic Regression with TF-IDF Vectors}
 
-% \begin{table*}[htbp]
-% \floatconts
-%   {tab:operatornames}%
-%   {\caption{Predefined Operator Names (taken from 
-%   \textsf{amsmath} documentation)}}%
-%   {%
-% \begin{tabular}{rlrlrlrl}
-% \cs{arccos} & $\arccos$ &  \cs{deg} & $\deg$ &  \cs{lg} & $\lg$ &  \cs{projlim} & $\projlim$ \\
-% \cs{arcsin} & $\arcsin$ &  \cs{det} & $\det$ &  \cs{lim} & $\lim$ &  \cs{sec} & $\sec$ \\
-% \cs{arctan} & $\arctan$ &  \cs{dim} & $\dim$ &  \cs{liminf} & $\liminf$ &  \cs{sin} & $\sin$ \\
-% \cs{arg} & $\arg$ &  \cs{exp} & $\exp$ &  \cs{limsup} & $\limsup$ &  \cs{sinh} & $\sinh$ \\
-% \cs{cos} & $\cos$ &  \cs{gcd} & $\gcd$ &  \cs{ln} & $\ln$ &  \cs{sup} & $\sup$ \\
-% \cs{cosh} & $\cosh$ &  \cs{hom} & $\hom$ &  \cs{log} & $\log$ &  \cs{tan} & $\tan$ \\
-% \cs{cot} & $\cot$ &  \cs{inf} & $\inf$ &  \cs{max} & $\max$ &  \cs{tanh} & $\tanh$ \\
-% \cs{coth} & $\coth$ &  \cs{injlim} & $\injlim$ &  \cs{min} & $\min$ \\
-% \cs{csc} & $\csc$ &  \cs{ker} & $\ker$ &  \cs{Pr} & $\Pr$
-% \end{tabular}\par
-% \begin{tabular}{rlrl}
-% \cs{varlimsup} & $\varlimsup$ 
-% & \cs{varinjlim} & $\varinjlim$\\
-% \cs{varliminf} & $\varliminf$ 
-% & \cs{varprojlim} & $\varprojlim$
-% \end{tabular}
-% }
-% \end{table*}
+\paragraph{(3) Model 1 + Model 2}
 
-\section{Vectors and Sets}
-\label{sec:vec}
-
-Vectors should be typeset using \cs{vec}. For example $\vec{x}$.
-(The original version of \cs{vec} can also be accessed using
-\cs{orgvec}, for example $\orgvec{x}$.)
-The \textsf{jmlr} class also provides \cs{set} to typeset a
-set. For example $\set{S}$.
-
-\section{Floats}
-\label{sec:floats}
-
-Floats, such as figures, tables and algorithms, are moving
-objects and are supposed to float to the nearest convenient
-location. Please don't force them to go in a particular place. In
-general it's best to use the \texttt{htbp} specifier and don't
-put the figure or table in the middle of a paragraph (that is
-make sure there's a paragraph break above and below the float).
-Floats are supposed to have a little extra space above and below
-them to make them stand out from the rest of the text. This extra
-spacing is put in automatically and shouldn't need modifying.
-
-If your article will later be reprinted in the Challenges for
-Machine Learning, please be aware that the CiML books use a
-different paper size, so if you want to resize any images use a
-scale relative to the line width (\verb|\linewidth|), text width
-(\verb|\textwidth|) or text height (\verb|\textheight|).
-
-To ensure consistency, please \emph{don't} try changing the format of the caption by doing
-something like:
-\begin{verbatim}
-\caption{\textit{A Sample Caption.}}
-\end{verbatim}
-or
-\begin{verbatim}
-\caption{\em A Sample Caption.}
-\end{verbatim}
-You can, of course, change the font for individual words or 
-phrases, for example:
-\begin{verbatim}
-\caption{A Sample Caption With Some \emph{Emphasized Words}.}
-\end{verbatim}
-
-\subsection{Tables}
-\label{sec:tables}
-
-Tables should go in the \texttt{table} environment. Within this
-environment use \verb|\floatconts| (defined by \textsf{jmlr})
-to set the caption correctly and center the table contents.
-The location of the caption depends on the \verb|tablecaption|
-setting in the document class options.
-
-\begin{table}[htbp]
- % The first argument is the label.
- % The caption goes in the second argument, and the table contents
- % go in the third argument.
-\floatconts
-  {tab:example}%
-  {\caption{An Example Table}}%
-  {\begin{tabular}{ll}
-  \bfseries Dataset & \bfseries Result\\
-  Data1 & 0.12345\\
-  Data2 & 0.67890\\
-  Data3 & 0.54321\\
-  Data4 & 0.09876
-  \end{tabular}}
-\end{table}
-
-If you want horizontal rules you can use the \textsf{booktabs}
-package which provides the commands \verb|\toprule|, 
-\verb|\midrule| and \verb|\bottomrule|. For example, see
-\tableref{tab:example-booktabs}.
-
-\begin{table}[hbtp]
-\floatconts
-  {tab:example-booktabs}
-  {\caption{A Table With Horizontal Lines}}
-  {\begin{tabular}{ll}
-  \toprule
-  \bfseries Dataset & \bfseries Result\\
-  \midrule
-  Data1 & 0.12345\\
-  Data2 & 0.67890\\
-  Data3 & 0.54321\\
-  Data4 & 0.09876\\
-  \bottomrule
-  \end{tabular}}
-\end{table}
-
-If you really want vertical lines as well, you can't use the
-\textsf{booktabs} commands as there'll be some unwanted gaps.
-Instead you can use \LaTeX's \verb|\hline|, but the rows may
-appear a bit cramped.  You can add extra space above or below a
-row using \verb|\abovestrut| and \verb|\belowstrut|. For example,
-see \tableref{tab:example-hline}. However, you might want to read
-the \textsf{booktabs} documentation regarding the use of vertical
-lines.
-
-\begin{table}[htbp]
-\floatconts
-  {tab:example-hline}
-  {\caption{A Table With Horizontal and Vertical Lines}}%
-  {%
-    \begin{tabular}{|l|l|}
-    \hline
-    \abovestrut{2.2ex}\bfseries Dataset & \bfseries Result\\\hline
-    \abovestrut{2.2ex}Data1 & 0.12345\\
-    Data2 & 0.67890\\
-    Data3 & 0.54321\\
-    \belowstrut{0.2ex}Data4 & 0.09876\\\hline
-    \end{tabular}
-  }
-\end{table}
-
-If you want to align numbers on their decimal point, you can
-use the \textsf{siunitx} package. For example, see
-\tableref{tab:example-siunitx}. For further details see the
-\textsf{siunitx} documentation\footnote{Either \texttt{texdoc
-siunitx} or \url{http://www.ctan.org/pkg/siunitx}}.
-
-\begin{table}[htbp]
-\floatconts
-  {tab:example-siunitx}
-  {\caption{A Table With Numbers Aligned on the Decimal Point}}
-  {\begin{tabular}{lS[tabformat=3.5]}
-  \bfseries Dataset & {\bfseries Result}\\
-  Data1 & 0.12345\\
-  Data2 & 10.6789\\
-  Data3 & 50.543\\
-  Data4 & 200.09876
-  \end{tabular}}
-\end{table}
-
-If the table is too wide, you can adjust the inter-column
-spacing by changing the value of \verb|\tabcolsep|. For
-example:
-\begin{verbatim}
-\setlength{\tabcolsep}{3pt}
-\end{verbatim}
-If the table is very wide but not very long, you can use the
-\texttt{sidewaystable} environment defined in the
-\textsf{rotating} package (so use \verb|\usepackage{rotating}|).
-If the table is too long to fit on a page, you can use the
-\texttt{longtable} environment defined in the \textsf{longtable}
-package (so use \verb|\usepackage{longtable}|).
-
-\subsection{Figures}
-\label{sec:figures}
-
-Figures should go in the \texttt{figure} environment. Within this
-environment, use \verb|\floatconts| to correctly position the
-caption and center the image. Use \verb|\includegraphics|
-for external graphics files but omit the file extension. Do not
-use \verb|\epsfig| or \verb|\psfig|. If you want to scale the
-image, it's better to use a fraction of the line width rather
-than an explicit length. For example, see \figureref{fig:nodes}.
-
-\begin{figure}[htbp]
- % Caption and label go in the first argument and the figure contents
- % go in the second argument
-\floatconts
-  {fig:nodes}
-  {\caption{Example Image}}
-  {\includegraphics[width=0.5\linewidth]{images/nodes}}
-\end{figure}
-
-If your image is made up of \LaTeX\ code (for example, commands
-provided by the \textsf{pgf} package) you can include it using
-\cs{includeteximage} (defined by the \textsf{jmlr} class). This
-can be scaled and rotated in the same way as \cs{includegraphics}.
-For example, see \figureref{fig:teximage}.
-
-\begin{figure}[htbp]
-\floatconts
-  {fig:teximage}
-  {\caption{Image Created Using \LaTeX\ Code}}
-  {\includeteximage[angle=45]{images/teximage}}
-\end{figure}
-
-If the figure is too wide to fit on the page, you can use the
-\texttt{sidewaysfigure} environment defined in the
-\textsf{rotating} package.
-
-Don't use \verb|\graphicspath|.\footnote{This is specific to the
-\textsf{jmlr} class, not a general recommendation. The main file
-that generates the proceedings or the CiML book is typically in a
-different directory to the imported articles, so it modifies the
-graphics path when it imports an article.} If the images 
-are contained in a subdirectory, specify this when you include the image, for
-example \verb|\includegraphics{figures/mypic}|.
-
-\subsubsection{Sub-Figures}
-\label{sec:subfigures}
-
-Sub-figures can be created using \verb|\subfigure|, which is
-defined by the \textsf{jmlr} class. The optional argument allows
-you to provide a subcaption. The label should be placed in the
-mandatory argument of \verb|\subfigure|. You can reference the
-entire figure, for example \figureref{fig:subfigex}, or you can
-reference part of the figure using \verb|\figureref|, for example
-\figureref{fig:circle}. Alternatively you can reference the
-subfigure using \verb|\subfigref|, for example
-\subfigref{fig:circle,fig:square} in \figureref{fig:subfigex}.
-
-\begin{figure}[htbp]
-\floatconts
-  {fig:subfigex}
-  {\caption{An Example With Sub-Figures.}}
-  {%
-    \subfigure[A Circle]{\label{fig:circle}%
-      \includegraphics[width=0.2\linewidth]{images/circle}}%
-    \qquad
-    \subfigure[A Square]{\label{fig:square}%
-      \includegraphics[width=0.2\linewidth]{images/square}}
-  }
-\end{figure}
-
-By default, the sub-figures are aligned on the baseline.
-This can be changed using the second optional argument
-of \verb|\subfigure|. This may be \texttt{t} (top), \texttt{c}
-(centered) or \texttt{b} (bottom). For example, the subfigures
-\subfigref{fig:circle2,fig:square2} in \figureref{fig:subfigex2}
-both have \verb|[c]| as the second optional argument.
-
-\begin{figure}[htbp]
-\floatconts
-  {fig:subfigex2}
-  {\caption{Another Example With Sub-Figures.}}
-  {%
-    \subfigure[A Small Circle][c]{\label{fig:circle2}%
-      \includegraphics[width=0.1\linewidth]{images/circle}}%
-    \qquad
-    \subfigure[A Square][c]{\label{fig:square2}%
-      \includegraphics[width=0.2\linewidth]{images/square}}
-  }
-\end{figure}
-
-\subsection{Sub-Tables}
-\label{sec:subtables}
-There is an analogous command \verb|\subtable| for sub-tables.
-It has the same syntax as \verb|\subfigure| described above.
-You can reference the table using \verb|\tableref|, for example
-\tableref{tab:subtabex} or you can reference part of the table,
-for example \tableref{tab:ab}. Alternatively you can reference the
-subtable using \verb|\subtabref|, for example
-\subtabref{tab:ab,tab:cd} in \tableref{tab:subtabex}.
-
-\begin{table}[htbp]
-\floatconts
- {tab:subtabex}
- {\caption{An Example With Sub-Tables}}
- {%
-   \subtable{%
-     \label{tab:ab}%
-     \begin{tabular}{cc}
-     \bfseries A & \bfseries B\\
-     1 & 2
-     \end{tabular}
-   }\qquad
-   \subtable{%
-     \label{tab:cd}%
-     \begin{tabular}{cc}
-     \bfseries C & \bfseries D\\
-     3 & 4\\
-     5 & 6
-     \end{tabular}
-   }
- }
-\end{table}
-
-By default, the sub-tables are aligned on the top.
-This can be changed using the second optional argument
-of \verb|\subtable|. This may be \texttt{t} (top), \texttt{c}
-(centered) or \texttt{b} (bottom). For example, the sub-tables
-\subtabref{tab:ab2,tab:cd2} in \tableref{tab:subtabex2}
-both have \verb|[c]| as the second optional argument.
-
-\begin{table}[htbp]
-\floatconts
- {tab:subtabex2}
- {\caption{Another Example With Sub-Tables}}
- {%
-   \subtable[][c]{%
-     \label{tab:ab2}%
-     \begin{tabular}{cc}
-     \bfseries A & \bfseries B\\
-     1 & 2
-     \end{tabular}
-   }\qquad
-   \subtable[][c]{%
-     \label{tab:cd2}%
-     \begin{tabular}{cc}
-     \bfseries C & \bfseries D\\
-     3 & 4\\
-     5 & 6
-     \end{tabular}
-   }
- }
-\end{table}
+\paragraph{(4) Transformer Based Sequence Classification Language Model}
 

### 2021-08-18 Submission/Paper/ML4H/Paper.tex
first 2 models drafted

--- 2021-07-27 Submission/Paper/ML4H/Paper.tex
@@
 
-% Authors
-\if0\blind {
-    \title {
-        \bf Title
-    }
+\maketitle
 
-    \author {
-        Author 1 \\
-        Department of YYY, University of XXX\\
-        and \\
-        Author 2 \\
-        Department of ZZZ, University of WWW
-    }
+\begin{abstract}
+\tab Dementia is a neurodegenerative disorder that causes cognitive decline and affects more than 50 million people worldwide.
+Dementia is under-diagnosed by healthcare professionals—only one in four people who suffer from dementia are diagnosed.
+Even when a diagnosis is made, it may not be entered as a structured diagnosis code in a patient’s charts.
+Information relevant to cognitive impairment is often found within electronic health records but manual review of clinician notes by experts is both time consuming and often prone to errors.
+Automated evaluation of these notes presents an opportunity to label patients with cognitive impairment (CI) in real-world data.
+\end{abstract}
+\begin{keywords}
+EHR, NLP, Demetia
+\end{keywords}
 
-    \maketitle
-} \fi
+\section{Introduction}
+\label{sec:intro}
 
-% TOC
-\newpage
-    \tableofcontents
-\newpage
+\section{Related Works}
+\label{sec:RelatedWorks}
 
-% Abstract
-\section{Abstract}
+\section{Dataset, Preprocessing, and Annotations}
 
-\input{sections/abstract}
+\paragraph{Dataset}
+\label{sec:Dataset} Our gold-standard dataset consisted of a cohort (N=16,428) of patients from the Mass General Brigham (MGB) HealthCare (formerly Partner's Healthcare, comprising two major academic hospitals, community hospitals, and community health centers in the Boston area) system who were older than 60 years (as of July 13, 2021) and had APOE genotype data available from the BioBank.
+Each patients' EHR record was then annotated by neurologists using a web-based annotation tool (UI Interface in Appendix A) as 1) Yes, i.e., patient has CI; 2) No i.e., Patient does not have CI; and 3) Neither i.e., sequence has no information on patient’s cognition.
 
-% Introduction
-\section{Introduction}
-	\subsection{Background}
-
-	\subsection{Related Work}
-
-% Methodology
-\section{Methodology}
-	\subsection{Acquisition of Data}
-	\tab Our gold-standard dataset consisted of 16K sampled patients with APOE gene <insert info about Biobank>.
-Each patient's EHR record was reviewed by an expert clinician (neurologist, psychiatrist, or geriatric psychiatrist) to annotate patients with presence, absence, or inconclusiveness of cognitive impairment.
-
-	\subsection{Preprocessing}
-	\tab We first created a list of keywords related to cognitive impairment (full list with frequency matches in Appendix A).
-For each patient in the BioBank data repository (mentioned above), we extracted all sequences containing any of the keywords.
-Several preprocessing steps were completed to increase the sequences to 800 characters minimum (more details in Appendix B) to allow for annotators to have more context when evaluating sequences.The preprocessed sequences were used as input for all models.
-
-	% \subsubsection{Obtaining Gold Standard Labels} Fair Header (where you would talk about SLAT)
-
-	\subsection{Machine Learning Models}
-		% \subsubsection{TFIDF Vectors} Fair Header
-
-	\subsection{Deep Learning Model}
-		% \subsubsection{BERT and Transformers} Fair Header
-
-% Results
-\section{Results}
-	\subsection{Model Results and Comparison}
-
-% Conclusion
-\section{Conclusion}
-
-% Future Work
-\section{Future Work}
-
-% References
-\section{References}
-
-\section{Appendix A}
+\paragraph{Preprocessing}
+\label{sec:Preprocessing} For each patient in our gold-standard dataset, we extracted unstructured clinician notes, identified matches to dementia-related keywords (listed in Table 1), and constructed 800 character sequences from the note text around each of these matches.
+Our cohort of 16,428 patients had 279,224 sequences in total.
 
 \begin{table*}[htbp]
-
+\floatconts
+  {tab:operatornames}
+  {\caption{Keywords indicative of Cognitive Impairment}}%
     {
-		\begin{tabular}{c|c|c}
+        \begin{tabular}{lcc}
             \toprule
-	    \textbf{Rank} & \textbf{Keyword} & \textbf{Match Count} \\
+            \bfseries Keyword & \bfseries Match Count \\
             \midrule
 
-		1 & \textbf{Memory} & 109218 \\ 
-		2 & \textbf{Cognition}  & 87655 \\ 
-		3 & \textbf{Dementia} & 51034 \\ 
-		4 & \textbf{Cerebral} &  45886 \\ 
-		5 & \textbf{Cerebrovascular} & 36370 \\ 
-		6 & \textbf{Cerebellar} & 26863 \\
-		7 & \textbf{Cognitive Impairment} & 20267 \\ 
-		8 & \textbf{Alzheimer} & 20581 \\ 
-		9 & \textbf{MOCA} & 9767 \\ 
-		10 & \textbf{Neurocognitive} & 7711 \\ 
-		11 & \textbf{MCI} & 3889 \\ 
-		12 & \textbf{Amnesia} & 3695 \\ 
-		13 & \textbf{AD} & 2673 \\ 
-		14 & \textbf{Lewy} & 2561 \\ 
-		15 & \textbf{MMSE} & 2134 \\ 
-		16 & \textbf{LBD} & 224 \\ 
-		17 & \textbf{Corticobasal} & 147 \\ 
-		18 & \textbf{Pick's} & 41 \\
+            \textbf{Memory} & \fseries 109218 \\ 
+            \textbf{Cognition}  & \fseries 87655 \\ 
+            \textbf{Dementia} & \fseries 51034 \\ 
+            \textbf{Cerebral} & \fseries 45886 \\ 
+            \textbf{Cerebrovascular} & \fseries 36370 \\ 
+            \textbf{Cerebellar} & \fseries 26863 \\
+            \textbf{Cognitive Impairment} & \fseries 20267 \\ 
+            \textbf{Alzheimer} & \fseries 20581 \\ 
+            \textbf{MOCA} & \fseries 9767 \\ 
+            \textbf{Neurocognitive} & \fseries 7711 \\ 
+            \textbf{MCI} & \fseries 3889 \\ 
+            \textbf{Amnesia} & \fseries 3695 \\ 
+            \textbf{AD} & \fseries 2673 \\ 
+            \textbf{Lewy} & \fseries 2561 \\ 
+            \textbf{MMSE} & \fseries 2134 \\ 
+            \textbf{LBD} & \fseries 224 \\ 
+            \textbf{Corticobasal} & \fseries 147 \\ 
+            \textbf{Pick's} & \fseries 41 \\
 
@@
     }
-	{\caption{Keywords indicative of Cognitive Impairment}}
-
 \end{table*}
 
-\section{Appendix B}
+\paragraph{Annotations}
+\label{sec:Annotations} We initially assigned 5,000 sequences diversified by keyword matches from 5,000 unique patients for neurologist labeling.
+As the manual annotation of 279,000+ sequences in not feasible, we devised a scheme to expedite annotations known as "always patterns".
+An always pattern is defined as a phrase or regex expression that in any context indicates the phrase will be labeled with a particular class (i.e.
+yes, no, or neither).
+If an always pattern is inputted, all other sequences have language that matches with the phrase will be automatically labeled accordingly.
+% {List any other sequence assignment schemes} %
+Currently, 8,656 sequences have been annotated, 8,050 through always patterns and 606 manually. % {Will change} %
+
+The final dataset was split between train (95\%) and holdout test (5\%) sets, stratified across label and proportion of sequences annotated manually and through always patterns. % {Will change} % 
+Validation datasets were split from the train set using techniques described in the Methodology section. Table 2 shows demographics of the cohort of patients.
+
+\section{Methodology}
+\label{sec:Methodology}
+
+We built x models and compared performance to baseline model.
+
+\paragraph{(1) Baseline Model} We performed L1 regularized logistic regression where the cognitive concern label was regressed on the counts of medications and ICD codes relevant to CI.
+The lambda value was selected through 10-fold Cross Validation (CV) to maximize the average area under the Receiver Operator Characteristic (ROC).
+% {To be implemented} %
+
+\paragraph{(2) Logistic Regression with TF-IDF Vectors} We performed TF-IDF (term frequency-inverse document frequency) vectorization on the annotated sequences and selected features based on a term's Pearson correlation coefficient with the outcome.
+L1 Regularized logistic regression was applied with the annotated cognitive impairment labels.
+We used different correlation coefficients as thresholds to select features and iterated over different lambda values to determine the optimal lambda value and correlation coefficient threshold.
+
+\paragraph{(3) Model 1 + Model 2} % {TBD} %
+
+\paragraph{(4) Transformer Based Sequence Classification Language Model} % {To be implemented} %
 

### 2021-08-18 Submission/Paper/ML4H/Paper.tex
added conversion to binary labels section

@@
 \paragraph{Dataset}
-\label{sec:Dataset} Our gold-standard dataset consisted of a cohort (N=16,428) of patients from the Mass General Brigham (MGB) HealthCare (formerly Partner's Healthcare, comprising two major academic hospitals, community hospitals, and community health centers in the Boston area) system who were older than 60 years (as of July 13, 2021) and had APOE genotype data available from the BioBank.
+\label{sec:Dataset} Our gold-standard dataset consisted of a cohort (N = 16,428) of patients from the Mass General Brigham (MGB) HealthCare (formerly Partner's Healthcare, comprising two major academic hospitals, community hospitals, and community health centers in the Boston area) system who were older than 60 years (as of July 13, 2021) and had APOE genotype data available from the BioBank.
 Each patients' EHR record was then annotated by neurologists using a web-based annotation tool (UI Interface in Appendix A) as 1) Yes, i.e., patient has CI; 2) No i.e., Patient does not have CI; and 3) Neither i.e., sequence has no information on patient’s cognition.
@@
 Validation datasets were split from the train set using techniques described in the Methodology section. Table 2 shows demographics of the cohort of patients.  
-
 \section{Methodology}
@@
 
-We built x models and compared performance to baseline model.
+We built 4 models and compared performance to the baseline model.
+It is important to note that these models were trained on binary labels, despite annotators labeling sequences with 3 classes.
+This was done because our overall task was to classify if a patient had CI, not whether a sequence indicates CI.
+This means that a label of neither is not relevant, as a patient can only be classified as having or not having CI.
+In order to convert this problem to binary labels, we aggregated no and neither labels to class 0 and yes labels to class 1.
 
-\paragraph{(1) Baseline Model} We performed L1 regularized logistic regression where the cognitive concern label was regressed on the counts of medications and ICD codes relevant to CI.
+\label{sec:Baseline}  
+\paragraph{(1) Baseline Model} We performed L1 regularized logistic regression where the cognitive concern label was regressed on the counts of medications, keyword counts, and ICD codes relevant to CI.
 The lambda value was selected through 10-fold Cross Validation (CV) to maximize the average area under the Receiver Operator Characteristic (ROC).
@@
 
+\label{sec:TFIDF}  
 \paragraph{(2) Logistic Regression with TF-IDF Vectors} We performed TF-IDF (term frequency-inverse document frequency) vectorization on the annotated sequences and selected features based on a term's Pearson correlation coefficient with the outcome.
@@
 
+\label{sec:BaselineTFIDF}  
 \paragraph{(3) Model 1 + Model 2} % {TBD} %
 
+\label{sec:Transformer}  
 \paragraph{(4) Transformer Based Sequence Classification Language Model} % {To be implemented} %
 
+\section{Results}
+\label{sec:Results}
+
 \end{document}

### 2021-08-18 Submission/Paper/ML4H/Paper.tex
changed keyword table to appendix

@@
 \end{abstract}
+
 \begin{keywords}
@@
 \paragraph{Preprocessing}
-\label{sec:Preprocessing} For each patient in our gold-standard dataset, we extracted unstructured clinician notes, identified matches to dementia-related keywords (listed in Table 1), and constructed 800 character sequences from the note text around each of these matches.
+\label{sec:Preprocessing} For each patient in our gold-standard dataset, we extracted unstructured clinician notes, identified matches to dementia-related keywords (Appendix B), and constructed 800 character sequences from the note text around each of these matches.
 Our cohort of 16,428 patients had 279,224 sequences in total.
 
-\begin{table*}[htbp]
+\paragraph{Annotations}
+\label{sec:Annotations} We initially assigned 5,000 sequences diversified by keyword matches from 5,000 unique patients for neurologist labeling.
+As the manual annotation of 279,000+ sequences in not feasible, we devised a scheme to expedite annotations known as "always patterns".
+An always pattern is defined as a phrase or regex expression that in any context indicates the phrase will be labeled with a particular class (i.e.
+yes, no, or neither).
+If an always pattern is inputted, all other sequences have language that matches with the phrase will be automatically labeled accordingly.
+% {List any other sequence assignment schemes} %
+Currently, 8,656 sequences have been annotated, 8,050 through always patterns and 606 manually. % {Will change} %
+
+The final dataset was split between train (95\%) and holdout test (5\%) sets, stratified across label and proportion of sequences annotated manually and through always patterns. % {Will change} % 
+Validation datasets were split from the train set using techniques described in the Methodology section. Table 2 shows demographics of the cohort of patients.
+
+\section{Methodology}
+\label{sec:Methodology}
+
+We built 4 models and compared performance to the baseline model.
+It is important to note that these models were trained on binary labels, despite annotators labeling sequences with 3 classes.
+This was done because our overall task was to classify if a patient had CI, not whether a sequence indicates CI.
+This means that a label of neither is not relevant, as a patient can only be classified as having or not having CI.
+In order to convert this problem to binary labels, we aggregated no and neither labels to class 0 and yes labels to class 1.
+
+\label{sec:Baseline}  
+\paragraph{(1) Baseline Model} We performed L1 regularized logistic regression where the cognitive concern label was regressed on the counts of medications, keyword counts, and ICD codes relevant to CI.
+The lambda value was selected through 10-fold Cross Validation (CV) to maximize the average area under the Receiver Operator Characteristic (ROC).
+% {To be implemented} %
+
+\label{sec:TFIDF}  
+\paragraph{(2) Logistic Regression with TF-IDF Vectors} We performed TF-IDF (term frequency-inverse document frequency) vectorization on the annotated sequences and selected features based on a term's Pearson correlation coefficient with the outcome.
+L1 Regularized logistic regression was applied with the annotated cognitive impairment labels.
+We used different correlation coefficients as thresholds to select features and iterated over different lambda values to determine the optimal lambda value and correlation coefficient threshold.
+
+\label{sec:Baseline+TFIDF}  
+\paragraph{(3) Model 1 + Model 2} % {TBD} %
+
+\label{sec:Transformer}  
+\paragraph{(4) Transformer Based Sequence Classification Language Model} % {To be implemented} %
+
+% binary classification model stats - probability threshold of 0.89
+\begin{table*}[hbtp]
+%   {\caption{TF-IDF Vector Features Correlation}}
+  {\begin{tabular}{lccccccc}
+    \toprule
+
+    \bfseries Model & \bfseries AUCROC & \bfseries ACC & \bfseries Sensitivity & \bfseries Specificity & \bfseries FP & \bfseries FN & \bfseries Prediction Threshold \\ 
+    Model 2 & 0.94 & 0.90 & 0.73 & 0.94 & __ & __ & 0.89 \\
+
+    \bottomrule
+  \end{tabular}}
+
+\end{table*}
+
+\section{Results}
+\label{sec:Results}
+
+% Talk about Stats
+% TF-IDF model struggles with understanding context of words around keyword match
+
+We evaluated each model using a prediction threshold to maximize the accuracy and calculated performance metrics based on that threshold. Model performance for each model in shown in Table 2.
+
+\section{Conclusion and Future Work} 
+\label{sec:ConclusionFutureWork} We applied innovative Machine Learning and Deep Learning NLP techniques to identify patients with CI in EHR.
+Our work can help combat the issues of underdiagnosis and misdiagnosis for dementia.
+
+Future plans include reducing false positives by gathering more annotated sequences and using deep learning natural language.
+Currently, many of our false positives are from the model identifying the presence of a keyword but struggling to understand the context around the keyword match; many of these contexts negate the presence of CI for the patient in question.
+Deep Learning can leverage contextual information, making it promising for this task.
+
+\clearpage
+\appendix
+
+% Appendix A
+\section{UI of Annotation Tool}
+Placeholder
+
+% Appendix B
+\section{Keywords} % wi
+\begin{table}[hbtp] 
 \floatconts  
 {tab:operatornames}
-  {\caption{Keywords indicative of Cognitive Impairment}}%
+    {\caption{Keywords indicative of Cognitive Impairment}} \\
     {
-        \begin{tabular}{lcc}
+        \begin{tabular}{lccc}
         \toprule
-            \bfseries Keyword & \bfseries Match Count \\
+        \bfseries Keyword & \bfseries Match Count\\
         \midrule
@@
     }
-\end{table*}
-
-\paragraph{Annotations}
-\label{sec:Annotations} We initially assigned 5,000 sequences diversified by keyword matches from 5,000 unique patients for neurologist labeling.
-As the manual annotation of 279,000+ sequences in not feasible, we devised a scheme to expedite annotations known as "always patterns".
-An always pattern is defined as a phrase or regex expression that in any context indicates the phrase will be labeled with a particular class (i.e.
-yes, no, or neither).
-If an always pattern is inputted, all other sequences have language that matches with the phrase will be automatically labeled accordingly.
-% {List any other sequence assignment schemes} %
-Currently, 8,656 sequences have been annotated, 8,050 through always patterns and 606 manually. % {Will change} %
-
-The final dataset was split between train (95\%) and holdout test (5\%) sets, stratified across label and proportion of sequences annotated manually and through always patterns. % {Will change} % 
-Validation datasets were split from the train set using techniques described in the Methodology section. Table 2 shows demographics of the cohort of patients.  
-\section{Methodology}
-\label{sec:Methodology}
-
-We built 4 models and compared performance to the baseline model.
-It is important to note that these models were trained on binary labels, despite annotators labeling sequences with 3 classes.
-This was done because our overall task was to classify if a patient had CI, not whether a sequence indicates CI.
-This means that a label of neither is not relevant, as a patient can only be classified as having or not having CI.
-In order to convert this problem to binary labels, we aggregated no and neither labels to class 0 and yes labels to class 1.
-
-\label{sec:Baseline}  
-\paragraph{(1) Baseline Model} We performed L1 regularized logistic regression where the cognitive concern label was regressed on the counts of medications, keyword counts, and ICD codes relevant to CI.
-The lambda value was selected through 10-fold Cross Validation (CV) to maximize the average area under the Receiver Operator Characteristic (ROC).
-% {To be implemented} %
-
-\label{sec:TFIDF}  
-\paragraph{(2) Logistic Regression with TF-IDF Vectors} We performed TF-IDF (term frequency-inverse document frequency) vectorization on the annotated sequences and selected features based on a term's Pearson correlation coefficient with the outcome.
-L1 Regularized logistic regression was applied with the annotated cognitive impairment labels.
-We used different correlation coefficients as thresholds to select features and iterated over different lambda values to determine the optimal lambda value and correlation coefficient threshold.
-
-\label{sec:BaselineTFIDF}  
-\paragraph{(3) Model 1 + Model 2} % {TBD} %
-
-\label{sec:Transformer}  
-\paragraph{(4) Transformer Based Sequence Classification Language Model} % {To be implemented} %
-
-\section{Results}
-\label{sec:Results}
+\end{table}
 

### 2021-08-19 Submission/Paper/ML4H/Paper.tex

@@
 
- % Use \Name{Author Name} to specify the name.
- % If the surname contains spaces, enclose the surname
- % in braces, e.g. \Name{John {Smith Jones}} similarly
- % if the name has a "von" part, e.g \Name{Jane {de Winter}}.
- % If the first letter in the forenames is a diacritic
- % enclose the diacritic in braces, e.g. \Name{{\'E}louise Smith}
-
- % \thanks must come after \Name{...} not inside the argument for
- % example \Name{John Smith}\nametag{\thanks{A note}} NOT \Name{John
- % Smith\thanks{A note}}
-
- % Anything in the name that should appear in the title but not in the 
- % article's header or footer or in the volume's
- % table of contents should be placed inside \nametag{}
-
- % Two authors with the same address
- % \author{%
- %  \Name{Author Name1\nametag{\thanks{A note}}} \Email{abc@sample.com}\and
- %  \Name{Author Name2} \Email{xyz@sample.com}\\
- %  \addr Address
- % }
-
- % Three or more authors with the same address:
- % \author{%
- %  \Name{Author Name1} \Email{an1@sample.com}\\
- %  \Name{Author Name2} \Email{an2@sample.com}\\
- %  \Name{Author Name3} \Email{an3@sample.com}\\
- %  \Name{Author Name4} \Email{an4@sample.com}\\
- %  \Name{Author Name5} \Email{an5@sample.com}\\
- %  \Name{Author Name6} \Email{an6@sample.com}\\
- %  \Name{Author Name7} \Email{an7@sample.com}\\
- %  \Name{Author Name8} \Email{an8@sample.com}\\
- %  \Name{Author Name9} \Email{an9@sample.com}\\
- %  \Name{Author Name10} \Email{an10@sample.com}\\
- %  \Name{Author Name11} \Email{an11@sample.com}\\
- %  \Name{Author Name12} \Email{an12@sample.com}\\
- %  \Name{Author Name13} \Email{an13@sample.com}\\
- %  \Name{Author Name14} \Email{an14@sample.com}\\
- %  \addr Address
- % }
-
- % Authors with different addresses and equal first authors:
-\author{%
-\Name{First Author 1}\equal{These authors contributed equally} \Email{abc@sample.com}\\
-\addr University X, Country 1
-\AND
-% footnotemark[1] is to refer to the \equal footnote
-\Name{First Author 2}\footnotemark[1] \Email{def@sample.com}\\
-\addr University Y, Country 2
-\AND
-\Name{Last Author} \Email{ghi@sample.com}\\
-\addr University Z, Country 3
+\author{Tanish Tyagi \nametag{\thanks{Authors contributed equally}\SUP{1}},
+Colin G. Magdamo\nametag{\footnotemark[1]\SUP{1}}, 
+Ayush Noori \SUP{1},
+Mayuresh Deodhar \SUP{1},
+Zhuoqiao Hong \SUP{1},
+Dimitry Propenko \SUP{1},
+Rudy E. Tanzi \SUP{1},
+Deborah Blacker \SUP{1},
+Bradley T. Hyman \SUP{1},
+Shibani S. Mukerji \SUP{1},
+M. Brandon Westover \SUP{1},
+Sudeshna Das\SUP{1},
+\centering \Email{
+\\[\bigskipamount] 
+\SUP{1}\{ttanish, 
+cmagdamo,
+anoori1,
+...
+sdas5\}
+@mgh.harvard.edu}
+% 
+\begin{center}\addr Massachusetts General Hospital, Boston, MA\end{center}
 }
@@
 Automated evaluation of these notes presents an opportunity to label patients with cognitive impairment (CI) in real-world data.
+In order to identify patients with cognitive impairment, we applied natural language processing (NLP) techniques.
+Model performance was compared to a baseline model that utilized structured features such as medication and ICD counts.
+% Add which model had highest performance %
 \end{abstract}
@@
 \begin{keywords}
-EHR, NLP, Demetia
+EHR, NLP, Dementia
 \end{keywords}
@@
 \section{Introduction}
-\label{sec:intro}
+\label{sec:intro} The possibility of early diagnosis of dementia is important for improving clinical outcomes and patient management of dementia.
+Often, diagnosis is given once patient has reached moderate dementia, but irreversible damage has already been done to the brain.
+% https://www.dementiacarecentral.com/aboutdementia/facts/stages/ %
+Yet, dementia is not formally diagnosed or coded in claims data for over 50\% of older adults living with probable dementia.
+Tools that can efficiently and effectively analyze medical records for warning signs of dementia and recommend patients for care can be critical to obtaining early diagnosis for dementia.
+In this project, we aim to use NLP to detect signs of cognitive impairment from unstructured clinician notes in electronic health records (EHR) by using machine and deep learning techniques.
 
@@
 \paragraph{Dataset}
-\label{sec:Dataset} Our gold-standard dataset consisted of a cohort (N = 16,428) of patients from the Mass General Brigham (MGB) HealthCare (formerly Partner's Healthcare, comprising two major academic hospitals, community hospitals, and community health centers in the Boston area) system who were older than 60 years (as of July 13, 2021) and had APOE genotype data available from the BioBank.
+\label{sec:Dataset} Our gold-standard dataset consisted of a cohort (N = 16,428) of patients from the Mass General Brigham (MGB) HealthCare (formerly Partner's Healthcare, comprising two major academic hospitals, community hospitals, and community health centers in the Boston area) system who were older than 60 years (as of July 13, 2021) and had APOE genotype (biggest genetic risk factor for dementia) data available from the BioBank.
 Each patients' EHR record was then annotated by neurologists using a web-based annotation tool (UI Interface in Appendix A) as 1) Yes, i.e., patient has CI; 2) No i.e., Patient does not have CI; and 3) Neither i.e., sequence has no information on patient’s cognition.
@@
 % TF-IDF model struggles with understanding context of words around keyword match
+% Future plans include reducing false positives by gathering more annotated sequences and using deep learning natural language.
+Currently, many of our false positives are from the model identifying the presence of a keyword but struggling to understand the context around the keyword match; many of these contexts negate the presence of CI for the patient in question.
+Deep Learning can leverage contextual information, making it promising for this task.
 
@@
 Our work can help combat the issues of underdiagnosis and misdiagnosis for dementia.
-
-Future plans include reducing false positives by gathering more annotated sequences and using deep learning natural language.
-Currently, many of our false positives are from the model identifying the presence of a keyword but struggling to understand the context around the keyword match; many of these contexts negate the presence of CI for the patient in question.
-Deep Learning can leverage contextual information, making it promising for this task.
+% {More coming soon } %
 

### 2021-08-30 Submission/Paper/ML4H/Paper.tex
added table 1

@@
 % Customized Tabs
-\newcommand\mytab{\tab \hspace{-5cm}}
+\newcommand\mytab{\hspace{10mm} \hspace{-5cm}}
 
@@
 \begin{abstract}
-\tab Dementia is a neurodegenerative disorder that causes cognitive decline and affects more than 50 million people worldwide.
+\hspace{10mm} Dementia is a neurodegenerative disorder that causes cognitive decline and affects more than 50 million people worldwide.
 Dementia is under-diagnosed by healthcare professionals—only one in four people who suffer from dementia are diagnosed.
 Even when a diagnosis is made, it may not be entered as a structured diagnosis code in a patient’s charts.
-Information relevant to cognitive impairment is often found within electronic health records but manual review of clinician notes by experts is both time consuming and often prone to errors.
-Automated evaluation of these notes presents an opportunity to label patients with cognitive impairment (CI) in real-world data.
+Information relevant to cognitive impairment is often found within electronic health records (EHR) but manual review of clinician notes by experts is both time consuming and often prone to errors.
+Automated mining of these notes presents an opportunity to label patients with cognitive impairment (CI) in real-world data.
 In order to identify patients with cognitive impairment, we applied natural language processing (NLP) techniques.
@@
 \label{sec:intro} The possibility of early diagnosis of dementia is important for improving clinical outcomes and patient management of dementia.
-Often, diagnosis is given once patient has reached moderate dementia, but irreversible damage has already been done to the brain.
+Often, a diagnosis is given once patient has reached moderate dementia, but irreversible damage has already been done to the brain.
 % https://www.dementiacarecentral.com/aboutdementia/facts/stages/ %
 Yet, dementia is not formally diagnosed or coded in claims data for over 50\% of older adults living with probable dementia.
-Tools that can efficiently and effectively analyze medical records for warning signs of dementia and recommend patients for care can be critical to obtaining early diagnosis for dementia.
-In this project, we aim to use NLP to detect signs of cognitive impairment from unstructured clinician notes in electronic health records (EHR) by using machine and deep learning techniques.
+Tools that can efficiently and effectively analyze medical records for warning signs of dementia and recommend patients for follow up with a specialist can be critical to obtaining early diagnosis for dementia.
+We aim to use NLP to detect signs of cognitive impairment from unstructured clinician notes by using deep learning techniques.
 
@@
 \section{Dataset, Preprocessing, and Annotations}
+\label{sec:Dataset+Preprocessing+Annotations}
 
@@
 \paragraph{Preprocessing}
-\label{sec:Preprocessing} For each patient in our gold-standard dataset, we extracted unstructured clinician notes, identified matches to dementia-related keywords (Appendix B), and constructed 800 character sequences from the note text around each of these matches.
+\label{sec:Preprocessing} For each patient in our gold-standard dataset, we extracted unstructured clinician notes, identified matches to dementia-related keywords (Appendix B), and constructed sequences from the note text around each of these matches (of length 800 characters).
 Our cohort of 16,428 patients had 279,224 sequences in total.
@@
 If an always pattern is inputted, all other sequences have language that matches with the phrase will be automatically labeled accordingly.
-% {List any other sequence assignment schemes} %
-Currently, 8,656 sequences have been annotated, 8,050 through always patterns and 606 manually. % {Will change} %
+Currently, 8,656 sequences have been annotated, 8,050 through always patterns and 606 manually.
+% {Will change} %
 
 The final dataset was split between train (95\%) and holdout test (5\%) sets, stratified across label and proportion of sequences annotated manually and through always patterns. % {Will change} % 
-Validation datasets were split from the train set using techniques described in the Methodology section. Table 2 shows demographics of the cohort of patients.
+Validation datasets were split from the train set using techniques described in the Methodology section. Table 1 shows demographics of the cohort of patients.
+
+%% Table 1 - Demographics of Dataset %%
+\begin{table*}[hbtp]
+\centering 
+    {\caption{Demographics of Data}} \\
+    {
+
+        \begin{tabular}{lccc}
+        \toprule
+        \bfseries Characteristic & \bfseries (N = 16428) \\
+        \midrule
+
+        \textbf{Age (years) mean (SD)} & \fseries 73.01 (7.96) \\
+
+        \textbf{Gender Male, \emph n (\%)}  & \fseries 8740 (53.2)\\
+
+        \textbf{Race, \emph n (\%)} \\ 
+            \hspace{10mm} White & 14896 (90.7) \\
+            \hspace{10mm} Other/Not Recorded & 608 (3.7) \\
+            \hspace{10mm} Black & 570 (3.5) \\
+            \hspace{10mm} Hispanic & 170 (1.0) \\
+            \hspace{10mm} Asian & 168 (1.0) \\
+            \hspace{10mm} Indigenous & 16 (0.01) \\
+
+        \textbf{APOE Genotype, \emph n (\%)} \\ 
+            \hspace{10mm} {APOE ${\bm{\varepsilon}}$2 & 2028 (12.3)} \\
+            \hspace{10mm} {APOE ${\bm{\varepsilon}}$3 & 10177 (62.0)} \\
+            \hspace{10mm} {APOE ${\bm{\varepsilon}}$4 & 4223 (25.7)} \\
+
+        \textbf{Average Speciality Visits (SD)} & 1.67 (4.6) \\
+
+        \textbf{Average PCP Encounters (SD)} &  5.25 (5.63) \\
+
+        % \textbf{Encounters AVG (SD)} & 14.55 (23.2) \\
+
+        % \textbf{Keyword Matches AVG (SD)} & 26 (54.03) \\
+
+        \bottomrule
+        \end{tabular}
+    }
+\end{table*}
 
@@
 \label{sec:Methodology}  
-
-We built 4 models and compared performance to the baseline model.
+{We built 4 models and compared performance to the baseline model.
 It is important to note that these models were trained on binary labels, despite annotators labeling sequences with 3 classes.
 This was done because our overall task was to classify if a patient had CI, not whether a sequence indicates CI.
-This means that a label of neither is not relevant, as a patient can only be classified as having or not having CI.
+% phrase better %
+A label of neither does not pertain  patient can only be classified as having or not having CI.
 In order to convert this problem to binary labels, we aggregated no and neither labels to class 0 and yes labels to class 1.
+}
 
@@
 
-\label{sec:Baseline+TFIDF}  
-\paragraph{(3) Model 1 + Model 2} % {TBD} %
+% \label{sec:Baseline+TFIDF}  
+% \paragraph{(3) Model 1 + Model 2} % {TBD} %
 
 \label{sec:Transformer}  
-\paragraph{(4) Transformer Based Sequence Classification Language Model} % {To be implemented} %
+\paragraph{(3)Transformer Based Sequence Classification Language Model} % {To be implemented} %
 
-% binary classification model stats - probability threshold of 0.89
+\section{Results}
+\label{sec:Results}  
+% talk abt performance
+% which patients are correctly classified for each model
+% compare conf mat's for each model
+% distribution of CI/not CI labels
+% talk about different patient aggregation scheme
+% address lack of not patient level labels
+% TFIDF might have lot of false positives b/c of use of vocab that doesn't discuss patient, deep learning will be able to use context
+% start with justification to aggregation to patient level
+% sensivity should hopefully improve, deep learning should reduce specificity b/c of use of contextual information
+% discuss if certain patients were predicted differently for all models
+% some ppl will be classified as 0, until deep learning, where it will be hopefully changed to 1
+% group of ppl who get 0 for baseline, prediction of 1 with tf-idf and deep
+% group of ppl who get 1 for tf-idf, 0 for deep learning b/c of high false positive rate, vocab cld be talking abt family member (tf-idf will address underdiagnosis, deep learning will address misdiagnosis better)
+% tf-idf is easy to "trigger", deep learning will evaulate based on context
+% Talk about Stats
+% TF-IDF model struggles with understanding context of words around keyword match
+% Future plans include reducing false positives by gathering more annotated sequences and using deep learning natural language.
+Currently, many of our false positives are from the model identifying the presence of a keyword but struggling to understand the context around the keyword match; many of these contexts negate the presence of CI for the patient in question.
+Deep Learning can leverage contextual information, making it promising for this task.
+
+We evaluated each model using a prediction threshold to maximize the accuracy and calculated performance metrics based on that threshold. Model performance for each model in shown in Table 2.
+
+% Table 2 - Results
 \begin{table*}[hbtp]
@@
 \end{table*}
-
-\section{Results}
-\label{sec:Results}
-
-% Talk about Stats
-% TF-IDF model struggles with understanding context of words around keyword match
-% Future plans include reducing false positives by gathering more annotated sequences and using deep learning natural language.
-Currently, many of our false positives are from the model identifying the presence of a keyword but struggling to understand the context around the keyword match; many of these contexts negate the presence of CI for the patient in question.
-Deep Learning can leverage contextual information, making it promising for this task.
-
-We evaluated each model using a prediction threshold to maximize the accuracy and calculated performance metrics based on that threshold. Model performance for each model in shown in Table 2.
 

### 2021-08-30 Submission/Paper/ML4H/Paper.tex
8/29 changes

@@
  \documentclass[pmlr,twocolumn,10pt]{jmlr} % W&CP article
+
+ \let\SUP\textsuperscript
 
@@
 \label{sec:Annotations} We initially assigned 5,000 sequences diversified by keyword matches from 5,000 unique patients for neurologist labeling.
-As the manual annotation of 279,000+ sequences in not feasible, we devised a scheme to expedite annotations known as "always patterns".
+In order to expedite annotations, we devised a scheme to known as "always patterns".
 An always pattern is defined as a phrase or regex expression that in any context indicates the phrase will be labeled with a particular class (i.e.
@@
 \label{sec:Transformer}  
-\paragraph{(3)Transformer Based Sequence Classification Language Model} % {To be implemented} %
+\paragraph{(3) Transformer Based Sequence Classification Language Model} % {To be implemented} %
 

### 2021-09-02 Submission/Paper/ML4H/Paper.tex
added figure 1
added tfidf model stats

@@
 \usepackage{graphicx}
+\graphicspath{ {images/} }
+
 \usepackage{natbib}
@@
 Each patients' EHR record was then annotated by neurologists using a web-based annotation tool (UI Interface in Appendix A) as 1) Yes, i.e., patient has CI; 2) No i.e., Patient does not have CI; and 3) Neither i.e., sequence has no information on patient’s cognition.
+% link
+Appendix C shows examples of example sequences for all 3 classes.
 
@@
 % Table 2 - Results
-\begin{table*}[hbtp]
-%   {\caption{TF-IDF Vector Features Correlation}}
-  {\begin{tabular}{lccccccc}
+\begin{table}[hbtp]
+  {\begin{tabular}{lcccccccc}
     \toprule 
-
-    \bfseries Model & \bfseries AUCROC & \bfseries ACC & \bfseries Sensitivity & \bfseries Specificity & \bfseries FP & \bfseries FN & \bfseries Prediction Threshold \\ 
-    Model 2 & 0.94 & 0.90 & 0.73 & 0.94 & __ & __ & 0.89 \\
-
+    \bfseries Model & \bfseries AUC & \bfseries Accuracy & \bfseries Sensitivity & \bfseries Specificity & \bfseries Micro F1  & \bfseries Macro F1 & \bfseries Weighted F1 \\ 
+    \midrule
+    TF-IDF & 0.95 & 0.84 & 0.83 & 0.92 & 0.84 & 0.814 & 0.843 \\
     \bottomrule
   \end{tabular}}
-
-\end{table*}
+  {\caption{F1 Scores for TF-IDF, Transformer}}
+\end{table}
 
@@
 Placeholder
+
+\newpage
 
@@
 
+\newpage
+
+% Appendix C
+
+\label{sec:AppendixC}
+\section{Example Sequences} 
+\includegraphics[width = 15cm, height = 5cm]{Figure-1.png}
+\caption{Figure 1: Example Sequences}
+
 \end{document}

### 2021-09-02 Submission/Paper/ML4H/Paper.tex
added  draft of transformer in methodology

@@
 \label{sec:Methodology}  
-{We built 4 models and compared performance to the baseline model.
+% {We built 4 models and compared performance to the baseline model.
 It is important to note that these models were trained on binary labels, despite annotators labeling sequences with 3 classes.
@@
 % phrase better %
-A label of neither does not pertain  patient can only be classified as having or not having CI.
+% A label of neither does not pertain  patient can only be classified as having or not having CI.
 In order to convert this problem to binary labels, we aggregated no and neither labels to class 0 and yes labels to class 1.
@@
 
-\label{sec:Baseline}  
-\paragraph{(1) Baseline Model} We performed L1 regularized logistic regression where the cognitive concern label was regressed on the counts of medications, keyword counts, and ICD codes relevant to CI.
+% \label{sec:Baseline}  
+% \paragraph{(1) Baseline Model} We performed L1 regularized logistic regression where the cognitive concern label was regressed on the counts of medications, keyword counts, and ICD codes relevant to CI.
 The lambda value was selected through 10-fold Cross Validation (CV) to maximize the average area under the Receiver Operator Characteristic (ROC).
@@
 \label{sec:TFIDF}  
-\paragraph{(2) Logistic Regression with TF-IDF Vectors} We performed TF-IDF (term frequency-inverse document frequency) vectorization on the annotated sequences and selected features based on a term's Pearson correlation coefficient with the outcome.
+\paragraph{(1) Logistic Regression with TF-IDF Vectors} We performed TF-IDF (term frequency-inverse document frequency) vectorization on the annotated sequences and selected features based on a term's Pearson correlation coefficient with the outcome.
 L1 Regularized logistic regression was applied with the annotated cognitive impairment labels.
@@
 \label{sec:Transformer}  
-\paragraph{(3) Transformer Based Sequence Classification Language Model} % {To be implemented} %
+\paragraph{(2) Transformer Based Sequence Classification Language Model} We utilized a pre-trained language model called Clinical-BERT, which was trained on the MIMIC II database containing EHR records from ICU patients.
+We used the implementation in the Huggingface Transformer and Simpletransformers packages.
+After text preprocessing, input texts were tokenized with the default tokenizer and converted to embeddings.
+The model was initialized with pre-trained parameters and later fine-tuned on our labeled training set.
+Hyperparameters were tuned on the held-out validation set for the cognitive impairment classification task.
 

### 2021-09-02 Submission/Paper/ML4H/Paper.tex
Update Paper.tex

@@
 \centering 
-    {\caption{Demographics of Data}} \\
     {
-
         \begin{tabular}{lccc}
@@
         \midrule
-
         \textbf{Age (years) mean (SD)} & \fseries 73.01 (7.96) \\ 
-
         \textbf{Gender Male, \emph n (\%)}  & \fseries 8740 (53.2)\\ 
-
         \textbf{Race, \emph n (\%)} \\ 
@@
             \hspace{10mm} Indigenous & 16 (0.01) \\
-
         \textbf{APOE Genotype, \emph n (\%)} \\ 
@@
             \hspace{10mm} {APOE ${\bm{\varepsilon}}$4 & 4223 (25.7)} \\
-
         \textbf{Average Speciality Visits (SD)} & 1.67 (4.6) \\ 
-
         \textbf{Average PCP Encounters (SD)} &  5.25 (5.63) \\ 
-
         % \textbf{Encounters AVG (SD)} & 14.55 (23.2) \\
-
         % \textbf{Keyword Matches AVG (SD)} & 26 (54.03) \\
-
         \bottomrule
         \end{tabular}
+        {\caption{Demographics of Data}} \\
     }
@@
 
-We evaluated each model using a prediction threshold to maximize the accuracy and calculated performance metrics based on that threshold. Model performance for each model in shown in Table 2.
+We evaluated each model using a prediction threshold to maximize the accuracy and calculated performance metrics based on that threshold.
+Model performance for each model in shown in Table 2.
+All performance metrics are based on the sequence level class assignments.
+% discuss sequence level stats (notes above)%
+
+In order to obtain a patient level class assignment assignments from the models,  %discuss%
 
@@
   \end{tabular}}
-  {\caption{F1 Scores for TF-IDF, Transformer}}
+  {\caption{Model Performance}}
 \end{table}
@@
 \section{Conclusion and Future Work} 
-\label{sec:ConclusionFutureWork} We applied innovative Machine Learning and Deep Learning NLP techniques to identify patients with CI in EHR.
+\label{sec:ConclusionFutureWork} We applied innovative Machine Learning and Deep Learning NLP techniques to identify patients with cognitive impairment in EHR.
 Our work can help combat the issues of underdiagnosis and misdiagnosis for dementia.

### 2021-09-03 Submission/Paper/ML4H/Paper.tex
added figure 1

@@
 % link
-Appendix C shows examples of example sequences for all 3 classes.
+\figureref{fig:fig1} shows examples of example sequences for all 3 classes.
+
+% Figure 1 - Example Sequences
+\begin{figure*}[h!]
+\label{fig:fig1}
+\centering 
+\includegraphics[width = 15cm, height = 5cm]{Figure-1.png}
+\caption{Example Sequences}
+\end{figure*}
 
@@
 If an always pattern is inputted, all other sequences have language that matches with the phrase will be automatically labeled accordingly.
-Currently, 8,656 sequences have been annotated, 8,050 through always patterns and 606 manually.
-% {Will change} %
 
 The final dataset was split between train (95\%) and holdout test (5\%) sets, stratified across label and proportion of sequences annotated manually and through always patterns. % {Will change} % 
-Validation datasets were split from the train set using techniques described in the Methodology section. Table 1 shows demographics of the cohort of patients.
+Validation datasets were split from the train set using techniques described in the Methodology section. \tableref{tab:table1} shows demographics of the cohort of patients.
 
@@
 \begin{table*}[hbtp]
+\floatconts
+{tab:table1}
 \centering 
+{\caption{Demographics of Data}} \\
     {
@@
         \end{tabular}
-        {\caption{Demographics of Data}} \\
+
     }
@@
 \begin{table}[hbtp]
+\floatconts
+{tab:table2}
   {\begin{tabular}{lcccccccc}
@@
 \floatconts
-{tab:operatornames}
+{tab:keywords}
     {\caption{Keywords indicative of Cognitive Impairment}} \\
@@
 
-\label{sec:AppendixC}
-\section{Example Sequences} 
-\includegraphics[width = 15cm, height = 5cm]{Figure-1.png}
-\caption{Figure 1: Example Sequences}
-
 \end{document}

### 2021-09-03 Submission/Paper/ML4H/Paper.tex
added tables 3 + 4

@@
 \centering 
-{\caption{Demographics of Data}} \\
     {
@@
         \end{tabular}
-
+        {\caption{Demographics of Data}} \\
     }
@@
 We evaluated each model using a prediction threshold to maximize the accuracy and calculated performance metrics based on that threshold.
-Model performance for each model in shown in Table 2.
+Model performance for each model in shown in \tableref{tab:table2}.
 All performance metrics are based on the sequence level class assignments.
@@
 % Table 2 - Results
-\begin{table}[hbtp]
+\begin{table*}[hbtp]
 \floatconts
@@
   {\caption{Model Performance}}
-\end{table}
+\end{table*}
 
+% Table 3 + 4 - Relation of Med/ICD Codes to Model Predictions
+\begin{table*}[hbtp]
+\floatconts
+{tab:table3}
+\centering 
+  {\begin{tabular}{cccccc}
+    \toprule 
+    \bfseries  & \bfseries Count & \bfseries Yes (\%) & \bfseries No/Ntr (\%)  & \bfseries Med/ICD Code (\%)  \\ 
+    \midrule
+    \bfseries{APOE ${\bm{\varepsilon}}$2} & \fseries 1754 & \fseries 0.15 & \fseries 0.85 & \fseries 0.11  \\
+    \bfseries{APOE ${\bm{\varepsilon}}$3} & \fseries 8751 & \fseries 0.15 & \fseries 0.85 & \fseries 0.11  \\
+    \bfseries{APOE ${\bm{\varepsilon}}$4} & \fseries 3436 & \fseries 0.18 & \fseries 0.82 & \fseries 0.17  \\
+
+    \bottomrule
+  \end{tabular}}
+{\caption{Comparison between Other Indicators of Cognitive Impairment and TF-IDF}} \\
+\end{table*}
+
+\begin{table*}[hbtp]
+\floatconts
+{tab:table4}
+\centering 
+    {\begin{tabular}{cccccc}
+    \toprule 
+    \bfseries  & \bfseries Count & \bfseries Yes (\%) & \bfseries No/Ntr (\%)  & \bfseries Med/ICD Code (\%) \\ 
+    \midrule
+    \bfseries{APOE ${\bm{\varepsilon}}$2} & \fseries 1754 & \fseries 0.15 & \fseries 0.85 & \fseries 0.11  \\
+    \bfseries{APOE ${\bm{\varepsilon}}$3} & \fseries 8751 & \fseries 0.15 & \fseries 0.85 & \fseries 0.11  \\
+    \bfseries{APOE ${\bm{\varepsilon}}$4} & \fseries 3436 & \fseries 0.18 & \fseries 0.82 & \fseries 0.17  \\
+
+    \bottomrule
+  \end{tabular}}
+  {\caption{Comparison between Other Indicators of Cognitive Impairment and Clinical-BERT}} \\
+\end{table*}
+
+%% Conclusion + Future Work %%
 \section{Conclusion and Future Work} 
@@
 {tab:keywords}
-    {\caption{Keywords indicative of Cognitive Impairment}} \\
-    {
-        \begin{tabular}{lccc}
+    {\begin{tabular}{lccc}
         \toprule
@@
         \bottomrule
-        \end{tabular}
-    }
+        \end{tabular}}
+        {\caption{Keywords indicative of Cognitive Impairment}} \\
+
 \end{table}

### 2021-09-07 Submission/Paper/ML4H/Paper.tex
added title and paper status
fixed the issue of weird spacing between appendix elements and added tf-idf feature correlation table

@@
 \graphicspath{ {images/} }
-
+\usepackage{float}
 \usepackage{natbib}
@@
  % change the arguments, as appropriate, in the following:
-\jmlrvolume{LEAVE UNSET}
+\jmlrvolume{ML4H Extended Abstract Arxiv Index}
 \jmlryear{2021}
-\jmlrsubmitted{LEAVE UNSET}
-\jmlrpublished{LEAVE UNSET}
+\jmlrsubmitted{201}
+\jmlrpublished{}
 \jmlrworkshop{Machine Learning for Health (ML4H) 2021} % W&CP title
@@
  % The optional argument of \title is used in the header
-\title[Short Title]{Full Title of Article\titlebreak This Title Has
-A Line Break}
+\title[NLP Techniques to Detect Cognitive Impairment]{Using Deep Learning to Identify Cognitive Impairment in Electronic Health Records}
 
@@
 We aim to use NLP to detect signs of cognitive impairment from unstructured clinician notes by using deep learning techniques.
+An overview of our project can be found in Appendix A.
 
@@
 \centering 
-\includegraphics[width = 15cm, height = 5cm]{Figure-1.png}
+\includegraphics[scale = 0.35]{Figure-1.png}
 \caption{Example Sequences}
@@
 The model was initialized with pre-trained parameters and later fine-tuned on our labeled training set.
-Hyperparameters were tuned on the held-out validation set for the cognitive impairment classification task.
+Optuna was used to perform a 20-trial study and tune the learning rate, adam epilson, and the number of train epochs on the held-out validation set.
 
@@
 % Appendix A
-\section{UI of Annotation Tool}
-Placeholder
+% Figure 2 - Overview
+\section{Overview}
+\label{fig:fig2}
+\begin{figure}[h]
+\floatplacement{figure*}[h]
+\centering 
+\includegraphics[scale = 0.14]{Overview.png}
+\caption{Overview}
+\end{figure}
 
-\newpage
+\clearpage
 
 % Appendix B
-\section{Keywords} % wi
+\section{Keywords} 
 \begin{table}[hbtp] 
 \floatconts
-{tab:keywords}
+{app:keywords}
     {\begin{tabular}{lccc}
@@
 \end{table}
-
-\newpage
+\clearpage
 
 % Appendix C
+\section{Top TF-IDF Word Features}
+\begin{table}[hbtp]
+    {\begin{tabular}{cccc}
+    \toprule 
+    \bfseries Word & \bfseries Corr & \bfseries Word & \bfseries Corr &
+    \midrule
+
+    \textbf{Intact} & \fseries 0.56 & \textbf{Experiences} & \fseries 0.36 \\
+    \textbf{Oriented} & \fseries 0.43 & \textbf{Associations} & \fseries 0.36 \\ 
+    \textbf{Concentration} & \fseries 0.42 & \textbf{Homicidal} & \fseries 0.36 \\ 
+    \textbf{Orientation} & \fseries 0.41 & \textbf{Observation} & \fseries 0.36 \\
+    \textbf{Sensorium} & \fseries 0.40 & \textbf{Knowledge} & \fseries 0.36 \\ 
+    \textbf{Perceptions} & \fseries 0.40 & \textbf{Abstract} & \fseries 0.36 \\
+    \textbf{Judgement} & \fseries 0.39 & \textbf{Suicidal} & \fseries 0.35 \\
+    \textbf{Fund} & \fseries 0.38 & \textbf{Attention} & \fseries 0.35 \\
+    \textbf{Insight } & \fseries 0.36 & \textbf{Content} & \fseries 0.34 \\ 
+    \textbf{Ideation} & \fseries 0.36 & \textbf{Thought} & \fseries 0.34  \\
+
+    \bottomrule
+  \end{tabular}}
+\end{table}
 

### 2021-09-08 Submission/Paper/ML4H/Paper.tex
added bert patient level figures
Update Paper.tex

@@
 \\[\bigskipamount] 
-\SUP{1}\{ttanish, 
+\SUP{1}\{ttyagi, 
 cmagdamo,
@@
 
-We evaluated each model using a prediction threshold to maximize the accuracy and calculated performance metrics based on that threshold.
+We evaulated each model based on sequence level class assignments.
 Model performance for each model in shown in \tableref{tab:table2}.
-All performance metrics are based on the sequence level class assignments.
-% discuss sequence level stats (notes above)%
-
-In order to obtain a patient level class assignment assignments from the models,  %discuss%
+TF-IDF achieved AUC of 0.95 and accuracy f 0.84.
+The 20 words with the highest correlation coefficients using TF-IDF word vectorization are shown in Appendix B.
+While TF-IDF was able to identify the presence of a keyword or always pattern in a sequence, it was unable to leverage the context around each keyword match, which occasionally would negate the presence of CI.
+This led to the model over-zealously predicting sequences as demonstrating CI.
+ClincalBERT was able to overcome these issues due to its high complexity transformer architecture, and achieved AUC of 0.98 and accuracy of 0.93.
 
@@
     \toprule 
+    % add precision and recall, 
     \bfseries Model & \bfseries AUC & \bfseries Accuracy & \bfseries Sensitivity & \bfseries Specificity & \bfseries Micro F1  & \bfseries Macro F1 & \bfseries Weighted F1 \\ 
     \midrule
-    TF-IDF & 0.95 & 0.84 & 0.83 & 0.92 & 0.84 & 0.814 & 0.843 \\
+    TF-IDF & 0.95 & 0.84 & 0.83 & 0.92 & 0.84 & 0.81 & 0.84 \\
+    ClincialBERT & 0.98 & 0.93 & 0.91 & 0.96 & 0.93 & 0.92 & 0.93 \\
     \bottomrule
@@
 
+% \begin{figure*}[h!]
+% \label{fig:fig2}
+% \centering 
+% \includegraphics[scale = 0.75]{tfidf_patient_predictions.png}
+% \caption{Patient Predictions for TF-IDF}
+% \end{figure*}
+
 % Table 3 + 4 - Relation of Med/ICD Codes to Model Predictions
-\begin{table*}[hbtp]
-\floatconts
-{tab:table3}
-\centering 
-  {\begin{tabular}{cccccc}
-    \toprule 
-    \bfseries  & \bfseries Count & \bfseries Yes (\%) & \bfseries No/Ntr (\%)  & \bfseries Med/ICD Code (\%)  \\ 
-    \midrule
-    \bfseries{APOE ${\bm{\varepsilon}}$2} & \fseries 1754 & \fseries 0.15 & \fseries 0.85 & \fseries 0.11  \\
-    \bfseries{APOE ${\bm{\varepsilon}}$3} & \fseries 8751 & \fseries 0.15 & \fseries 0.85 & \fseries 0.11  \\
-    \bfseries{APOE ${\bm{\varepsilon}}$4} & \fseries 3436 & \fseries 0.18 & \fseries 0.82 & \fseries 0.17  \\
+% \begin{table*}[hbtp]
+% \floatconts
+% {tab:table3}
+% \centering 
+%   {\begin{tabular}{cccccc}
+%     \toprule 
+%     \bfseries  & \bfseries Count & \bfseries Yes (\%) & \bfseries No/Ntr (\%)  & \bfseries Med/ICD Code (\%)  \\ 
+%     \midrule
+%     \bfseries{APOE ${\bm{\varepsilon}}$2} & \fseries 1754 & \fseries 0.15 & \fseries 0.85 & \fseries 0.11  \\
+%     \bfseries{APOE ${\bm{\varepsilon}}$3} & \fseries 8751 & \fseries 0.15 & \fseries 0.85 & \fseries 0.11  \\
+%     \bfseries{APOE ${\bm{\varepsilon}}$4} & \fseries 3436 & \fseries 0.18 & \fseries 0.82 & \fseries 0.17  \\
 
-    \bottomrule
-  \end{tabular}}
-{\caption{Comparison between Other Indicators of Cognitive Impairment and TF-IDF}} \\
-\end{table*}
+%     \bottomrule
+%   \end{tabular}}
+% {\caption{Comparison between Other Indicators of Cognitive Impairment and TF-IDF}} \\
+% \end{table*}
 
@@
     \midrule
-    \bfseries{APOE ${\bm{\varepsilon}}$2} & \fseries 1754 & \fseries 0.15 & \fseries 0.85 & \fseries 0.11  \\
-    \bfseries{APOE ${\bm{\varepsilon}}$3} & \fseries 8751 & \fseries 0.15 & \fseries 0.85 & \fseries 0.11  \\
-    \bfseries{APOE ${\bm{\varepsilon}}$4} & \fseries 3436 & \fseries 0.18 & \fseries 0.82 & \fseries 0.17  \\
+    \bfseries{APOE ${\bm{\varepsilon}}$2} & \fseries 1754 & \fseries 0.17 & \fseries 0.83 & \fseries 0.11  \\
+    \bfseries{APOE ${\bm{\varepsilon}}$3} & \fseries 8751 & \fseries 0.17 & \fseries 0.83 & \fseries 0.11  \\
+    \bfseries{APOE ${\bm{\varepsilon}}$4} & \fseries 3436 & \fseries 0.21 & \fseries 0.79 & \fseries 0.17  \\
 
@@
 \end{table*}
+
+\begin{figure*}[h!]
+\label{fig:fig2}
+\centering 
+\includegraphics[scale = 0.75]{bert_patient_predictions.png}
+\caption{Patient Level Predictions for ClinicalBERT}
+\end{figure*}
 
@@
 \begin{figure}[h]
-\floatplacement{figure*}[h]
 \centering 
@@
 \end{table}
-\clearpage
+% \clearpage
 
@@
 \end{table}
+\clearpage
 

### 2021-09-08 Submission/Paper/ML4H/Paper.tex
mostly done with results section

@@
 TF-IDF achieved AUC of 0.95 and accuracy f 0.84.
-The 20 words with the highest correlation coefficients using TF-IDF word vectorization are shown in Appendix B.
+The 20 words with the highest correlation coefficients using TF-IDF word vectorization are shown in Appendix \ref{app:app3}.
 While TF-IDF was able to identify the presence of a keyword or always pattern in a sequence, it was unable to leverage the context around each keyword match, which occasionally would negate the presence of CI.
 This led to the model over-zealously predicting sequences as demonstrating CI.
-ClincalBERT was able to overcome these issues due to its high complexity transformer architecture, and achieved AUC of 0.98 and accuracy of 0.93.
+ClinicalBERT was able to overcome these issues due to its high complexity transformer architecture, and achieved AUC of 0.98 and accuracy of 0.93.
+In order to generate accurate patient level class assignments, we applied ClinicalBERT to 186,730 sequences from the N = 13,941 unique patients that were not patient of our training/validation/set sets.
+With these sequence level predictions, we generated patient level class assignments by empirically tuning a sequence threshold that represented the number of sequences predicted as Positive by ClinicalBERT.
+We identified the most optimal threshold by comparing the percentage of patients being predicted as having CI (stratified by APOE allele) to the percentages of patients with CI related Meds/ICD codes (also stratified by APOE allele).
+\tableref{tab:table4} shows the comparison of Med/ICD codes to ClinicalBERT patient level class assignments with a sequence threshold of 2.
 
@@
 % Appendix C
-\section{Top TF-IDF Word Features}
+\section{Top TF-IDF Word Features} \label{app:app3}
 \begin{table}[hbtp]

### 2021-09-08 Submission/Paper/ML4H/Paper.tex
results section done

@@
 We identified the most optimal threshold by comparing the percentage of patients being predicted as having CI (stratified by APOE allele) to the percentages of patients with CI related Meds/ICD codes (also stratified by APOE allele).
-\tableref{tab:table4} shows the comparison of Med/ICD codes to ClinicalBERT patient level class assignments with a sequence threshold of 2.
+\tableref{tab:table4} and \figureref{fig:fig2} shows the comparison of Med/ICD codes to ClinicalBERT patient level class assignments with a sequence threshold of 2.
+As shown, ClinicalBERT was able to identify a significant proportion of patients that went undetected by current clinical methods, highlighting the utility of such a tool in a clinical environment.
 
@@
 \section{Overview}
-\label{fig:fig2}
+\label{fig:fig3}
 \begin{figure}[h]

### 2021-09-08 Submission/Paper/ML4H/Paper.tex
reorganized figures and tables

@@
 
-\section{Dataset, Preprocessing, and Annotations}
-\label{sec:Dataset+Preprocessing+Annotations}
-
-\paragraph{Dataset}
-\label{sec:Dataset} Our gold-standard dataset consisted of a cohort (N = 16,428) of patients from the Mass General Brigham (MGB) HealthCare (formerly Partner's Healthcare, comprising two major academic hospitals, community hospitals, and community health centers in the Boston area) system who were older than 60 years (as of July 13, 2021) and had APOE genotype (biggest genetic risk factor for dementia) data available from the BioBank.
-Each patients' EHR record was then annotated by neurologists using a web-based annotation tool (UI Interface in Appendix A) as 1) Yes, i.e., patient has CI; 2) No i.e., Patient does not have CI; and 3) Neither i.e., sequence has no information on patient’s cognition.
-% link
-\figureref{fig:fig1} shows examples of example sequences for all 3 classes.
-
-% Figure 1 - Example Sequences
-\begin{figure*}[h!]
-\label{fig:fig1}
-\centering 
-\includegraphics[scale = 0.35]{Figure-1.png}
-\caption{Example Sequences}
-\end{figure*}
-
-\paragraph{Preprocessing}
-\label{sec:Preprocessing} For each patient in our gold-standard dataset, we extracted unstructured clinician notes, identified matches to dementia-related keywords (Appendix B), and constructed sequences from the note text around each of these matches (of length 800 characters).
-Our cohort of 16,428 patients had 279,224 sequences in total.
-
-\paragraph{Annotations}
-\label{sec:Annotations} We initially assigned 5,000 sequences diversified by keyword matches from 5,000 unique patients for neurologist labeling.
-In order to expedite annotations, we devised a scheme to known as "always patterns".
-An always pattern is defined as a phrase or regex expression that in any context indicates the phrase will be labeled with a particular class (i.e.
-yes, no, or neither).
-If an always pattern is inputted, all other sequences have language that matches with the phrase will be automatically labeled accordingly.
-
-The final dataset was split between train (95\%) and holdout test (5\%) sets, stratified across label and proportion of sequences annotated manually and through always patterns. % {Will change} % 
-Validation datasets were split from the train set using techniques described in the Methodology section. \tableref{tab:table1} shows demographics of the cohort of patients.
-
 %% Table 1 - Demographics of Dataset %%
@@
     }
+\end{table*}
+
+\section{Dataset, Preprocessing, and Annotations}
+\label{sec:Dataset+Preprocessing+Annotations}
+
+\paragraph{Dataset}
+\label{sec:Dataset} Our gold-standard dataset consisted of a cohort (N = 16,428) of patients from the Mass General Brigham (MGB) HealthCare (formerly Partner's Healthcare, comprising two major academic hospitals, community hospitals, and community health centers in the Boston area) system who were older than 60 years (as of July 13, 2021) and had APOE genotype (biggest genetic risk factor for dementia) data available from the BioBank.
+Each patients' EHR record was then annotated by neurologists using a web-based annotation tool (Appendix \ref{app:slat}) as 1) Yes, i.e., patient has CI; 2) No i.e., Patient does not have CI; and 3) Neither i.e., sequence has no information on patient’s cognition.
+% link
+\figureref{fig:example} in Appendix \ref{app:examples} shows examples of example sequences for all 3 classes.
+
+\paragraph{Preprocessing}
+\label{sec:Preprocessing} For each patient in our gold-standard dataset, we extracted unstructured clinician notes, identified matches to dementia-related keywords (Appendix \ref{app:keywords}), and constructed sequences from the note text around each of these matches (of length 800 characters).
+Our cohort of 16,428 patients had 279,224 sequences in total.
+
+\paragraph{Annotations}
+\label{sec:Annotations} We initially assigned 5,000 sequences diversified by keyword matches from 5,000 unique patients for neurologist labeling.
+In order to expedite annotations, we devised a scheme to known as "always patterns".
+An always pattern is defined as a phrase or regex expression that in any context indicates the phrase will be labeled with a particular class (i.e.
+yes, no, or neither).
+If an always pattern is inputted, all other sequences have language that matches with the phrase will be automatically labeled accordingly.
+
+The final dataset was split between train (95\%) and holdout test (5\%) sets, stratified across label and proportion of sequences annotated manually and through always patterns. % {Will change} % 
+Validation datasets were split from the train set using techniques described in the Methodology section. \tableref{tab:table1} shows demographics of the cohort of patients.
+
+% Table 2 - Results
+\begin{table*}[hbtp]
+\floatconts
+{tab:table2}
+  {\begin{tabular}{lcccccccc}
+    \toprule 
+    % add precision and recall, 
+    \bfseries Model & \bfseries AUC & \bfseries Accuracy & \bfseries Sensitivity & \bfseries Specificity & \bfseries Micro F1  & \bfseries Macro F1 & \bfseries Weighted F1 \\ 
+    \midrule
+    TF-IDF & 0.95 & 0.84 & 0.83 & 0.92 & 0.84 & 0.81 & 0.84 \\
+    ClincialBERT & 0.98 & 0.93 & 0.91 & 0.96 & 0.93 & 0.92 & 0.93 \\
+    \bottomrule
+  \end{tabular}}
+  {\caption{Model Performance}}
 \end{table*}
@@
 Model performance for each model in shown in \tableref{tab:table2}.
-TF-IDF achieved AUC of 0.95 and accuracy f 0.84.
+TF-IDF achieved AUC of 0.95 and accuracy of 0.84.
 The 20 words with the highest correlation coefficients using TF-IDF word vectorization are shown in Appendix \ref{app:app3}.
@@
 As shown, ClinicalBERT was able to identify a significant proportion of patients that went undetected by current clinical methods, highlighting the utility of such a tool in a clinical environment.
-
-% Table 2 - Results
-\begin{table*}[hbtp]
-\floatconts
-{tab:table2}
-  {\begin{tabular}{lcccccccc}
-    \toprule 
-    % add precision and recall, 
-    \bfseries Model & \bfseries AUC & \bfseries Accuracy & \bfseries Sensitivity & \bfseries Specificity & \bfseries Micro F1  & \bfseries Macro F1 & \bfseries Weighted F1 \\ 
-    \midrule
-    TF-IDF & 0.95 & 0.84 & 0.83 & 0.92 & 0.84 & 0.81 & 0.84 \\
-    ClincialBERT & 0.98 & 0.93 & 0.91 & 0.96 & 0.93 & 0.92 & 0.93 \\
-    \bottomrule
-  \end{tabular}}
-  {\caption{Model Performance}}
-\end{table*}
 
@@
 % Appendix B
+\section{Pictures of UI Interface for Annotations} 
+\label{app:slat}
+\begin{figure}[h]
+\centering 
+\caption{Pictures of UI Interface for Annotations}
+\end{figure}
+
+\clearpage
+
+\clearpage
+
+% Appendix B
 \section{Keywords} 
@@
 \end{table}
-% \clearpage
+
+\clearpage
+
+% Figure 1 - Example Sequences
+\section{Example Sequences} 
+\begin{figure}[h!] \label{app:examples}
+\centering 
+\includegraphics[scale = 0.35]{Figure-1.png}
+\caption{Example Sequences}
+\end{figure}
+\clearpage
 

### 2021-09-08 Submission/Paper/ML4H/Paper.tex
first draft of conclusion -- still short so will iterate more

@@
 % compare conf mat's for each model
-% distribution of CI/not CI labels
+% distribution of CI/not cognitive impairmentlabels
 % talk about different patient aggregation scheme
@@
 % Future plans include reducing false positives by gathering more annotated sequences and using deep learning natural language.
-Currently, many of our false positives are from the model identifying the presence of a keyword but struggling to understand the context around the keyword match; many of these contexts negate the presence of CI for the patient in question.
+Currently, many of our false positives are from the model identifying the presence of a keyword but struggling to understand the context around the keyword match; many of these contexts negate the presence of cognitive impairmentfor the patient in question.
 Deep Learning can leverage contextual information, making it promising for this task.
 
-We evaulated each model based on sequence level class assignments.
+We evaluated each model based on sequence level class assignments.
 Model performance for each model in shown in \tableref{tab:table2}.
@@
 With these sequence level predictions, we generated patient level class assignments by empirically tuning a sequence threshold that represented the number of sequences predicted as Positive by ClinicalBERT.
-We identified the most optimal threshold by comparing the percentage of patients being predicted as having CI (stratified by APOE allele) to the percentages of patients with CI related Meds/ICD codes (also stratified by APOE allele).
-\tableref{tab:table4} and \figureref{fig:fig2} shows the comparison of Med/ICD codes to ClinicalBERT patient level class assignments with a sequence threshold of 2.
+We identified the most optimal threshold by comparing the percentage of patients being predicted as having cognitive impairment(stratified by APOE allele) to the percentages of patients with cognitive impairment related Meds/ICD codes (also stratified by APOE allele).
+Appendix \ref{app:bert} shows the comparison of Med/ICD codes to ClinicalBERT patient level class assignments with a sequence threshold of 2.
 As shown, ClinicalBERT was able to identify a significant proportion of patients that went undetected by current clinical methods, highlighting the utility of such a tool in a clinical environment.
-
-% \begin{figure*}[h!]
-% \label{fig:fig2}
-% \centering 
-% \includegraphics[scale = 0.75]{tfidf_patient_predictions.png}
-% \caption{Patient Predictions for TF-IDF}
-% \end{figure*}
-
-% Table 3 + 4 - Relation of Med/ICD Codes to Model Predictions
-% \begin{table*}[hbtp]
-% \floatconts
-% {tab:table3}
-% \centering 
-%   {\begin{tabular}{cccccc}
-%     \toprule 
-%     \bfseries  & \bfseries Count & \bfseries Yes (\%) & \bfseries No/Ntr (\%)  & \bfseries Med/ICD Code (\%)  \\ 
-%     \midrule
-%     \bfseries{APOE ${\bm{\varepsilon}}$2} & \fseries 1754 & \fseries 0.15 & \fseries 0.85 & \fseries 0.11  \\
-%     \bfseries{APOE ${\bm{\varepsilon}}$3} & \fseries 8751 & \fseries 0.15 & \fseries 0.85 & \fseries 0.11  \\
-%     \bfseries{APOE ${\bm{\varepsilon}}$4} & \fseries 3436 & \fseries 0.18 & \fseries 0.82 & \fseries 0.17  \\
-
-%     \bottomrule
-%   \end{tabular}}
-% {\caption{Comparison between Other Indicators of Cognitive Impairment and TF-IDF}} \\
-% \end{table*}
-
-\begin{table*}[hbtp]
-\floatconts
-{tab:table4}
-\centering 
-    {\begin{tabular}{cccccc}
-    \toprule 
-    \bfseries  & \bfseries Count & \bfseries Yes (\%) & \bfseries No/Ntr (\%)  & \bfseries Med/ICD Code (\%) \\ 
-    \midrule
-    \bfseries{APOE ${\bm{\varepsilon}}$2} & \fseries 1754 & \fseries 0.17 & \fseries 0.83 & \fseries 0.11  \\
-    \bfseries{APOE ${\bm{\varepsilon}}$3} & \fseries 8751 & \fseries 0.17 & \fseries 0.83 & \fseries 0.11  \\
-    \bfseries{APOE ${\bm{\varepsilon}}$4} & \fseries 3436 & \fseries 0.21 & \fseries 0.79 & \fseries 0.17  \\
-
-    \bottomrule
-  \end{tabular}}
-  {\caption{Comparison between Other Indicators of Cognitive Impairment and Clinical-BERT}} \\
-\end{table*}
-
-\begin{figure*}[h!]
-\label{fig:fig2}
-\centering 
-\includegraphics[scale = 0.75]{bert_patient_predictions.png}
-\caption{Patient Level Predictions for ClinicalBERT}
-\end{figure*}
 
@@
 \section{Conclusion and Future Work} 
-\label{sec:ConclusionFutureWork} We applied innovative Machine Learning and Deep Learning NLP techniques to identify patients with cognitive impairment in EHR.
-Our work can help combat the issues of underdiagnosis and misdiagnosis for dementia.
-% {More coming soon } %
+\label{sec:ConclusionFutureWork} We applied NLP algorithms to identify patients with cognitive impairment in EHR and
+compared a machine learning model with a deep learning model on performance of sequence level class assignment predictions.
+Our work can help combat the issues of under-diagnosis and misdiagnosis for dementia.
+The the deep learning model's performance was significantly better than the machine learning model.
+We used the sequence level class assignments of the deep learning model to generate patient level class assignment by assigning a patient a label of cognitive impairment if their number of sequences predicted positive was greater than or equal to a empirically tuned threshold.
+However, a lack of patient level class assignments generated by annotators prevents us from measuring the true accuracy of our results.
+In order to fix this issue, we plan to gather 1000 patient level class assignments.
+We also plan to further improve the generalisability of our models by gathering more manually reviewed sequences.
+An active learning loop will be used to pick particular patients and sequences by using entropy score to label uncertain cases and UMAP clustering of ClinicalBERT word embeddings.
 
 \clearpage
+
 \appendix
@@
 
-\clearpage
-
-% Appendix B
+% Appendix C
 \section{Keywords} 
@@
         {\caption{Keywords indicative of Cognitive Impairment}} \\
-
 \end{table}
@@
 
-% Figure 1 - Example Sequences
+% Appendix D / Figure 1 - Example Sequences
 \section{Example Sequences} 
@@
 \end{figure}
+
 \clearpage
 
-% Appendix C
+% Appendix E
 \section{Top TF-IDF Word Features} \label{app:app3}
@@
 \end{table}
+
 \clearpage
 
+% \begin{figure*}[h!]
+% \label{fig:fig2}
+% \centering 
+% \includegraphics[scale = 0.75]{tfidf_patient_predictions.png}
+% \caption{Patient Predictions for TF-IDF}
+% \end{figure*}
+
+% Table 3 + 4 - Relation of Med/ICD Codes to Model Predictions
+% \begin{table*}[hbtp]
+% \floatconts
+% {tab:table3}
+% \centering 
+%   {\begin{tabular}{cccccc}
+%     \toprule 
+%     \bfseries  & \bfseries Count & \bfseries Yes (\%) & \bfseries No/Ntr (\%)  & \bfseries Med/ICD Code (\%)  \\ 
+%     \midrule
+%     \bfseries{APOE ${\bm{\varepsilon}}$2} & \fseries 1754 & \fseries 0.15 & \fseries 0.85 & \fseries 0.11  \\
+%     \bfseries{APOE ${\bm{\varepsilon}}$3} & \fseries 8751 & \fseries 0.15 & \fseries 0.85 & \fseries 0.11  \\
+%     \bfseries{APOE ${\bm{\varepsilon}}$4} & \fseries 3436 & \fseries 0.18 & \fseries 0.82 & \fseries 0.17  \\
+
+%     \bottomrule
+%   \end{tabular}}
+% {\caption{Comparison between Other Indicators of Cognitive Impairment and TF-IDF}} \\
+% \end{table*}
+
+\section{Assessment of ClinicalBERT Patient Level Class Assignments} \label{app:bert}
+
+\begin{table}[hbtp]
+\floatconts
+{tab:table4}
+\centering 
+    {\begin{tabular}{cccccc}
+    \toprule 
+    \bfseries  & \bfseries Count & \bfseries Yes (\%) & \bfseries No/Ntr (\%)  & \bfseries Med/ICD Code (\%) \\ 
+    \midrule
+    \bfseries{APOE ${\bm{\varepsilon}}$2} & \fseries 1754 & \fseries 0.17 & \fseries 0.83 & \fseries 0.11  \\
+    \bfseries{APOE ${\bm{\varepsilon}}$3} & \fseries 8751 & \fseries 0.17 & \fseries 0.83 & \fseries 0.11  \\
+    \bfseries{APOE ${\bm{\varepsilon}}$4} & \fseries 3436 & \fseries 0.21 & \fseries 0.79 & \fseries 0.17  \\
+
+    \bottomrule
+  \end{tabular}}
+  {\caption{Comparison between Other Indicators of Cognitive Impairment and Clinical-BERT}} \\
+\end{table}
+
+\begin{figure}[h!]
+\label{fig:fig2}
+\centering 
+\includegraphics[scale = 0.75]{bert_patient_predictions.png}
+\caption{Confusion Matrix Patient Level Prediction Counts for ClinicalBERT}
+\end{figure}
+
 \end{document}

### 2021-09-08 Submission/Paper/ML4H/Paper.tex
every section besides related works done; proofreading now

@@
 We also plan to further improve the generalisability of our models by gathering more manually reviewed sequences.
-An active learning loop will be used to pick particular patients and sequences by using entropy score to label uncertain cases and UMAP clustering of ClinicalBERT word embeddings.
+An active learning loop will be used to pick particular patients and sequences by using entropy score to label uncertain cases and UMAP clustering of ClinicalBERT word embeddings from the sequences of the N = 13,941 patients.
+The new gold-standard dataset will serve as the basis for the next iteration of the active learning loop to further improve model performance and detect patients with cognitive impairment at an earlier stage.
 

### 2021-09-08 Submission/Paper/ML4H/Paper.tex
first draft of paper done minus related works; proofreading done.

@@
 \hspace{10mm} Dementia is a neurodegenerative disorder that causes cognitive decline and affects more than 50 million people worldwide.
-Dementia is under-diagnosed by healthcare professionals—only one in four people who suffer from dementia are diagnosed.
+Dementia is under-diagnosed by healthcare professionals — only one in four people who suffer from dementia are diagnosed.
 Even when a diagnosis is made, it may not be entered as a structured diagnosis code in a patient’s charts.
@@
 In order to identify patients with cognitive impairment, we applied natural language processing (NLP) techniques.
-Model performance was compared to a baseline model that utilized structured features such as medication and ICD counts.
-% Add which model had highest performance %
+A machine learning and deep learning model were compared; the deep learning model significantly outperformed the former.
 \end{abstract}
@@
 \label{sec:RelatedWorks} 
+% To Be Done
 
@@
 \label{sec:Dataset} Our gold-standard dataset consisted of a cohort (N = 16,428) of patients from the Mass General Brigham (MGB) HealthCare (formerly Partner's Healthcare, comprising two major academic hospitals, community hospitals, and community health centers in the Boston area) system who were older than 60 years (as of July 13, 2021) and had APOE genotype (biggest genetic risk factor for dementia) data available from the BioBank.
-Each patients' EHR record was then annotated by neurologists using a web-based annotation tool (Appendix \ref{app:slat}) as 1) Yes, i.e., patient has CI; 2) No i.e., Patient does not have CI; and 3) Neither i.e., sequence has no information on patient’s cognition.
-% link
-\figureref{fig:example} in Appendix \ref{app:examples} shows examples of example sequences for all 3 classes.
+Each patients EHR record was then annotated by neurologists using a web-based annotation tool (Appendix \ref{app:slat}) as 1) Yes, i.e., patient has CI; 2) No i.e., Patient does not have CI; and 3) Neither i.e., sequence has no information on patient’s cognition.
+Appendix \ref{app:examples} shows examples of example sequences for all 3 classes.
 
@@
 yes, no, or neither).
-If an always pattern is inputted, all other sequences have language that matches with the phrase will be automatically labeled accordingly.
+If an always pattern is inputted, all other sequences that have language that matches with the phrase will be automatically labeled accordingly.
 
@@
 L1 Regularized logistic regression was applied with the annotated cognitive impairment labels.
-We used different correlation coefficients as thresholds to select features and iterated over different lambda values to determine the optimal lambda value and correlation coefficient threshold.
+We used 10-fold cross validation to select different correlation coefficients as thresholds to select features and iterated over different lambda values to determine the optimal lambda value and correlation coefficient threshold.
 
@@
 \label{sec:Transformer}  
-\paragraph{(2) Transformer Based Sequence Classification Language Model} We utilized a pre-trained language model called Clinical-BERT, which was trained on the MIMIC II database containing EHR records from ICU patients.
+\paragraph{(2) Transformer Based Sequence Classification Language Model} We utilized a pre-trained language model called ClinicalBERT, which was trained on the MIMIC II database containing EHR records from ICU patients.
 We used the implementation in the Huggingface Transformer and Simpletransformers packages.
@@
 The model was initialized with pre-trained parameters and later fine-tuned on our labeled training set.
-Optuna was used to perform a 20-trial study and tune the learning rate, adam epilson, and the number of train epochs on the held-out validation set.
+Optuna was used to perform a 20-trial study and tune the learning rate, adam epilson, and the number of train epochs on the held-out validation set to maximize AUC.
 
@@
 The 20 words with the highest correlation coefficients using TF-IDF word vectorization are shown in Appendix \ref{app:app3}.
-While TF-IDF was able to identify the presence of a keyword or always pattern in a sequence, it was unable to leverage the context around each keyword match, which occasionally would negate the presence of CI.
-This led to the model over-zealously predicting sequences as demonstrating CI.
-ClinicalBERT was able to overcome these issues due to its high complexity transformer architecture, and achieved AUC of 0.98 and accuracy of 0.93.
+While TF-IDF was able to identify the presence of a keyword or always pattern in a sequence, it was unable to leverage the context around each keyword match.
+The context would often contain useful information regarding a patient's cognitive status, and on occasion would negate the presence of cognitive impairment.
+This led to the model over-zealously predict sequences as demonstrating CI.
+ClinicalBERT was able to overcome these issues and leverage the meaning of the contexts due to its high complexity transformer architecture, resulting in an AUC of 0.98 and accuracy of 0.93.
 In order to generate accurate patient level class assignments, we applied ClinicalBERT to 186,730 sequences from the N = 13,941 unique patients that were not patient of our training/validation/set sets.
-With these sequence level predictions, we generated patient level class assignments by empirically tuning a sequence threshold that represented the number of sequences predicted as Positive by ClinicalBERT.
-We identified the most optimal threshold by comparing the percentage of patients being predicted as having cognitive impairment(stratified by APOE allele) to the percentages of patients with cognitive impairment related Meds/ICD codes (also stratified by APOE allele).
+With these sequence level predictions, we generated patient level class assignments by assigned patients a cognitive impairment label if their number of sequences predicted positive was greater than an empirically tuned a sequence threshold.
+We identified the most optimal threshold (from a range of 1 - 10) by comparing the percentage of patients being predicted as having cognitive impairment stratified by APOE allele to the percentages of patients with cognitive impairment related Meds/ICD codes stratified by APOE allele.
 Appendix \ref{app:bert} shows the comparison of Med/ICD codes to ClinicalBERT patient level class assignments with a sequence threshold of 2.
@@
 Our work can help combat the issues of under-diagnosis and misdiagnosis for dementia.
-The the deep learning model's performance was significantly better than the machine learning model.
+The deep learning model's performance was significantly better than the machine learning model.
 We used the sequence level class assignments of the deep learning model to generate patient level class assignment by assigning a patient a label of cognitive impairment if their number of sequences predicted positive was greater than or equal to a empirically tuned threshold.
 However, a lack of patient level class assignments generated by annotators prevents us from measuring the true accuracy of our results.
-In order to fix this issue, we plan to gather 1000 patient level class assignments.
+In order to fix this issue, we plan to gather 1000 patient level class assignments through our annotation tool.
 We also plan to further improve the generalisability of our models by gathering more manually reviewed sequences.
-An active learning loop will be used to pick particular patients and sequences by using entropy score to label uncertain cases and UMAP clustering of ClinicalBERT word embeddings from the sequences of the N = 13,941 patients.
+An active learning loop will be used to pick particular patients and sequences by using entropy scores to label uncertain cases and UMAP clustering of ClinicalBERT word embeddings on the sequences of the N = 13,941 patients.
 The new gold-standard dataset will serve as the basis for the next iteration of the active learning loop to further improve model performance and detect patients with cognitive impairment at an earlier stage.
@@
 
-% Appendix C
+% Appendix C / Figure 1 - Example Sequences
+\section{Example Sequences} 
+\begin{figure}[h!] \label{app:examples}
+\centering 
+\includegraphics[scale = 0.35]{Figure-1.png}
+\caption{Example Sequences}
+\end{figure}
+
+\clearpage
+
+% Appendix D
 \section{Keywords} 
@@
 \end{table}
-
-\clearpage
-
-% Appendix D / Figure 1 - Example Sequences
-\section{Example Sequences} 
-\begin{figure}[h!] \label{app:examples}
-\centering 
-\includegraphics[scale = 0.35]{Figure-1.png}
-\caption{Example Sequences}
-\end{figure}
-
 \clearpage

### 2021-09-12 Submission/Paper/ML4H/Paper.tex
slat pics and revised overview diagram

@@
 \jmlryear{2021}
-\jmlrsubmitted{201}
+\jmlrsubmitted{2021}
 \jmlrpublished{}
@@
  % The optional argument of \title is used in the header
-\title[NLP Techniques to Detect Cognitive Impairment]{Using Deep Learning to Identify Cognitive Impairment in Electronic Health Records}
+\title[NLP Techniques to Detect Cognitive Impairment]{Using Deep Learning to Identify Patients with Cognitive Impairment in Electronic Health Records}
 
@@
 Zhuoqiao Hong \SUP{1},
+Alberto Serrano-Pozo \SUP{1},
 Dimitry Propenko \SUP{1},
@@
 Dementia is under-diagnosed by healthcare professionals — only one in four people who suffer from dementia are diagnosed.
-Even when a diagnosis is made, it may not be entered as a structured diagnosis code in a patient’s charts.
-Information relevant to cognitive impairment is often found within electronic health records (EHR) but manual review of clinician notes by experts is both time consuming and often prone to errors.
-Automated mining of these notes presents an opportunity to label patients with cognitive impairment (CI) in real-world data.
-In order to identify patients with cognitive impairment, we applied natural language processing (NLP) techniques.
-A machine learning and deep learning model were compared; the deep learning model significantly outperformed the former.
+Even when a diagnosis is made, it may not be entered as a structured International Classification of Diseases (ICD) diagnosis code in a patient’s charts.
+Indeed, information relevant to cognitive impairment is often found within electronic health records (EHR) but manual review of clinician notes by experts is both time consuming and often prone to errors.
+Automated mining of these notes presents an opportunity to label patients with cognitive impairment (CI) in EHR data.
+We applied natural language processing (NLP) tools to identify patients with cognitive impairment and demonstrate that attention based deep learning model outperform other models.
 \end{abstract}
@@
 \section{Introduction}
-\label{sec:intro} The possibility of early diagnosis of dementia is important for improving clinical outcomes and patient management of dementia.
-Often, a diagnosis is given once patient has reached moderate dementia, but irreversible damage has already been done to the brain.
+\label{sec:intro} Dementia is the most common neurodegenerative disease affecting older adults, progressing from mild cognitive impairment (MCI) to mild, moderate, and severe dementia.
+Dementia is under-diagnosed: dementia is not formally diagnosed or coded in claims data for over 50\% of older adults living with probable dementia % needs citation %
+Often, a diagnosis is given once patient has reached moderate dementia, and irreversible damage has already been done to the brain, and 
 % https://www.dementiacarecentral.com/aboutdementia/facts/stages/ %
-Yet, dementia is not formally diagnosed or coded in claims data for over 50\% of older adults living with probable dementia.
-Tools that can efficiently and effectively analyze medical records for warning signs of dementia and recommend patients for follow up with a specialist can be critical to obtaining early diagnosis for dementia.
+The early detection of the first signs of cognitive impairment, however, is important for improving clinical outcomes and patient management.
+Tools that can efficiently and effectively analyze medical records for warning signs of dementia and recommend patients for follow up with a specialist can be critical to obtaining an early diagnosis for dementia.
+Such a tool could be also useful in recruiting into clinical trials as well as a variety of research studies ranging from in-silico trials for drug repurposing to evaluating how policies and programs meet the needs of patients and caregivers.
 We aim to use NLP to detect signs of cognitive impairment from unstructured clinician notes by using deep learning techniques.
+We apply our deep learning algorithm to patients in Mass General Brigham (MGB) Healthcare who have genotype data available from the MGB BioBank.
 An overview of our project can be found in Appendix A.
-
-\section{Related Works}
-\label{sec:RelatedWorks} 
-% To Be Done
 
@@
         {\caption{Demographics of Data}} \\
+
     }
 \end{table*}
+
+\section{Related Works}
+\label{sec:RelatedWorks} 
+Prior works have used NLP techniques to detect various diseases from EHR. Rajkmoar et al. % https://www.nature.com/articles/s41746-018-0029-1%22
+used recurrent neural networks (long short-term memory (LSTM)) among others to predict inpatient mortality using EHR data from the University of California, San Francisco (UCSF) from 2012 to 2016, and the University of Chicago Medicine (UCM) from 2009 to 2016.
+Glicksberg et al.
+% https://www.worldscientific.com/doi/epdf/10.1142/9789813235533_0014
+performed phenotyping for diseases such as Attention Deficit Hyperactivity Disorder (ADHD) by clustering on word2vec embeddings from EHR of the Mount Sinai Hospital (MSH) in New York City.
+These studies have shown that the application of NLP techniques to EHR have improved disease detection, and that NLP techniques can be applied to dementia detecton to achieve similar results.
+Our work uses deep learning NLP techniques, which has achieved impressive results when applied to general text due to the use of word embeddings and attention-based models, but has had limited applications in healthcare.
+%(Vaswani et al., 2017; Mikolov et al., 2013; Pennington et al., 2014; Peters et al., 2018; Devlin et al., 2018),
 
@@
 \paragraph{Dataset}
-\label{sec:Dataset} Our gold-standard dataset consisted of a cohort (N = 16,428) of patients from the Mass General Brigham (MGB) HealthCare (formerly Partner's Healthcare, comprising two major academic hospitals, community hospitals, and community health centers in the Boston area) system who were older than 60 years (as of July 13, 2021) and had APOE genotype (biggest genetic risk factor for dementia) data available from the BioBank.
-Each patients EHR record was then annotated by neurologists using a web-based annotation tool (Appendix \ref{app:slat}) as 1) Yes, i.e., patient has CI; 2) No i.e., Patient does not have CI; and 3) Neither i.e., sequence has no information on patient’s cognition.
-Appendix \ref{app:examples} shows examples of example sequences for all 3 classes.
+\label{sec:Dataset} Our dataset consisted of a cohort (N = 16,428) of patients from the Mass General Brigham (MGB) HealthCare (formerly Partner's Healthcare, comprising two major academic hospitals, community hospitals, and community health centers in the Boston area) system who were older than 60 years (as of July 13, 2021) and had APOE genotype (biggest genetic risk factor for dementia) data available from the MGB BioBank.
+\tableref{tab:table1} shows demographics of the cohort of patients.
 
 \paragraph{Preprocessing}
-\label{sec:Preprocessing} For each patient in our gold-standard dataset, we extracted unstructured clinician notes, identified matches to dementia-related keywords (Appendix \ref{app:keywords}), and constructed sequences from the note text around each of these matches (of length 800 characters).
-Our cohort of 16,428 patients had 279,224 sequences in total.
+\label{sec:Preprocessing} For each patient in our dataset, we extracted unstructured clinician notes, identified matches to dementia-related keywords (Appendix \ref{app:keywords}), and constructed sequences from the note text spanning each of these matches (of length 800 characters).
+Our cohort of 16,428 patients had 279,224 sequences with dementia-related keywords in total.
 
 \paragraph{Annotations}
-\label{sec:Annotations} We initially assigned 5,000 sequences diversified by keyword matches from 5,000 unique patients for neurologist labeling.
-In order to expedite annotations, we devised a scheme to known as "always patterns".
+\label{sec:Annotations} A subset of sequences was annotated for indication of cognitive impairment (CI) by experts using a web-based annotation tool (Appendix \ref{app:slat}) as 1) Yes, i.e., patient has CI; 2) No i.e., Patient does not have CI; and 3) Neither i.e., sequence has no information on patient’s cognition.
+Appendix \ref{app:examples} shows examples of example sequences for all 3 classes.
+We assigned 5,000 sequences containing at least one match to every keyword from 5,000 unique patients for  labeling.
+In order to expedite annotations, we utilized a scheme known as "always patterns".
 An always pattern is defined as a phrase or regex expression that in any context indicates the phrase will be labeled with a particular class (i.e.
 yes, no, or neither).
-If an always pattern is inputted, all other sequences that have language that matches with the phrase will be automatically labeled accordingly.
+Once an always pattern is defined, all other sequences that match the pattern are automatically labeled accordingly.
 
-The final dataset was split between train (95\%) and holdout test (5\%) sets, stratified across label and proportion of sequences annotated manually and through always patterns. % {Will change} % 
-Validation datasets were split from the train set using techniques described in the Methodology section. \tableref{tab:table1} shows demographics of the cohort of patients.
+The final dataset was split between train (90\%) and holdout test (10\%) sets, stratified across label and proportion of sequences annotated manually and through always patterns. % {Will change} % 
+Validation datasets were split from the train set using techniques described in the Methodology section.
 
@@
 \section{Methodology}
-\label{sec:Methodology}  
-% {We built 4 models and compared performance to the baseline model.
-It is important to note that these models were trained on binary labels, despite annotators labeling sequences with 3 classes.
-This was done because our overall task was to classify if a patient had CI, not whether a sequence indicates CI.
-% phrase better %
-% A label of neither does not pertain  patient can only be classified as having or not having CI.
-In order to convert this problem to binary labels, we aggregated no and neither labels to class 0 and yes labels to class 1.
-}
 
-% \label{sec:Baseline}  
-% \paragraph{(1) Baseline Model} We performed L1 regularized logistic regression where the cognitive concern label was regressed on the counts of medications, keyword counts, and ICD codes relevant to CI.
-The lambda value was selected through 10-fold Cross Validation (CV) to maximize the average area under the Receiver Operator Characteristic (ROC).
-% {To be implemented} %
+We developed two NLP models for the classification task and compared them to each other.
 
@@
 Optuna was used to perform a 20-trial study and tune the learning rate, adam epilson, and the number of train epochs on the held-out validation set to maximize AUC.
+An early stopping rule of 3 epochs was also used to prevent overfitting.
 
@@
 \label{sec:Results}
-% talk abt performance
-% which patients are correctly classified for each model
-% compare conf mat's for each model
-% distribution of CI/not cognitive impairmentlabels
-% talk about different patient aggregation scheme
-% address lack of not patient level labels
-% TFIDF might have lot of false positives b/c of use of vocab that doesn't discuss patient, deep learning will be able to use context
-% start with justification to aggregation to patient level
-% sensivity should hopefully improve, deep learning should reduce specificity b/c of use of contextual information
-% discuss if certain patients were predicted differently for all models
-% some ppl will be classified as 0, until deep learning, where it will be hopefully changed to 1
-% group of ppl who get 0 for baseline, prediction of 1 with tf-idf and deep
-% group of ppl who get 1 for tf-idf, 0 for deep learning b/c of high false positive rate, vocab cld be talking abt family member (tf-idf will address underdiagnosis, deep learning will address misdiagnosis better)
-% tf-idf is easy to "trigger", deep learning will evaulate based on context
-% Talk about Stats
-% TF-IDF model struggles with understanding context of words around keyword match
-% Future plans include reducing false positives by gathering more annotated sequences and using deep learning natural language.
-Currently, many of our false positives are from the model identifying the presence of a keyword but struggling to understand the context around the keyword match; many of these contexts negate the presence of cognitive impairmentfor the patient in question.
-Deep Learning can leverage contextual information, making it promising for this task.
+
+% (at what threshold?
+This gap is possible but odd if accuracy maximizing threshold Tanish -- I never tuned for a specific accuracy threshold.
+I don't know if you can tune for a threshold for multi-class problems because a particular sequence could have a max probability that isn't above the threshold, but since there are more than 2 classes, it is foggy regarding which class that sequence will now go in.
+But I think the discrepancy in the numbers is because the sequences that TF-IDF got wrong were never corrected like they were for BERT.).
+
+%  (not necessarily true, it just has the CAPACITY to do this but we haven't proved so Tanish -- How do we go about proving this?)
 
@@
 The 20 words with the highest correlation coefficients using TF-IDF word vectorization are shown in Appendix \ref{app:app3}.
-While TF-IDF was able to identify the presence of a keyword or always pattern in a sequence, it was unable to leverage the context around each keyword match.
-The context would often contain useful information regarding a patient's cognitive status, and on occasion would negate the presence of cognitive impairment.
-This led to the model over-zealously predict sequences as demonstrating CI.
+While TF-IDF was able to identify the presence of a keyword or always pattern in a sequence, it was unable to leverage the order of words around each keyword match.
+The order of words often contained useful information regarding a patient's cognitive status, and on occasion would negate the presence of cognitive impairment.
+This led to the model over-zealously predict sequences as demonstrating cognitive impairment, resulting in a large count of false positives.
 ClinicalBERT was able to overcome these issues and leverage the meaning of the contexts due to its high complexity transformer architecture, resulting in an AUC of 0.98 and accuracy of 0.93.
 In order to generate accurate patient level class assignments, we applied ClinicalBERT to 186,730 sequences from the N = 13,941 unique patients that were not patient of our training/validation/set sets.
-With these sequence level predictions, we generated patient level class assignments by assigned patients a cognitive impairment label if their number of sequences predicted positive was greater than an empirically tuned a sequence threshold.
-We identified the most optimal threshold (from a range of 1 - 10) by comparing the percentage of patients being predicted as having cognitive impairment stratified by APOE allele to the percentages of patients with cognitive impairment related Meds/ICD codes stratified by APOE allele.
-Appendix \ref{app:bert} shows the comparison of Med/ICD codes to ClinicalBERT patient level class assignments with a sequence threshold of 2.
-As shown, ClinicalBERT was able to identify a significant proportion of patients that went undetected by current clinical methods, highlighting the utility of such a tool in a clinical environment.
+With these sequence level predictions, we generated patient level class assignments by assigning patients a cognitive impairment label if their number of sequences predicted positive was greater than an empirically tuned threshold.
+We identified the most optimal threshold (from a range of 1 - 10) by comparing the percentage of patients being predicted as having cognitive impairment stratified by APOE allele to the percentages of patients with cognitive impairment related Meds/ICD codes stratified by APOE allele (MED/ICD code column in Table \ref{tab:bert}) .
+Table \ref{tab:bert} shows the comparison of Med/ICD codes to ClinicalBERT patient level class assignments with a sequence threshold of 2.
+As shown, ClinicalBERT was able to identify a significant proportion of patients that went undetected by current clinical methods, highlighting the utility of such a tool in a clinical setting.
+
+% \section{Assessment of ClinicalBERT Patient Level Class Assignments}
+
+\begin{table*}[hbtp]
+\label{tab:bert}
+\floatconts
+{tab:table3}
+\centering 
+    {\begin{tabular}{cccccc}
+    \toprule 
+    \bfseries  & \bfseries Count & \bfseries Yes (\%) & \bfseries No/Ntr (\%)  & \bfseries Med/ICD Code (\%) \\ 
+    \midrule
+    \bfseries{APOE ${\bm{\varepsilon}}$2} & \fseries 1754 & \fseries 0.17 & \fseries 0.83 & \fseries 0.11  \\
+    \bfseries{APOE ${\bm{\varepsilon}}$3} & \fseries 8751 & \fseries 0.17 & \fseries 0.83 & \fseries 0.11  \\
+    \bfseries{APOE ${\bm{\varepsilon}}$4} & \fseries 3436 & \fseries 0.21 & \fseries 0.79 & \fseries 0.17  \\
+
+    \bottomrule
+  \end{tabular}}
+  {\caption{Comparison between Other Indicators of Cognitive Impairment and ClinicalBERT}} \\
+\end{table*}
+
+\begin{figure*}[h!]
+\label{fig:fig2}
+\centering 
+\includegraphics[scale = 0.75]{bert_patient_predictions.png}
+\caption{Confusion Matrix Patient Level Prediction Counts for ClinicalBERT}
+\end{figure*}
 
@@
 \label{sec:ConclusionFutureWork} We applied NLP algorithms to identify patients with cognitive impairment in EHR and
-compared a machine learning model with a deep learning model on performance of sequence level class assignment predictions.
+compared a baseline machine learning model with an attention based deep learning model on performance of sequence level class assignment predictions.
 Our work can help combat the issues of under-diagnosis and misdiagnosis for dementia.
@@
 In order to fix this issue, we plan to gather 1000 patient level class assignments through our annotation tool.
-We also plan to further improve the generalisability of our models by gathering more manually reviewed sequences.
+We also plan to further improve the generalizability of our models by gathering more manually annotated sequences.
 An active learning loop will be used to pick particular patients and sequences by using entropy scores to label uncertain cases and UMAP clustering of ClinicalBERT word embeddings on the sequences of the N = 13,941 patients.
@@
 \centering 
-\includegraphics[scale = 0.14]{Overview.png}
+\includegraphics[scale = 0.30]{APOE SLAT Overview.png}
 \caption{Overview}
@@
 \centering 
-\caption{Pictures of UI Interface for Annotations}
+\includegraphics[scale = 0.43]{slat_picture_1.png}
+\caption{Annotation UI}
+\end{figure}
+
+\label{app:slat}
+\begin{figure}[h]
+\centering 
+\includegraphics[scale = 0.3]{slat_picture_2.png}
+\caption{Always Pattern List Generated by Annotations}
 \end{figure}
@@
 \end{table}
-\clearpage
 
@@
   \end{tabular}}
+  {\caption{Top 20 TF-IDF Word Features and their Correlation Coefficient}}
 \end{table}
-
-\clearpage
 
@@
 
-\section{Assessment of ClinicalBERT Patient Level Class Assignments} \label{app:bert}
-
-\begin{table}[hbtp]
-\floatconts
-{tab:table4}
-\centering 
-    {\begin{tabular}{cccccc}
-    \toprule 
-    \bfseries  & \bfseries Count & \bfseries Yes (\%) & \bfseries No/Ntr (\%)  & \bfseries Med/ICD Code (\%) \\ 
-    \midrule
-    \bfseries{APOE ${\bm{\varepsilon}}$2} & \fseries 1754 & \fseries 0.17 & \fseries 0.83 & \fseries 0.11  \\
-    \bfseries{APOE ${\bm{\varepsilon}}$3} & \fseries 8751 & \fseries 0.17 & \fseries 0.83 & \fseries 0.11  \\
-    \bfseries{APOE ${\bm{\varepsilon}}$4} & \fseries 3436 & \fseries 0.21 & \fseries 0.79 & \fseries 0.17  \\
-
-    \bottomrule
-  \end{tabular}}
-  {\caption{Comparison between Other Indicators of Cognitive Impairment and Clinical-BERT}} \\
-\end{table}
-
-\begin{figure}[h!]
-\label{fig:fig2}
-\centering 
-\includegraphics[scale = 0.75]{bert_patient_predictions.png}
-\caption{Confusion Matrix Patient Level Prediction Counts for ClinicalBERT}
-\end{figure}
-
 \end{document}

### 2021-09-12 Submission/Paper/ML4H/Paper.tex
authors added

@@
 Alberto Serrano-Pozo \SUP{1},
-Dimitry Propenko \SUP{1},
-Rudy E. Tanzi \SUP{1},
+Dimitry Prokopenko \SUP{1},
+Rudy E. Tanzi \SUP{2},
 Deborah Blacker \SUP{1},
@@
 anoori1,
-...
+mdeodhar,
+zhong1,
+aserrano1,
+dprokopenko,
+dblacker,
+bhyman,
+smukerji,
+mwestover,
 sdas5\}
 @mgh.harvard.edu}
+\centering \Email{
+\\[\bigskipamount] 
+\SUP{2}\{tanzi
+\}@helix.mgh.harvard.edu
+}
 % 

### 2021-09-12 Submission/Paper/ML4H/Paper.tex
corrected table 5 to table 3

@@
 \\[\bigskipamount] 
-\SUP{2}\{tanzi
-\}@helix.mgh.harvard.edu
+\SUP{2}\{tanzi\}@helix.mgh.harvard.edu
 }
@@
 We apply our deep learning algorithm to patients in Mass General Brigham (MGB) Healthcare who have genotype data available from the MGB BioBank.
-An overview of our project can be found in Appendix A.
+An overview of our project can be found in Appendix \ref{app:overview}.
 
@@
 {tab:table2}
-  {\begin{tabular}{lcccccccc}
+\centering
+  {
+  \begin{tabular}{lcccccccc}
     \toprule 
@@
     \bottomrule
-  \end{tabular}}
-  {\caption{Model Performance}}
+  \end{tabular}
+  }
+  {\caption{Model Performance}} \\
 \end{table*}
@@
 With these sequence level predictions, we generated patient level class assignments by assigning patients a cognitive impairment label if their number of sequences predicted positive was greater than an empirically tuned threshold.
-We identified the most optimal threshold (from a range of 1 - 10) by comparing the percentage of patients being predicted as having cognitive impairment stratified by APOE allele to the percentages of patients with cognitive impairment related Meds/ICD codes stratified by APOE allele (MED/ICD code column in Table \ref{tab:bert}) .
+We identified the most optimal threshold (from a range of 1 - 10) by comparing the percentage of patients being predicted as having cognitive impairment stratified by APOE allele to the percentages of patients with cognitive impairment related Meds/ICD codes stratified by APOE allele (MED/ICD code column in Table \ref{tab:bert}).
 Table \ref{tab:bert} shows the comparison of Med/ICD codes to ClinicalBERT patient level class assignments with a sequence threshold of 2.
@@
 \begin{table*}[hbtp]
-\label{tab:bert}
 \floatconts
-{tab:table3}
+
 \centering 
     {\begin{tabular}{cccccc}
+
     \toprule 
@@
   \end{tabular}}
-  {\caption{Comparison between Other Indicators of Cognitive Impairment and ClinicalBERT}} \\
+  \caption{Comparison between Other Indicators of Cognitive Impairment and ClinicalBERT}
+\label{tab:bert}
 \end{table*}
@@
 \section{Overview}
-\label{fig:fig3}
-\begin{figure}[h]
+\begin{figure}[h] \label{app:overview}
 \centering 
@@
 \caption{Overview}
+
 \end{figure}
@@
 
-\label{app:slat}
 \begin{figure}[h]

### 2021-09-12 Submission/Paper/ML4H/Paper.tex
fixed latex table mislabeling

@@
 {tab:table2}
+{\caption{Model Performance}}
 \centering
@@
   }
-  {\caption{Model Performance}} \\
+
+  \label{tab:modelperf}
 \end{table*}
@@
 We evaluated each model based on sequence level class assignments.
-Model performance for each model in shown in \tableref{tab:table2}.
+Model performance for each model in shown in Table \ref{tab:modelperf}.
 TF-IDF achieved AUC of 0.95 and accuracy of 0.84.
@@
 With these sequence level predictions, we generated patient level class assignments by assigning patients a cognitive impairment label if their number of sequences predicted positive was greater than an empirically tuned threshold.
-We identified the most optimal threshold (from a range of 1 - 10) by comparing the percentage of patients being predicted as having cognitive impairment stratified by APOE allele to the percentages of patients with cognitive impairment related Meds/ICD codes stratified by APOE allele (MED/ICD code column in Table \ref{tab:bert}).
-Table \ref{tab:bert} shows the comparison of Med/ICD codes to ClinicalBERT patient level class assignments with a sequence threshold of 2.
+We identified the most optimal threshold (from a range of 1 - 10) by comparing the percentage of patients being predicted as having cognitive impairment stratified by APOE allele to the percentages of patients with cognitive impairment related Meds/ICD codes stratified by APOE allele (MED/ICD code column in Table \tableref{tab:bert}).
+\tableref{tab:bert} shows the comparison of Med/ICD codes to ClinicalBERT patient level class assignments with a sequence threshold of 2.
 As shown, ClinicalBERT was able to identify a significant proportion of patients that went undetected by current clinical methods, highlighting the utility of such a tool in a clinical setting.
@@
 \floatconts
-
+{tab:bert}
+{\caption{Comparison between Other Indicators of Cognitive Impairment and ClinicalBERT}}
 \centering 
@@
   \end{tabular}}
-  \caption{Comparison between Other Indicators of Cognitive Impairment and ClinicalBERT}
-\label{tab:bert}
 \end{table*}

### 2021-09-12 Submission/Paper/ML4H/Paper.tex
made table captions consistent
citations blueprint

@@
 \label{sec:intro} Dementia is the most common neurodegenerative disease affecting older adults, progressing from mild cognitive impairment (MCI) to mild, moderate, and severe dementia.
-Dementia is under-diagnosed: dementia is not formally diagnosed or coded in claims data for over 50\% of older adults living with probable dementia % needs citation %
+Dementia is under-diagnosed: dementia is not formally diagnosed or coded in claims data for over 50\% of older adults living with probable dementia.
 Often, a diagnosis is given once patient has reached moderate dementia, and irreversible damage has already been done to the brain, and
@@
 \begin{table*}[hbtp]
+\centering 
 \floatconts
 {tab:table1}
-\centering 
+{\caption{Demographics of Data}} 
     {
@@
         \end{tabular}
-        {\caption{Demographics of Data}} \\
-
     }
@@
 \begin{table*}[hbtp]
+\centering 
 \floatconts
@@
 {\caption{Comparison between Other Indicators of Cognitive Impairment and ClinicalBERT}}
-\centering 
+
     {\begin{tabular}{cccccc}
@@
 The new gold-standard dataset will serve as the basis for the next iteration of the active learning loop to further improve model performance and detect patients with cognitive impairment at an earlier stage.
+
+\clearpage
+
+% References
+
+\bibliography{jmlr-sample}
+\nocite{*}
+% \citet{rajkomar2018scalable}
 

### 2021-09-12 Submission/Paper/ML4H/Paper.tex
first round of citations

@@
 \label{sec:RelatedWorks} 
-Prior works have used NLP techniques to detect various diseases from EHR. Rajkmoar et al. % https://www.nature.com/articles/s41746-018-0029-1%22
+Prior works have used NLP techniques to detect various diseases from EHR. \citep{rajkomar2018scalable} % https://www.nature.com/articles/s41746-018-0029-1%22
 used recurrent neural networks (long short-term memory (LSTM)) among others to predict inpatient mortality using EHR data from the University of California, San Francisco (UCSF) from 2012 to 2016, and the University of Chicago Medicine (UCM) from 2009 to 2016.
-Glicksberg et al.
-% https://www.worldscientific.com/doi/epdf/10.1142/9789813235533_0014
+\citep{glicksberg2018automated} % https://www.worldscientific.com/doi/epdf/10.1142/9789813235533_0014
 performed phenotyping for diseases such as Attention Deficit Hyperactivity Disorder (ADHD) by clustering on word2vec embeddings from EHR of the Mount Sinai Hospital (MSH) in New York City.
 These studies have shown that the application of NLP techniques to EHR have improved disease detection, and that NLP techniques can be applied to dementia detecton to achieve similar results.
-Our work uses deep learning NLP techniques, which has achieved impressive results when applied to general text due to the use of word embeddings and attention-based models, but has had limited applications in healthcare.
+Our work uses deep learning NLP techniques, which has achieved impressive results when applied to general text due to the use of word embeddings and attention-based models \citep{vaswani2017attention,mikolov2013distributed,pennington2014glove,peters2018deep, devlin2018bert}, but have had limited applications in healthcare.
 %(Vaswani et al., 2017; Mikolov et al., 2013; Pennington et al., 2014; Peters et al., 2018; Devlin et al., 2018),
@@
 \paragraph{(1) Logistic Regression with TF-IDF Vectors} We performed TF-IDF (term frequency-inverse document frequency) vectorization on the annotated sequences and selected features based on a term's Pearson correlation coefficient with the outcome.
-L1 Regularized logistic regression was applied with the annotated cognitive impairment labels.
+L1 Regularized logistic regression \citep{tibshirani1996regression} was applied with the annotated cognitive impairment labels.
 We used 10-fold cross validation to select different correlation coefficients as thresholds to select features and iterated over different lambda values to determine the optimal lambda value and correlation coefficient threshold.
@@
 \label{sec:Transformer}  
-\paragraph{(2) Transformer Based Sequence Classification Language Model} We utilized a pre-trained language model called ClinicalBERT, which was trained on the MIMIC II database containing EHR records from ICU patients.
-We used the implementation in the Huggingface Transformer and Simpletransformers packages.
+\paragraph{(2) Transformer Based Sequence Classification Language Model} We utilized a pre-trained language model called ClinicalBERT \citep{alsentzer2019publicly}, which was trained on the MIMIC II database containing EHR records from ICU patients.
+We used the implementation in the Huggingface Transformer \citep{Wolf2019HuggingFacesTS} and Simpletransformers \citep{simple2020thilina} packages.
 After text preprocessing, input texts were tokenized with the default tokenizer and converted to embeddings.
 The model was initialized with pre-trained parameters and later fine-tuned on our labeled training set.
-Optuna was used to perform a 20-trial study and tune the learning rate, adam epilson, and the number of train epochs on the held-out validation set to maximize AUC.
+Optuna \citep{akiba2019optuna} was used to perform a 20-trial study and tune the learning rate, adam epilson, and the number of train epochs on the held-out validation set to maximize AUC.
 An early stopping rule of 3 epochs was also used to prevent overfitting.

### 2021-09-14 Submission/Paper/ML4H/Paper.tex
almost at word count

@@
 
-\author{Tanish Tyagi \nametag{\thanks{Authors contributed equally}\SUP{1}},
-Colin G. Magdamo\nametag{\footnotemark[1]\SUP{1}}, 
-Ayush Noori \SUP{1},
-Mayuresh Deodhar \SUP{1},
-Zhuoqiao Hong \SUP{1},
-Alberto Serrano-Pozo \SUP{1},
-Dimitry Prokopenko \SUP{1},
-Rudy E. Tanzi \SUP{2},
-Deborah Blacker \SUP{1},
-Bradley T. Hyman \SUP{1},
-Shibani S. Mukerji \SUP{1},
-M. Brandon Westover \SUP{1},
-Sudeshna Das\SUP{1},
-\centering \Email{
-\\[\bigskipamount] 
-\SUP{1}\{ttyagi, 
-cmagdamo,
-anoori1,
-mdeodhar,
-zhong1,
-aserrano1,
-dprokopenko,
-dblacker,
-bhyman,
-smukerji,
-mwestover,
-sdas5\}
-@mgh.harvard.edu}
-\centering \Email{
-\\[\bigskipamount] 
-\SUP{2}\{tanzi\}@helix.mgh.harvard.edu
-}
+% \author{Tanish Tyagi \nametag{\thanks{Authors contributed equally}\SUP{1}},
+% Colin G. Magdamo\nametag{\footnotemark[1]\SUP{1}}, 
+% Ayush Noori \SUP{1},
+% Mayuresh Deodhar \SUP{1},
+% Zhuoqiao Hong \SUP{1},
+% Alberto Serrano-Pozo \SUP{1},
+% Dimitry Prokopenko \SUP{1},
+% Rudy E. Tanzi \SUP{2},
+% Deborah Blacker \SUP{1},
+% Bradley T. Hyman \SUP{1},
+% Shibani S. Mukerji \SUP{1},
+% M. Brandon Westover \SUP{1},
+% Sudeshna Das\SUP{1},
+% \centering \Email{
+% \\[\bigskipamount] 
+% \SUP{1}\{ttyagi, 
+% cmagdamo,
+% anoori1,
+% mdeodhar,
+% zhong1,
+% aserrano1,
+% dprokopenko,
+% dblacker,
+% bhyman,
+% smukerji,
+% mwestover,
+% sdas5\}
+% @mgh.harvard.edu}
+% \centering \Email{
+% \\[\bigskipamount] 
+% \SUP{2}\{tanzi\}@helix.mgh.harvard.edu
+% }
 % 
-\begin{center}\addr Massachusetts General Hospital, Boston, MA\end{center}
-}
+% \begin{center}\addr Massachusetts General Hospital, Boston, MA\end{center}
+% }
 
@@
 Even when a diagnosis is made, it may not be entered as a structured International Classification of Diseases (ICD) diagnosis code in a patient’s charts.
-Indeed, information relevant to cognitive impairment is often found within electronic health records (EHR) but manual review of clinician notes by experts is both time consuming and often prone to errors.
-Automated mining of these notes presents an opportunity to label patients with cognitive impairment (CI) in EHR data.
-We applied natural language processing (NLP) tools to identify patients with cognitive impairment and demonstrate that attention based deep learning model outperform other models.
+Indeed, information relevant to cognitive impairment (CI) is often found within electronic health records (EHR) but manual review of clinician notes by experts is both time consuming and often prone to errors.
+Automated mining of these notes presents an opportunity to label patients with cognitive impairment in EHR data.
+We developed natural language processing (NLP) tools to identify patients with cognitive impairment and demonstrate that linguistic context enhances performance for the classification task.
+We fine-tuned our attention based deep learning model, which can learn from complex language structures, and substantially improved accuracy (0.93) relative to a baseline NLP model (0.84).
+Further, we show that deep learning NLP can successfully identify dementia patients without dementia-related ICD codes or medications.
 \end{abstract}
@@
 Dementia is under-diagnosed: dementia is not formally diagnosed or coded in claims data for over 50\% of older adults living with probable dementia.
-Often, a diagnosis is given once patient has reached moderate dementia, and irreversible damage has already been done to the brain, and
+Often, a diagnosis is given once patient has reached moderate dementia, and irreversible damage has already been done to the brain.
 % https://www.dementiacarecentral.com/aboutdementia/facts/stages/ %
@@
 Tools that can efficiently and effectively analyze medical records for warning signs of dementia and recommend patients for follow up with a specialist can be critical to obtaining an early diagnosis for dementia.
-Such a tool could be also useful in recruiting into clinical trials as well as a variety of research studies ranging from in-silico trials for drug repurposing to evaluating how policies and programs meet the needs of patients and caregivers.
+Such a tool could also be useful in recruiting into clinical trials as well as a variety of research studies ranging from in-silico trials for drug repurposing to evaluating how policies and programs meet the needs of patients and caregivers.
 We aim to use NLP to detect signs of cognitive impairment from unstructured clinician notes by using deep learning techniques.
@@
 These studies have shown that the application of NLP techniques to EHR have improved disease detection, and that NLP techniques can be applied to dementia detecton to achieve similar results.
-Our work uses deep learning NLP techniques, which has achieved impressive results when applied to general text due to the use of word embeddings and attention-based models \citep{vaswani2017attention,mikolov2013distributed,pennington2014glove,peters2018deep, devlin2018bert}, but have had limited applications in healthcare.
-%(Vaswani et al., 2017; Mikolov et al., 2013; Pennington et al., 2014; Peters et al., 2018; Devlin et al., 2018),
+Our work uses deep learning NLP techniques, which has achieved impressive results when applied to general text due to the use of word embeddings and attention-based models \citep{vaswani2017attention,mikolov2013distributed,pennington2014glove,peters2018deep, devlin2018bert}, but have had limited applications in healthcare, particularly in dementia research.
 
@@
 \paragraph{Dataset}
-\label{sec:Dataset} Our dataset consisted of a cohort (N = 16,428) of patients from the Mass General Brigham (MGB) HealthCare (formerly Partner's Healthcare, comprising two major academic hospitals, community hospitals, and community health centers in the Boston area) system who were older than 60 years (as of July 13, 2021) and had APOE genotype (biggest genetic risk factor for dementia) data available from the MGB BioBank.
+\label{sec:Dataset} Our dataset consisted of a cohort (N = 16,428) of patients from the Mass General Brigham (MGB) HealthCare (formerly Partner's Healthcare, comprising two major academic hospitals, community hospitals, and community health centers in the Boston area) system who were older than 60 years (as of July 13, 2021), had APOE genotype \citep{mahley2000apolipoprotein} (biggest genetic risk factor for dementia) data available from the MGB BioBank, and at least one clinician note with a dementia-related keyword.
 \tableref{tab:table1} shows demographics of the cohort of patients.
@@
 \paragraph{Preprocessing}
-\label{sec:Preprocessing} For each patient in our dataset, we extracted unstructured clinician notes, identified matches to dementia-related keywords (Appendix \ref{app:keywords}), and constructed sequences from the note text spanning each of these matches (of length 800 characters).
+\label{sec:Preprocessing} For each patient in our dataset, we extracted unstructured clinician notes, identified matches to 18 dementia-related keywords (Appendix \ref{app:keywords}, including those related to memory, cognition, neuropsychological tests, and dementia diagnoses.
+We constructed sequences from the note text spanning each of these matches (of length 800 characters).
 Our cohort of 16,428 patients had 279,224 sequences with dementia-related keywords in total.
@@
 \paragraph{Annotations}
-\label{sec:Annotations} A subset of sequences was annotated for indication of cognitive impairment (CI) by experts using a web-based annotation tool (Appendix \ref{app:slat}) as 1) Yes, i.e., patient has CI; 2) No i.e., Patient does not have CI; and 3) Neither i.e., sequence has no information on patient’s cognition.
+\label{sec:Annotations} A subset of sequences was annotated for indication of cognitive impairments.
+We defined cognitive impairment as evidence of MCI, where one cognitive domain is involved, or dementia, where more than one cognitive domain is involved and activities of daily living are affected.
+Concern from the family of the patient or the patient was not considered as cognitive impairment.
+Experts annotated sequences using a web-based annotation tool (Appendix \ref{app:slat}) as 1) Yes, i.e., patient has CI; 2) No i.e., Patient does not have CI; and 3) Neither i.e., sequence has no information on patient’s cognition.
 Appendix \ref{app:examples} shows examples of example sequences for all 3 classes.
-We assigned 5,000 sequences containing at least one match to every keyword from 5,000 unique patients for  labeling.
-In order to expedite annotations, we utilized a scheme known as "always patterns".
+
+We assigned 5,000 diverse sequences containing at least one match to every keyword from 5,000 unique patients for labeling.
+In order to expedite annotations, we utilized an “always pattern" scheme.
 An always pattern is defined as a phrase or regex expression that in any context indicates the phrase will be labeled with a particular class (i.e.
 yes, no, or neither).
-Once an always pattern is defined, all other sequences that match the pattern are automatically labeled accordingly.
+Once an always pattern is defined, all other sequences that match the pattern are automatically labeled with that always pattern's class.
+For examples of always patterns for all three classes (Yes, No, Neither), see Appendix \ref{app:examples}.
 
-The final dataset was split between train (90\%) and holdout test (10\%) sets, stratified across label and proportion of sequences annotated manually and through always patterns. % {Will change} % 
+The final dataset of 8,656 annotated sequences from N = 2,487 unique patients was split between train (90\%) and holdout test (10\%) sets, stratified across label and proportion of sequences annotated manually and through always patterns.
 Validation datasets were split from the train set using techniques described in the Methodology section.
@@
 L1 Regularized logistic regression \citep{tibshirani1996regression} was applied with the annotated cognitive impairment labels.
-We used 10-fold cross validation to select different correlation coefficients as thresholds to select features and iterated over different lambda values to determine the optimal lambda value and correlation coefficient threshold.
-
-% \label{sec:Baseline+TFIDF}  
-% \paragraph{(3) Model 1 + Model 2} % {TBD} %
+We used 10-fold cross validation to determine the optimal lambda value and correlation coefficient threshold to select features.
 
 \label{sec:Transformer}  
-\paragraph{(2) Transformer Based Sequence Classification Language Model} We utilized a pre-trained language model called ClinicalBERT \citep{alsentzer2019publicly}, which was trained on the MIMIC II database containing EHR records from ICU patients.
-We used the implementation in the Huggingface Transformer \citep{Wolf2019HuggingFacesTS} and Simpletransformers \citep{simple2020thilina} packages.
+\paragraph{(2) Transformer Based Sequence Classification Language Model} We utilized a pre-trained language model called ClinicalBERT \citep{alsentzer2019publicly}, which was trained on the MIMIC II \citep{saeed2011multiparameter} database containing EHR records from ICU patients.
+We used the implementation in the Huggingface Transformers \citep{Wolf2019HuggingFacesTS} and Simpletransformers \citep{simple2020thilina} packages.
 After text preprocessing, input texts were tokenized with the default tokenizer and converted to embeddings.
@@
 Optuna \citep{akiba2019optuna} was used to perform a 20-trial study and tune the learning rate, adam epilson, and the number of train epochs on the held-out validation set to maximize AUC.
-An early stopping rule of 3 epochs was also used to prevent overfitting.
+An early stopping rule was used to prevent overfitting by ensuring that training stopped if the loss did not change substantially over 3 epochs.
 
@@
 We evaluated each model based on sequence level class assignments.
-Model performance for each model in shown in Table \ref{tab:modelperf}.
-TF-IDF achieved AUC of 0.95 and accuracy of 0.84.
+Model performance for each model on the held-out test set are shown in Table \ref{tab:modelperf}.
+To compute each metric, we used the threshold that maximized accuracy.
+The TF-IDF model achieved an AUC of 0.95 and accuracy of 0.84.
 The 20 words with the highest correlation coefficients using TF-IDF word vectorization are shown in Appendix \ref{app:app3}.
-While TF-IDF was able to identify the presence of a keyword or always pattern in a sequence, it was unable to leverage the order of words around each keyword match.
-The order of words often contained useful information regarding a patient's cognitive status, and on occasion would negate the presence of cognitive impairment.
-This led to the model over-zealously predict sequences as demonstrating cognitive impairment, resulting in a large count of false positives.
-ClinicalBERT was able to overcome these issues and leverage the meaning of the contexts due to its high complexity transformer architecture, resulting in an AUC of 0.98 and accuracy of 0.93.
-In order to generate accurate patient level class assignments, we applied ClinicalBERT to 186,730 sequences from the N = 13,941 unique patients that were not patient of our training/validation/set sets.
+While TF-IDF was able to identify the presence of a keyword or always pattern in a sequence, it was unable to the leverage the context around each keyword match.
+The context of the keywords and the agents within the sentence often contained useful information regarding a patient's cognitive status.
+For example, the sentence "Patient is caregiver for wife who has dementia" has the keyword dementia, but does not pertain to the patient's cognitive diagnosis.
+This led the baseline TF-IDF model to incorrectly predict sequences as evidence of cognitive impairment, resulting in a large count of false positives.
+
+ClinicalBERT, with its more complex architecture, was able to leverage the context of the keyword matches within the sequences and overcome these issues.
+The fine-tuned ClinicalBERT model achieved an AUC of 0.98 and substantially improved accuracy to 0.93 (specificity of 0.96, sensitivity of 0.91, micro F1 of 0.93, macro F1 of 0.92, and weighted F1 of 0.93).
+
+In order to generate patient level class assignments, we applied ClinicalBERT to all 186,730 sequences from the N = 13,941 unique patients that were not patient of our training/validation/set sets.
 With these sequence level predictions, we generated patient level class assignments by assigning patients a cognitive impairment label if their number of sequences predicted positive was greater than an empirically tuned threshold.
-We identified the most optimal threshold (from a range of 1 - 10) by comparing the percentage of patients being predicted as having cognitive impairment stratified by APOE allele to the percentages of patients with cognitive impairment related Meds/ICD codes stratified by APOE allele (MED/ICD code column in Table \tableref{tab:bert}).
+We identified the most optimal threshold (from a range of 1 - 10) by comparing the percentage of patients being predicted as having cognitive impairment stratified by APOE allele to the percentages of patients with cognitive impairment related Meds/ICD codes stratified by APOE allele (MED/ICD code column in \tableref{tab:bert}).
 \tableref{tab:bert} shows the comparison of Med/ICD codes to ClinicalBERT patient level class assignments with a sequence threshold of 2.
@@
 \section{Conclusion and Future Work} 
-\label{sec:ConclusionFutureWork} We applied NLP algorithms to identify patients with cognitive impairment in EHR and
-compared a baseline machine learning model with an attention based deep learning model on performance of sequence level class assignment predictions.
-Our work can help combat the issues of under-diagnosis and misdiagnosis for dementia.
-The deep learning model's performance was significantly better than the machine learning model.
-We used the sequence level class assignments of the deep learning model to generate patient level class assignment by assigning a patient a label of cognitive impairment if their number of sequences predicted positive was greater than or equal to a empirically tuned threshold.
-However, a lack of patient level class assignments generated by annotators prevents us from measuring the true accuracy of our results.
-In order to fix this issue, we plan to gather 1000 patient level class assignments through our annotation tool.
-We also plan to further improve the generalizability of our models by gathering more manually annotated sequences.
-An active learning loop will be used to pick particular patients and sequences by using entropy scores to label uncertain cases and UMAP clustering of ClinicalBERT word embeddings on the sequences of the N = 13,941 patients.
+\label{sec:ConclusionFutureWork} We applied NLP algorithms to identify patients with cognitive impairment in EHR and compared a baseline TF-IDF model with an attention based deep learning model on performance of sequence level class assignment predictions.
+Our work can help combat the under-diagnosis of dementia and alert caregivers to do a formal cognitive evaluation or refer to specialists.
+Such a tool can be used to generate cohorts for dementia research studies to identify risk and protective factors of dementia as well as recruit patients into observational studies or clinical trials.
+
+The deep learning model's performance was significantly better than the TF-IDF model as it was able to fully leverage the context of sequences.
+Our work illustrates the need of more complex, expressive language models for the nuanced task of detecting dementia in electronic health records.
+
+We used the sequence level class assignments of the deep learning model to generate patient level classes.
+We show that our model can successfully identify patients with cognitive impairment who lack dementia-related ICD codes or medications in their records.
+However, a lack of patient level annotations prevents us from measuring the true accuracy of our results.
+In order to address this issue, we plan to generate 1000 patient level class assignments using our annotation tool.
+We also plan to further improve the generalizability of our models by labeling more sequences that do not match an always pattern.
+An active learning loop will be used to pick particular patients and sequences by using entropy scores to label uncertain cases and UMAP clustering \citep{mcinnes2018umap} of ClinicalBERT word embeddings on the sequences of the N = 13,941 patients.
 The new gold-standard dataset will serve as the basis for the next iteration of the active learning loop to further improve model performance and detect patients with cognitive impairment at an earlier stage.

### 2021-10-16 Submission/Paper/ML4H/Reponse.tex
current version of response doc

\documentclass{article}

\usepackage{mlfh}
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{fancyhdr}
\usepackage{mwe}
\usepackage{wrapfig}
\usepackage{caption}
\captionsetup[table]{labelsep=space}
\rhead{ML4H Author Response 2021}

\begin{document}
\pagestyle{fancy}

We sincerely thank the reviewers for their feedback. We have developed a deep learning NLP pipeline to detect signs of cognitive impairment from unstructured clinician notes in electronic health records (EHR). The reviewers noted several key strengths including the relevance to healthcare (as dementia is often underdiagnosed, and EHR may not accurately capture the diagnosis as a structured diagnosis code [ICD code]), as well as the novelty of our approach. The many methodological innovations as described by Reviewer #C are: (1) combination of rule-based filters (regex on keywords to identify candidate sentences) and NLP methods applied on sentences to further improve model performance; (2) adjudication at sentence-level; (3) a novel dataset with manual annotation by clinician experts; and (4) use of genomic data and subgroup analysis based on APOE alleles. There were also several criticisms, which we address below.

\textbf{Bias in study data:} Reviewers A and B raised concerns that constructing our study sample using the 18 pre-selected keywords may lead to biases in the study. To clarify, our 18 keywords were based on careful literature review of established methods [1-3] for identifying patients with dementia using EHR. We collaborated with our memory-division physicians and ensured that these keywords comprehensively capture evidence of cognitive impairment, and that it would be exceedingly rare to describe cognitive impairment (or the lack thereof) in EHR notes without using one of these keywords. In our revised camera-ready manuscript, we will elaborate on the source of these keywords and include the references mentioned above.

\begin{wrapfigure}{l}{0.5\textwidth}
\centering
\includegraphics[width=.75\linewidth]{umap.png}
\caption{}
% \caption{UMAP Clustering of ClinicalBert Embeddings}
\end{wrapfigure}

\textbf{Generalization of the sequence-level model:} Reviewer A noted thar our annotations were primarily derived from regular expressions (always-patterns). We thank the reviewer for their insightful comment. Per their suggestion, we tested the model’s generalizability using a small dataset of manually annotated sequences (n=150) which did not match an always-pattern. The ClinicalBERT embeddings were able to able accurately discriminate between all three classes (0: no cognitive impairment; 1: neither; 2: cognitive impairment); see Figure 1.

\textbf{Patient level annotation:} Reviewers A, B, and C all noted the lack of patient-level gold-standard labels. We agree that this is one of the main limitations of our study. Per the suggestion of Reviewer B, we performed several manual chart reviews of patients who were classified as cognitively impaired from our ClinicalBERT model but did not have a dementia-related ICD code or medication. We identified many subtle examples where a non-specialist care provider notes cognitive impairment. For example, a physical therapist note states, “XX y.o. male who presents to PT with primary impairments in balance, cognition,” and a geriatrician reports, “Risk of delirium is moderate due to age, acute care setting, and underlying dementia.” Although our next step is to construct a carefully adjudicated patient-level annotated dataset, these two illustrative excerpts suggest that the ClinicalBERT model may indeed correctly classify patients with cognitive impairment who do not have structured data in EHR. In our updated manuscript, we will provide metrics on a set of patients (n=300) with clinically adjudicated labels.

\textbf{Other issues:} Reviewer B noted presentation issues with Table 1 and Figure 1. We thank the reviewer and will addresses these issues in the revised manuscript. We will also add details on the TF-IDF and ClinicalBERT setup, as suggested by Reviewer D, and will elaborate on future plans to evaluate our models at other institutions and healthcare settings.

\textbf{REFERENCES}

1.	Gilmore-Bykovskyi, A.L., et al., Unstructured clinical documentation reflecting cognitive and behavioral dysfunction: toward an EHR-based phenotype for cognitive impairment. J Am Med Inform Assoc, 2018. 25(9): p. 1206-1212.

2.	Reuben, D.B., et al., An Automated Approach to Identifying Patients with Dementia Using Electronic Medical Records. J Am Geriatr Soc, 2017. 65(3): p. 658-659.

3.	Amra, S., et al., Derivation and validation of the automated search algorithms to identify cognitive impairment and dementia in electronic health records. J Crit Care, 2017. 37: p. 202-205.

\end{document}

### 2021-11-02 Submission/Paper/ML4H/Paper.tex
edits to make it camera ready since it has been accepted

@@
  %\title{Title of the Article\titletag{\thanks{Some footnote}}}
+% figure out later
 
-% \author{Tanish Tyagi \nametag{\thanks{Authors contributed equally}\SUP{1}},
-% Colin G. Magdamo\nametag{\footnotemark[1]\SUP{1}}, 
-% Ayush Noori \SUP{1},
-% Mayuresh Deodhar \SUP{1},
-% Zhuoqiao Hong \SUP{1},
-% Alberto Serrano-Pozo \SUP{1},
-% Dimitry Prokopenko \SUP{1},
-% Rudy E. Tanzi \SUP{2},
-% Deborah Blacker \SUP{1},
-% Bradley T. Hyman \SUP{1},
-% Shibani S. Mukerji \SUP{1},
-% M. Brandon Westover \SUP{1},
-% Sudeshna Das\SUP{1},
+% \author{test \nametag{\thanks{Authors contributed equally}},
 % \centering \Email{ 
 % \\[\bigskipamount]  
-% \SUP{1}\{ttyagi, 
-% cmagdamo,
-% anoori1,
-% mdeodhar,
-% zhong1,
-% aserrano1,
-% dprokopenko,
-% dblacker,
-% bhyman,
-% smukerji,
-% mwestover,
-% sdas5\}
-% @mgh.harvard.edu}
-% \centering \Email{
-% \\[\bigskipamount] 
-% \SUP{2}\{tanzi\}@helix.mgh.harvard.edu
+% TEST, }
 % }
-% 
-% \begin{center}\addr Massachusetts General Hospital, Boston, MA\end{center}
-% }
+
+% ===============================================================
+
+\author{Tanish Tyagi \nametag{\thanks{Authors contributed equally} \SUP{1}},
+Colin G. Magdamo\nametag{\footnotemark[1]\SUP{1}}, 
+Ayush Noori \SUP{1},
+Zhaozhi Li \SUP{1},
+Xiao Liu \SUP{1},
+Mayuresh Deodhar \SUP{1},
+Zhuoqiao Hong \SUP{1},
+Wendong Ge \SUP{1},
+Alberto Serrano-Pozo \SUP{1},
+Sahar Zafar \SUP{1}, 
+Nicole Benson \SUP{1},
+Lidia Moura \SUP{1},
+John Hsu \SUP{1},
+Dimitry Prokopenko \SUP{1},
+Rudy E. Tanzi \SUP{1},
+Bradley T. Hyman \SUP{1},
+Deborah Blacker \SUP{1},
+Shibani S. Mukerji \SUP{1},
+M. Brandon Westover \SUP{1},
+Sudeshna Das\SUP{1}
+\centering \Email{
+\\[\bigskipamount] 
+\SUP{1}\{ttyagi, 
+cmagdamo,
+anoori1,
+zli39,
+xliu61,
+mdeodhar,
+zhong1,
+wendong.ge,
+aserrano1,
+sfzafar, 
+nbenson, 
+lidia.moura, 
+john.hsu,
+dprokopenko,
+dblacker,
+rtanzi,
+bhyman,
+smukerji,
+mwestover,
+sdas5\}
+@mgh.harvard.edu}
+\centering
+\begin{center}\addr Massachusetts General Hospital, Boston, MA\end{center}
+}
 
@@
 Tools that can efficiently and effectively analyze medical records for warning signs of dementia and recommend patients for follow up with a specialist can be critical to obtaining an early diagnosis for dementia.
-Such a tool could also be useful in recruiting into clinical trials as well as a variety of research studies ranging from in-silico trials for drug repurposing to evaluating how policies and programs meet the needs of patients and caregivers.
 We aim to use NLP to detect signs of cognitive impairment from unstructured clinician notes by using deep learning techniques.
@@
 
-%% Table 1 - Demographics of Dataset %%
-\begin{table*}[hbtp]
-\centering 
-\floatconts
-{tab:table1}
-{\caption{Demographics of Data}} 
-    {
+\section{Related Works}
+\label{sec:RelatedWorks} 
+Prior works have used NLP techniques to detect various diseases from EHR. \citep{rajkomar2018scalable} % https://www.nature.com/articles/s41746-018-0029-1%22
+used recurrent neural networks (long short-term memory (LSTM)) among others to predict inpatient mortality using EHR data from the University of California, San Francisco (UCSF) from 2012 to 2016, and the University of Chicago Medicine (UCM) from 2009 to 2016.
+\citep{glicksberg2018automated} % https://www.worldscientific.com/doi/epdf/10.1142/9789813235533_0014
+performed phenotyping for diseases such as Attention Deficit Hyperactivity Disorder (ADHD) by clustering on word2vec embeddings from EHR of the Mount Sinai Hospital (MSH) in New York City.
+These studies have shown that the application of NLP techniques to EHR have improved disease detection, and that NLP techniques can be applied to dementia detecton to achieve similar results.
+Our work uses deep learning NLP techniques, which has achieved impressive results when applied to general text due to the use of word embeddings and attention-based models \citep{vaswani2017attention,mikolov2013distributed,pennington2014glove,peters2018deep, devlin2018bert}, but have had limited applications in healthcare, particularly in dementia research.
+
+\section{Dataset, Preprocessing, and Annotations}
+\label{sec:Dataset+Preprocessing+Annotations}
+
+\paragraph{Dataset}
+\label{sec:Dataset} Our dataset consisted of a cohort (N = 16,428) of patients from the Mass General Brigham (MGB) HealthCare (formerly Partner's Healthcare, comprising two major academic hospitals, community hospitals, and community health centers in the Boston area) system who were older than 60 years (as of July 13, 2021), had APOE genotype \citep{mahley2000apolipoprotein} (biggest genetic risk factor for dementia) data available from the MGB BioBank, and at least one clinician note with a dementia-related keyword.
+\tableref{tab:table1} shows demographics of the cohort of patients.
+
+\paragraph{Preprocessing}
+\label{sec:Preprocessing} For each patient in our dataset, we extracted unstructured clinician notes, identified matches to 18 dementia-related keywords (Appendix \ref{app:keywords}, including those related to memory, cognition, neuropsychological tests, and dementia diagnoses.
+We constructed sequences from the note text spanning each of these matches (of length 800 characters).
+Our cohort of 16,428 patients had 279,224 sequences with dementia-related keywords in total.
+
+\begin{table}[htb]
+\resizebox{\columnwidth}{!}{%
 \begin{tabular}{lccc}
@@
 }
-\end{table*}
-
-\section{Related Works}
-\label{sec:RelatedWorks} 
-Prior works have used NLP techniques to detect various diseases from EHR. \citep{rajkomar2018scalable} % https://www.nature.com/articles/s41746-018-0029-1%22
-used recurrent neural networks (long short-term memory (LSTM)) among others to predict inpatient mortality using EHR data from the University of California, San Francisco (UCSF) from 2012 to 2016, and the University of Chicago Medicine (UCM) from 2009 to 2016.
-\citep{glicksberg2018automated} % https://www.worldscientific.com/doi/epdf/10.1142/9789813235533_0014
-performed phenotyping for diseases such as Attention Deficit Hyperactivity Disorder (ADHD) by clustering on word2vec embeddings from EHR of the Mount Sinai Hospital (MSH) in New York City.
-These studies have shown that the application of NLP techniques to EHR have improved disease detection, and that NLP techniques can be applied to dementia detecton to achieve similar results.
-Our work uses deep learning NLP techniques, which has achieved impressive results when applied to general text due to the use of word embeddings and attention-based models \citep{vaswani2017attention,mikolov2013distributed,pennington2014glove,peters2018deep, devlin2018bert}, but have had limited applications in healthcare, particularly in dementia research.
-
-\section{Dataset, Preprocessing, and Annotations}
-\label{sec:Dataset+Preprocessing+Annotations}
-
-\paragraph{Dataset}
-\label{sec:Dataset} Our dataset consisted of a cohort (N = 16,428) of patients from the Mass General Brigham (MGB) HealthCare (formerly Partner's Healthcare, comprising two major academic hospitals, community hospitals, and community health centers in the Boston area) system who were older than 60 years (as of July 13, 2021), had APOE genotype \citep{mahley2000apolipoprotein} (biggest genetic risk factor for dementia) data available from the MGB BioBank, and at least one clinician note with a dementia-related keyword.
-\tableref{tab:table1} shows demographics of the cohort of patients.
-
-\paragraph{Preprocessing}
-\label{sec:Preprocessing} For each patient in our dataset, we extracted unstructured clinician notes, identified matches to 18 dementia-related keywords (Appendix \ref{app:keywords}, including those related to memory, cognition, neuropsychological tests, and dementia diagnoses.
-We constructed sequences from the note text spanning each of these matches (of length 800 characters).
-Our cohort of 16,428 patients had 279,224 sequences with dementia-related keywords in total.
+\end{table}
 
@@
 ClinicalBERT, with its more complex architecture, was able to leverage the context of the keyword matches within the sequences and overcome these issues.
+Indeed, using a small dataset of manually annotated sequences (n=150) which did not match an always-pattern, the ClinicalBERT embeddings were able to able accurately discriminate between all three classes (see Appendix).
 The fine-tuned ClinicalBERT model achieved an AUC of 0.98 and substantially improved accuracy to 0.93 (specificity of 0.96, sensitivity of 0.91, micro F1 of 0.93, macro F1 of 0.92, and weighted F1 of 0.93).

### 2021-11-03 Submission/Paper/ML4H/Paper.tex
added figures so that they only take up 1 column

@@
 \begin{table}[htb]
+{\caption{Demographics of Data}}
 \resizebox{\columnwidth}{!}{%
@@
 
+\begin{figure}[htb]
+\caption{UMAP Clustering of ClinicalBert Embeddings}
+\resizebox{\columnwidth}{!}{%
+\label{fig:fig2}
+\centering 
+\includegraphics[width=.75\linewidth]{umap (1).png}
+
+}
+\end{figure}
+
 ClinicalBERT, with its more complex architecture, was able to leverage the context of the keyword matches within the sequences and overcome these issues.
@@
 % \section{Assessment of ClinicalBERT Patient Level Class Assignments} 
-
-\begin{table*}[hbtp]
-\centering 
-\floatconts
-{tab:bert}
+\begin{table}[htb]
 {\caption{Comparison between Other Indicators of Cognitive Impairment and ClinicalBERT}}
-
+\resizebox{\columnwidth}{!}{%
 {\begin{tabular}{cccccc}
@@
     \toprule 
-    \bfseries  & \bfseries Count & \bfseries Yes (\%) & \bfseries No/Ntr (\%)  & \bfseries Med/ICD Code (\%) \\ 
+    \bfseries  & \bfseries Count & \bfseries Yes (\%) & \bfseries No/Ntr (\%)  & \bfseries M/I (\%) \\ 
     \midrule
@@
   \end{tabular}} 
-\end{table*}
+}
 
-\begin{figure*}[h!]
+\bfseries M/I = Med/ICD Code 
+\end{table}
+
+\begin{figure}[htb]
+\caption{Confusion Matrix Patient Level Prediction Counts for ClinicalBERT}
+\resizebox{\columnwidth}{!}{%
 \label{fig:fig2}
@@
 \includegraphics[scale = 0.75]{bert_patient_predictions.png}
-\caption{Confusion Matrix Patient Level Prediction Counts for ClinicalBERT}
-\end{figure*}
+
+}
+\end{figure}
 

### 2021-11-03 Submission/Paper/ML4H/Paper.tex
first draft of camera ready paper done - will edit if get feedback

--- 2021-11-02 Submission/Paper/ML4H/Paper.tex
@@
 \begin{table}[htb]
+\floatconts
+{tab:table1}
+{\caption{Demographics of Data}}
 \resizebox{\columnwidth}{!}{%
@@
 
+\begin{figure}[htb]
+\floatconts
+{fig:umap}
+{\caption{UMAP Clustering of ClinicalBert Embeddings}}
+% \label{fig:umap}
+\resizebox{\columnwidth}{!}{%
+% \label{fig:umap}
+\centering 
+\includegraphics[width=.95\linewidth]{umap (1).png}
+}
+\end{figure}
+
 ClinicalBERT, with its more complex architecture, was able to leverage the context of the keyword matches within the sequences and overcome these issues.
-Indeed, using a small dataset of manually annotated sequences (n=150) which did not match an always-pattern, the ClinicalBERT embeddings were able to able accurately discriminate between all three classes (see Appendix).
+Indeed, using a small dataset of manually annotated sequences (n=150) which did not match an always-pattern, the ClinicalBERT embeddings were able to able accurately discriminate between all three classes (see Figure \ref{fig:umap}).
 The fine-tuned ClinicalBERT model achieved an AUC of 0.98 and substantially improved accuracy to 0.93 (specificity of 0.96, sensitivity of 0.91, micro F1 of 0.93, macro F1 of 0.92, and weighted F1 of 0.93).
@@
 % \section{Assessment of ClinicalBERT Patient Level Class Assignments} 
-
-\begin{table*}[hbtp]
-\centering 
+\begin{table}[htb]
 \floatconts
@@
 {\caption{Comparison between Other Indicators of Cognitive Impairment and ClinicalBERT}}
-
+\centering
+\resizebox{\columnwidth}{!}{%
 {\begin{tabular}{cccccc}

### 2021-11-05 Submission/Paper/ML4H/Paper.tex
fixed figure scale
fixed resolution of figures

@@
 \usepackage[load-configurations=version-1]{siunitx} % newer version
+
 %\usepackage{siunitx}
@@
 
-\author{Tanish Tyagi \nametag{\thanks{Authors contributed equally} \SUP{1}},
+\author{Tanish Tyagi\nametag{\thanks{Authors contributed equally}\SUP{1}},
 Colin G. Magdamo\nametag{\footnotemark[1]\SUP{1}}, 
-Ayush Noori \SUP{1},
-Zhaozhi Li \SUP{1},
-Xiao Liu \SUP{1},
-Mayuresh Deodhar \SUP{1},
-Zhuoqiao Hong \SUP{1},
-Wendong Ge \SUP{1},
-Alberto Serrano-Pozo \SUP{1},
-Sahar Zafar \SUP{1}, 
-Nicole Benson \SUP{1},
-Lidia Moura \SUP{1},
-John Hsu \SUP{1},
-Dimitry Prokopenko \SUP{1},
-Rudy E. Tanzi \SUP{1},
-Bradley T. Hyman \SUP{1},
-Deborah Blacker \SUP{1},
-Shibani S. Mukerji \SUP{1},
-M. Brandon Westover \SUP{1},
+Ayush Noori\SUP{1},
+Zhaozhi Li\SUP{1},
+Xiao Liu\SUP{1},
+Mayuresh Deodhar\SUP{1},
+Zhuoqiao Hong\SUP{1},
+Wendong Ge\SUP{1},
+Elissa M. Ye\SUP{1},
+Yi-han Sheu\SUP{1},
+Haitham Alabsi\SUP{1},
+Laura Brenner\SUP{1},
+Gregory K. Robbins\SUP{1},
+Sahar Zafar\SUP{1}, 
+Nicole Benson\SUP{1},
+Lidia Moura\SUP{1},
+John Hsu\SUP{1},
+Alberto Serrano-Pozo\SUP{1},
+Dimitry Prokopenko\SUP{1},
+Rudolph E. Tanzi\SUP{1},
+Bradley T. Hyman\SUP{1},
+Deborah Blacker\SUP{1},
+Shibani S. Mukerji\SUP{1},
+M. Brandon Westover\SUP{1},
 Sudeshna Das\SUP{1}
@@
 wendong.ge,
-aserrano1,
+emye,
+ysheu,
+halabsi,
+lnbrenner,
+grobbins,
 sfzafar, 
@@
 john.hsu,
+aserrano1,
 dprokopenko,
@@
 We developed natural language processing (NLP) tools to identify patients with cognitive impairment and demonstrate that linguistic context enhances performance for the classification task.
-We fine-tuned our attention based deep learning model, which can learn from complex language structures, and substantially improved accuracy (0.93) relative to a baseline NLP model (0.84).
+We fine-tuned our attention based deep learning model, which can learn from complex language structures, and substantially improved accuracy (0.93) relative to a baseline TF-IDF (term frequency-inverse document frequency) NLP model (0.84).
 Further, we show that deep learning NLP can successfully identify dementia patients without dementia-related ICD codes or medications.
@@
 We aim to use NLP to detect signs of cognitive impairment from unstructured clinician notes by using deep learning techniques.
+Such a tool could also
+be useful in recruiting into clinical trials as well as a
+variety of research studies.
 We apply our deep learning algorithm to patients in Mass General Brigham (MGB) Healthcare who have genotype data available from the MGB BioBank.
@@
 \paragraph{Dataset}
-\label{sec:Dataset} Our dataset consisted of a cohort (N = 16,428) of patients from the Mass General Brigham (MGB) HealthCare (formerly Partner's Healthcare, comprising two major academic hospitals, community hospitals, and community health centers in the Boston area) system who were older than 60 years (as of July 13, 2021), had APOE genotype \citep{mahley2000apolipoprotein} (biggest genetic risk factor for dementia) data available from the MGB BioBank, and at least one clinician note with a dementia-related keyword.
+\label{sec:Dataset} Our dataset consisted of a cohort (N = 16,428) of patients from the Mass General Brigham (MGB) HealthCare (formerly Partner's Healthcare, comprising two major academic hospitals, community hospitals, and community health centers in the Boston area) system who were older than 60 years (as of July 13, 2021), had APOE genotypes—the biggest genetic risk factor for Alzheimer's disease  \citep{mahley2000apolipoprotein}—available from the MGB BioBank, and at least one clinician note with a dementia-related keyword.
 \tableref{tab:table1} shows demographics of the cohort of patients.
@@
 Concern from the family of the patient or the patient was not considered as cognitive impairment.
-Experts annotated sequences using a web-based annotation tool (Appendix \ref{app:slat}) as 1) Yes, i.e., patient has CI; 2) No i.e., Patient does not have CI; and 3) Neither i.e., sequence has no information on patient’s cognition.
+Experts annotated sequences using a web-based annotation tool (Appendix \ref{app:slat}) and labeled them as 1) Yes, i.e., patient has CI; 2) No i.e., Patient does not have CI; and 3) Neither (NTR) i.e., sequence has no information on patient’s cognition.
 Appendix \ref{app:examples} shows examples of example sequences for all 3 classes.
@@
 \centering 
-\includegraphics[width=.95\linewidth]{umap (1).png}
+\includegraphics[width=.95\linewidth]{UMAP Figure 2 Final.png}
 }
@@
 With these sequence level predictions, we generated patient level class assignments by assigning patients a cognitive impairment label if their number of sequences predicted positive was greater than an empirically tuned threshold.
-We identified the most optimal threshold (from a range of 1 - 10) by comparing the percentage of patients being predicted as having cognitive impairment stratified by APOE allele to the percentages of patients with cognitive impairment related Meds/ICD codes stratified by APOE allele (MED/ICD code column in \tableref{tab:bert}).
+We identified the most optimal threshold (from a range of 1 - 10) by comparing the percentage of patients being predicted as having cognitive impairment stratified by APOE allele to the percentages of patients with cognitive impairment related Meds/ICD codes stratified by APOE allele (M/I code column in \tableref{tab:bert}).
 \tableref{tab:bert} shows the comparison of Med/ICD codes to ClinicalBERT patient level class assignments with a sequence threshold of 2.
@@
 \centering 
-\includegraphics[scale = 0.75]{bert_patient_predictions.png}
+\includegraphics[scale = 0.95]{Confusion Matrix Figure 3.png}
 
@@
 \label{sec:ConclusionFutureWork} We applied NLP algorithms to identify patients with cognitive impairment in EHR and compared a baseline TF-IDF model with an attention based deep learning model on performance of sequence level class assignment predictions.
-Our work can help combat the under-diagnosis of dementia and alert caregivers to do a formal cognitive evaluation or refer to specialists.
+Our work can help address the under-diagnosis of dementia and alert primary care physcians to do a formal cognitive evaluation or refer to specialists.
 Such a tool can be used to generate cohorts for dementia research studies to identify risk and protective factors of dementia as well as recruit patients into observational studies or clinical trials.
@@
 We used the sequence level class assignments of the deep learning model to generate patient level classes.
-We show that our model can successfully identify patients with cognitive impairment who lack dementia-related ICD codes or medications in their records.
-However, a lack of patient level annotations prevents us from measuring the true accuracy of our results.
+For a few patients, we manually verified that our model can successfully identify patients with cognitive impairment who lack dementia-related ICD codes or medications in their records.
+However, a lack of patient level annotations prevents us from measuring the true accuracy of these results.
 In order to address this issue, we plan to generate 1000 patient level class assignments using our annotation tool.
@@
 An active learning loop will be used to pick particular patients and sequences by using entropy scores to label uncertain cases and UMAP clustering \citep{mcinnes2018umap} of ClinicalBERT word embeddings on the sequences of the N = 13,941 patients.
-The new gold-standard dataset will serve as the basis for the next iteration of the active learning loop to further improve model performance and detect patients with cognitive impairment at an earlier stage.
+The new gold-standard dataset will serve as the basis for the next iteration of the active learning loop to further improve model performance and detect patients with cognitive impairment with improved accuracy.
 
@@
 \centering 
-\includegraphics[scale = 0.30]{APOE SLAT Overview.png}
+\includegraphics[scale = 0.60]{APOE SLAT Overview High Resolution.png}
 \caption{Overview}

### 2021-11-10 Submission/Paper/ML4H/Paper.tex
minor fixes according to other authors

@@
 \hspace{10mm} Dementia is a neurodegenerative disorder that causes cognitive decline and affects more than 50 million people worldwide.
-Dementia is under-diagnosed by healthcare professionals — only one in four people who suffer from dementia are diagnosed.
+Dementia is underdiagnosed by healthcare professionals — only one in four people who suffer from dementia are diagnosed.
 Even when a diagnosis is made, it may not be entered as a structured International Classification of Diseases (ICD) diagnosis code in a patient’s charts.
@@
 \label{sec:intro} Dementia is the most common neurodegenerative disease affecting older adults, progressing from mild cognitive impairment (MCI) to mild, moderate, and severe dementia.
-Dementia is under-diagnosed: dementia is not formally diagnosed or coded in claims data for over 50\% of older adults living with probable dementia.
+Dementia is underdiagnosed \citep{AlzheimerAssociation}: dementia is not formally diagnosed or coded in claims data for over 50\% of older adults living with probable dementia.
 Often, a diagnosis is given once patient has reached moderate dementia, and irreversible damage has already been done to the brain.
@@
 \paragraph{Dataset}
-\label{sec:Dataset} Our dataset consisted of a cohort (N = 16,428) of patients from the Mass General Brigham (MGB) HealthCare (formerly Partner's Healthcare, comprising two major academic hospitals, community hospitals, and community health centers in the Boston area) system who were older than 60 years (as of July 13, 2021), had APOE genotypes—the biggest genetic risk factor for Alzheimer's disease  \citep{mahley2000apolipoprotein}—available from the MGB BioBank, and at least one clinician note with a dementia-related keyword.
+\label{sec:Dataset} Our dataset consisted of a cohort (N = 16,428) of patients from the Mass General Brigham (MGB) HealthCare \citep{jpm6010011} (formerly Partner's Healthcare, comprising two major academic hospitals, community hospitals, and community health centers in the Boston area) system who were older than 60 years (as of July 13, 2021), had \textit{APOE} genotypes—the biggest genetic risk factor for Alzheimer's disease  \citep{mahley2000apolipoprotein}—available from the MGB BioBank, and at least one clinician note with a dementia-related keyword.
 \tableref{tab:table1} shows demographics of the cohort of patients.
@@
 {\caption{Demographics of Data}}
-\resizebox{\columnwidth}{!}{%
+\resizebox{\columnwidth}{}{%
 \begin{tabular}{lccc}
@@
             \hspace{10mm} Indigenous & 16 (0.01) \\
-        \textbf{APOE Genotype, \emph n (\%)} \\ 
-            \hspace{10mm} {APOE ${\bm{\varepsilon}}$2 & 2028 (12.3)} \\
-            \hspace{10mm} {APOE ${\bm{\varepsilon}}$3 & 10177 (62.0)} \\
-            \hspace{10mm} {APOE ${\bm{\varepsilon}}$4 & 4223 (25.7)} \\
+        \textbf{\textit{APOE} Genotype, \emph n (\%)} \\ 
+            \hspace{10mm} {\textit{APOE} ${\bm{\varepsilon}}$2 & 2028 (12.3)} \\
+            \hspace{10mm} {\textit{APOE} ${\bm{\varepsilon}}$3 & 10177 (62.0)} \\
+            \hspace{10mm} {\textit{APOE} ${\bm{\varepsilon}}$4 & 4223 (25.7)} \\
         \textbf{Average Speciality Visits (SD)} & 1.67 (4.6) \\ 
@@
 Experts annotated sequences using a web-based annotation tool (Appendix \ref{app:slat}) and labeled them as 1) Yes, i.e., patient has CI; 2) No i.e., Patient does not have CI; and 3) Neither (NTR) i.e., sequence has no information on patient’s cognition.
-Appendix \ref{app:examples} shows examples of example sequences for all 3 classes.
+Appendix \ref{app:examples} shows example sequences for all 3 classes.
 
@@
 \label{sec:TFIDF}  
-\paragraph{(1) Logistic Regression with TF-IDF Vectors} We performed TF-IDF (term frequency-inverse document frequency) vectorization on the annotated sequences and selected features based on a term's Pearson correlation coefficient with the outcome.
+\paragraph{(1) Logistic Regression with TF-IDF Vectors} We performed TF-IDF (term frequency-inverse document frequency) vectorization on the annotated sequences and selected features based on a term's Pearson correlation coefficient with the cognitive impairment outcome.
 L1 Regularized logistic regression \citep{tibshirani1996regression} was applied with the annotated cognitive impairment labels.
@@
 The model was initialized with pre-trained parameters and later fine-tuned on our labeled training set.
-Optuna \citep{akiba2019optuna} was used to perform a 20-trial study and tune the learning rate, adam epilson, and the number of train epochs on the held-out validation set to maximize AUC.
+Optuna \citep{akiba2019optuna} was used to perform a 20-trial study and tune the learning rate, Adam epilson, and the number of train epochs on the held-out validation set to maximize AUC.
 An early stopping rule was used to prevent overfitting by ensuring that training stopped if the loss did not change substantially over 3 epochs.
@@
 {\caption{UMAP Clustering of ClinicalBert Embeddings}}
+\centering 
 % \label{fig:umap}
@@
 % \label{fig:umap}
-\centering 
-\includegraphics[width=.95\linewidth]{UMAP Figure 2 Final.png}
+
+\includegraphics[width=.75\linewidth]{UMAP Figure 2 Final.png}
 }
@@
 With these sequence level predictions, we generated patient level class assignments by assigning patients a cognitive impairment label if their number of sequences predicted positive was greater than an empirically tuned threshold.
-We identified the most optimal threshold (from a range of 1 - 10) by comparing the percentage of patients being predicted as having cognitive impairment stratified by APOE allele to the percentages of patients with cognitive impairment related Meds/ICD codes stratified by APOE allele (M/I code column in \tableref{tab:bert}).
+We identified the most optimal threshold (from a range of 1 - 10) by comparing the percentage of patients being predicted as having cognitive impairment stratified by \textit{APOE} allele to the percentages of patients with cognitive impairment related Meds/ICD codes stratified by \textit{APOE} allele (M/I code column in \tableref{tab:bert}).
 \tableref{tab:bert} shows the comparison of Med/ICD codes to ClinicalBERT patient level class assignments with a sequence threshold of 2.
@@
     \midrule
-    \bfseries{APOE ${\bm{\varepsilon}}$2} & \fseries 1754 & \fseries 0.17 & \fseries 0.83 & \fseries 0.11  \\
-    \bfseries{APOE ${\bm{\varepsilon}}$3} & \fseries 8751 & \fseries 0.17 & \fseries 0.83 & \fseries 0.11  \\
-    \bfseries{APOE ${\bm{\varepsilon}}$4} & \fseries 3436 & \fseries 0.21 & \fseries 0.79 & \fseries 0.17  \\
+    \bfseries{\textit{APOE} ${\bm{\varepsilon}}$2} & \fseries 1754 & \fseries 0.17 & \fseries 0.83 & \fseries 0.11  \\
+    \bfseries{\textit{APOE} ${\bm{\varepsilon}}$3} & \fseries 8751 & \fseries 0.17 & \fseries 0.83 & \fseries 0.11  \\
+    \bfseries{\textit{APOE} ${\bm{\varepsilon}}$4} & \fseries 3436 & \fseries 0.21 & \fseries 0.79 & \fseries 0.17  \\
 
@@
 \centering 
-\includegraphics[scale = 0.95]{Confusion Matrix Figure 3.png}
+\includegraphics[scale=0.5]{Confusion Matrix Figure 3.png}
 
@@
 \label{sec:ConclusionFutureWork} We applied NLP algorithms to identify patients with cognitive impairment in EHR and compared a baseline TF-IDF model with an attention based deep learning model on performance of sequence level class assignment predictions.
-Our work can help address the under-diagnosis of dementia and alert primary care physcians to do a formal cognitive evaluation or refer to specialists.
+Our work can help address the underdiagnosis of dementia and alert primary care physcians to do a formal cognitive evaluation or refer to specialists.
 Such a tool can be used to generate cohorts for dementia research studies to identify risk and protective factors of dementia as well as recruit patients into observational studies or clinical trials.

### 2021-11-12 Submission/Paper/ML4H/Paper.tex
in the middle of getting ready for arXiv
more errors fixed...
9 more errors left...
FIXED ALL THE ERRORS THANK GOD

@@
 \usepackage{tabto}    
+\usepackage{bm}
 \usepackage{graphicx}
@@
 \usepackage{url}
+\usepackage{textcomp}
+% \usepackage{syntonly}
+% \syntaxonly
 
@@
 {\caption{Demographics of Data}}
-\resizebox{\columnwidth}{}{%
+\centering
+\resizebox{\columnwidth}{!}{
         \begin{tabular}{lccc}
@@
             \midrule
-        \textbf{Age (years) mean (SD)} & \fseries 73.01 (7.96) \\ 
-        \textbf{Gender Male, \emph n (\%)}  & \fseries 8740 (53.2)\\ 
-        \textbf{Race, \emph n (\%)} \\ 
+            \bfseries Age (years) mean (SD) & 73.01 (7.96) \\ 
+            \bfseries Gender Male, \emph n (\%) & 8740 (53.2)\\ 
+            \bfseries Race, \emph n (\%) \\ 
                 \hspace{10mm} White & 14896 (90.7) \\
@@
                 \hspace{10mm} Indigenous & 16 (0.01) \\
-        \textbf{\textit{APOE} Genotype, \emph n (\%)} \\ 
-            \hspace{10mm} {\textit{APOE} ${\bm{\varepsilon}}$2 & 2028 (12.3)} \\
-            \hspace{10mm} {\textit{APOE} ${\bm{\varepsilon}}$3 & 10177 (62.0)} \\
-            \hspace{10mm} {\textit{APOE} ${\bm{\varepsilon}}$4 & 4223 (25.7)} \\
-        \textbf{Average Speciality Visits (SD)} & 1.67 (4.6) \\ 
-        \textbf{Average PCP Encounters (SD)} &  5.25 (5.63) \\ 
-        % \textbf{Encounters AVG (SD)} & 14.55 (23.2) \\
-        % \textbf{Keyword Matches AVG (SD)} & 26 (54.03) \\
+            \bfseries \textit{APOE} Genotype, \emph n (\%) \\ 
+                \hspace{10mm} \textit{APOE} ${\bm{\varepsilon}}$2 & 2028 (12.3) \\
+                \hspace{10mm} \textit{APOE} ${\bm{\varepsilon}}$3 & 10177 (62.0) \\
+                \hspace{10mm} \textit{APOE} ${\bm{\varepsilon}}$4 & 4223 (25.7) \\
+            \bfseries Average Speciality Visits (SD) & 1.67 (4.6) \\ 
+            \bfseries Average PCP Encounters (SD) &  5.25 (5.63) \\ 
+            % \bfseriesEncounters AVG (SD)} & 14.55 (23.2) \\
+            % \bfseriesKeyword Matches AVG (SD)} & 26 (54.03) \\
             \bottomrule
@@
 
-\includegraphics[width=.75\linewidth]{UMAP Figure 2 Final.png}
+\includegraphics[width=.75\linewidth]{UMAP_Figure_2_Final.png}
 }
@@
     \midrule
-    \bfseries{\textit{APOE} ${\bm{\varepsilon}}$2} & \fseries 1754 & \fseries 0.17 & \fseries 0.83 & \fseries 0.11  \\
-    \bfseries{\textit{APOE} ${\bm{\varepsilon}}$3} & \fseries 8751 & \fseries 0.17 & \fseries 0.83 & \fseries 0.11  \\
-    \bfseries{\textit{APOE} ${\bm{\varepsilon}}$4} & \fseries 3436 & \fseries 0.21 & \fseries 0.79 & \fseries 0.17  \\
+    \bfseries \textit{APOE} ${\bm{\varepsilon}}$2 & 1754 & 0.17 & 0.83 & 0.11  \\
+    \bfseries \textit{APOE} ${\bm{\varepsilon}}$3 & 8751 & 0.17 & 0.83 & 0.11  \\
+    \bfseries \textit{APOE} ${\bm{\varepsilon}}$4 & 3436 & 0.21 & 0.79 & 0.17  \\
 
     \bottomrule
-  \end{tabular}} 
+  \end{tabular}
+}
+
 }
@@
 \centering 
-\includegraphics[scale=0.5]{Confusion Matrix Figure 3.png}
+\includegraphics[scale=0.5]{bert_patient_predictions.png}
 
@@
 \centering 
-\includegraphics[scale = 0.60]{APOE SLAT Overview High Resolution.png}
+\includegraphics[scale = 0.60]{APOE_SLAT_Overview_High_Resolution.png}
 \caption{Overview}
@@
 {app:keywords}
-    {\begin{tabular}{lccc}
+{\caption{Keywords indicative of Cognitive Impairment}}
+\centering
+    \begin{tabular}{lcc}
         \toprule
-        \bfseries Keyword & \bfseries Match Count\\
+        \bfseries Keyword & \bfseries Match Count \\
         \midrule
 
-        \textbf{Memory} & \fseries 109218 \\ 
-        \textbf{Cognition}  & \fseries 87655 \\ 
-        \textbf{Dementia} & \fseries 51034 \\ 
-        \textbf{Cerebral} & \fseries 45886 \\ 
-        \textbf{Cerebrovascular} & \fseries 36370 \\ 
-        \textbf{Cerebellar} & \fseries 26863 \\
-        \textbf{Cognitive Impairment} & \fseries 20267 \\ 
-        \textbf{Alzheimer} & \fseries 20581 \\ 
-        \textbf{MOCA} & \fseries 9767 \\ 
-        \textbf{Neurocognitive} & \fseries 7711 \\ 
-        \textbf{MCI} & \fseries 3889 \\ 
-        \textbf{Amnesia} & \fseries 3695 \\ 
-        \textbf{AD} & \fseries 2673 \\ 
-        \textbf{Lewy} & \fseries 2561 \\ 
-        \textbf{MMSE} & \fseries 2134 \\ 
-        \textbf{LBD} & \fseries 224 \\ 
-        \textbf{Corticobasal} & \fseries 147 \\ 
-        \textbf{Pick's} & \fseries 41 \\
+        \bfseries Memory & 109218 \\ 
+        \bfseries Cognition & 87655 \\ 
+        \bfseries Dementia & 51034 \\ 
+        \bfseries Cerebral & 45886 \\ 
+        \bfseries Cerebrovascular & 36370 \\ 
+        \bfseries Cerebellar & 26863 \\
+        \bfseries Cognitive Impairment & 20267 \\ 
+        \bfseries Alzheimer & 20581 \\ 
+        \bfseries MOCA & 9767 \\ 
+        \bfseries Neurocognitive & 7711 \\ 
+        \bfseries MCI & 3889 \\ 
+        \bfseries Amnesia & 3695 \\ 
+        \bfseries AD & 2673 \\ 
+        \bfseries Lewy & 2561 \\ 
+        \bfseries MMSE & 2134 \\ 
+        \bfseries LBD & 224 \\ 
+        \bfseries Corticobasal & 147 \\ 
+        \bfseries Picks & 41 \\
 
         \bottomrule
-        \end{tabular}}
-        {\caption{Keywords indicative of Cognitive Impairment}} \\
+        \end{tabular}
+
 \end{table}
@@
 \begin{table}[hbtp]
-    {\begin{tabular}{cccc}
+    \begin{tabular}{lcccc}
     \toprule 
-    \bfseries Word & \bfseries Corr & \bfseries Word & \bfseries Corr &
+    \bfseries Word & \bfseries Corr & \bfseries Word & \bfseries Corr \\
     \midrule
 
-    \textbf{Intact} & \fseries 0.56 & \textbf{Experiences} & \fseries 0.36 \\
-    \textbf{Oriented} & \fseries 0.43 & \textbf{Associations} & \fseries 0.36 \\ 
-    \textbf{Concentration} & \fseries 0.42 & \textbf{Homicidal} & \fseries 0.36 \\ 
-    \textbf{Orientation} & \fseries 0.41 & \textbf{Observation} & \fseries 0.36 \\
-    \textbf{Sensorium} & \fseries 0.40 & \textbf{Knowledge} & \fseries 0.36 \\ 
-    \textbf{Perceptions} & \fseries 0.40 & \textbf{Abstract} & \fseries 0.36 \\
-    \textbf{Judgement} & \fseries 0.39 & \textbf{Suicidal} & \fseries 0.35 \\
-    \textbf{Fund} & \fseries 0.38 & \textbf{Attention} & \fseries 0.35 \\
-    \textbf{Insight } & \fseries 0.36 & \textbf{Content} & \fseries 0.34 \\ 
-    \textbf{Ideation} & \fseries 0.36 & \textbf{Thought} & \fseries 0.34  \\
+    \bfseries Intact &  0.56 & \bfseries Experiences & 0.36 \\
+    \bfseries Oriented &  0.43 & \bfseries Associations & 0.36 \\ 
+    \bfseries Concentration &  0.42 & \bfseries Homicidal & 0.36 \\ 
+    \bfseries Orientation &  0.41 & \bfseries Observation & 0.36 \\
+    \bfseries Sensorium &  0.40 & \bfseries Knowledge & 0.36 \\ 
+    \bfseries Perceptions &  0.40 & \bfseries Abstract & 0.36 \\
+    \bfseries Judgement &  0.39 & \bfseries Suicidal & 0.35 \\
+    \bfseries Fund & 0.38 & \bfseries Attention & 0.35 \\
+    \bfseries Insight &  0.36 & \bfseries Content & 0.34 \\ 
+    \bfseries Ideation &  0.36 & \bfseries Thought & 0.34  \\
 
     \bottomrule
-  \end{tabular}}
+  \end{tabular}
   {\caption{Top 20 TF-IDF Word Features and their Correlation Coefficient}}
@@
 %     \midrule
-%     \bfseries{APOE ${\bm{\varepsilon}}$2} & \fseries 1754 & \fseries 0.15 & \fseries 0.85 & \fseries 0.11  \\
-%     \bfseries{APOE ${\bm{\varepsilon}}$3} & \fseries 8751 & \fseries 0.15 & \fseries 0.85 & \fseries 0.11  \\
-%     \bfseries{APOE ${\bm{\varepsilon}}$4} & \fseries 3436 & \fseries 0.18 & \fseries 0.82 & \fseries 0.17  \\
+%     \bfseriesAPOE ${\bm{\varepsilon}}$2} &  1754 &  0.15 &  0.85 &  0.11  \\
+%     \bfseriesAPOE ${\bm{\varepsilon}}$3} &  8751 &  0.15 &  0.85 &  0.11  \\
+%     \bfseriesAPOE ${\bm{\varepsilon}}$4} &  3436 &  0.18 &  0.82 &  0.17  \\
 

### 2021-11-24 nlp_annotator-dev/app/accounts/admin.py
end of fall term update commit 2

@@ -1,13 +1,0 @@
-from django.contrib import admin
-from django.contrib.auth import get_user_model
-from django.contrib.auth.admin import UserAdmin
-
-from .forms import SignUpForm
-from .models import CustomUser
-
-class CustomUserAdmin(UserAdmin):
-    add_form = SignUpForm
-    model = CustomUser
-    list_display = ['first_name', 'last_name', 'username', 'email', 'Phone', 'AssignedPatients', 'date_joined', 'last_login', 'is_staff', 'is_active']
-
-admin.site.register(CustomUser, CustomUserAdmin)

### 2021-11-24 nlp_annotator-dev/app/accounts/forms.py

@@ -1,21 +1,0 @@
-from django import forms
-from django.forms import Form, ModelForm, Textarea
-from django.core.validators import MaxValueValidator, MinValueValidator 
-from .models import CustomUser
-from django.utils.translation import gettext_lazy as _
-# from django.contrib.auth.models import User
-
-# user authentication
-from django.contrib.auth.forms import UserCreationForm, UserChangeForm, AuthenticationForm
-
-# form to sign up new user for login view
-class SignUpForm(UserCreationForm):
-    class Meta:
-        model = CustomUser
-        fields = ('first_name', 'last_name', 'username', 'email', 'password1', 'password2')
-
-
-# form to request additional patients for dashboard view
-class RequestPatientsForm(Form):
-    num_to_add = forms.IntegerField(validators=[MinValueValidator(1), MaxValueValidator(100)], label = '')
-    

### 2021-11-24 nlp_annotator-dev/app/accounts/migrations/0001_initial.py

@@ -1,45 +1,0 @@
-# Generated by Django 2.2.5 on 2020-12-16 18:38
-
-import django.contrib.auth.models
-import django.contrib.auth.validators
-from django.db import migrations, models
-import django.utils.timezone
-
-
-class Migration(migrations.Migration):
-
-    initial = True
-
-    dependencies = [
-        ('auth', '0011_update_proxy_permissions'),
-    ]
-
-    operations = [
-        migrations.CreateModel(
-            name='CustomUser',
-            fields=[
-                ('id', models.AutoField(auto_created=True, primary_key=True, serialize=False, verbose_name='ID')),
-                ('password', models.CharField(max_length=128, verbose_name='password')),
-                ('last_login', models.DateTimeField(blank=True, null=True, verbose_name='last login')),
-                ('is_superuser', models.BooleanField(default=False, help_text='Designates that this user has all permissions without explicitly assigning them.', verbose_name='superuser status')),
-                ('username', models.CharField(error_messages={'unique': 'A user with that username already exists.'}, help_text='Required. 150 characters or fewer. Letters, digits and @/./+/-/_ only.', max_length=150, unique=True, validators=[django.contrib.auth.validators.UnicodeUsernameValidator()], verbose_name='username')),
-                ('first_name', models.CharField(blank=True, max_length=30, verbose_name='first name')),
-                ('last_name', models.CharField(blank=True, max_length=150, verbose_name='last name')),
-                ('email', models.EmailField(blank=True, max_length=254, verbose_name='email address')),
-                ('is_staff', models.BooleanField(default=False, help_text='Designates whether the user can log into this admin site.', verbose_name='staff status')),
-                ('is_active', models.BooleanField(default=True, help_text='Designates whether this user should be treated as active. Unselect this instead of deleting accounts.', verbose_name='active')),
-                ('date_joined', models.DateTimeField(default=django.utils.timezone.now, verbose_name='date joined')),
-                ('Phone', models.IntegerField(blank=True, null=True)),
-                ('AssignedPatients', models.TextField(blank=True, default='None', null=True)),
-                ('Keywords', models.TextField(blank=True, default='dementia', null=True)),
-                ('groups', models.ManyToManyField(blank=True, help_text='The groups this user belongs to. A user will get all permissions granted to each of their groups.', related_name='user_set', related_query_name='user', to='auth.Group', verbose_name='groups')),
[…]

### 2021-11-24 nlp_annotator-dev/app/accounts/migrations/0002_auto_20210105_1935.py

@@ -1,18 +1,0 @@
-# Generated by Django 3.1.2 on 2021-01-06 03:35
-
-from django.db import migrations, models
-
-
-class Migration(migrations.Migration):
-
-    dependencies = [
-        ('accounts', '0001_initial'),
-    ]
-
-    operations = [
-        migrations.AlterField(
-            model_name='customuser',
-            name='first_name',
-            field=models.CharField(blank=True, max_length=150, verbose_name='first name'),
-        ),
-    ]

### 2021-11-24 nlp_annotator-dev/app/annotator_gui/settings.py

@@ -1,156 +1,0 @@
-"""
-Django settings for annotator_gui project.
-
-Generated by 'django-admin startproject' using Django 3.1.
-
-For more information on this file, see
-https://docs.djangoproject.com/en/3.1/topics/settings/
-
-For the full list of settings and their values, see
-https://docs.djangoproject.com/en/3.1/ref/settings/
-"""
-
-from pathlib import Path
-import os  # see line 123
-from django.contrib.messages import constants as messages # to assign Bootstrap alerts to Django message tags
-
-# Build paths inside the project like this: BASE_DIR / 'subdir'.
-BASE_DIR = Path(__file__).resolve(strict=True).parent.parent
-
-
-# Quick-start development settings - unsuitable for production
-# See https://docs.djangoproject.com/en/3.1/howto/deployment/checklist/
-
-# SECURITY WARNING: keep the secret key used in production secret!
-SECRET_KEY = '6a8a0d78d99677f21c18eaa3773541b7d3eb918e4897'
-
-# SECURITY WARNING: don't run with debug turned on in production!
-ENVIRONMENT = os.getenv("DJANGO_ENVIRONMENT", "dev")
-if ENVIRONMENT == "dev":
-    DEBUG = True
-elif ENVIRONMENT == "prod":
-    DEBUG = False
-else:
-    raise ValueError(f"Invalid DJANGO_ENVIRONMENT {ENVIRONMENT}! Must be 'dev' or 'prod'")
-
-
-_hosts = ['127.0.0.1', 'localhost', '0.0.0.0', 'rc-nat.partners.org', 'nat.partners.org']
-ALLOWED_HOSTS = _hosts
-
-CSRF_TRUSTED_ORIGINS = _hosts
-CSRF_COOKIE_SECURE = True
-
-SECURE_PROXY_SSL_HEADER = ('HTTP_X_FORWARDED_PROTO', 'https')
-
-# Application definition
-
-INSTALLED_APPS = [
-    'gui.apps.GuiConfig',
-    'django.contrib.admin',
-    'django.contrib.auth',
-    'django.contrib.contenttypes',
-    'django.contrib.sessions',
-    'django.contrib.messages',
-    'django.contrib.staticfiles',
-    'import_export', # for django-import-export library, install via pip install django-import-export
-    # 'csvimport.app.CSVImportConf',  # use AppConfig for django >=1.7 csvimport >=2.2
-    'django_extensions',
-    'accounts',
-]
-
-MIDDLEWARE = [
[…]

### 2021-11-24 nlp_annotator-dev/app/gui/admin.py

@@ -1,20 +1,0 @@
-from django.contrib import admin, messages
-from import_export import resources
-from import_export.admin import ImportExportModelAdmin
-from .models import PatientDemographic
-
-# class PatientDemographicResource(resources.ModelResource):
-#     class Meta:
-#         model = PatientDemographic
-
-# class PatientDemographicAdmin(ImportExportModelAdmin):
-#     resource_class = PatientDemographicResource
-#     list_display = ('PatientID', 'MRN', 'BirthDTS', 'EthnicGroupDSC',
-#     'MaritalStatusDSC', 'SexDSC', 'EducationLevelDSC',
-#     'CoordinationNote', 'PatientLabs', 'PatientImaging', 'RefillRequests', 'Assigned',
-#     'CognitiveConcern', 'StageImpairment', 
-#     # 'CognitiveConcern', 'SyndromicDiagnosis', 'CINDSeverity', 'DementiaSeverity',
-#     'Annotator', 'DateAnnotated', 'Scratchpad', 'Consensus', 'ConsensusActor') 
-
-# # register patient model
-# admin.site.register(PatientDemographic, PatientDemographicAdmin)

### 2021-11-24 nlp_annotator-dev/app/gui/management/commands/_load_data.py

@@ -1,126 +1,0 @@
-# import libraries
-import csv, os
-from datetime import datetime
-import json
-from pathlib import Path
-import openpyxl
-import django.shortcuts
-import logging
-from gui.models import Sentence, SeedRegex, PatientDemographic, Note, SentenceSeedRegex
-from django.db import transaction
-
-
-logging.basicConfig(level="INFO", format='%(asctime)s %(levelname)-8s %(message)s')
-logger = logging.getLogger("load_data")
-
-@transaction.atomic
-def load_data(filename, start_row=1):
-    # everything is relative to this file
-    # ROOT_DIR = Path(__file__).parent
-
-    # specify the import filename
-    # filename = "test_data.csv"
-    fpath = filename
-
-    columns = [
-        "PatientID",
-        "MRN",
-        "EMPI",
-        "PatientEncounterID", 
-        "NoteType",
-        "NoteID",
-        "Sentence",
-        "RegexMatches",
-        "Date"
-    ]
-    column_overrides = {
-        "Sentence": "regex_sent",
-        "RegexMatches": "regex_match",
-        "Date": "ContactDTS",
-    }
-    column_mapping = {
-        c: column_overrides.get(c, c) for c in columns
-    }
-
-    date_fmt = "%Y-%m-%d"
-
-    patients = {}
-    notes = {}
-    regexes = {}
-    sentences = []
-
-    def get_or_create_patient(patient_id, mrn, empi):
-        existing = patients.get(patient_id)
-        if existing:
-            return existing
-        p, created = PatientDemographic.objects.get_or_create(PatientID=patient_id, MRN=mrn, EMPI=empi)
-        p.save()
-        if created:
-            patients[patient_id] = p
-        return p
-
-    def get_or_create_note(patient_id, note_id, encounter_id, date):
-        existing = notes.get(note_id)
-        if existing:
-            return existing
-        n, created = Note.objects.get_or_create(PatientID=patient_id, PatientEncounterID=encounter_id, NoteID=note_id, Date=date)
-        n.save()
-        if created:
-            notes[note_id] = n
-        return n
-
-    def get_or_create_seed_regex(pattern):
-        pattern = pattern.strip()
-        existing = regexes.get(pattern)
-        if existing:
-            return existing
-        r, created = SeedRegex.objects.get_or_create(Pattern=pattern)
-        r.save()
-        if created:
-            regexes[pattern] = r
-        return r
-
[…]

### 2021-11-24 nlp_annotator-dev/app/gui/migrations/0003_auto_20210428_1544.py

@@ -1,18 +1,0 @@
-# Generated by Django 3.1.6 on 2021-04-28 15:44
-
-from django.db import migrations, models
-
-
-class Migration(migrations.Migration):
-
-    dependencies = [
-        ('gui', '0002_auto_20210428_0505'),
-    ]
-
-    operations = [
-        migrations.AlterField(
-            model_name='patientdemographic',
-            name='PatientID',
-            field=models.TextField(blank=True, unique=True),
-        ),
-    ]

### 2021-11-24 nlp_annotator-dev/app/gui/models.py

@@ -1,103 +1,0 @@
-import re
-
-from django.db import models
-
-# to reset databsae:
-    # run python manage.py reset_db (from django-extensions package)
-
-# to delete all data from the table:
-# python manage.py shell
-# >> from gui.models import PatientDemographic, PatientYear, Note
-# >> PatientDemographic.objects.all().delete()
-# >> PatientYear.objects.all().delete()
-# >> Note.objects.all().delete()
-
-# to add data:
-# update .csv files in load_data/data
-# python manage.py shell
-# >> %run load_data/load_data.py
-
-# each element in choices is a tuple of actual value to be stored, then human readable translation
-# in our case, these are the same
-
-BaseModel = models.Model
-
-
-class Sentence(BaseModel):
-    Contents = models.TextField(blank = False, null = False)
-    Note = models.ForeignKey("gui.Note", null = False, on_delete=models.PROTECT)
-
-    @classmethod
-    def unassigned(cls):
-        return cls.objects.filter(sentenceassignment__isnull=True).order_by('id')
-
-
-class SentenceAssignment(BaseModel):
-    User = models.ForeignKey("accounts.CustomUser", null = False, on_delete=models.PROTECT)
-    Sentence = models.ForeignKey("gui.Sentence", null = False, on_delete=models.PROTECT)
-    CompletedAt = models.DateTimeField(null=True)
-    class Meta:
-        constraints = [
-            models.UniqueConstraint(fields=['User', 'Sentence'], name='uq_assignment')
-        ]
-
-class SentenceAnnotation(BaseModel):
-    class AnnotationLabel(models.TextChoices):
-        YES = 'YES', "Yes"
-        NO = 'NO', "No"
-        NEITHER = 'NTR', "Neither"
-    
-    Sentence = models.ForeignKey("gui.Sentence", null = False, on_delete=models.PROTECT)
-    Label = models.CharField(max_length=3, choices=AnnotationLabel.choices, null = False)
-    Annotator = models.ForeignKey("accounts.CustomUser", null = False, on_delete=models.PROTECT)
-
-class SeedRegex(BaseModel):
-    Pattern = models.TextField(blank = False, null = False, unique = True)
-
-    @property
-    def regex(self):
-        return re.compile(self.Pattern, flags=re.IGNORECASE)
-
-class SentenceSeedRegex(BaseModel):
[…]

### 2021-11-24 nlp_annotator-dev/app/gui/static/js/script.js

@@ -1,154 +1,0 @@
-// COLLAPSIBLE VIEW FUNCTION
-var coll = document.getElementsByClassName("collapsible");
-var i;
-
-for (i = 0; i < coll.length; i++) {
-  coll[i].addEventListener("click", function() {
-    this.classList.toggle("active");
-    var content = this.nextElementSibling;
-    if (content.style.maxHeight){
-      content.style.maxHeight = null;
-    } else {
-      content.style.maxHeight = content.scrollHeight + "px";
-    } 
-  });
-}
-
-
-// FADE OUT ALERTS
-var close = document.getElementsByClassName("btn-close");
-var i;
-
-for (i = 0; i < close.length; i++) {
-  close[i].onclick = function(){
-    var div = this.parentElement;
-    div.style.opacity = "0";
-    setTimeout(function(){ div.style.display = "none"; }, 600);
-  }
-}
-
-
-// TABLESORTER
-$(function() {
-  $("table").tablesorter();
-});
-
-
-// CONDITIONAL FORM FOR PATIENT ANNOTATION
-// $('#id_CognitiveConcern').show();
-
-// var cognitive_concern = $('#id_CognitiveConcern option:selected').text();
-
-// if (cognitive_concern == 'Cognitive Concern') {
-  
-//   $('.id_SyndromicDiagnosis').show();
-
-//   var syndromic_dx = $('#id_SyndromicDiagnosis option:selected').text();
-
-//   if (syndromic_dx == 'Cognitive Impairment Not Dementia') {
-//     $('.id_CINDSeverity').show();
-//     $('.id_DementiaSeverity').hide();  
-//   } else if (syndromic_dx == 'Dementia') {
-//     $('.id_DementiaSeverity').show();
-//     $('.id_CINDSeverity').hide(); 
-//   } else {
-//     $('.id_DementiaSeverity').hide();
-//     $('.id_CINDSeverity').hide(); 
-//   }
-
-// } else {
-//   $('.id_SyndromicDiagnosis').hide();
-//   $('.id_DementiaSeverity').hide();  
-//   $('.id_CINDSeverity').hide(); 
-// }
-
-// $('#id_CognitiveConcern').change(function () {
-
-//   var cognitive_concern = $('#id_CognitiveConcern option:selected').text();
-
-//   if (cognitive_concern == 'Cognitive Concern') {
-    
-//     $('.id_SyndromicDiagnosis').show();
-
[…]

### 2021-11-24 nlp_annotator-dev/app/gui/tests.py

@@ -1,9 +1,0 @@
-from django.test import TestCase, Client, RequestFactory
-from django.shortcuts import reverse
-from accounts.models import CustomUser
-from gui.models import PatientDemographic
-from gui.views import annotator_home, user_profile
-
-
-class GuiViewsTests(TestCase):
-    pass

### 2021-11-24 nlp_annotator-dev/app/gui/views.py

@@ -1,969 +1,0 @@
-from django import forms
-from django.core.exceptions import ObjectDoesNotExist
-from django.forms import Form, ModelForm, Textarea
-from django.http.response import HttpResponseNotAllowed, HttpResponseNotFound
-from django.shortcuts import render, get_list_or_404, get_object_or_404, redirect
-from django.http import HttpResponse, HttpResponseRedirect, JsonResponse, HttpResponseForbidden
-from django.template import loader
-from django import forms
-from django.template.response import TemplateResponse
-from django.views.decorators.csrf import csrf_exempt
-from django.db.models import FilteredRelation, Q, Count
-from django.db import IntegrityError, transaction
-from django.core.paginator import Paginator
-import json
-import regex as re
-import functools
-import datetime
-from time import sleep
-from collections import Counter
-from itertools import chain, cycle
-import itertools
-from .models import (
-    PatientDemographic, 
-    Sentence, 
-    SentenceAssignment, SentenceAnnotation, AlwaysRegex, 
-    SentenceAlwaysRegex, SentenceSeedRegex
-)
-from accounts.forms import SignUpForm
-from django.contrib import messages
-
-from accounts.models import CustomUser
-User = CustomUser
-
-#reading in headers
-import pandas as pd
-
-# log-in and sign-up forms
-from django.contrib.auth.forms import AuthenticationForm
-from django.contrib.auth import login, logout, authenticate
-from django.contrib.auth.decorators import login_required
-
-Form = forms.Form
-
-
-def custom_error_404(request, exception):
-    template = loader.get_template('gui/error.html')
-    context = {'exception': "404"}
-    print("404 for: ", request)
-    return HttpResponse(template.render(context, request), status, status=404)
-
-def custom_error_500(request):
-    template = loader.get_template('gui/error.html')
-    context = {'exception': "500"}
-    print("500 for: ", request)
-    return HttpResponse(template.render(context, request), status=500)
-
-def custom_error_403(request, exception):
-    template = loader.get_template('gui/error.html')
-    context = {'exception': "403"}
-    print("403 for: ", request)
-    return HttpResponse(template.render(context, request), status=403)
-
-
-def get_page_params(request):
-    page = request.GET.get("page", 1)
-    page_size = request.GET.get("page_size", 100)
-    return page, page_size
-
-## INDEX VIEW
-def index(request):
-
-    # retrieve information of currently logged in user
[…]

### 2021-11-24 nlp_annotator-dev/app/load_data/gen_sample_data.py

@@ -1,55 +1,0 @@
-import csv
-import json
-from pathlib import Path
-from faker import Faker
-import random
-from datetime import datetime, timedelta
-
-directory = Path(__file__).parent
-
-fake = Faker()
-
-patients = 406
-patient_ids = [fake.unique.ean(length=13) for _ in range(patients)]
-
-first_date = datetime(year=2000, month=1, day=1)
-
-rows = []
-for patient_id in patient_ids:
-    encounter_ids = [
-        fake.unique.ean(length=8)
-        for _ in range(random.randint(1, 5))
-    ]
-    for encounter_id in encounter_ids:
-        note_ids = [fake.unique.ean(length=13) for _ in range(random.randint(1, 3))]
-        days = random.randint(40, 4586)
-        date = (
-            first_date + timedelta(days=days)
-        )
-        date = date.strftime("%Y-%m-%d")
-        for note_id in note_ids:
-            for sentence in [fake.paragraph(nb_sentences=4) for _ in range(random.randint(1, 3))]:
-                words = sentence.split()
-                num_matches = random.randint(1, len(words))
-                regex_matches = random.choices(words, k=num_matches)
-                row = {
-                    "PatientID": patient_id,
-                    "MRN": patient_id,
-                    "EMPI": patient_id,
-                    "PatientEncounterID": encounter_id,
-                    "NoteID": note_id,
-                    "ContactDTS": date,
-                    "regex_sent": json.dumps(sentence),
-                    "regex_match": json.dumps(regex_matches)
-                }
-                rows.append(row)
-
-with open(directory / "test_data.csv", "w") as f:
-    w = csv.DictWriter(f, fieldnames=rows[0].keys())
-    w.writeheader()
-    w.writerows(rows)
-
-print(f"Wrote {len(rows)} rows")
-
-
-

### 2021-11-24 nlp_annotator-dev/app/load_data/load_data.py

@@ -1,88 +1,0 @@
-# %run load_data/load_data.py
-
-# import libraries
-import csv, os
-import json
-from pathlib import Path
-import django.shortcuts
-from gui.models import Sentence, SeedRegex, PatientDemographic, Note
-import sys
-
-csv.field_size_limit(1000000000)
-
-# everything is relative to this file
-ROOT_DIR = Path(__file__).parent
-
-# specify the import filename
-filename = "char_limit.csv"
-
-columns = [
-    "PatientID",
-    "MRN",
-    "EMPI",
-    "PatientEncounterID", 
-    "NoteType",
-    "NoteID",
-    "Sentence",
-    "RegexMatches"
-]
-column_overrides = {
-    "Sentence": "regex_sent",
-    "RegexMatches": "regex_match"
-}
-column_mapping = {
-    c: column_overrides.get(c, c) for c in columns
-}
-
-print("CM: ", column_mapping)
-
-patients = {}
-notes = {}
-regexes = {}
-# read file and create patients, notes and seed regexes
-with open(ROOT_DIR / filename, "r", encoding = 'utf-8') as f:
-    rows = csv.DictReader(f)
-    patient_ids = set() # (patient_id, mrn, empi)
-    note_ids = set() # (patient_id, note_id, encounter_id)
-    all_regexes = set()
-    for row in rows:
-        pid = row[column_mapping["PatientID"]]
-        mrn = row[column_mapping["MRN"]]
-        empi = row[column_mapping["EMPI"]]
-        patient_ids.add((pid, mrn, empi))
-        nid = row[column_mapping["NoteID"]]
-        eid = row[column_mapping["PatientEncounterID"]]
-        note_ids.add((pid, nid, eid))
-        regex_match = row[column_mapping['RegexMatches']]
-        try:
-            regexes = json.loads(regex_match)
-            for regex in regexes:
-                all_regexes.add(regex)
-        except:
-            pass
-    for patient_id, mrn, empi in patient_ids:
-        p = PatientDemographic(PatientID=patient_id, MRN=mrn, EMPI=empi).save()
-        patients[patient_id] = p
-    #print("NoteIDS: ", note_ids)
-    for patient_id, note_id, encounter_id in note_ids:
-        #print("PI: ", patient_id, "NI: ", note_id, "EI: ", encounter_id, "Date: ", Note(PatientID=patient_id, PatientEncounterID=encounter_id, NoteID=note_id).Date)
[…]

### 2021-11-24 nlp_annotator-dev/app/migrate.py

@@ -1,12 +1,0 @@
-# migrate when you change the schema (i.e. framework for database)
-# when you change values, no need to remigrate
-
-# python manage.py makemigrations
-# python manage.py migrate
-# python manage.py shell
-
-from gui.models import PatientDemographic, PatientYear, Note, Timeline
-
-# n = Note.objects.get(PATIENT_NUM=1)
-# n.IDX = 1  # change field
-# n.save() # this will update only

### 2021-11-24 Submission/Paper/ML4H/Paper.tex

@@
  %\documentclass[tablecaption=bottom]{jmlr}% journal article
+ %\pdfoutput=1
  \documentclass[pmlr,twocolumn,10pt]{jmlr} % W&CP article
@@
 \centering
-\begin{center}\addr Massachusetts General Hospital, Boston, MA\end{center}
+\begin{center}\addr Massachusetts General Hospital and McCance Center for Brain Health, Boston, MA 
+\end{center}
 }
@@
 \paragraph{Dataset}
-\label{sec:Dataset} Our dataset consisted of a cohort (N = 16,428) of patients from the Mass General Brigham (MGB) HealthCare \citep{jpm6010011} (formerly Partner's Healthcare, comprising two major academic hospitals, community hospitals, and community health centers in the Boston area) system who were older than 60 years (as of July 13, 2021), had \textit{APOE} genotypes—the biggest genetic risk factor for Alzheimer's disease  \citep{mahley2000apolipoprotein}—available from the MGB BioBank, and at least one clinician note with a dementia-related keyword.
+\label{sec:Dataset} Our dataset consisted of a cohort (N = 16,428) of patients from the Mass General Brigham (MGB) HealthCare  (formerly Partner's Healthcare, comprising two major academic hospitals, community hospitals, and community health centers in the Boston area) system who were older than 60 years (as of July 13, 2021), had \textit{APOE} genotypes—the biggest genetic risk factor for Alzheimer's disease  \citep{mahley2000apolipoprotein}—available from the MGB BioBank, and at least one clinician note with a dementia-related keyword.
 \tableref{tab:table1} shows demographics of the cohort of patients.
@@
 \label{sec:Transformer}  
-\paragraph{(2) Transformer Based Sequence Classification Language Model} We utilized a pre-trained language model called ClinicalBERT \citep{alsentzer2019publicly}, which was trained on the MIMIC II \citep{saeed2011multiparameter} database containing EHR records from ICU patients.
+\paragraph{(2) Transformer Based Sequence Classification Language Model} We utilized a pre-trained language model called ClinicalBERT \citep{alsentzer-etal-2019-publicly}, which was trained on the MIMIC II \citep{saeed2011multiparameter} database containing EHR records from ICU patients.
 We used the implementation in the Huggingface Transformers \citep{Wolf2019HuggingFacesTS} and Simpletransformers \citep{simple2020thilina} packages.
@@
 \centering 
-\includegraphics[scale=0.5]{bert_patient_predictions.png}
+\includegraphics[scale=0.5]{Confusion_Matrix.png}
 

### 2021-12-05 Med-ICD-Counts-Model/baseline_model.R
preparing davidson codebase - more reorganization

@@ -1,91 +1,0 @@
-library(glmnet)
-library(ROCR)
-library(tidyverse)
-library(data.table)
-library(lubridate)
-
-# read in EDW data 
-meds<-fread("data/medications.csv")
-diagnoses <- fread('data/icd_diagnosis.csv')
-diagnoses[,Date := ymd(ContactDTS)]
-meds[,Date := ymd(OrderDTS)]
-
-# date time filters
-#diagnoses <- diagnoses[Date >= '2018-01-01' & Date <= '2018-12-31']
-#meds <- meds[Medication_Date >= '2018-01-01' & Date <= '2018-12-31']
-
-AD_Meds <- c("Galantamine", "Donepezil", "Rivastigmine", "Razadyne", "Razadyne ER", "Aricept", "Exelon","Namenda","Memantine");
-
-meds[,AD := grepl(paste(AD_Meds, collapse="|"),MedicationDSC,ignore.case = T)]
-
-diagnoses[,AD := (grepl("Dementia|Alzheimer's|cognitive impairment|memory loss|frontotemporal dementia",DiagnosisNM,ignore.case = TRUE) | grepl("^290|^294|^331|G30|G31|780.93",ICD9CD,ignore.case = TRUE) | grepl("^290|^294|^331|G30|G31|780.93",ICD10CD,ignore.case = TRUE)) & !grepl("hydrocephalus",DiagnosisNM,ignore.case = TRUE)];
-
-structured_variables <- data.table(PatientID = unique(c(diagnoses$PatientID,meds$PatientID)))
-
-structured_variables[diagnoses[AD==1,.N,by=.(PatientID)],on=.(PatientID),Dx_Count := i.N]
-structured_variables[meds[AD==1,.N,by=.(PatientID)],on=.(PatientID),Med_Count := i.N]
-structured_variables[is.na(structured_variables)] <- 0
-structured_variables[,AD_Med_or_ICD_Code := ifelse(Dx_Count > 0 | Med_Count > 0,1,0)]
-
-
-# tanish set 
-
-tanish <- fread('data/20K_sample.csv')
-# need EMPI for tanish's set, get from EDW data
-tanish[rbindlist(list(meds,diagnoses),fill =T),on=.(patient_id = PatientID),EMPI := i.EMPI]
-# 0 = no, 1 = neither, 2 = CI
-tanish[,Binary_CI := ifelse(prediction == 2,1,0)]
-# at least one CI, give 1 for patient level cognitive impairment 
[…]

### 2021-12-05 Model-Performance/BertV2.py

@@ -1,273 +1,0 @@
-# base libraries
-import numpy as np
-import pandas as pd
-import regex as re
-import itertools
-import sklearn.metrics as sk
-from functools import reduce
-
-# deep learning libraries
-import torch
-import transformers
-from sklearn.model_selection import train_test_split
-from simpletransformers.classification import ClassificationModel, ClassificationArgs
-
-# hyperparameter optimization
-import optuna
-from optuna.samplers import TPESampler
-import optuna.visualization.matplotlib as oviz
-
-# file system manipulation
-import os
-import shutil
-from pathlib import Path
-import pickle
-import copy
-
-# logging
-import logging
-import time
-
-# define directories
-data_dir = Path("../Data")
-results_dir = Path("../Results/")
-
-# set seeds
-np.random.seed(1234)
-torch.manual_seed(1234)
-
-# check CUDA availability
-cuda_available = torch.cuda.is_available()
-print("Is CUDA available? ", "Yes" if cuda_available else "No")
-
-always_patterns = pd.read_csv("input_optimized.csv") 
-manual_review = pd.read_csv(r"C:\\Users\\MIND_DS\\Dropbox (Partners HealthCare)\\NLP\\Tanish\\APOE-SLAT\\Modeling\\test_and_validation.csv")
-manual_review = manual_review[['patient_id', 'sequence', 'annotator_label']]
-always_patterns = always_patterns[['patient_id', 'sequence', 'annotator_label']]
-
-def split_data(trial):
-    # stratify across sequences with and without always pattern matches and class_label (Y, N, NTR)    
-    # stratifying across sequences with always pattern
-    X_train, X_other = train_test_split(always_patterns, random_state = 0,test_size = 0.1, stratify = always_patterns["annotator_label"].to_numpy())
-    X_valid, X_test = train_test_split(X_other, random_state = 0, test_size = 0.25, stratify = X_other["annotator_label"].to_numpy())
-    
-    # stratifying across sequences without always pattern
-    X_train_2, X_other_2 = train_test_split(manual_review, random_state = 0,test_size = 0.6, stratify = manual_review["annotator_label"].to_numpy())
-    X_valid_2, X_test_2 = train_test_split(X_other_2, random_state = 0, test_size = (0.25/0.6), stratify = X_test_2["annotator_label"].to_numpy())
-    
[…]

### 2021-12-21 Annotation-Tool/app/annotator_gui/settings.py
added SLAT code

@@ -1,0 +1,156 @@
+"""
+Django settings for annotator_gui project.
+
+Generated by 'django-admin startproject' using Django 3.1.
+
+For more information on this file, see
+https://docs.djangoproject.com/en/3.1/topics/settings/
+
+For the full list of settings and their values, see
+https://docs.djangoproject.com/en/3.1/ref/settings/
+"""
+
+from pathlib import Path
+import os  # see line 123
+from django.contrib.messages import constants as messages # to assign Bootstrap alerts to Django message tags
+
+# Build paths inside the project like this: BASE_DIR / 'subdir'.
+BASE_DIR = Path(__file__).resolve(strict=True).parent.parent
+
+
+# Quick-start development settings - unsuitable for production
+# See https://docs.djangoproject.com/en/3.1/howto/deployment/checklist/
+
+# SECURITY WARNING: keep the secret key used in production secret!
+SECRET_KEY = '6a8a0d78d99677f21c18eaa3773541b7d3eb918e4897'
+
+# SECURITY WARNING: don't run with debug turned on in production!
+ENVIRONMENT = os.getenv("DJANGO_ENVIRONMENT", "dev")
+if ENVIRONMENT == "dev":
+    DEBUG = True
+elif ENVIRONMENT == "prod":
+    DEBUG = False
+else:
+    raise ValueError(f"Invalid DJANGO_ENVIRONMENT {ENVIRONMENT}! Must be 'dev' or 'prod'")
+
+
+_hosts = ['127.0.0.1', 'localhost', '0.0.0.0', 'rc-nat.partners.org', 'nat.partners.org', 'apoe.nat.partners.org']
+ALLOWED_HOSTS = _hosts
+
+CSRF_TRUSTED_ORIGINS = _hosts
+CSRF_COOKIE_SECURE = True
+
+SECURE_PROXY_SSL_HEADER = ('HTTP_X_FORWARDED_PROTO', 'https')
+
+# Application definition
+
+INSTALLED_APPS = [
+    'gui.apps.GuiConfig',
+    'django.contrib.admin',
+    'django.contrib.auth',
+    'django.contrib.contenttypes',
+    'django.contrib.sessions',
+    'django.contrib.messages',
+    'django.contrib.staticfiles',
+    'import_export', # for django-import-export library, install via pip install django-import-export
+    # 'csvimport.app.CSVImportConf',  # use AppConfig for django >=1.7 csvimport >=2.2
+    'django_extensions',
+    'accounts',
+]
+
[…]

### 2021-12-21 Annotation-Tool/app/annotator_gui/urls.py

@@ -1,0 +1,33 @@
+"""annotator_gui URL Configuration
+
+The `urlpatterns` list routes URLs to views. For more information please see:
+    https://docs.djangoproject.com/en/3.1/topics/http/urls/
+Examples:
+Function views
+    1. Add an import:  from my_app import views
+    2. Add a URL to urlpatterns:  path('', views.home, name='home')
+Class-based views
+    1. Add an import:  from other_app.views import Home
+    2. Add a URL to urlpatterns:  path('', Home.as_view(), name='home')
+Including another URLconf
+    1. Import the include() function: from django.urls import include, path
+    2. Add a URL to urlpatterns:  path('blog/', include('blog.urls'))
+"""
+from django.contrib import admin
+from django.urls import include, path
+
+# for errors
+from django.conf.urls import handler404, handler500, handler403
+
+urlpatterns = [
+    # path has route, a string that contains a URL pattern and view. 
+    # When Django finds a matching pattern, it calls the specified view \
+    # function with an HttpRequest object as the first argument and any “captured” \
+    # values from the route as keyword arguments
+    path('admin/', admin.site.urls),
+    path('', include('gui.urls'))
+]
+
+handler404 = 'gui.views.custom_error_404'
+handler500 = 'gui.views.custom_error_500'
+handler403 = 'gui.views.custom_error_403'

### 2021-12-21 Annotation-Tool/app/gui/management/commands/load.py

@@ -1,0 +1,21 @@
+from django.core.management.base import BaseCommand, CommandError
+from accounts.models import CustomUser as User
+from gui.models import Sentence, SentenceAssignment
+from ._load_data import load_data
+
+class Command(BaseCommand):
+    help = 'Assign random sentences'
+
+    def add_arguments(self, parser):
+        parser.add_argument('filename', type=str)
+        parser.add_argument('-s', '--start_row', type=int, default=1)
+
+    def handle(self, *args, **options):
+        try:
+            print(f"Starting from row {options['start_row']}")
+            load_data(options['filename'], options['start_row'])
+        except Exception as e:
+            self.stderr.write("Encountered error %s" % e)
+            raise
+        self.stdout.write("Finished!")
+                

### 2021-12-21 Annotation-Tool/app/gui/management/commands/seed.py

@@ -1,0 +1,33 @@
+from faker import Faker
+from django.core.management.base import BaseCommand, CommandError
+from gui.models import Sentence, SeedRegex, SentenceSeedRegex
+import random
+
+
+class Command(BaseCommand):
+    help = 'Generate random sentences'
+    fake = Faker()
+
+    def add_arguments(self, parser):
+        parser.add_argument('num', type=int)
+
+    def handle(self, *args, **options):
+        if options['num'] < 1:
+            self.stdout.write(self.style.ERROR('Number of sentences must be greater than 0!'))
+        else:
+            for _ in range(options['num']):
+                text = self.fake.paragraph(nb_sentences=1, variable_nb_sentences=False)
+                sentence = Sentence(Contents=text)
+                sentence.save()
+                seed_regexes(sentence)
+            self.stdout.write(self.style.SUCCESS('Added %s sentences' % options['num']))
+        
+
+def seed_regexes(sentence):
+    words = sentence.Contents.split()
+    k = max(len(words) // 3, 1)
+    seed_words = random.sample(words, k)
+    for word in seed_words:
+        regex, _ = SeedRegex.objects.get_or_create(Pattern=word)
+        assoc = SentenceSeedRegex(Sentence=sentence, SeedRegex=regex)
+        assoc.save()

### 2021-12-21 Annotation-Tool/app/gui/models.py

@@ -1,0 +1,103 @@
+import re
+
+from django.db import models
+
+# to reset databsae:
+    # run python manage.py reset_db (from django-extensions package)
+
+# to delete all data from the table:
+# python manage.py shell
+# >> from gui.models import PatientDemographic, PatientYear, Note
+# >> PatientDemographic.objects.all().delete()
+# >> PatientYear.objects.all().delete()
+# >> Note.objects.all().delete()
+
+# to add data:
+# update .csv files in load_data/data
+# python manage.py shell
+# >> %run load_data/load_data.py
+
+# each element in choices is a tuple of actual value to be stored, then human readable translation
+# in our case, these are the same
+
+BaseModel = models.Model
+
+
+class Sentence(BaseModel):
+    Contents = models.TextField(blank = False, null = False)
+    Note = models.ForeignKey("gui.Note", null = False, on_delete=models.PROTECT)
+
+    @classmethod
+    def unassigned(cls):
+        return cls.objects.filter(sentenceassignment__isnull=True).order_by('id')
+
+
+class SentenceAssignment(BaseModel):
+    User = models.ForeignKey("accounts.CustomUser", null = False, on_delete=models.PROTECT)
+    Sentence = models.ForeignKey("gui.Sentence", null = False, on_delete=models.PROTECT)
+    CompletedAt = models.DateTimeField(null=True)
+    class Meta:
+        constraints = [
+            models.UniqueConstraint(fields=['User', 'Sentence'], name='uq_assignment')
+        ]
+
+class SentenceAnnotation(BaseModel):
+    class AnnotationLabel(models.TextChoices):
+        YES = 'YES', "Yes"
+        NO = 'NO', "No"
+        NEITHER = 'NTR', "Neither"
+    
+    Sentence = models.ForeignKey("gui.Sentence", null = False, on_delete=models.PROTECT)
+    Label = models.CharField(max_length=3, choices=AnnotationLabel.choices, null = False)
+    Annotator = models.ForeignKey("accounts.CustomUser", null = False, on_delete=models.PROTECT)
+
+class SeedRegex(BaseModel):
+    Pattern = models.TextField(blank = False, null = False, unique = True)
+
+    @property
+    def regex(self):
+        return re.compile(self.Pattern, flags=re.IGNORECASE)
+
+class SentenceSeedRegex(BaseModel):
[…]

### 2021-12-21 Annotation-Tool/app/gui/templatetags/notes_filter.py

@@ -1,0 +1,129 @@
+from django import template
+from django.utils import html
+import regex as re
+
+register = template.Library()
+
+@register.filter(name = 'filter_note')
+def filter_note(notelist, pk):
+    # filters notes by patient ID
+    return notelist.filter(PatientID = pk)
+
+@register.filter(name = 'filter_patient_year')
+def filter_patient_year(patientyearlist, pk):
+    # filters notes by patient ID
+    return patientyearlist.filter(PatientID = pk)
+
+
+@register.filter(name = 'get_age')
+def get_age(patient, notelist):
+
+    birth = patient.BirthDTS
+    first_contact = notelist[0].ContactDTS
+
+    if first_contact is not None and birth is not None: 
+        age_at_encounter = first_contact - birth
+        years_at_encounter = divmod(age_at_encounter.days, 365)[0]
+        return(str(years_at_encounter) + " YR")
+    else:
+        return("Unavailable")
+
+@register.filter(name = 'get_sex')
+def get_sex(patient):
+    return(patient.SexDSC[0])
+
+
+# for the note level annotation; this feature is not currently used
+@register.filter(name = 'fill_table')
+def fill_table(note):
+    return("#F1F1F1")
+    # if note.Label == "0":
+    #     return("#D1E7DD")
+    # elif note.Label == "1":
+    #     return("#F8D7DA")
+    # else:
+    #     return("#F1F1F1")
+
+
+@register.filter(name = 'fill_patient_table')
+def fill_patient_table(patient):
+    if patient.CognitiveConcern == "No Cognitive Concern":
+        return("#D1E7DD")
+    elif patient.CognitiveConcern == "Cognitive Concern":
+        return("#F8D7DA")
+    elif patient.CognitiveConcern == "Undetermined":
+        return("#E4D5C8")
+    else:
+        return("#F1F1F1")
+
+
+@register.filter(name = 'fill_patient_collapsible')
+def fill_patient_collapsible(patient):
+    if patient.CognitiveConcern == "No Cognitive Concern":
+        return("background-color: #5FAB88; --my-hover-var: #BCDCCD;")
+    elif patient.CognitiveConcern == "Cognitive Concern":
+        return("background-color: #E0525D; --my-hover-var: #F3B9BF;")
+    elif patient.CognitiveConcern == "Undetermined":
[…]

### 2021-12-21 Annotation-Tool/app/gui/tests.py

@@ -1,0 +1,9 @@
+from django.test import TestCase, Client, RequestFactory
+from django.shortcuts import reverse
+from accounts.models import CustomUser
+from gui.models import PatientDemographic
+from gui.views import annotator_home, user_profile
+
+
+class GuiViewsTests(TestCase):
+    pass

### 2021-12-21 Annotation-Tool/app/gui/urls.py

@@ -1,0 +1,27 @@
+from django.urls import include, path
+
+# for favicon
+from django.contrib.staticfiles.storage import staticfiles_storage
+from django.views.generic.base import RedirectView
+from django.conf import settings
+
+from . import views
+
+urlpatterns = [
+    path('', views.index, name='index'),
+    path('about',views.about,name='about'),
+    path('search',views.search,name='search'),
+    path('consensus',views.group_consensus,name='group_consensus'),
+    path('login',views.user_login,name='user_login'),
+    path('logout', views.user_logout, name='user_logout'),
+    path('profile', views.user_profile, name='user_profile'),
+    path('home',views.annotator_home,name='annotator_home'),
+    path('highlight',views.highlight_sentence,name='highlight_sentence'),
+    path('annotate/<int:patient_id>/<int:local_note_id>',views.show_note,name='show_note'),
+    path("favicon.ico", RedirectView.as_view(url=staticfiles_storage.url("favicon.ico"))),
+    path("admin-menu", views.admin_menu, name='admin_menu'),
+    path("new-user", views.create_user, name='new_user'),
+    path("assign", views.assign_new, name='assign_new'),
+    path("patterns", views.always_pattern_list, name="pattern_list"),
+    path("pattern/<int:pattern_id>/undo", views.undo_always_pattern, name="undo_pattern"),
+]

### 2021-12-21 Annotation-Tool/app/gui/views.py

@@ -1,0 +1,963 @@
+from django import forms
+from django.core.exceptions import ObjectDoesNotExist
+from django.forms import Form, ModelForm, Textarea
+from django.http.response import HttpResponseNotAllowed, HttpResponseNotFound
+from django.shortcuts import render, get_list_or_404, get_object_or_404, redirect
+from django.http import HttpResponse, HttpResponseRedirect, JsonResponse, HttpResponseForbidden
+from django.template import loader
+from django import forms
+from django.template.response import TemplateResponse
+from django.views.decorators.csrf import csrf_exempt
+from django.db.models import FilteredRelation, Q, Count
+from django.db import IntegrityError, transaction
+from django.core.paginator import Paginator
+import json
+import regex as re
+import functools
+import datetime
+from time import sleep
+from collections import Counter
+from itertools import chain, cycle
+import itertools
+from .models import (
+    PatientDemographic, 
+    Sentence, 
+    SentenceAssignment, SentenceAnnotation, AlwaysRegex, 
+    SentenceAlwaysRegex, SentenceSeedRegex
+)
+from accounts.forms import SignUpForm
+from django.contrib import messages
+
+from accounts.models import CustomUser
+User = CustomUser
+
+#reading in headers
+import pandas as pd
+
+# log-in and sign-up forms
+from django.contrib.auth.forms import AuthenticationForm
+from django.contrib.auth import login, logout, authenticate
+from django.contrib.auth.decorators import login_required
+
+Form = forms.Form
+
+
+def custom_error_404(request, exception):
+    template = loader.get_template('gui/error.html')
+    context = {'exception': "404"}
+    print("404 for: ", request)
+    return HttpResponse(template.render(context, request), status, status=404)
+
+def custom_error_500(request):
+    template = loader.get_template('gui/error.html')
+    context = {'exception': "500"}
+    print("500 for: ", request)
+    return HttpResponse(template.render(context, request), status=500)
+
+def custom_error_403(request, exception):
+    template = loader.get_template('gui/error.html')
+    context = {'exception': "403"}
+    print("403 for: ", request)
+    return HttpResponse(template.render(context, request), status=403)
+
+
+def get_page_params(request):
+    page = request.GET.get("page", 1)
+    page_size = request.GET.get("page_size", 100)
+    return page, page_size
+
+## INDEX VIEW
+def index(request):
+
+    # retrieve information of currently logged in user
[…]

### 2021-12-21 Annotation-Tool/app/manage.py

@@ -1,0 +1,22 @@
+#!/usr/bin/env python
+"""Django's command-line utility for administrative tasks."""
+import os
+import sys
+
+
+def main():
+    """Run administrative tasks."""
+    os.environ.setdefault('DJANGO_SETTINGS_MODULE', 'annotator_gui.settings')
+    try:
+        from django.core.management import execute_from_command_line
+    except ImportError as exc:
+        raise ImportError(
+            "Couldn't import Django. Are you sure it's installed and "
+            "available on your PYTHONPATH environment variable? Did you "
+            "forget to activate a virtual environment?"
+        ) from exc
+    execute_from_command_line(sys.argv)
+
+
+if __name__ == '__main__':
+    main()

### 2021-12-23 Web-Tool/app/app/settings.py
django project config

@@ -1,0 +1,125 @@
+"""
+Django settings for app project.
+
+Generated by 'django-admin startproject' using Django 3.2.5.
+
+For more information on this file, see
+https://docs.djangoproject.com/en/3.2/topics/settings/
+
+For the full list of settings and their values, see
+https://docs.djangoproject.com/en/3.2/ref/settings/
+"""
+
+from pathlib import Path
+
+# Build paths inside the project like this: BASE_DIR / 'subdir'.
+BASE_DIR = Path(__file__).resolve().parent.parent
+
+
+# Quick-start development settings - unsuitable for production
+# See https://docs.djangoproject.com/en/3.2/howto/deployment/checklist/
+
+# SECURITY WARNING: keep the secret key used in production secret!
+SECRET_KEY = 'django-insecure-70h5uvv6yc_ua2lo1%)fd$l$bae999%hy-%qv&jx1iykd&&sic'
+
+# SECURITY WARNING: don't run with debug turned on in production!
+DEBUG = True
+
+ALLOWED_HOSTS = []
+
+
+# Application definition
+
+INSTALLED_APPS = [
+    'django.contrib.admin',
+    'django.contrib.auth',
+    'django.contrib.contenttypes',
+    'django.contrib.sessions',
+    'django.contrib.messages',
+    'django.contrib.staticfiles',
+]
+
+MIDDLEWARE = [
+    'django.middleware.security.SecurityMiddleware',
+    'django.contrib.sessions.middleware.SessionMiddleware',
+    'django.middleware.common.CommonMiddleware',
+    'django.middleware.csrf.CsrfViewMiddleware',
+    'django.contrib.auth.middleware.AuthenticationMiddleware',
+    'django.contrib.messages.middleware.MessageMiddleware',
+    'django.middleware.clickjacking.XFrameOptionsMiddleware',
+]
+
+ROOT_URLCONF = 'app.urls'
+
+TEMPLATES = [
+    {
+        'BACKEND': 'django.template.backends.django.DjangoTemplates',
+        'DIRS': [],
+        'APP_DIRS': True,
+        'OPTIONS': {
+            'context_processors': [
+                'django.template.context_processors.debug',
+                'django.template.context_processors.request',
+                'django.contrib.auth.context_processors.auth',
+                'django.contrib.messages.context_processors.messages',
[…]

### 2021-12-23 Web-Tool/app/gui/views.py
starting sequence extraction pipeline code

@@ -1,3 +1,4 @@
 from django.shortcuts import render
 
-# Create your views here.
+def sequence_extraction_pipeline():
+    pass 

### 2021-12-23 Web-Tool/app/gui/views.py
pipeline code up to finding regex_matches

@@ -1,4 +1,78 @@
 from django.shortcuts import render
 
-def sequence_extraction_pipeline():
-    pass 
+import pandas as pd
+import regex as re
+
+regex = pd.read_csv(r"static/keywords.csv")
+
+def compile_regex():
+    # importing keywords and case
+    k = regex["REGEX"].to_list()
+    c = regex["CASE"].to_list()
+    p_list = []
+
+    # compiling regex
+    for i in range(len(k)):
+        if (c[i] == 1):
+            p_list.append(re.compile(k[i]))
+        else:
+            p_list.append(re.compile(k[i], re.IGNORECASE))
+
+    return p_list 
+
+def read_notes(note_txt):
+    # dataframe to save notes to 
+    note_df = pd.DataFrame(columns = ["NoteTXT"])
+
+    # opening file and extracting lines
+    notes = open(note_txt, "r")
+    lines = notes.readlines()
+    note_list = []
+
+    for line in lines:
+        # print("line", line.strip())
+        note_list.append(line.strip())
+
+    note_df["NoteTXT"] = note_list
+    
+    return note_df 
+
+def find_matches(notes, keywords):
+    # array for storing keyword matches
+    matches = [] 
+
+    for note in notes["NoteTXT"]:
+        curr = []
+
+        # finding matches 
+        for p in (keywords):
+            m = list(set(re.findall(p, note)))
+            m = list(set(map(str.lower, m)))
+            if (m != []):
+                curr.append("".join(m))
+
+        matches.append(str(curr))
+
+    return matches 
+
+def sequence_extraction_pipeline(note_txt):
+    """
+    note_txt: file path (?) that contains all notes, notes are separated by a line
+    """
+    # TODO: clean up extraction pipeline from web form 
+    notes = read_notes(note_txt)
+
+    # creation of compiled keyword list
+    keywords = compile_regex()
+
+    # getting matches from notes
+    matches = find_matches(notes, keywords)
+    notes["regex_matches"] = matches  
+
+    return notes 
+
+def tester():
+    notes = sequence_extraction_pipeline(r"C:\Users\tanis\OneDrive - Phillips Exeter Academy\Data\Programming\APOE-SLAT\Web-Tool\app\gui\static\test_notes.txt")
+    print(notes["regex_matches"]) 
+
+tester()

### 2021-12-23 Web-Tool/app/gui/views.py
finished up to merged context windows

@@ -1,3 +1,5 @@
+# Author: Tanish Tyagi
+
 from django.shortcuts import render
 
 import pandas as pd
@@ -21,6 +23,9 @@ def compile_regex():
     return p_list 
 
 def read_notes(note_txt):
+    """
+    note_txt: file path that contains notes
+    """
     # dataframe to save notes to 
     note_df = pd.DataFrame(columns = ["NoteTXT"])
 
@@ -38,6 +43,10 @@ def read_notes(note_txt):
     return note_df 
 
 def find_matches(notes, keywords):
+    """
+    notes: dataframe
+    keywords: list of compiled regex expressions for 18 dementia-related keywords
+    """
     # array for storing keyword matches
     matches = [] 
 
@@ -55,9 +64,95 @@ def find_matches(notes, keywords):
 
     return matches 
 
+def find_character_locations(notes, keywords):
+    """
+    notes: dataframe 
+    keywords: list of compiled regex expressions for 18 dementia-related keywords
+    """
+    # array for storing character locations of matches; list of tuples
+    locations = []
+
+    for r in (notes['NoteTXT']):
+        curr_loc = []
+
+        # finding character locations
+        for p in keywords:
+            for match in re.finditer(p ,r):
+                curr_loc.append(match.span())
+                
+        # TODO: decide if need to keep this code
+        # current logic; if no character location is found, something is wrong
+        if (curr_loc == []):
+            print("STOP")
+            break
+            
+        locations.append(curr_loc)
+    
+    return locations 
+
+# TODO: This function may not be needed if rows that have no keyword matches are kept 
+def create_context_windows(notes, i):
+    """
+    notes: dataframe 
+    i: int that represents index in notes
+    """
+    merged = []
+    context_length_one_direction = 100
+    
+    for j in range(len(notes["regex_location"][i])):
+        start = notes["regex_location"][i][j][0]
+        end = notes["regex_location"][i][j][1]
+
+        # creating context windows
+        prune_start = False
+        prune_end = False
+
+        if (start - context_length_one_direction <= 0):
+            start = 0
+            prune_start = True
+        if (end + context_length_one_direction >= len(notes["NoteTXT"][i]) - 1):
+            end = len(notes["NoteTXT"][i]) - 1
+            prune_end = True 
+
+        if (prune_start and prune_end):
+            merged.append((start, end))
+        else:
+            if (prune_start):
+                merged.append((start, end + context_length_one_direction))
[…]

### 2021-12-23 Web-Tool/app/gui/views.py
need to finish last 2 steps of pipeline

@@ -5,6 +5,10 @@ from django.shortcuts import render
 import pandas as pd
 import regex as re
 
+from transformers import AutoTokenizer
+
+# constants
+tokenizer = AutoTokenizer.from_pretrained("emilyalsentzer/Bio_ClinicalBERT")
 regex = pd.read_csv(r"static/keywords.csv")
 
 def compile_regex():
@@ -127,6 +131,7 @@ def create_context_windows(notes, i):
     
     return merged
 
+# TODO: will not be needed for notes that don't have keyword matches 
 def merge(intervals):  
     """
     intervals: list of tuples representing context windows 
@@ -149,6 +154,106 @@ def merge(intervals):
             
     ans.append(tempans)
     return ans
+
+# TODO: will not be needed for notes that don't have keyword matches 
+def pull_context_windows(notes, i, col):
+    """
+    notes: dataframe 
+    i: int that represents index in notes
+    col: name of column that has merged context windows 
+    """
+    # string that holds text for pulled context windows
+    sequence = ""
+    
+    for j in range(len(notes[col][i])):
+        # if multiple context windows per note
+        if j > 0 and sequence != "":
+            sequence += " ----- "
+            
+        start = notes[col][i][j][0]
+        end = notes[col][i][j][1]
+        
+        sequence += notes["NoteTXT"][i][start : end]
+    
+    return sequence
+
+def clinical_bert_tokenize(notes, i, col):
+    """
+    notes: dataframe 
+    i: int that represents index in notes
+    col: name of column that has merged context windows 
+    """
+    tokens = tokenizer.encode_plus(notes[col][i], add_special_tokens = False, return_tensors = 'pt')
+
+    return (len(tokens['input_ids'][0]))
+
+def generate_padded_context_windows(notes, i):
+    """
+    notes: dataframe 
+    i: int that represents index in notes
+    """    
+    if (notes["token_length"][i] <= 400):
+        locs = list((notes["merged_row_location"][i]))
+        length = len(locs)
+        start = locs[0][0] 
+        end = locs[length - 1][1]
+        
+        #print(start, end)
+                
+        seq_length = 1000
+        length_to_add_one_side = int((seq_length - notes["sequence_length"][i]) / 2)
+        
+        #print(length_to_add_one_side, notes["sequence_length"][i])
+        
+        prune_start = False
[…]

### 2021-12-25 Web-Tool/app/gui/sequence_extraction_pipeline.py
sequence extraction pipeline done

@@ -1,0 +1,332 @@
+# Author: Tanish Tyagi
+
+import pandas as pd
+import regex as re
+import warnings
+warnings.filterwarnings("ignore")
+
+from transformers import AutoTokenizer
+
+# constants
+tokenizer = AutoTokenizer.from_pretrained("emilyalsentzer/Bio_ClinicalBERT")
+regex = pd.read_csv(r"static/keywords.csv")
+
+def compile_regex():
+    # importing keywords and case
+    k = regex["REGEX"].to_list()
+    c = regex["CASE"].to_list()
+    p_list = []
+
+    # compiling regex
+    for i in range(len(k)):
+        if (c[i] == 1):
+            p_list.append(re.compile(k[i]))
+        else:
+            p_list.append(re.compile(k[i], re.IGNORECASE))
+
+    return p_list 
+
+def read_notes(note_txt):
+    """
+    note_txt: file path that contains notes
+    """
+    # dataframe to save notes to 
+    note_df = pd.DataFrame(columns = ["NoteTXT"])
+
+    # opening file and extracting lines
+    notes = open(note_txt, "r")
+    lines = notes.readlines()
+    note_list = []
+
+    for line in lines:
+        # print("line", line.strip())
+        note_list.append(line.strip())
+
+    note_df["NoteTXT"] = note_list
+    
+    return note_df 
+
+def find_matches(notes, keywords):
+    """
+    notes: dataframe
+    keywords: list of compiled regex expressions for 18 dementia-related keywords
+    """
+    # array for storing keyword matches
+    matches = [] 
+
+    for note in notes["NoteTXT"]:
+        curr = []
+
+        # finding matches 
+        for p in (keywords):
+            m = list(set(re.findall(p, note)))
+            m = list(set(map(str.lower, m)))
+            if (m != []):
+                curr.append("".join(m))
+
+        matches.append(str(curr))
+
+    return matches 
+
+def find_character_locations(notes, keywords):
+    """
+    notes: dataframe 
+    keywords: list of compiled regex expressions for 18 dementia-related keywords
+    """
+    # array for storing character locations of matches; list of tuples
+    locations = []
+
+    for r in (notes['NoteTXT']):
+        curr_loc = []
+
+        # finding character locations
+        for p in keywords:
+            for match in re.finditer(p ,r):
+                curr_loc.append(match.span())
+                
+        # TODO: decide if need to keep this code
+        # current logic; if no character location is found, something is wrong
+        if (curr_loc == []):
[…]

### 2021-12-25 Web-Tool/app/gui/views.py

@@ -1,330 +1,3 @@
 # Author: Tanish Tyagi
 
 from django.shortcuts import render
-
-import pandas as pd
-import regex as re
-
-from transformers import AutoTokenizer
-
-# constants
-tokenizer = AutoTokenizer.from_pretrained("emilyalsentzer/Bio_ClinicalBERT")
-regex = pd.read_csv(r"static/keywords.csv")
-
-def compile_regex():
-    # importing keywords and case
-    k = regex["REGEX"].to_list()
-    c = regex["CASE"].to_list()
-    p_list = []
-
-    # compiling regex
-    for i in range(len(k)):
-        if (c[i] == 1):
-            p_list.append(re.compile(k[i]))
-        else:
-            p_list.append(re.compile(k[i], re.IGNORECASE))
-
-    return p_list 
-
-def read_notes(note_txt):
-    """
-    note_txt: file path that contains notes
-    """
-    # dataframe to save notes to 
-    note_df = pd.DataFrame(columns = ["NoteTXT"])
-
-    # opening file and extracting lines
-    notes = open(note_txt, "r")
-    lines = notes.readlines()
-    note_list = []
-
-    for line in lines:
-        # print("line", line.strip())
-        note_list.append(line.strip())
-
-    note_df["NoteTXT"] = note_list
-    
-    return note_df 
-
-def find_matches(notes, keywords):
-    """
-    notes: dataframe
-    keywords: list of compiled regex expressions for 18 dementia-related keywords
-    """
-    # array for storing keyword matches
-    matches = [] 
-
-    for note in notes["NoteTXT"]:
-        curr = []
-
-        # finding matches 
-        for p in (keywords):
-            m = list(set(re.findall(p, note)))
-            m = list(set(map(str.lower, m)))
-            if (m != []):
-                curr.append("".join(m))
-
-        matches.append(str(curr))
-
-    return matches 
-
-def find_character_locations(notes, keywords):
-    """
-    notes: dataframe 
-    keywords: list of compiled regex expressions for 18 dementia-related keywords
-    """
-    # array for storing character locations of matches; list of tuples
-    locations = []
-
-    for r in (notes['NoteTXT']):
-        curr_loc = []
-
-        # finding character locations
-        for p in keywords:
-            for match in re.finditer(p ,r):
-                curr_loc.append(match.span())
-                
-        # TODO: decide if need to keep this code
-        # current logic; if no character location is found, something is wrong
-        if (curr_loc == []):
-            print("STOP")
-            break
[…]

### 2021-12-25 Web-Tool/app/gui/run_clinical_bert.py
running clinicalbert code

@@ -1,1 +1,107 @@
 # Author: Tanish Tyagi 
+
+# base libraries
+import numpy as np
+import pandas as pd
+import regex as re
+import itertools
+import sklearn.metrics as sk
+from functools import reduce
+
+# deep learning libraries
+import torch
+import transformers
+from sklearn.model_selection import train_test_split
+from simpletransformers.classification import ClassificationModel, ClassificationArgs
+
+# hyperparameter optimization
+import optuna
+from optuna.samplers import TPESampler
+import optuna.visualization.matplotlib as oviz
+
+# file system manipulation
+import os
+import shutil
+from pathlib import Path
+import pickle
+import copy
+
+# logging
+import logging
+import time# base libraries
+import numpy as np
+import pandas as pd
+import regex as re
+import itertools
+import sklearn.metrics as sk
+from functools import reduce
+
+# deep learning libraries
+import torch
+import transformers
+from sklearn.model_selection import train_test_split
+from simpletransformers.classification import ClassificationModel, ClassificationArgs
+
+# hyperparameter optimization
+import optuna
+from optuna.samplers import TPESampler
+import optuna.visualization.matplotlib as oviz
+
+# file system manipulation
+import os
+import shutil
+from pathlib import Path
+import pickle
+import copy
+
+# logging
+import logging
+import time
+
+path = r"C:\Users\tanis\OneDrive - Phillips Exeter Academy\Data\Programming\APOE-SLAT\Models\Bert\best_model\trial_0"
+
+best_model = ClassificationModel(
+    "bert",
+    path  
+)
+
+def run_cb(notes):
+    """
+    notes: dataframe generated from sequence_extraction_pipeline.py 
+    """
+    # notes.columns = ["text"]
+    preds, outputs = best_model.predict(
+        notes 
+    )
+
+    max_prob_list = []
+    test_prob_list = []
+    test_pred_list = []
+    for i in range(len(notes)):
+        # prob_list = list(torch.softmax(torch.from_numpy(model_outputs[i]), axis=0)[:,1])
+        prob_list = torch.softmax(torch.from_numpy(outputs[i]), axis=0)
+        #print("Prob List: ", prob_list, type(prob_list))
+
+        extracted_prob_list = []
+        for i in range(len(prob_list)):
+            extracted_prob_list.append(float(prob_list[i]))
+
+        #print("Extracted Prob List: ", extracted_prob_list)
+        # find max one in each submatrix of length 3
[…]

### 2022-06-05 Submission/STS/Research_Notebook.tex
Create Research_Notebook.tex

\documentclass[11pt,letterpaper]{article}

\newcommand{\workingDate}{\textsc{2022 $|$ January $|$ 01}}
\newcommand{\userName}{Tanish Tyagi}
\newcommand{\institution}{Massachusetts General Hospital/Harvard Medical School}
\usepackage{researchdiary_png}
\usepackage{url}

\usepackage{graphicx}
\graphicspath{ {images/} }

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=blue,      
    urlcolor=blue,
    pdfpagemode=FullScreen,
    }

\begin{document}
\begin{titlepage}

\newcommand{\HRule}{\rule{\linewidth}{0.5mm}} % Defines a new command for the horizontal lines, change thickness here

\center
\includegraphics[scale=0.5]{images/mgh_logo.eps}\\[1cm] % Include a department/university logo - this will require the graphicx package

\center % Center everything on the page

\textsc{\LARGE NeuraHealth Research Notebook}\\[1.5cm] % Name of your university/college
\textsc{\Large Massachusetts General Hospital}\\[0.5cm] % Major heading such as course name
\textsc{\large MIND Data Science Lab}\\[0.5cm] % Minor heading such as course title

\begin{minipage}{0.4\textwidth}
\begin{flushleft} \large
\emph{Author:}\\
Tanish Tyagi % Your name
\end{flushleft}
\end{minipage}
~
\begin{minipage}{0.4\textwidth}
\begin{flushright} \large
\emph{Mentor:} \\
Dr. Sudeshna Das \\[1.2em] % Supervisor's Name
\end{flushright}
\end{minipage}\\[2cm]
\makeatother

{\large \today}\\[2cm]

\vfill

\end{titlepage}

\section{March 6, 2022}

Code Location: \texttt{APOE-V2/Analysis/Sequence v. Full Note Model Comparison.ipynb}

The main phenomenon I am currently investigating is why the model Xiao trained using full notes as opposed to sequences has completely different predictions than the sequence model I trained for ML4H. Today I made a distribution plot of the ratios of sequences to notes stratified by cognitive statuses. I used the annotations from NAT (\url{nat.partners.org}) for this experiment.

\begin{figure}[ht!]
\centering
\includegraphics[width=10cm]{ratio_sequences_notes.png}
\caption{Distribution Plot of Ratio of Sequences to Notes by Cognitive Status}
\end{figure}

This figure confirmed my hypothesis that those with normal cognition would have a smaller sequence:note ratio. We also decided to have an average note:sequence ratio be around 0.1 based off this plot.

\section{March 7, 2022}

Code Location: \texttt{APOE-V2/Analysis/Sequence v. Full Note Model Comparison.ipynb}

At the daily meeting today, we looked at the sequences that the full note model and sequence model were run on. We concluded that the sequence level model was more accurate in its predictions, and that even when the sequence text was equivalent to the entire note, both models would give completely different class predictions. We also noticed that the full note model seemed much more unsure in its predictions compared to the sequence level model, as shown by the figure below:

\begin{figure}[ht!]
\centering
\includegraphics[width=10cm]{predicted_probabilites_sequence_full_note.png}
\caption{Distribution Plot of Predicted Probabilites from Sequence and Full-Note models}
\end{figure}

Based of these observations, I will be meeting with Xiao tomorrow to go over her code for the full note model to see if there are any errors.

\section{March 8, 2022}

I met with Xiao today to discuss the discrepancies between the sequence and full-note models. Upon looking at her code, I realized that she was using my sequence level model but instead making predictions using text of full-notes, meaning that there was no error in importing the model or with the attention weights as I had previously thought. In fact, all of her code was very similar to my prediction pipeline I made over the summer. Based off this, we both came to the conclusion that the process of using full-notes confuses the model as full-notes often contain conflicting information that can make a model uncertain and incorrect in its predictions.

\section{March 9, 2022}

Code Location: \texttt{APOE-V2/ClinicalBERT/ClinicalBERT NAT Sequence and Note Predictions.ipynb}

We noticed a minor bug in my training code that could affect the predicted class assignments and decided to retrain both the sequence and full-note models. The full-note model code also had some bugs, and we thought retraining it using my code would fix the low predicted probabilities and incorrect predictions to some extent. However, upon training, the probability distribution for both models remained the same and worse, the sequence level model predictions changed, leading the model to predict more sequences incorrectly. Will investigate more tomorrow.

\section{March 10 and 11, 2022}

My attention during these two days was primarily focused on getting annotations using the new design web app. The current clusters of sequences loaded in are matches from memory and cognition, with sub-clusters of having impair, having intact, having both intact and impair, or neither. I was able to annotate three chunks adding up 114 sequences. I have also marked 9 sequences for further consensus to bring up at a future meeting.

\section{March 14, 2022}

Code Location: \texttt{APOE-V2/ClinicalBERT/ClinicalBERT Pipeline Inspection.ipynb}

In a further attempt to understand the differences between predicting on the sequence vs. full-note level, I extracted the attention weights for the model when a test sequence or test note is inputted for prediction. When the sequence is equal to the full-note are the exact same, the attention weights are the same as well. When the sequence is a snippet of the note, the attention weights are considerably different, which makes sense.

\section{March 15, 2022}

Code Location: \texttt{APOE-V2/ClinicalBERT/ClinicalBERT Pipeline Inspection.ipynb}

During the daily 11:30 meeting, I extracted the pooling layers for the models when it encounters a sequence vs. full-note. I got similar results to results I got when the attention weights were extracted, which once again made sense.

A minor breakthrough was made when we went back to further examining the predictions of the models that Xiao and I trained on 3/9/2022. When the sequence equals the full note, both the predictions of the sequence model and full note model are the same as well as the probability, which actually makes a lot of sense since the attention weights and pooling layers are the same among others.

\end{document}

### 2022-06-08 Submission/STS/Research_Notebook.tex
research notebook up to 6/8/2022

@@
 
-\newcommand{\workingDate}{\textsc{2022 $|$ January $|$ 01}}
+\newcommand{\workingDate}{\textsc{\today}}
 \newcommand{\userName}{Tanish Tyagi}
@@
 
-A minor breakthrough was made when we went back to further examining the predictions of the models that Xiao and I trained on 3/9/2022.
+A minor breakthrough was made when we went back to further examining the predictions of the models that I trained on 3/9/2022.
 When the sequence equals the full note, both the predictions of the sequence model and full note model are the same as well as the probability, which actually makes a lot of sense since the attention weights and pooling layers are the same among others.
 
+\section{June 6, 2022}
+
+Code Location: \texttt{APOE-V2/ClinicalBERT/ClinicalBERT\_Training\_Script.ipynb}
+
+Today was my first day doing full-time research at the lab since last summer, and it was a great feeling to finally get back into it!
+I used the ClinicalBERT training script I created to train the sequence level deep learning model and applied it to the current database of annotated sequences (around 4700).
+Future plans include to apply the ClinicalBERT model to a final dataset of around 6500 sequences so that it can become a great sequence level predictor.
+By improving the sequence level predictions, the logistic regression patient level predictor model will also become significantly improved.
+
+\section{June 7, 2022}
+
+Code Location: \texttt{APOE-V2/ClinicalBERT/ClinicalBERT\_Training\_Script.ipynb}
+
+I encountered a weird error when running the optuna study that I had not seen before.
+The terminal said that said \texttt{CUDA error: device-side assert triggered.
+CUDA kernel errors might be asynchronously reported at some other API call,so the stacktrace below might be incorrect.
+For debugging consider passing CUDA\_LAUNCH\_BLOCKING=1.} This error really did not tell me much, so I asked my colleagues and they recommended checking the dataset to ensure there are no bugs and to run the script from the commmand line as a python file instead of a jupyter notebook while specifying the GPU ports to use.
+
+None of the above fixes worked, but luckily I was able to find a fix which was to remove all the columns in my train, validation, and test sets except "text" and "labels" and restarting the kernel.
+This was quite a strange fix, but at the same time I was given a strange error.
+The model will finish training tomorrow.
+
+\section{June 8, 2022}
+
+Code Location: \texttt{APOE-V2/ClinicalBERT/ClinicalBERT\_Training\_Script.ipynb} \\ and \texttt{APOE-V2/ClinicalBERT/Analysis/ClinicalBERT\_Trial\_Analysis.ipynb}
+
+The model finished training this morning.
+The best trial was trial 10: with 0.974 AUC and 0.897 ACC on the evalulation set.
+The hyperparameters that were varied throughout the study had the below values for trial 10:
+
+\begin{itemize}
+   \item adam epilson: 5.3157E-06
+   \item early stopping patience: 3
+   \item learning rate: 5.5703E-05
+   \item num train epochs: 1
+\end{itemize}
+
+The AUC and ACC were not as good as the previous iteration of the model, which means that I will have to spend more time finding hyperparameters to tune.
+Some options for this include increasing the number of trials in the Optuna study from 20 to 40 (potentially), having the Optuna study maximize AUC instead of ACC, increasing the range of possible values for the learning rate, and finding other hyperparameters to include in the Optuna tuning process in addition to the four mentioned above.
+
+To dig deeper, I performed an analysis of the hyperparameters values for each trial and the corresponding AUC and ACC.
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[width=10cm]{auc_trial.png}
+\caption{AUC per Trial}
+\end{figure}
+
 \end{document}

### 2022-06-11 Submission/STS/Research_Notebook.tex
entries up to 6/11/2022

@@
 \usepackage{url}
-
+\usepackage{amsmath}
+\usepackage{natbib}
+\bibliographystyle{abbrvnat}
+\setcitestyle{authoryear,open={(},close={)}}
 \usepackage{graphicx}
@@
     urlcolor=blue,
+    allcolors=blue,
     pdfpagemode=FullScreen,
@@
 
-Code Location: \texttt{APOE-V2/ClinicalBERT/ClinicalBERT Pipeline Inspection.ipynb}
+Code Location: \texttt{APOE-V2/ClinicalBERT/Analysis/ClinicalBERT Pipeline Inspection.ipynb}
 
@@
 
-Code Location: \texttt{APOE-V2/ClinicalBERT/ClinicalBERT\_Training\_Script.ipynb}
+Code Location: \texttt{APOE-V2/ClinicalBERT/Models/ClinicalBERT\_Training\_Script\_0606.ipynb}
 
@@
 
-Code Location: \texttt{APOE-V2/ClinicalBERT/ClinicalBERT\_Training\_Script.ipynb} \\ and \texttt{APOE-V2/ClinicalBERT/Analysis/ClinicalBERT\_Trial\_Analysis.ipynb}
+Code Location: \texttt{APOE-V2/ClinicalBERT/Models/ClinicalBERT\_Training\_Script\_0606.ipynb} \\ and \texttt{APOE-V2/ClinicalBERT/Analysis/ClinicalBERT\_Trial\_Analysis.ipynb}
 
@@
 The best trial was trial 10: with 0.974 AUC and 0.897 ACC on the evalulation set.
+On the held out test set, the model achieved 0.829 ACC And 0.933 AUC.
 The hyperparameters that were varied throughout the study had the below values for trial 10:
@@
 
+\section{June 10, 2022}
+
+To start the day, I cleaning up my folder on mindds and got my gitlab repo in order.
+I had neglected git duties for many months now, and I thought I would fix it today.
+Took a while, but I was able to get everything in order and resolve all merge conflicts.
+
+Now, I explored options with tuning the hyperparameters for ClinicalBERT.
+I found that the important hyperparameters were already being tuned via Optuna.
+Learning rate stood out to me as a very important parameter, and found the paper by \citep{sun2019fine} titled, "How to fine-tune BERT for text classification?" very helpful for this task.
+Tuning the learning rate is very important to prevent catastrophic forgetting \citep{mccloskey1989catastrophic},  where the pre-trained knowledge is erased during learning of new knowledge.
+In \citep{sun2019fine}, the authors trained BERT on text classification for movie reviews, which shares similarities with my task.
+They tested multiple learning rates, which had the results shown in the convergence graphs shown below:
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[width=17cm]{learning_rates.png}
+\caption{Learning Rates and Convergence, Source: \citep{sun2019fine}}
+\end{figure}
+
+From the authors: ``We find that a lower learning rate, such as 2e-5, is necessary to make BERT overcome the catastrophic forgetting problem.
+With an aggressive learn rate of 4e-4, the training set fails to converge." With these results, I went to examine the learning rate of the best trial from my Optuna study.
+The learning rate was approximately 5e-5, and the loss on the evaluation set was 0.31.
+I figured that with an Optuna study of 40-50 trials, the model was come closer to a learning rate of 2e-5 and the loss would converge.
+
+I also closely examined my values for the number of training epochs.
+From online research, I found that the max number of epochs needed for NLP tasks and transformers in general is 5, so I increased the max number of possible training epochs to 5 instead of 3.
+
+I then started a 50 trial Optuna study to see if anything changes.
+
+\section{June 11, 2022}
+Code Location: \texttt{APOE-V2/ClinicalBERT/Models/ClinicalBERT\_Training\_Script\_0610.ipynb}
+
+Having an Optuna trial run for 50 trials did not change the performance much, if anything at all.
+The best trial was \#6, which was fairly disappointing considering that this was quite early in the study.
+The hyperparameters for this trial are as follows:
+
+\begin{itemize}
+   \item adam epilson: 2.4209E-06
+   \item early stopping patience: 2
+   \item learning rate: 6.6236E-06
+   \item num train epochs: 3
+\end{itemize}
+
+The learning did decrease from approximately 5E-5, but I am wondering whether this learning rate has the model learning too slow.
+I decided to also investigate the adam epsilon parameter and any way to tune the adam optimizer in general.
+After reading through numerous blog posts and scouring complicated equations I didn't understand, I came to the conclusion that the epilson parameter should be the only one that needs to be tuned during the training process.
+
+The adam optimizer combines the RMSProp and Momentum optimizers. The equations for the adam optimizer are as follows:
+
+\begin{center}
+$m_0 = 0, v_0 = 0$ \\
+Modified Momentum Equation: $m_{t+1} = \beta_{1}m_t + (1 - \beta_{1})\nabla_{\theta_{j}}\mathcal{L}(\theta)$ \\
+Modified RMSProp Equation: $v_{t+1} = \beta_{2}m_t + (1 - \beta_{2})\nabla_{\theta_{j}}\mathcal{L}(\theta)^2$ \\
+Correction: $\hat{m}_{t+1} = \frac{m_{t+1}}{1-(\beta_1)^2}$ and $\hat{v}_{t+1} = \frac{m_{t+1}}{1-(\beta_2)^2}$ \\
+$\theta_{j+1} = \theta_{j} - \frac{\epsilon}{\sqrt{v_{t+1}} + 1e^{-5}}m_{t+1}$
+\end{center}
+
+The $\beta_1$ and $\beta_2$ parameters are repeatedly multiplied with each other, so they should start at numbers close to 1 so that over time they approach 0 as gradient descent comes to a close.
+Pytorch, along with all other popular deep learning libraries, initializes $\beta_1$ to 0.9 and $\beta_2$ to 0.999, so they are fine as is.
+The tensorflow documentation, however, cautions against leaving the adam epilson value as is, saying, ``The default value of 1e-8 for epsilon might not be a good default in general.
+For example, when training an Inception network on ImageNet a current good choice is 1.0 or 0.1." So my current tuning mechanisms seem to be holding up.
+
+\clearpage
+\bibliography{main.bib}
+\nocite{*}
+
 \end{document}

### 2022-06-18 Submission/STS/Research_Notebook.tex
entries up to 6/17/2022

@@
 \begin{figure}[ht!]
+\label{auc_trial_20}
 \centering
@@
 
+\section{June 13, 2022}
+
+Code Locations: \texttt{APOE-V2/ClinicalBERT/Analysis/ClinicalBERT\_Trial\_Analysis.py} \\ and \texttt{APOE-V2/ClinicalBERT/Models/ClinicalBERT\_Sequence\_Model.py}
+
+First, I created a general \texttt{Trial Analysis} class that I could use for gathering all the needed data from my Optuna studies and applied it to my 50 trial study.
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=12cm]{50_trial.png}
+\caption{AUC per trial for 50 trial study}
+\end{figure}
+
+This graph is similar to the previous graph, as there is no clear trend.
+Upon looking at the learning rates chosen by Optuna and their corresponding AUCs, all learning rates of form \texttt{x} $\cdot 10^{-5}$ yield the highest AUCs.
+After trials with this learning rates, the sampler would mysteriously recommend a learning rate much smaller, which resulted in poor performance.
+The trial analysis spreadsheet is full of such trends, and yet the sampler is unable to pick up on the pattern.
+
+On a separate note, I created a class for the \texttt{ClinicalBERT Sequence Model} for further hyperparameter tuning trials. I am running into a database error which I will address tomorrow.
+
+\section{June 14, 2022}
+
+Code Locations: \texttt{APOE-V2/ClinicalBERT/Models/ClinicalBERT\_Sequence\_Model.py} \\ and \texttt{APOE-V2/ClinicalBERT/Models/ClinicalBERT\_Training\_0616.ipynb}
+
+I fixed the errors with the \texttt{ClinicalBERT Sequence Model} class.
+The gold standard dataset consists of $\approx$ 6500 annotated sequences with keywords and 500 sequences that contain no keywords.
+I started training the model with one edit: changing the range of the learning from 1E-6 to 1E-4 as learning rates under 1E-6 inhibited the model's learning.
+
+\section{June 15, 2022}
+
+Code Location: \texttt{APOE-V2/ClinicalBERT/Models/ClinicalBERT\_Training\_0616.ipynb}
+
+I realized that there was an error in the generation of the sequences that did not have a keyword match and had to stop training.
+The performance was quite similar to the previous study, but I believe there is potential for higher performance with correctly chosen sequences with no keywords.
+
+\section{June 16, 2022}
+
+Code Location: \texttt{APOE-V2/ClinicalBERT/Models/ClinicalBERT\_Training\_0616.ipynb}
+
+I trained on solely the 6500 sequences with a possible range of learning rates from 1E-6 to 1E-3 to further explore the learning rate space.
+I found the performance was extremely poor (0.5 AUC), as the model was learning too fast and forgetting past knowledge and patterns.
+
+\section{June 17, 2022}
+
+Code Location: \texttt{APOE-V2/ClinicalBERT/Models/ClinicalBERT\_Training\_0616.ipynb} \\ and \texttt{APOE-V2/ClinicalBERT/Preprocessing/Generating\_No\_Keyword\_Sequences.ipynb}
+
+I created the new set of 500 sequences by sampling random 800 character portions from notes and started running a 50 study Optuna trial.
+The training will finish over the weekend, after which I will conduct a thorough analysis of the loss curves and parameter configurations.
+
 \clearpage
